### 2021-06-13 article/main.tex
Create article

\documentclass[final]{article}

\usepackage{todonotes}
\setlength{\marginparwidth}{4cm}

\RequirePackage[utf8]{inputenc}
\DeclareUnicodeCharacter{00A0}{ }

\RequirePackage{color}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
\definecolor{egyptianblue}{rgb}{0.06, 0.2, 0.65}

\RequirePackage{listings}
\lstset{
    basicstyle=\small
}

\RequirePackage{graphicx}

\RequirePackage{amsthm}
\RequirePackage{amsmath}
\RequirePackage{amsfonts}
\RequirePackage{soul}
\RequirePackage{xspace}
\RequirePackage{bussproofs}
\RequirePackage[customcolors]{hf-tikz}

\RequirePackage{tikz}
\RequirePackage{setspace}

\RequirePackage{multicol}
\RequirePackage{lipsum}
\RequirePackage{textpos}

\setlength{\parindent}{0pt}
\setlength{\parskip}{.7em}

\title{Combinatorial interpretations of holonomic recurrences}
\author{Bartłomiej Puget}

% \date{Kraków, 19 maja 2021}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[subsection]

\theoremstyle{remark}
\newtheorem{example}{Example}[subsection]

\newcounter{highlightid}
\newcommand{\mhl}[1]{{\tikzmarkin[set fill color=red!30,set border color=red]{highlight-\arabic{highlightid}}(0.02,-0.15)(-0.02,0.35){#1}\tikzmarkend{highlight-\arabic{highlightid}}\stepcounter{highlightid}}}

\newcommand{\gf}[1]{\ensuremath{\mathcal{#1}}}

\DeclareMathOperator{\textiff}{\text{iff}}
\DeclareMathOperator{\N}{\mathbb{N}}
\DeclareMathOperator{\poly}{\mathbb{P}}

\begin{document}

\begin{titlepage}
	\begin{center}
	\textsc{\LARGE Jagiellonian University}

	\Large Faculty of Mathematics and Computer Science

	\Large Theoretical Computer Science

	\vfill

	\vspace{1cm}
	\hrulefill
	\vspace{0.5cm}

    \makeatletter
    \huge \textsc{\@title}
    \makeatother

	\vspace{0.2cm}
	\hrulefill

	\vspace{1cm}
    \makeatletter
	\textsc{\Large \@author}
    \makeatother

	\vspace{1cm}
    \normalsize

	Master Thesis\\
	Advisor: \textsc{Katarzyna Grygiel}

	\vfill

    \makeatletter
    \@date
    \makeatother
	\end{center}
\end{titlepage}

\section*{Abstract}

We analyze problem of finding combinatorial interpretations of holonomic recurrences and show some techniques that were used to achieve known results.

We also try to find combinatorial interpretation of holonomic recurrence for trees of lambda terms in de Bruijn notation.

\clearpage

\section{Introduction}

\subsection{Notation}

In order to make reading this article easier, let's fix some notation and make some assumptions. Any deviation from this will be clearly stated.

\(\poly\) is set of all polynomials.

\(n, m, i, j, k\) are implicitly assumed to be natural numbers.

\(f, g\) are implicitly assumed to be functions.

\(f^{(n)}\) is implicitly defined as \(n\)-th derivative of function \(f\).

\(x_i\) is implicitly assumed to be \(i\)-th element of the sequence \(X\), where \(x\) can be any lower-case letter and \(X\) is upper-case \(x\).

Calligraphic \(\gf{X}\) is implicitly assumed to be generating function of the sequence \(X\) where \(X\) is any upper-case letter.

\subsection{Structurally recursive objects}

We will be analyzing structures that can be expressed using recursive expressions. Eg.\ we can define full binary tree recursively as a node having no children (ie.\ being a leaf) or having exactly two subtrees being full binary trees. To express the alternative in the construction rule, we use \(+\). The reason will become obvious soon.

\[B = \text{leaf} + B^2\]

\todo{Add some image}

\subsection{Generating functions}

In the article we use ordinary generating functions to describe and count structures.

\begin{definition}
The ordinary generating function of sequence \(A = (a_i)_{i=0}^{\infty}\) is defined as:
\[\gf{A}(z) = \sum_{i=0}^{\infty} a_i z^i\]
\end{definition}

Note that in order to compute \(k\)-th element of the sequence, \(a_k\), we just need to find constant corresponding to indeterminate \(z^k\).

\begin{example}
    \label{ex-bin-gf}
    Having our recursive definition of the object, we can easily construct a generating function for it. Let's create generating function that will count number of full binary trees consisting of exactly \(k\) internal nodes.

\[\gf{B}(z) = 1 + z\gf{B}^2(z)\]

Note that we used \(z\) to count internal nodes and left the leaf part as \(1\).

In order to get some intuition on how it works unbeneath, let's take a look on how we can find number of the full binary trees of size \(2\). We can expand the recurrence a bit:

\[\begin{array}{rcl}
        \gf{B}(z) &=& 1 + z\gf{B}^2(z)\\
                  &=& 1 + z\bigg(1 + z\gf{B}^2(z)\bigg)\bigg(1 + z\gf{B}^2(z)\bigg)\\
                  &=& 1 + \mhl{z}\bigg(1 + \mhl{z}\Big(\mhl{1} + z\gf{B}^2(z)\Big)\Big(\mhl{1} + z\gf{B}^2(z)\Big)\bigg)\bigg(\mhl{1} + z\gf{B}^2(z)\bigg)
\end{array}\]

The highlighted terms are describing following tree:

iilll\todo{Add image}
\end{example}

There exist multiple well-known methods and tools that allow us to work with generating functions without need of digging into details. The tool we will be using extensively in this work is Maple package called GFUN\cite{gfun}.

\subsection{Holonomic recurrences}

Most of the time we will be working with holonomic recurrences, let's introduce them.

\begin{definition}
    \label{def-holo-1}
    \cite{holotoolkit}
    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is called holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) exists holonomic recurrence for it, ie.:

\[\exists_{r \in \N} \exists_{p_0, \ldots, p_r \in \poly} \forall_{n \in \N} \sum_{i=0}^r p_i(n)a_{n+i} = 0\]
\end{definition}

Note that the sum can only take finite number of subsequent elements of the sequence \(A\) into the relation.

\begin{example}
    \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because:
    \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0\]
\end{example}

\begin{example}
    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic.
\end{example}

\begin{definition}
    \label{def-holo-2}
    \cite{holotoolkit, complexity}
    Equivalently to definition\ \ref{def-holo-1}, an analytic function \(y\) is called holonomic \(\textiff\) it satisfies differential equation in the following form:
    \[\sum_{i=0}^{r} p_i(z) y^{(i)}(z) = b(z)\]
    for some fixed \(r \in \N\); \(b, p_0, \ldots, p_r \in \poly\) not all identically zero.
\end{definition}

\begin{example}
    \(y(z) = \frac{5n - 3}{3n + 5}\) is holonomic, because:
    \[(5z-3)(3z+5)y'(z) - 34y(z) = 0\]
\end{example}

Equivalence of these two definitions assures us that if we find differential equation describing the desired objects satisfying definition\ \ref{def-holo-2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def-holo-1}.

\begin{example}
    For generating function full binary trees defined in example\ \ref{ex-bin-gf}, ie.:
    \[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
    we can use GFUN\cite{gfun} to immediately find holonomic recurrence of our interest:

    \begin{lstlisting}
> with(gfun):
> RootOf(B = B^2*z + 1, B);
                                 2
                        RootOf(_Z  z - _Z + 1)

> algfuntoalgeq(%, B(z));
                              2
                             B  z - B + 1

> algeqtodiffeq(%, B(z));
                                        2      /d      \
              1 + (-1 + 2 z) B(z) + (4 z  - z) |-- B(z)|
                                               \dz     /

> rec := diffeqtorec(%, B(z), B(n));
        rec := {(2 + 4 n) B(n) + (-2 - n) B(n + 1), B(0) = 1}
    \end{lstlisting}

\end{example}

\subsection{Combinatorial interpretations}

Combinatorial interpretation is just fancy name for something you probably know and use. Eg.\ if you know the binomial coefficient \(\binom{n}{k}\), I bet it was introduced to you as something like: "let's assume you have \(n\) distinguishable balls. If you want to choose \(k\) from them, then you can do it in \(\binom{n}{k}\) ways" and now, whenever you see the term \(\binom{n}{k}\) you interpret it as number of ways to choose \(k\) objects from the set of size \(n\). This is the combinatorial interpretation of the binomial coefficient.

Holonomic recurrences are very useful if we want to count objects of given size. Of course, size can be defined in more complex ways, eg.\ we may want to find number of trees with \(n\) internal nodes having exactly \(m\) nodes beging left child of its parent.

Unfortunately, as for the most of auto-generated code, they almost never come with intuitive interpretation. They are just some recurrences, but there is no commonly known method to find, how they correspond to the structures they describe.

In the article we try to gather methods and results that may be helpful for anyone who will try to find such interpretation, as we believe that such interpretation may give better insight into the nature of the structure and make it easier to study its behaviour.

\section{Known results}

\subsection{Binary trees}

\subsection{Schröder trees}

\subsection{Unary-binary trees}

\section{Approaches}

\subsection{Defining the size carefully}

\subsection{Weights variablization}

\subsection{Inductive translation}

\subsection{Brutal iterative approach}

\section{Further work}

\clearpage

\begin{thebibliography}{9}
    \bibitem{remy}
    Laurent Alonso Alonso, Jean-Luc Remy, and René Schott,
    \textit{A Linear-Time Algorithm for the Generation of Trees},
    Algorithmica 17,
    1997,
    p. 162-182

    \bibitem{motzkin}
    Serge Dulucq, Jean-Guy Penaud,
    \textit{Interprétation bijective d'une récurrence des nombres de Motzkin},
    Discrete Mathematics,
    Volume 256, Issue 3,
    2002,
    p. 671-676

    \bibitem{schroder}
    Dominique Foata, Doron Zeilberger,
    \textit{A Classic Proof of a Recurrence for a Very Classical Sequence}
    J. Comb., Ser. A, 80,
    1997, 380-384

    \bibitem{generation}
    Jean-Luc Rémy,
    \textit{Un procédé itératif de dénombrement d’arbres binaires et son application à leur génération aléatoire}
    Informatique théorique, tome 19, no 2, 
    1985,
    p. 179-195

    \bibitem{doron}
    Doron Zeilberger,
    \textit{e-mail conversation},
    2020

    \bibitem{note}
    Jarmo Siltaneva, Erkki Mäkinen,
    \textit{A Note on Rémy's Algorithm for Generating Random Binary Trees},
    Missouri Journal of Mathematical Sciences. 15. 103-109. 10.35834/2003/1502103,
    2003

    \bibitem{bodini}
    Axel Bacher, Olivier Bodini, Alice Jacquot,
    Efficient random sampling of binary and unary-binary trees via holonomic equations,
    2014

    \bibitem{complexity}
    Igor Pak,
    \textit{Complexity problems in enumerative combinatorics},
    2018

    \bibitem{gfun}
    Bruno Salvy, Paul Zimmermann,
    \textit{GFUN : a maple package for the manipulation of generating and holonomic functions in one variable}
    [Research Report] RT-0143, INRIA. 1992, pp.14. ffinria-00070025f

    \bibitem{holotoolkit}
    Manuel Kauers,
    \textit{The Holonomic Toolkit},
    in: Carsten Schneider, Johannes Blümlein (eds) Computer Algebra in Quantum Field Theory. Texts \& Monographs in Symbolic Computation (A Series of the Research Institute for Symbolic Computation, Johannes Kepler University, Linz, Austria),
    Springer, Vienna,
    2013

\end{thebibliography}

\end{document}

### 2021-06-13 article/main.tex
Fix introduction

@@
 
-We analyze problem of finding combinatorial interpretations of holonomic recurrences and show some techniques that were used to achieve known results.
+We analyze the problem of finding combinatorial interpretations of holonomic recurrences and show some techniques that were used to achieve known results.
 
@@
 
-In order to make reading this article easier, let's fix some notation and make some assumptions. Any deviation from this will be clearly stated.
+In order to make reading of this article easier, let's fix some notation and make some assumptions. Any deviation from this will be clearly stated.
 
-\(\poly\) is set of all polynomials.
+\(\textiff\) means if and only if.
+
+\(\poly\) is a set of all polynomials.
 
@@
 
-Calligraphic \(\gf{X}\) is implicitly assumed to be generating function of the sequence \(X\) where \(X\) is any upper-case letter.
+Calligraphic \(\gf{X}\) is implicitly assumed to be a generating function of the sequence \(X\) where \(X\) is any upper-case letter.
 
@@
     \cite{holotoolkit}
-    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is called holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) exists holonomic recurrence for it, ie.:
+    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) exists holonomic recurrence for it, ie.:
 
@@
 \begin{example}
-    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic.
+    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic, ie. none of them satisifies a linear recurrence equation with polynomial coefficients\cite{nonholo}.
 \end{example}
@@
     \label{def-holo-2}
-    \cite{holotoolkit, complexity}
-    Equivalently to definition\ \ref{def-holo-1}, an analytic function \(y\) is called holonomic \(\textiff\) it satisfies differential equation in the following form:
-    \[\sum_{i=0}^{r} p_i(z) y^{(i)}(z) = b(z)\]
+    \cite{complexity}
+    Equivalently to definition\ \ref{def-holo-1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) exists generating function in the following form:
+    \[\sum_{i=0}^{r} p_i(z) \gf{A}^{(i)}(z) = b(z)\]
     for some fixed \(r \in \N\); \(b, p_0, \ldots, p_r \in \poly\) not all identically zero.
@@
 
-\begin{example}
-    \(y(z) = \frac{5n - 3}{3n + 5}\) is holonomic, because:
-    \[(5z-3)(3z+5)y'(z) - 34y(z) = 0\]
-\end{example}
-
-Equivalence of these two definitions assures us that if we find differential equation describing the desired objects satisfying definition\ \ref{def-holo-2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def-holo-1}.
+Equivalence of these two definitions assures us that if we find generating function describing the desired objects satisfying definition\ \ref{def-holo-2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def-holo-1}.\cite{complexity}
 
@@
     \end{lstlisting}
+
+    Our holonomic recurrence is then:
+    \[\left\{\begin{array}{rcl}
+                B(0) &=& 1\\
+                (2 + 4 n) B(n) + (-2 - n) B(n + 1) &=& 0
+    \end{array}\right.\]
+
+    For our purposes we will often ignore the initial conditions, as they can be easily described by exact number of the objects.
+The most interesting part for us is the relation between the finite number consecutive elements.
 
@@
 
+    \bibitem{nonholo}
+    Stefan Gerhold,
+    \textit{Combinatorial sequences: Non-holonomicity and inequalities. Ph.D. thesis},
+    RISC-Linz, Johannes Kepler Universitat Linz,
+    2005
+
 \end{thebibliography}

### 2021-06-24 article/main.tex
Write sketch of new sections

@@
 \usepackage{todonotes}
-\setlength{\marginparwidth}{4cm}
+\setlength{\marginparwidth}{2.5cm}
 
@@
 
+\RequirePackage{geometry}
 \RequirePackage{graphicx}
@@
 
+\newcommand{\ols}[1]{\mskip.5\thinmuskip\overline{\mskip-.5\thinmuskip {#1} \mskip-.5\thinmuskip}\mskip.5\thinmuskip} % overline short
+\newcommand{\olsi}[1]{\,\overline{\!{#1}}} % overline short italic
+
 \newcommand{\gf}[1]{\ensuremath{\mathcal{#1}}}
+\newcommand{\enc}[1]{\ensuremath{\ols{#1}}}
+\newcommand{\pointed}[1]{\ensuremath{{#1}^*}}
+\newcommand{\size}[1]{\ensuremath{\left|#1\right|}}
 
@@
 \DeclareMathOperator{\poly}{\mathbb{P}}
+\DeclareMathOperator{\troot}{\text{root}}
+\DeclareMathOperator{\tleft}{\text{left}}
+\DeclareMathOperator{\tright}{\text{right}}
+\DeclareMathOperator{\tLeft}{\text{Left}}
+\DeclareMathOperator{\tRight}{\text{Right}}
+\DeclareMathOperator{\tSub}{\text{Sub}}
+\DeclareMathOperator{\tPre}{\text{Pre}}
+\DeclareMathOperator{\tSuf}{\text{Suf}}
+\DeclareMathOperator{\n}{\bullet}
 
@@
 
+\(V(T)\) is implicitly defined as a set of nodes of the tree \(T\).
+
+\(E(T)\) is implicitly defined as a set of edges of the tree \(T\).
+
+\(u, v\) are implicitly assumed to be a nodes.
+
+\(e\) is implicitly assumed to be an edge.
+
+\(\troot(T)\) is implicitly defined as a root of tree \(T\).
+
+\(\tleft(v)\) is implicitly defined as a left child of node \(v\).
+
+\(\tright(v)\) is implicitly defined as a right child of node \(v\).
+
+\(\tSub(v)\) is implicitly defined as a whole subree rooted with node \(v\).
+
+\(\tLeft(v)\) is implicitly defined as a left subree of node \(v\).
+
+\(\tRight(v)\) is implicitly defined as a right subree of node \(v\).
+
+\(\n\) is implicitly defined as a default identifier a node.
+
+\(\o\) is implicitly defined as a identifier of non-existing node (eg.\ if \(v\) is a leaf, ie.\ has no children, \(\tleft(v) = \n\)).
+
+\(\pointed{v}\) is implicitly defined as a pointed node \(v\).
+
 \(x_i\) is implicitly assumed to be \(i\)-th element of the sequence \(X\), where \(x\) can be any lower-case letter and \(X\) is upper-case \(x\).
@@
 Calligraphic \(\gf{X}\) is implicitly assumed to be a generating function of the sequence \(X\) where \(X\) is any upper-case letter.
+
+\(\size{X}\) is implicitly defined as a size of the object \(X\).
+
+eg.\ stands for Latin exampli gratia, which means \textit{for example}.
+
+ie.\ stands for Latin id est, which means \textit{that is}.
 
@@
 \begin{example}
+    \label{ex-gfun-rec}
     For generating function full binary trees defined in example\ \ref{ex-bin-gf}, ie.:
@@
 
+\subsection{Pre-order notation}
+
+In order to make notation easier and unambiguous, we also introduce pre-order notation of \(n\)-ary tree.
+
+\begin{definition}
+    \(\enc{v}\) is an identifier of node \(v\). 
+\end{definition}
+
+\begin{definition}
+    Pre-order notation of \(n\)-ary tree \(T\), \(\enc{T}\), is defined recursively as \(\enc{\troot(T)} \prod_{i=1}^{n} \enc{i\text{-th subtree of } \troot(T)}\), ie.\ catenation of identifier of the root of the tree with encoded its subtrees from left to right.
+\end{definition}
+
+\begin{example}
+    \(\n \n \o \n \o \o \o\)
+    \todo{Add image}
+\end{example}
+
+We also can define prefix and suffix of \(T\).
+
+\begin{definition}
+    Let \(k\) be the index of its identifier in \enc{T}. Notation of prefix of \(T\) in relation to \(v\), \(\enc{\tPre(T, v)}\), is defined as a prefix of \enc{T} of size \(k - 1\).
+\end{definition}
+
+\begin{definition}
+    Let \(n\) be the size of \enc{T}.
+Notation of suffix of \(T\) in relation to \(v\), \(\enc{\tSuf(T, v)}\), is defined as a suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
+\end{definition}
+
+In the article we define some operations using its notation. As pre-order notation is bijective, you can obtain the structure the notation describe by reversing the process of encoding.
+
 \section{Known results}
@@
 \subsection{Binary trees}
+
+Let's start with probably the most known result, full binary trees\cite{binary}.
+
+We define the size of tree as a number of internal nodes (ie.\ nodes that are not leaves). Our generating function is therefore:
+
+\[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
+
+After a quick transformation, we get following holonomic recurrence:
+
+\[(n + 2)B(n + 1) = 2 (2n + 1)B(n)\]
+
+It is easy to see that tree of size \(n\) (\(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
+Analogically the tree of size \(n + 1\) has \(n + 2\) leaves and \(2n + 3\) nodes in total.
+If you see some resemblence to our holonomic recurrence, you are perfectly right.
+
+We are going to create bijection between left and right side of the recurrence.
+We will be using term \textit{bijective language} to describe talking about the recurrence using the objects it describes and their transformations.
+
+Let's translate the recurrence to the bijective language then.
+\begin{itemize}
+    \item \(B(n)\) is simply set of all full binary trees of size \(n\),
+    \item \((n + 2) B(n + 1)\) is set of all full binary trees of size \(n + 1\) with one of the leaves pointed,
+    \item \((2n + 1) B(n)\) is set of all full binary trees of size \(n\) with one of the nodes pointed (remember that the node can be internal node or leaf),
+    \item \(2\) at the beginning of \(2 (2n + 1) B(n)\) means that we will be using \(2\) copies of the set defined in previous bullet.
+\end{itemize}
+
+At the moment left side of the recurrence describe set of trees of size \(n + 1\), the right, on the other hand, of size \(n\). Therefore, we need to apply some transformation to make the sets equal.
+
+Let's define two local operations: \(R_l(T, v)\) and \(R_r(T, v)\).
+The term \textit{local} means that the operation can operate on just some finite fragment of tree with predefined size (eg.\ node and its 2 children, but can not traverse the whole tree).
+
+\begin{definition}
+    \(\enc{R_l(T, v)} = \enc{\tPre(T, v)} \n \pointed{\n} \o \o \enc{\tSub(v)} \enc{\tSuf(T, v)}\)
+\end{definition}
+
+\begin{definition}
+    \(\enc{R_r(T, v)} = \enc{\tPre(T, v)} \n \enc{\tSub(v)} \pointed{\n} \o \o \enc{\tSuf(T, v)} \)
+\end{definition}
+
+\todo{Add some illustration}
+
+We can now take the bijective interpretation of \((2n + 1) B(n)\), ie.
+trees of size \(n\) with single node pointed.
+For each of such trees, \(T\) we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a node that is pointed in \(T\).
+Therefore we generate \(2(2n + 1) B(n)\) trees of size \(n + 1\)
+
+The only thing that's left for us to verify is if we generate all trees of size \(n + 1\) with pointed leaf.
+As from the recursion, we know that \(2 (2n + 1) B(n)\) is total number of trees with single leaf pointed, it is enough to check if we do not generate any duplicate using \(R_l\) and \(R_r\).
+It can happen in 2 ways:
+\begin{enumerate}
+    \item operation itself generates duplicates or
+    \item 2 different operations generate the same tree.
+\end{enumerate}
+
+First case can be also split into 2 subcases. Without loss of the generality we can analyze just one of the operations, let it be \(R_l\). The second case will be symmetric.
+\begin{itemize}
+    \item for some nodes \(u \neq v\), \(R_l(T, u) = R_l(T, v)\).
+Let \(i_u, i_v\) be the indices of respectively \(\enc{u}\) and \(\enc{v}\) in \(\enc{T}\).
+Let \(\pointed{i}_u, \pointed{i}_v\) be the indices of pointed vertex respectively in \(\enc{R_l(T, u)}\) and \(\enc{R_l(T, v)}\).
+Due to the definition of \(R_l\), we get that \(\pointed{i}_u = i_u + 1\) and \(\pointed{i}_v = i_v + 1\), which implies that \(u = v\) what we assumed false.
+    \item for some trees \(T \neq S\), \(R_l(T, u) = R_l(S, v)\).
+Let \(i_u, i_v\) be the indices of respectively \(\enc{u}\) in \(\enc{T}\) and \(\enc{v}\) in \(\enc{S}\).
+Let \(\pointed{i}_u, \pointed{i}_v\) be the indices of pointed vertex respectively in \(\enc{R_l(T, u)}\) and \(\enc{R_l(S, v)}\).
+If \(\pointed{i}_u \neq \pointed{i}_v\), this case is trivially false, so we can assume that \(\pointed{i}_u = \pointed{i}_v\).
+Therefore, again from the definition of \(R_l\), we have that \(i_u = i_v\).
+That implies that \(\enc{\tPre(T, u)} \enc{\tSub(u)} \enc{\tSuf(T, u)} = \enc{\tPre(S, v)} \enc{\tSub(v)} \enc{\tSuf(S, v)} \), which then sums up to \(\enc{T} = \enc{S}\), which we assumed false.
+\end{itemize}
+
+In the second case it is enough to noitice that \(R_l\) generates trees with pointed vertex being a left child, and \(R_r\) generates trees with pointed vertex being right child.
+That immediately provides us with conclusion that we are generating no duplicates.
 
@@
 
+First thing that we have to select is defining the size carrefully. We have few standard choices of computing tree sizes:
+\begin{itemize}
+    \item counting all existing nodes,
+    \item counting internal nodes,
+    \item counting leaves,
+    \item counting null-nodes (ie.\ children of the leaves).
+\end{itemize}
+
+It may seem counter-intuitive at first, that this changes anything crucial, but the holonomic recurrence may change drastically making the problem more difficult than it should be.
+
+There are 2 most common symptoms that we may want to choose different method of counting the size:
+\begin{itemize}
+    \item we get empty classes of the objects, eg.\ if we analyze problem of full binary trees and define size as number of all existing nodes, we can not generate tree of even size, therefore half of our classes are empty;
+    \item we want to join trees using common root and we get many \(\pm1\) in our notes.
+Note that if you count internal nodes, such catenation creates tree of size being sum of sizes of the components increases by 1.
+If you had defined the size as number of leaves or null-nodes, the size would be just plain sum of sizes of the smaller trees.
+\todo{Add some example}
+\end{itemize}
+
 \subsection{Weights variablization}
+
+Most of the time we are operating on trees with some nodes of weight \(0\) and some of weight \(1\). We may as well try to make them variable or assign some other values (eg.\ small prime numbers).
+
+This method gives us some suggestion which kind of nodes are being modified in the operation
+
+Another benefit of this method is decreasing the sizes of particular classes, so we have less objects to look at.
+
+Unfortunately, decreasing size of the classes increases number of the sizes we need to analyze to get full result.
+
+\todo{Add some example}
 
@@
 
+Another method that may help finding the interpretation is inductive translation\cite{doron}.
+The method is based on the idea that most of the time there is easy to find some natural induction (not necessarily holonomic) that has trivial interpretation in bijective language.
+
+\todo{describe binary trees example}
+
+The method itself has proven to be helpful in order to divide the problem into smaller parts. Unfortunately It does not give any immediate interpretation for applying the inductive step.
+
 \subsection{Brutal iterative approach}
 
+If all elaborate methods has failed and the problem is still too big to interpret it by hand, a computer comes with help.
+
+As the main field of our interest was analyzis of terms of lambda trees, we will use it as an example to describe the method.\todo{Add definition}
+
+At first let's create generating functions that will keep track of more than just number of vertices, but also counts of each kind of vertices in the tree.
+The generating function will be parameterized then using following arguments:
+\begin{itemize}
+    \item \(z\) counting total number of virtual leaves
+    \item \(a\) counting number of application vertices
+    \item \(l\) counting number of lambda abstraction vertices
+    \item \(o\) counting number of bound variable vertices
+    \item \(s\) counting number of successors of bound variable vertices
+\end{itemize}
+
+In order to make the image cleaner, we will drop the arguments of generating functions, ie. \(\gf{L} := \gf{L}(z, a, l, o, s)\)
+\[\gf{L} = z a \gf{L}^2 + z l \gf{L} + \frac{o z}{1 - z s}\]
+\todo{add some image}
+\todo{describe how the frac is generated}
+
+Using a little bit of Maple magic, we can easily achieve following holonomic recurrence.
+
+\begin{lstlisting}
+l^2*s^2*n*B(n) + ((4*a*o*s*u - 2*l^2*s - 2*l*s^2)*n + 6*a*o*s*u - 2*l^2*s - 3*l*s^2)*B(1 + n) + ((-4*a*o*u + l^2 + 4*l*s + s^2)*n - 8*a*o*u + 2*l^2 + 10*l*s + 3*s^2)*B(n + 2) + ((-2*l - 2*s)*n - 7*l - 8*s)*B(n + 3) + (5 + n)*B(n + 4)
+\end{lstlisting}
+\todo{rewrite to LaTeX}
+
+You may notice that some potentially trivial terms are more complex that it seems.\todo{example}
+
+We also created a framework that may help visualize our work.
+It is based on the idea that every transformation described using bijective language can be translated to a function transforming vertex and finite number of its surrounding vertices.
+This function can not discriminate vertices on the grounds of their kind.
+The only discrimination that may occur may be connected to the following cases:
+\begin{itemize}
+    \item vertex has no children, ie.~is a virtual leaf (which corresponds to the size of the tree, \(n\));
+    \item vertex has has children, ie.~is not a virtual leaf (which corresponds to \(n - 1\));
+    \item vertex has its parent on the left, ie.~is right child of its parent;
+    \item vertex has its parent on the right, ie.~is left child of its parent.
+\end{itemize}
+
+The latest two are intruduced in order to make the analysis simpler, but do not have immediate interpretation in the world of holonomic recurrences.
+If we use them both, it sums up to all vertices except root (as root is neither left nor right child).
+
+\todo{split into classes / subclasses}
+\todo{define iteration}
+\todo{remind the cheat}
+
 \section{Further work}
+
+\todo{finish interpretation}
+\todo{missing formal proof}
 
@@
 
-    \bibitem{generation}
+    \bibitem{binary}
     Jean-Luc Rémy,

### 2021-07-18 article/main.tex
Start Schroder case

@@
 \newcommand{\pointed}[1]{\ensuremath{{#1}^*}}
+\newcommand{\weighted}[1]{\ensuremath{_{(#1)}}}
 \newcommand{\size}[1]{\ensuremath{\left|#1\right|}}
@@
 \DeclareMathOperator{\n}{\bullet}
+\DeclareMathOperator{\no}{\o}
 
@@
 
+\tableofcontents
+\clearpage
+
 \section{Introduction}
@@
 \subsection{Notation}
+\label{section-notation}
 
-In order to make reading of this article easier, let's fix some notation and make some assumptions. Any deviation from this will be clearly stated.
+In order to make reading of this article easier, let's fix some notation and make some assumptions.
+Any deviation from this will be clearly stated.
+If you have trouble guessing what some letter or word means, this should be your primary place to look for the answer.
 
@@
 
+Sibling of vertex \(v\) is defined as vertex \(u\) having the same parent as \(v\).
+
+Uncle of vertex \(v\) is defined as sibling of the parent of \(v\).
+
+We say that node \(v\) is an oneling \(\textiff\) \(v\) has no sibling. Note that the root is oneling even if it has no parent.
+
+We say that node \(v\) is twinling \(\textiff\) \(v\) has at least one sibling.
+
+We say that node \(v\) is an virtual-oneling \(\textiff\) \(v\) has no sibling being virtual node.
+
+We say that node \(v\) is virtual-twinling \(\textiff\) \(v\) has at least one sibling being virtual node.
+
+Leaf is a vertex which has no children.
+
 \(\n\) is implicitly defined as a default identifier a node.
 
-\(\o\) is implicitly defined as a identifier of non-existing node (eg.\ if \(v\) is a leaf, ie.\ has no children, \(\tleft(v) = \n\)).
+\(\no\) is implicitly defined as a identifier of non-existing node (eg.\ if \(v\) is a leaf, \(\tleft(v) = \n\)).
+
+Virtual node is artificially defined node that does not affect the structure definition (eg.\ we can define virtual leafs that are children of actual leaves of the binary tree.
+Such virtual leaves are not included when counting number of children of the node, so the actual leaves are still called leaves).
+
+Actual node is a node that is not virtual.
+
+We say that node \(v\) is right (left) \(\textiff\) \(v\) is a right (left) child of its parent.
+
+We say that node \(v\) has a right (left) parent \(u\) \(\textiff\) \(v\) is a left (right) child of \(u\).
 
 \(\pointed{v}\) is implicitly defined as a pointed node \(v\).
+
+\(v\weighted{n}\) is implicitly defined as a weighted node \(v\) with weight \(n\).
 
@@
 \begin{example}
-    \(\n \n \o \n \o \o \o\)
+    \(\n \n \no \n \no \no \no\)
     \todo{Add image}
@@
 
+This recurrence describes also Catalan numbers.
+
 It is easy to see that tree of size \(n\) (\(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
@@
 \begin{definition}
-    \(\enc{R_l(T, v)} = \enc{\tPre(T, v)} \n \pointed{\n} \o \o \enc{\tSub(v)} \enc{\tSuf(T, v)}\)
+    \(\enc{R_l(T, v)} = \enc{\tPre(T, v)} \n \pointed{\n} \no \no \enc{\tSub(v)} \enc{\tSuf(T, v)}\)
 \end{definition}
@@
 \begin{definition}
-    \(\enc{R_r(T, v)} = \enc{\tPre(T, v)} \n \enc{\tSub(v)} \pointed{\n} \o \o \enc{\tSuf(T, v)} \)
+    \(\enc{R_r(T, v)} = \enc{\tPre(T, v)} \n \enc{\tSub(v)} \pointed{\n} \no \no \enc{\tSuf(T, v)} \)
 \end{definition}
@@
 
+\subsection{Unary-binary trees}
+\label{section-unary-binary}
+
+Let's think, what would have changed if we introduce unary vertices to the binary case\cite{motzkin}. We will be counting edges. Note that tree having \(n\) edges has exactly \(n + 1\) vertices.
+
+\begin{definition}
+    Unary-binary tree is such tree of which any vertex can have either 0, 1 or 2 children.
+\end{definition}
+
+We can easily derive the generating function:
+
+\[\gf{U}(z) = 1 + z\gf{U}(z) + z^2 \gf{U}^2(z)\]
+
+And with a bit of Maple magic, we immediately get following recurrence:
+
+\[(n + 2)U(n) = (2n + 1)U(n - 1) + 3(n - 1)U(n - 2)\]
+
+The definition above is precise, but introduces a new kind of vertice that we would have to take care of.
+We can avoid it by using a trick to make the tree recall binary tree.
+We don't change the structure, just the notation.
+
+\begin{definition}
+    \label{def-unary-binary-2}
+    Left-leaning binary tree\todo{find official name; skewed binary tree is something different} is a binary tree with following constraint added: if a vertex has right child, it also have a left child.
+\end{definition}
+
+The bijection between unary-binary and left-leaning binary trees is very simple.
+We just represent unary vertices as vertices with just left child of left-leaning binary tree.
+The other cases translate immediately to corresponding ones.
+Please note that this transformation keeps the size of the tree (ie.~number of edges).
+
+The next step is to make binary trees full. Let's just define virtual leaves.
+
+\begin{definition}
+    Virtual leaf is a virtual node added to the vertex in place of non-existing child.
+\end{definition}
+
+As we have added \(n + 2\) virtual vertices, we have added as much virtual edges.
+
+\todo{image of transformation unary-binary to full-binary}
+
+Please note that \(n + 2\) matches the multiplier of \(U(n)\). Let's point the virtual leaves then.
+
+To present the interpretation in bijective language, we will have to introduce several types of the the virtual leaves (you may want to revisit section \ref{section-notation} Notation):
+
+\begin{enumerate}
+    \item Vro - virtual leaf being right virtual-oneling;
+    \item Vrt - virtual leaf being right virtual-twinling. We will divide this case into:
+        \begin{enumerate}
+            \item VrtUrv - Vri which uncle is a right virtual leaf;
+            \item VrtUra - Vri which uncle is a right actual node;
+            \item VrtUla - Vri which uncle is a left actual node.
+        \end{enumerate}
+    \item Vlt - virtual leaf left virtual-twinling. Note that from definition \ref{def-unary-binary-2}, left virtual leave can not have sibling being a actual node. We can divide also this case into:
+        \begin{enumerate}
+            \item VltUrv - Vlt which uncle is a right virtual leaf;
+            \item VltUra - Vlt which uncle is a right actual node;
+            \item VltUla - Vlt which uncle is a left actual node.
+        \end{enumerate}
+\end{enumerate}
+
+Note that it covers all possible cases of pointing virtual leaf and all the cases are mutually disjoint.
+
+All we need to show are the transformations from the smaller cases, ie. \(U(n-1)\) and \(U(n-2)\).
+
+Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point any vertex, as in a tree having \(n - 1\) edges, we have \(n\) actual and \(n + 1\) virtual ones.
+
+In case of \(U(n-2)\), the multiplier is \(3(n-1)\), that suggests that we should perform \(3\) transformations on the trees with a pointed actual node.
+
+\todo{draw the transformations}
+
+As you can see, we have satisfied all of the cases of \(U(n)\) with no repetitions, which concludes the construction.
+
 \subsection{Schröder trees}
 
-\subsection{Unary-binary trees}
+The next case we will show is case of Schröder trees\cite{schroder}.
+
+\begin{definition}
+    Schröder tree is a tree with no unary vertices.
+\end{definition}
+
+Simply speaking, vertex can have zero or strictly more than one children.
+
+\todo{example}
+
+This definition is quite precise, but is difficult to implement as a structural recursion. Let's transform it into something more manageable, ie.~of finite arity.
+
+\begin{definition}
+    Well-weighted binary plane tree is a weighted tree such that:
+    \begin{itemize}
+        \item leaves are unweighted;
+        \item internal nodes can have weight either \(1\) or \(2\);
+        \item if internal node has weight 2, then its right child is not a leaf.
+    \end{itemize}
+\end{definition}
+
+We can easily define the bijection \(\Phi\) between these two models using pre-order notation:
+\[\Phi(T) = \left\{\begin{array}{lcl}
+            \n \no \no &:& T = \n \no \no \\
+            \n\weighted{1}\; T_1\; T_2 &:& T = \n\; T_1\; T_2\\
+            \n\weighted{2}\; T_1\; \Phi(\n\; T_2 \ldots T_n) &:& T = \n\; T_1\; T_2 \ldots T_n
+\end{array}\right.\]
+
+Let's define size as a number of leaves. Note that the size is independent from which construction we use, as the leaf is translated to leaf and the internal node to internal nodes.
 
@@
     \item counting leaves,
-    \item counting null-nodes (ie.\ children of the leaves).
+    \item counting null-nodes (ie.\ children of the leaves),
+    \item edges.
 \end{itemize}
@@
 \end{itemize}
+
+\subsection{Tree binarization}
+
+If we describe some structure we may be tempted to use multiple kinds of vertices, eg.~unary and binary vertices.
+Having multiple kinds of vertices may cause problems, both in creating holonomic recurrence and finding the interpretation, as we have to keep track of how they can transform.
+
+As the most common trees are binary ones, it may be worth an effort to find the some structure based on binary trees that can represent original structure (see section~\ref{section-unary-binary}).
 
@@
 
-If all elaborate methods has failed and the problem is still too big to interpret it by hand, a computer comes with help.
+If all elaborate methods has failed and the problem is still too big to interpret it by hand, a computer comes handy.
 

### 2021-07-19 article/main.tex
Finish Schroder without images

@@
 
+The generating function equation is then:
+
+\[\left\{\begin{array}{rcl}
+            \gf{T}(z) &=& \gf{T}_1(z) + \gf{T}_2(z) + z\\
+            \gf{T}_1(z) &=& \gf{T}^2(z)\\
+            \gf{T}_2(z) &=& \gf{T}(z)(\gf{T}_1(z) + \gf{T}_2(z))
+\end{array}\right.\]
+
+To be able to use Maple to generate the recurrence, we need to transform this system of equations to a single one. We can eliminate \(\gf{T}_1(z)\) first.
+
+\[\left\{\begin{array}{rcl}
+            \gf{T}(z) &=& \gf{T}^2(z) + \gf{T}_2(z) + z\\
+            \gf{T}_2(z) &=& \gf{T}(z)(\gf{T}^2(z) + \gf{T}_2(z))
+\end{array}\right.\]
+
+\[\left\{\begin{array}{rcl}
+            \gf{T}(z) &=& \gf{T}^2(z) + \gf{T}_2(z) + z\\
+            \gf{T}_2(z)(1 - \gf{T}(z)) &=& \gf{T}^3(z)
+\end{array}\right.\]
+
+As we can not use division to get \(\gf{T}_2(z)\), let's multiply the first equation by \(1 - \gf{T}(z)\).
+
+\[\gf{T}(z)(1 - \gf{T}(z)) = \gf{T}^2(z)(1 - \gf{T}(z)) + \gf{T}^3(z) + z(1 - \gf{T}(z))\]
+
+It can be actually used now to generate the holonomic recurrence.
+
+\begin{lstlisting}
+> with(gfun):
+> RootOf(T*(1 - T) = T^2*(1 - T) + T^3 + z*(1 - T),  T);
+               2
+    RootOf(2 _Z  + (-z - 1) _Z + z)
+
+> algfuntoalgeq(%, T(z));
+       2
+    2 T  + (-z - 1) T + z
+
+> algeqtodiffeq(%, T(z));
+                               2            /d      \                    2
+    {z - 1 + (-z + 3) T(z) + (z  - 6 z + 1) |-- T(z)|, T(0) = RootOf(2 _Z  - _Z)}
+                                            \dz     /
+
+> diffeqtorec(%, T(z), T(n));
+
+    {(n - 1) T(n) + (-3 - 6 n) T(n + 1) + (n + 2) T(n + 2), ...}
+
+> subs(n = n - 1, %);
+
+    {(-2 + n) T(n - 1) + (3 - 6 n) T(n) + (n + 1) T(n + 1), ...}
+\end{lstlisting}
+
+We can also move \(\gf{T}(z)\) to the other side, ie.:
+
+\[3 (2 n - 1) T(n) = (n - 2) T(n - 1) + (n + 1) T(n + 1)\]
+
+This may seem counterintuitive, as by default we want to describe how to generate larger case from the smaller ones, but it will make the interpretation simpler.
+
+Let's translate the recurrence to the bijective language then.
+\begin{itemize}
+    \item \((2 n - 1) T(n)\) describes well-weighted binary plane trees of size \(n\) (ie. with \(n\) leaves) with some node pointed (internal or leaf),
+    \item \((n + 1) T(n + 1)\) describes well-weighted binary plane trees of size \(n - 1\) with some leaf pointed,
+    \item \((n - 2) T(n - 1)\) describes well-weighted binary plane trees of size \(n - 1\) with some internal node pointed.
+\end{itemize}
+
+We will show the bijection between two sides of the recursion.
+We will transform each tree from \((2 n - 1) T(n)\) in three ways in order to achieve all trees from \((n + 1) T(n + 1)\).
+We will get some extra ones which are not well-weighted, but we will deal with them in a minute.
+
+Let's define 3 transformations: \(L_1\), \(L_2\) and \(R_1\).
+
+\todo{image of the transformations}
+
+You can see that trees generated by \(L_1\) and \(R_1\) are always well-weighted. The problem appears when applying \(L_2\) when \(s\) is a leaf.
+
+When \(s\) is a leaf, we will look at the \(s\)'s parent. It can fall into one of following cases:
+
+\todo{image of the problematic cases}
+
+where \(t'\) can be any tree and \(t''\) can not be a leaf.
+
+When aplying \(L_2\) we achieve following cases respectively:
+
+\todo{images}
+
+In case 1. and 2. we can just swap the labels as follows:
+
+\todo{images}
+
+It is easy to show that it constructs bijection between \((n + 1) T(n + 1)\) and subset of \(\{L_1, L_2, R_1\} \times (2 n - 1) T(n)\) not falling into case 3.
+
+To achive trees from \((n - 2) T(n - 1)\), we can simply take trees from case 3.
+and replace the father of the \(s\) with \(t''\) and point root of \(t''\).
+In this way, we will loose \(2\) leaves and obtain each tree from \((n - 2) T(n - 1)\).
+
+\todo{image}
+
 \section{Approaches}
+
+\subsection{Introduction}
+
+As you could see in the examples above, most of the solutions base on the simple analysis of number of laves, internal nodes and other similar properties.
+In this section, we've gathered some methods that may be helpful when trying to analyze the problem of interpreting combinatorically some holonomic recurrence.
 

### 2021-07-25 article/main.tex
Describe lambda trees

@@
 \newcommand{\size}[1]{\ensuremath{\left|#1\right|}}
+\newcommand{\LambdadB}{\ensuremath{\Lambda_{\text{dB}}}}
 
@@
 
-\section*{Abstract}
+\section*{Abstract}%
+\label{sec:abstract}
 
@@
 
-\section{Introduction}
+\section{Introduction}%
+\label{sec:introduction}
 
-\subsection{Notation}
-\label{section-notation}
+\subsection{Notation}%
+\label{sub:notation}
 
@@
 
-\subsection{Structurally recursive objects}
+\subsection{Structurally recursive objects}%
+\label{sub:structurally_recursive_objects}
 
@@
 
-\subsection{Generating functions}
+\subsection{Generating functions}%
+\label{sub:generating_functions}
 
@@
 \begin{example}
-    \label{ex-bin-gf}
+    \label{ex:bin_gf}
     Having our recursive definition of the object, we can easily construct a generating function for it.
@@
 
-\subsection{Holonomic recurrences}
+\subsection{Holonomic recurrences}%
+\label{sub:holonomic_recurrences}
 
@@
 \begin{definition}
-    \label{def-holo-1}
+    \label{def:holo_1}
     \cite{holotoolkit}
@@
 \begin{definition}
-    \label{def-holo-2}
+    \label{def:holo_2}
     \cite{complexity}
-    Equivalently to definition\ \ref{def-holo-1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) exists generating function in the following form:
+    Equivalently to definition\ \ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) exists generating function in the following form:
     \[\sum_{i=0}^{r} p_i(z) \gf{A}^{(i)}(z) = b(z)\]
@@
 
-Equivalence of these two definitions assures us that if we find generating function describing the desired objects satisfying definition\ \ref{def-holo-2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def-holo-1}.\cite{complexity}
+Equivalence of these two definitions assures us that if we find generating function describing the desired objects satisfying definition\ \ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def:holo_1}.\cite{complexity}
 
 \begin{example}
-    \label{ex-gfun-rec}
-    For generating function full binary trees defined in example\ \ref{ex-bin-gf}, ie.:
+    \label{ex:gfun-rec}
+    For generating function full binary trees defined in example\ \ref{ex:bin_gf}, ie.:
     \[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
@@
 
-\subsection{Combinatorial interpretations}
+\subsection{Combinatorial interpretations}%
+\label{sub:combinatorial_interpretations}
 
@@
 
-\subsection{Pre-order notation}
+\subsection{Pre-order notation}%
+\label{sub:pre_order_notation}
 
@@
 
-\section{Known results}
+\section{Known results}%
+\label{sec:known_results}
 
-\subsection{Binary trees}
+\subsection{Binary trees}%
+\label{sub:binary_trees}
 
@@
 
-\subsection{Unary-binary trees}
-\label{section-unary-binary}
+\subsection{Unary-binary trees}%
+\label{sub:unary_binary_trees}
 
@@
 \begin{definition}
-    \label{def-unary-binary-2}
+    \label{def:unary_binary_2}
     Left-leaning binary tree\todo{find official name; skewed binary tree is something different} is a binary tree with following constraint added: if a vertex has right child, it also have a left child.
@@
 
-To present the interpretation in bijective language, we will have to introduce several types of the the virtual leaves (you may want to revisit section \ref{section-notation} Notation):
+To present the interpretation in bijective language, we will have to introduce several types of the the virtual leaves (you may want to revisit section \ref{sub:notation} Notation):
 
@@
         \end{enumerate}
-    \item Vlt - virtual leaf left virtual-twinling. Note that from definition \ref{def-unary-binary-2}, left virtual leave can not have sibling being a actual node. We can divide also this case into:
+    \item Vlt - virtual leaf left virtual-twinling. Note that from definition \ref{def:unary_binary_2}, left virtual leave can not have sibling being a actual node. We can divide also this case into:
         \begin{enumerate}
@@
 
-\subsection{Schröder trees}
+\subsection{Schröder trees}%
+\label{sub:schröder_trees}
 
@@
 
-\section{Approaches}
+\section{Approaches}%
+\label{sec:approaches}
 
-\subsection{Introduction}
+\subsection{Introduction}%
+\label{sub:introduction}
 
@@
 
-\subsection{Defining the size carefully}
+\subsection{Defining the size carefully}%
+\label{sub:defining_the_size_carefully}
 
@@
 
-\subsection{Tree binarization}
+\subsection{Tree binarization}%
+\label{sub:tree_binarization}
 
@@
 
-As the most common trees are binary ones, it may be worth an effort to find the some structure based on binary trees that can represent original structure (see section~\ref{section-unary-binary}).
+As the most common trees are binary ones, it may be worth an effort to find the some structure based on binary trees that can represent original structure (see section~\ref{sub:unary_binary_trees}).
 
-\subsection{Weights variablization}
+\subsection{Weights variablization}%
+\label{sub:weights_variablization}
 
@@
 
-\subsection{Inductive translation}
+\subsection{Inductive translation}%
+\label{sub:inductive_translation}
 
@@
 
-\subsection{Brutal iterative approach}
+\section{Brutal iterative approach}%
+\label{sec:brutal_iterative_approach}
 
@@
 
-As the main field of our interest was analyzis of terms of lambda trees, we will use it as an example to describe the method.\todo{Add definition}
+As the main field of our interest was analyzis of terms of lambda trees in unary de Bruijn notation, we will use it as an example to describe the method.\todo{Add definition}
 
-At first let's create generating functions that will keep track of more than just number of vertices, but also counts of each kind of vertices in the tree.
+\subsection{Lambda terms}%
+\label{sub:lambda_terms}
+
+\begin{definition}
+    Set of lambda terms \(\Lambda\) is defined recursively:
+    \begin{itemize}
+        \item if \(x\) is a variable, \(x \in \Lambda\)
+        \item if \(M, N \in \Lambda\), then \((M N) \in \Lambda\) (application of function \(M\) to an argument \(N\))
+        \item if \(x\) is a variable and \(M \in \Lambda\), then \((\lambda x .
+M) \in \Lambda\) (abstraction, ie.\ creating a function with an argument \(x\) and binding each occurence of \(x\) in \(M\) to this argument)
+    \end{itemize}
+\end{definition}
+
+The definition above is quite popular, but introduces several problems.
+One of them is problem of potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction is the variable is bound (or is it even free variable, ie.\ not bound).
+To address that, we can use de Bruijn indices.
+
+\begin{definition}
+    Set of lambda terms \(\LambdadB\) is defined recursively:
+    \begin{itemize}
+        \item if \(n \in \N\), \(n \in \LambdadB\) (\(n\) is a variable bound to lambda abstraction \(n\) levels above)
+        \item if \(M, N \in \LambdadB\), then \((M N) \in \LambdadB\) (application)
+        \item if \(M \in \LambdadB\), then \((\lambda M) \in \LambdadB\) (abstraction)
+    \end{itemize}
+\end{definition}
+
+As you can see, we managed to eliminate the arbitrary variables. We can also easily check if given variable is bound by checking its depth.
+
+\begin{example}
+    \(\lambda x . \lambda y . x\) is equivalent to \(\lambda \lambda 1\)
+\end{example}
+
+\begin{example}
+    \(\lambda x . (\lambda y . x) (\lambda y . y)\) is equivalent to \(\lambda (\lambda 1) (\lambda 0)\)
+\end{example}
+
+It also allows us to define tree representation of the terms.
+
+\begin{definition}
+    Injection from lambda terms in de Bruijn notation to binary trees \(\Phi\) is defined as follows:
+    \begin{itemize}
+        \item \(\Phi(0) = \n\; \no\; \no\)
+        \item \(\Phi(n) = \n\; \no\; \Phi(n - 1)\)
+        \item \(\Phi(\lambda M) = \n\; \Phi(M)\; \no\)
+        \item \(\Phi(M N) = \n\; \Phi(M)\; \Phi(N)\)
+    \end{itemize}
+\end{definition}
+
+To simplify the interpretation, we can introduce several kinds of the nodes: \(o\), \(s\), \(l\) and \(a\). They do not change the structure, but make the reading a bit easier:
+
+\begin{definition}
+    \(o\) is a leaf.
+\end{definition}
+
+\begin{definition}
+    \(s\) is a node with just right child.
+\end{definition}
+
+\begin{definition}
+    \(l\) is a node with just left child.
+\end{definition}
+
+\begin{definition}
+    \(a\) is a node with both children.
+\end{definition}
+
+Which leads to following interpreation of \(\Phi\):
+
+\begin{itemize}
+    \item \(\Phi(0) = o\; \no\; \no\)
+    \item \(\Phi(n) = s\; \no\; \Phi(n - 1)\)
+    \item \(\Phi(\lambda M) = l\; \Phi(M)\; \no\)
+    \item \(\Phi(M N) = a\; \Phi(M)\; \Phi(N)\)
+\end{itemize}
+
+You can note that not every binary tree represents valid term.
+
+\begin{example}
+    \(\n\; \no\; \n\; \n\; \no\; \no\; \no\) does not represent valid lambda term.
+\end{example}
+
+To see that, we can take a look at this tree with our node kinds used:
+    \[s\; \no\; l\; o\; \no\; \no\; \no\]
+
+\(s\) represents successor which can be applied only to \(n \in \N\), but is applied to lambda-abstracted term.
+
+\subsection{Enhanced holonomic reccurence}%
+\label{sub:enhanced_holonomic_reccurence}
+
+As we have our structure defined, let's create generating functions that will keep track of more than just number of vertices, but also counts of each kind of vertices in the tree.
 The generating function will be parameterized then using following arguments:
@@
     \item \(z\) counting total number of virtual leaves
+    \item \(o\) counting number of bound variable vertices
+    \item \(l\) counting number of lambda abstraction vertices
     \item \(a\) counting number of application vertices
-    \item \(l\) counting number of lambda abstraction vertices
-    \item \(o\) counting number of bound variable vertices
     \item \(s\) counting number of successors of bound variable vertices
@@
 
-In order to make the image cleaner, we will drop the arguments of generating functions, ie. \(\gf{L} := \gf{L}(z, a, l, o, s)\)
+In order to make the image cleaner, we will drop the arguments of generating functions, ie. \(\gf{L} := \gf{L}(z, o, l, a, s)\)
 \[\gf{L} = z a \gf{L}^2 + z l \gf{L} + \frac{o z}{1 - z s}\]
@@
 
-\begin{lstlisting}
-l^2*s^2*n*B(n) + ((4*a*o*s*u - 2*l^2*s - 2*l*s^2)*n + 6*a*o*s*u - 2*l^2*s - 3*l*s^2)*B(1 + n) + ((-4*a*o*u + l^2 + 4*l*s + s^2)*n - 8*a*o*u + 2*l^2 + 10*l*s + 3*s^2)*B(n + 2) + ((-2*l - 2*s)*n - 7*l - 8*s)*B(n + 3) + (5 + n)*B(n + 4)
-\end{lstlisting}
-\todo{rewrite to LaTeX}
+\[\begin{array}{rl}
+        & (n - 4) l^2 s^2 L(n - 4)\\
+        +& ((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) L(n - 3)\\
+        +& ((-4 n + 8) a o + (n - 2) l^2 + (4 n - 6) l s + (n - 1) s^2) L(n - 2)\\
+        +& ((-2 n + 1) l - 2 n s) L(n - 1)\\
+        +& (n + 1) L(n)
+\end{array}\]
 
-You may notice that some potentially trivial terms are more complex that it seems.\todo{example}
+You may notice that some potentially trivial terms are more complex that it seems. If we didn't count different types of vertices, we would achieve following holonomic recurrence:
+
+\[\begin{array}{rl}
+        & (n - 4) L(n - 4)\\
+        +& L(n - 3)\\
+        +& (2 n - 1) L(n - 2)\\
+        +& (-4 n + 1) L(n - 1)\\
+        +& (1 + n) L(n)
+\end{array}\]
+
+We can see that for example simple \(L(n-3)\) is expanded into \(((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) L(n - 3)\).
+
+\subsection{The framework}%
+\label{sub:the_framework}
 
@@
 
-\section{Further work}
+\section{Further work}%
+\label{sec:further_work}
 

### 2021-07-26 article/main.tex
Introduce classes

@@
 
-Sibling of vertex \(v\) is defined as vertex \(u\) having the same parent as \(v\).
+Sibling of node \(v\) is defined as node \(u\) having the same parent as \(v\).
 
-Uncle of vertex \(v\) is defined as sibling of the parent of \(v\).
+Uncle of node \(v\) is defined as sibling of the parent of \(v\).
 
@@
 
-Leaf is a vertex which has no children.
+Leaf is a node which has no children.
 
@@
 Let \(i_u, i_v\) be the indices of respectively \(\enc{u}\) and \(\enc{v}\) in \(\enc{T}\).
-Let \(\pointed{i}_u, \pointed{i}_v\) be the indices of pointed vertex respectively in \(\enc{R_l(T, u)}\) and \(\enc{R_l(T, v)}\).
+Let \(\pointed{i}_u, \pointed{i}_v\) be the indices of pointed node respectively in \(\enc{R_l(T, u)}\) and \(\enc{R_l(T, v)}\).
 Due to the definition of \(R_l\), we get that \(\pointed{i}_u = i_u + 1\) and \(\pointed{i}_v = i_v + 1\), which implies that \(u = v\) what we assumed false.
@@
 Let \(i_u, i_v\) be the indices of respectively \(\enc{u}\) in \(\enc{T}\) and \(\enc{v}\) in \(\enc{S}\).
-Let \(\pointed{i}_u, \pointed{i}_v\) be the indices of pointed vertex respectively in \(\enc{R_l(T, u)}\) and \(\enc{R_l(S, v)}\).
+Let \(\pointed{i}_u, \pointed{i}_v\) be the indices of pointed node respectively in \(\enc{R_l(T, u)}\) and \(\enc{R_l(S, v)}\).
 If \(\pointed{i}_u \neq \pointed{i}_v\), this case is trivially false, so we can assume that \(\pointed{i}_u = \pointed{i}_v\).
@@
 
-In the second case it is enough to noitice that \(R_l\) generates trees with pointed vertex being a left child, and \(R_r\) generates trees with pointed vertex being right child.
+In the second case it is enough to noitice that \(R_l\) generates trees with pointed node being a left child, and \(R_r\) generates trees with pointed node being right child.
 That immediately provides us with conclusion that we are generating no duplicates.
@@
 
-Let's think, what would have changed if we introduce unary vertices to the binary case\cite{motzkin}. We will be counting edges. Note that tree having \(n\) edges has exactly \(n + 1\) vertices.
+Let's think, what would have changed if we introduce unary nodes to the binary case\cite{motzkin}. We will be counting edges. Note that tree having \(n\) edges has exactly \(n + 1\) nodes.
 
 \begin{definition}
-    Unary-binary tree is such tree of which any vertex can have either 0, 1 or 2 children.
+    Unary-binary tree is such tree of which any node can have either 0, 1 or 2 children.
 \end{definition}
@@
     \label{def:unary_binary_2}
-    Left-leaning binary tree\todo{find official name; skewed binary tree is something different} is a binary tree with following constraint added: if a vertex has right child, it also have a left child.
+    Left-leaning binary tree\todo{find official name; skewed binary tree is something different} is a binary tree with following constraint added: if a node has right child, it also have a left child.
 \end{definition}
@@
 The bijection between unary-binary and left-leaning binary trees is very simple.
-We just represent unary vertices as vertices with just left child of left-leaning binary tree.
+We just represent unary nodes as nodes with just left child of left-leaning binary tree.
 The other cases translate immediately to corresponding ones.
@@
 \begin{definition}
-    Virtual leaf is a virtual node added to the vertex in place of non-existing child.
+    Virtual leaf is a virtual node added to the node in place of non-existing child.
 \end{definition}
 
-As we have added \(n + 2\) virtual vertices, we have added as much virtual edges.
+As we have added \(n + 2\) virtual nodes, we have added as much virtual edges.
 
@@
 
-Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point any vertex, as in a tree having \(n - 1\) edges, we have \(n\) actual and \(n + 1\) virtual ones.
+Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point any node, as in a tree having \(n - 1\) edges, we have \(n\) actual and \(n + 1\) virtual ones.
 
@@
 \begin{definition}
-    Schröder tree is a tree with no unary vertices.
+    Schröder tree is a tree with no unary nodes.
 \end{definition}
 
-Simply speaking, vertex can have zero or strictly more than one children.
+Simply speaking, node can have zero or strictly more than one children.
 
@@
 
-If we describe some structure we may be tempted to use multiple kinds of vertices, eg.~unary and binary vertices.
-Having multiple kinds of vertices may cause problems, both in creating holonomic recurrence and finding the interpretation, as we have to keep track of how they can transform.
+If we describe some structure we may be tempted to use multiple kinds of nodes, eg.~unary and binary nodes.
+Having multiple kinds of nodes may cause problems, both in creating holonomic recurrence and finding the interpretation, as we have to keep track of how they can transform.
 
@@
 
-As we have our structure defined, let's create generating functions that will keep track of more than just number of vertices, but also counts of each kind of vertices in the tree.
+As we have our structure defined, let's create generating functions that will keep track of more than just number of nodes, but also counts of each kind of nodes in the tree.
 The generating function will be parameterized then using following arguments:
@@
     \item \(z\) counting total number of virtual leaves
-    \item \(o\) counting number of bound variable vertices
-    \item \(l\) counting number of lambda abstraction vertices
-    \item \(a\) counting number of application vertices
-    \item \(s\) counting number of successors of bound variable vertices
+    \item \(o\) counting number of bound variable nodes
+    \item \(l\) counting number of lambda abstraction nodes
+    \item \(a\) counting number of application nodes
+    \item \(s\) counting number of successors of bound variable nodes
 \end{itemize}
@@
 
-You may notice that some potentially trivial terms are more complex that it seems. If we didn't count different types of vertices, we would achieve following holonomic recurrence:
+Appearing in the recurrence node kinds mean that we extend trees of given size using nodes of that kinds.
+
+\begin{example}
+    \((2n - 5) l s^2 L(n - 3)\) mean extending each tree of size \((n - 3)\) pointed in \((2n - 5)\) ways using single \(l\) node and two \(s\) nodes.
+\end{example}
+
+You may notice that some potentially trivial terms are more complex that it seems. If we didn't count different types of nodes, we would achieve following holonomic recurrence:
 
@@
 
-We can see that for example simple \(L(n-3)\) is expanded into \(((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) L(n - 3)\).
+\begin{example}
+    \(L(n-3)\) is expanded into \(((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) L(n - 3)\).
+\end{example}
 
@@
 We also created a framework that may help visualize our work.
-It is based on the idea that every transformation described using bijective language can be translated to a function transforming vertex and finite number of its surrounding vertices.
-This function can not discriminate vertices on the grounds of their kind.
+It is based on the idea that every transformation described using bijective language can be translated to a function transforming node and finite number of its surrounding nodes.
+This function can not discriminate nodes on the grounds of their kind.
 The only discrimination that may occur may be connected to the following cases:
 \begin{itemize}
-    \item vertex has no children, ie.~is a virtual leaf (which corresponds to the size of the tree, \(n\));
-    \item vertex has has children, ie.~is not a virtual leaf (which corresponds to \(n - 1\));
-    \item vertex has its parent on the left, ie.~is right child of its parent;
-    \item vertex has its parent on the right, ie.~is left child of its parent.
+    \item node has no children, ie.~is a virtual leaf (which corresponds to the size of the tree, \(n\));
+    \item node has has children, ie.~is not a virtual leaf (which corresponds to \(n - 1\));
+    \item node has its parent on the left, ie.~is right child of its parent;
+    \item node has its parent on the right, ie.~is left child of its parent.
 \end{itemize}
@@
 The latest two are intruduced in order to make the analysis simpler, but do not have immediate interpretation in the world of holonomic recurrences.
-If we use them both, it sums up to all vertices except root (as root is neither left nor right child).
+If we use them both, it sums up to all nodes except root (as root is neither left nor right child).
+
+\subsection{Transformation classes}%
+\label{sub:transformation_classes}
+
+We will be operating on transformation classes, sections and parts. Let's define them:
+
+\begin{definition}
+    Class \(T_i\) is defined as set of transformations of trees of size \((n - i)\) into trees of size \(n\).
+\end{definition}
+
+\begin{definition}
+    Section \(T_{i,j}\) is defined as subset of \(L_i\) adding specific set of nodes. We assign \(j\) according to the lexicographical order of lexicographically sorted node types that need 
+\end{definition}
 

### 2021-07-26 article/main.tex
Define iteration

@@
 \begin{definition}
-    Section \(T_{i,j}\) is defined as subset of \(L_i\) adding specific set of nodes. We assign \(j\) according to the lexicographical order of lexicographically sorted node types that need 
-\end{definition}
-
-\todo{split into classes / subclasses}
-\todo{define iteration}
-\todo{remind the cheat}
+    Section \(T_{i,j}\) is defined as subset of \(T_i\) adding specific set of nodes. We assign \(j\) according to the lexicographical order of lexicographically sorted node types.
+\end{definition}
+
+\begin{definition}
+    Part \(T_{i,j,k}\) is defined as single transformation in section \(T_{i,j}\). \(k\) is assigned according to the order of discovering the transformation.
+\end{definition}
+
+In order to make interpretation more human readable, we will be using local notation:
+
+\begin{definition}
+    In context of \(T_i\), \(k\) is defined as \((n - i)\).
+\end{definition}
+
+\begin{definition}
+    In context of \(T_i\), \(C_k\) is defined as \(L(n - i)\), ie.\ number of trees transformations from \(T_i\) are working on.
+\end{definition}
+
+\begin{definition}
+    Section equation \(E_{i, j}\) is an equation defined in context of \(T_i\) that evaluates to a total number of trees that should be generated by transformations from \(T_{i, j}\).
+\end{definition}
+
+\begin{definition}
+    Section expression \(S_{i, j}\) is pair of section equation and set of kinds of nodes the transformation introduces.
+\end{definition}
+
+For the problem of interpreting trees of lambda terms we define following section expressions:
+
+\[\begin{array}{rccrlc}
+        S_{0,0} &=& (& (k + 1) C_k,& \emptyset &)\\
+        S_{1,0} &=& (& - (2 k + 1) C_k,& \{l\} &)\\
+        S_{1,1} &=& (& - 2 (k + 1) C_k,& \{s\} &)\\
+        S_{2,0} &=& (& - (4 k) C_k,& \{aou\} &)\\
+        S_{2,1} &=& (& (k) C_k,& \{ll\} &)\\
+        S_{2,2} &=& (& (4 k + 2) C_k,& \{ls\} &)\\
+        S_{2,3} &=& (& (k + 1) C_k,& \{ss\} &)\\
+        S_{3,0} &=& (& 2 (2 k + 1) C_k,& \{aosu\} &)\\
+        S_{3,1} &=& (& - (2 k) C_k,& \{lls\} &)\\
+        S_{3,2} &=& (& - (2 k + 1) C_k,& \{lss\} &)\\
+        S_{4,0} &=& (& k C_k,& \{llss\} &)\\
+\end{array}\]
+
+Using context-based variables makes the equation simpler to interpret, as we can immediately see relation between \(k\) and multiplier.
+
+\subsection{Iteration}%
+\label{sub:iteration}
+
+As we want to make our work kind of organized, we are going to divide the process into iterations. Each iteration should be a small step into direction of solving the original problem.
+
+We are going to generate two kinds of trees.
+Positive and negative ones.
+When computing total number of trees, we count positive tree is counted as \(1\), negative as \(-1\).
+Our goal is to generate \(E_{i, j}\) trees for each section \(T_{i, j}\).
+
+We start with interpreting \(E_{0,0}\).
+
+\subsection{The cheat}%
+\label{sub:the_cheat}
+
+You may ask how we achieved such partial result.
 

### 2021-08-07 article/main.tex
Describe fragment of the brutal approach

@@
 \RequirePackage{graphicx}
+\RequirePackage{svg}
 
@@
 
+\newcommand{\includeinlinesvg}[2]{\begin{minipage}{#1\textwidth}\includesvg[width=\textwidth]{#2}\end{minipage}}
+
 \begin{document}
@@
 
-\(\pointed{v}\) is implicitly defined as a pointed node \(v\).
+\(\pointed{v}\) is implicitly defined as a pointed node \(v\). We can treat it as node with additional label \(\pointed{}\).
 
@@
 \[\begin{array}{rl}
-        & (n - 4) l^2 s^2 L(n - 4)\\
+        0 =& (n - 4) l^2 s^2 L(n - 4)\\
         +& ((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) L(n - 3)\\
@@
 \[\begin{array}{rl}
-        & (n - 4) L(n - 4)\\
+        0 =& (n - 4) L(n - 4)\\
         +& L(n - 3)\\
@@
 
-\subsection{The framework}%
+\subsection{The Transformator framework}%
 \label{sub:the_framework}
 
-We also created a framework that may help visualize our work.
+We also created a framework, called transformator, that may help visualize our work.
 It is based on the idea that every transformation described using bijective language can be translated to a function transforming node and finite number of its surrounding nodes.
@@
 
-We start with interpreting \(E_{0,0}\).
+Our brains like small examples, so we will consider small \(n = 3\). This will cause some classes to be empty at the beginning, but it's ok. That's less trees to look at.
+
+\begin{lstlisting}
+=== Classes stats ===
+[ ]  0,0:       0 of      16 | (k + 1) * Ck              []
+[ ]  1,0:       0 of     -10 | - (2 * k + 1) * Ck        [l]
+[ ]  1,1:       0 of     -12 | - 2 * (k + 1) * Ck        [s]
+[ ]  2,0:       0 of      -4 | - (4 * k) * Ck            [aou]
+[ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
+[ ]  2,2:       0 of       6 | (4 * k + 2) * Ck          [ls]
+[ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
+[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aosu]
+[x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
+[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Ck        [lss]
+[x]  4,0:       0 of       0 | k * Ck                    [llss]
+\end{lstlisting}
+
+This statistic tells us for each section, how many trees have been generated of expected total number of trees in that section. \verb|[x]| means that we generated enough trees for such section.
+
+We start with interpreting \(E_{0,0} = (k + 1) C_k\). From statistics above, we see that we should generate \(16\) trees. \((k + 1)\) suggests pointing virtual leaf. Let's do so.
+
+\begin{lstlisting}
+c.define_class(0)
+
+c.define_section(0)
+
+c.append_r_class_subtree_visitor(1,       # we define positive trees
+                                          # ie. that count as 1
+    lambda kind, left, right:
+        None if kind[0] is not None else  # we ignore all actual nodes
+        [kind + ("*", )] + left + right   # for each virtual node we point it
+)
+\end{lstlisting}
+
+\begin{lstlisting}
+# define 0,0: (k + 1) * Ck []
+=== Classes stats ===
+[x]  0,0:      16 of      16 | (k + 1) * Ck              []
+[ ]  1,0:       0 of     -10 | - (2 * k + 1) * Ck        [l]
+[ ]  1,1:       0 of     -12 | - 2 * (k + 1) * Ck        [s]
+[ ]  2,0:       0 of      -4 | - (4 * k) * Ck            [aou]
+[ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
+[ ]  2,2:       0 of       6 | (4 * k + 2) * Ck          [ls]
+[ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
+[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aosu]
+[x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
+[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Ck        [lss]
+[x]  4,0:       0 of       0 | k * Ck                    [llss]
+=== Diff stats ===
+0,0:     0    16
+\end{lstlisting}
+
+The framework informs us that we have generated all trees for section \(0,0\) for \(n = 3\). It also can provide us with the visualization of the trees we have generated. For example:
+
+\includeinlinesvg{.19}{images/trees_00/4_base.svg}%
+\(\Rightarrow\)
+\includeinlinesvg{.19}{images/trees_00/4.svg}%
+\includeinlinesvg{.19}{images/trees_00/5.svg}%
+\includeinlinesvg{.19}{images/trees_00/6.svg}%
+\includeinlinesvg{.19}{images/trees_00/7.svg}%
+
+If we take a look at more examples, we can start seeing some patterns:
+
+\includeinlinesvg{.33}{images/trees_00/2.svg}%
+\includeinlinesvg{.33}{images/trees_00/3.svg}%
+\includeinlinesvg{.33}{images/trees_00/7.svg}%
+
+\includeinlinesvg{.33}{images/trees_00/4.svg}%
+\includeinlinesvg{.33}{images/trees_00/12.svg}%
+\includeinlinesvg{.33}{images/trees_00/13.svg}%
+
+\includeinlinesvg{.20}{images/trees_00/0.svg}%
+\includeinlinesvg{.20}{images/trees_00/1.svg}%
+\includeinlinesvg{.20}{images/trees_00/5.svg}%
+\includeinlinesvg{.20}{images/trees_00/6.svg}%
+\includeinlinesvg{.20}{images/trees_00/8.svg}%
+
+\includeinlinesvg{.20}{images/trees_00/9.svg}%
+\includeinlinesvg{.20}{images/trees_00/10.svg}%
+\includeinlinesvg{.20}{images/trees_00/11.svg}%
+\includeinlinesvg{.20}{images/trees_00/14.svg}%
+\includeinlinesvg{.20}{images/trees_00/15.svg}%
+
+The order may be a bit suggestive.
+Let's take a look at class \(1\).
+Section \(1,0\) adds single \(l\) node, section \(1,1\) adds single \(s\) node.
+It actually suggests how can we can try to generate first and second line of the trees above.
+The first one is simple.
+Let's add \(l\) node with pointed right virtual node to each actual node:
+
+\begin{lstlisting}
+c.define_class(1)
+
+c.define_section(0)
+
+c.append_r_class_subtree_visitor(-1,                # negative node
+    lambda kind, left, right:
+        None if kind[0] is None else                # we ignore all virtual nodes
+        ["l", kind] + left + right + [(None, "*")]  # for each actual node we add
+                                                    # l node with right virtual
+                                                    # node pointed as a parent
+)
+\end{lstlisting}
+
+It creates following trees:
+
+\includeinlinesvg{.24}{images/trees_100/0_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/0.svg}%
+\includeinlinesvg{.24}{images/trees_100/1_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/1.svg}%
+
+\includeinlinesvg{.24}{images/trees_100/2_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/2.svg}%
+\includeinlinesvg{.24}{images/trees_100/3_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/3.svg}%
+
+It addresses all cases from the first line.
+It introduces incorrect lambda tree though in which \(s\) is parent of \(l\), which can not happen.
+We will fix it with the section \(2,2\) generating positive trees, which introduces one \(l\) node and one \(s\) by extending the tree with \(2\) nodes where \(s\) is parent of \(l\).
 

### 2021-08-15 article/main.tex
Fix images

@@
 \RequirePackage{svg}
+
+\svgpath{images/}
 
@@
 
-\includeinlinesvg{.19}{images/trees_00/4_base.svg}%
+\includeinlinesvg{.19}{trees_00__4_base.svg}%
 \(\Rightarrow\)
-\includeinlinesvg{.19}{images/trees_00/4.svg}%
-\includeinlinesvg{.19}{images/trees_00/5.svg}%
-\includeinlinesvg{.19}{images/trees_00/6.svg}%
-\includeinlinesvg{.19}{images/trees_00/7.svg}%
-
-If we take a look at more examples, we can start seeing some patterns:
-
-\includeinlinesvg{.33}{images/trees_00/2.svg}%
-\includeinlinesvg{.33}{images/trees_00/3.svg}%
-\includeinlinesvg{.33}{images/trees_00/7.svg}%
-
-\includeinlinesvg{.33}{images/trees_00/4.svg}%
-\includeinlinesvg{.33}{images/trees_00/12.svg}%
-\includeinlinesvg{.33}{images/trees_00/13.svg}%
-
-\includeinlinesvg{.20}{images/trees_00/0.svg}%
-\includeinlinesvg{.20}{images/trees_00/1.svg}%
-\includeinlinesvg{.20}{images/trees_00/5.svg}%
-\includeinlinesvg{.20}{images/trees_00/6.svg}%
-\includeinlinesvg{.20}{images/trees_00/8.svg}%
-
-\includeinlinesvg{.20}{images/trees_00/9.svg}%
-\includeinlinesvg{.20}{images/trees_00/10.svg}%
-\includeinlinesvg{.20}{images/trees_00/11.svg}%
-\includeinlinesvg{.20}{images/trees_00/14.svg}%
-\includeinlinesvg{.20}{images/trees_00/15.svg}%
+\includeinlinesvg{.19}{trees_00__4.svg}%
+\includeinlinesvg{.19}{trees_00__5.svg}%
+\includeinlinesvg{.19}{trees_00__6.svg}%
+\includeinlinesvg{.19}{trees_00__7.svg}%
+
+If we take a look at more examples from class \(0\), we can start seeing some patterns:
+
+\includeinlinesvg{.33}{trees_00__2.svg}%
+\includeinlinesvg{.33}{trees_00__3.svg}%
+\includeinlinesvg{.33}{trees_00__7.svg}%
+
+\includeinlinesvg{.33}{trees_00__4.svg}%
+\includeinlinesvg{.33}{trees_00__12.svg}%
+\includeinlinesvg{.33}{trees_00__13.svg}%
+
+\includeinlinesvg{.20}{trees_00__0.svg}%
+\includeinlinesvg{.20}{trees_00__1.svg}%
+\includeinlinesvg{.20}{trees_00__5.svg}%
+\includeinlinesvg{.20}{trees_00__6.svg}%
+\includeinlinesvg{.20}{trees_00__8.svg}%
+
+\includeinlinesvg{.20}{trees_00__9.svg}%
+\includeinlinesvg{.20}{trees_00__10.svg}%
+\includeinlinesvg{.20}{trees_00__11.svg}%
+\includeinlinesvg{.20}{trees_00__14.svg}%
+\includeinlinesvg{.20}{trees_00__15.svg}%
 
 The order may be a bit suggestive.
-Let's take a look at class \(1\).
-Section \(1,0\) adds single \(l\) node, section \(1,1\) adds single \(s\) node.
+Section \(1,0\) adds single \(l\) node, whereas section \(1,1\) adds single \(s\) node.
 It actually suggests how can we can try to generate first and second line of the trees above.
@@
 
-\includeinlinesvg{.24}{images/trees_100/0_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/0.svg}%
-\includeinlinesvg{.24}{images/trees_100/1_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/1.svg}%
-
-\includeinlinesvg{.24}{images/trees_100/2_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/2.svg}%
-\includeinlinesvg{.24}{images/trees_100/3_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{images/trees_100/3.svg}%
-
-It addresses all cases from the first line.
-It introduces incorrect lambda tree though in which \(s\) is parent of \(l\), which can not happen.
+\includeinlinesvg{.24}{trees_100__0_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__0.svg}%
+\includeinlinesvg{.24}{trees_100__1_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__1.svg}%
+
+\includeinlinesvg{.24}{trees_100__2_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__2.svg}%
+\includeinlinesvg{.24}{trees_100__3_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__3.svg}%
+
+It addresses all cases from the first line, but also introduces incorrect lambda tree in which \(s\) is parent of \(l\), which can not happen.
 We will fix it with the section \(2,2\) generating positive trees, which introduces one \(l\) node and one \(s\) by extending the tree with \(2\) nodes where \(s\) is parent of \(l\).

### 2021-08-16 article/main.tex
Describe lambda case

@@
 \definecolor{egyptianblue}{rgb}{0.06, 0.2, 0.65}
+\definecolor{lightgray}{gray}{0.60}
 
@@
 \lstset{
-    basicstyle=\small
+    basicstyle=\footnotesize\ttfamily,
+    comment=[l]{\#},
+    morecomment=[s]{/*}{*/},
+    commentstyle=\color{lightgray}\ttfamily,
+    escapeinside={<@}{@>}
 }
@@
 
+Green edges 
+\begin{minipage}{1.5em}
+\includesvg[width=\textwidth]{green_edge}
+\end{minipage}
+depict edges to \(\no\) nodes.
+
 Virtual node is artificially defined node that does not affect the structure definition (eg.\ we can define virtual leafs that are children of actual leaves of the binary tree.
@@
 
-\[B = \text{leaf} + B^2\]
-
-\todo{Add some image}
+\begin{center}
+    \begin{minipage}[t]{.2\textwidth}
+        \begin{center}
+            \(B\)\\
+            \includesvg[scale=0.5]{binary_tree_def_1}%
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.05\textwidth}
+        \begin{center}
+            \(=\)\\
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.2\textwidth}
+        \begin{center}
+            \(\text{leaf}\)\\
+            \includesvg[scale=0.5]{binary_tree_def_2}%
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.05\textwidth}
+        \begin{center}
+            \(+\)\\
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.2\textwidth}
+        \begin{center}
+            \(B^2\)\\
+            \includesvg[scale=0.5]{binary_tree_def_3}%
+        \end{center}
+    \end{minipage}%
+\end{center}
 
@@
 
-iilll\todo{Add image}
+\begin{center}
+    \includesvg[scale=.7]{iilll}
+\end{center}
 \end{example}
@@
     \(\n \n \no \n \no \no \no\)
-    \todo{Add image}
+    \begin{center}
+        \includesvg[scale=.7]{oononnn}
+    \end{center}
 \end{example}
@@
     \item node has has children, ie.~is not a virtual leaf (which corresponds to \(n - 1\));
+    \item node is a root (which corresponds to \(1\));
     \item node has its parent on the left, ie.~is right child of its parent;
@@
         S_{1,1} &=& (& - 2 (k + 1) C_k,& \{s\} &)\\
-        S_{2,0} &=& (& - (4 k) C_k,& \{aou\} &)\\
+        S_{2,0} &=& (& - (4 k) C_k,& \{ao\} &)\\
         S_{2,1} &=& (& (k) C_k,& \{ll\} &)\\
@@
         S_{2,3} &=& (& (k + 1) C_k,& \{ss\} &)\\
-        S_{3,0} &=& (& 2 (2 k + 1) C_k,& \{aosu\} &)\\
+        S_{3,0} &=& (& 2 (2 k + 1) C_k,& \{aos\} &)\\
         S_{3,1} &=& (& - (2 k) C_k,& \{lls\} &)\\
@@
 [ ]  1,1:       0 of     -12 | - 2 * (k + 1) * Ck        [s]
-[ ]  2,0:       0 of      -4 | - (4 * k) * Ck            [aou]
+[ ]  2,0:       0 of      -4 | - (4 * k) * Ck            [ao]
 [ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
@@
 [ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
-[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aosu]
+[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aos]
 [x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
@@
 
-\includeinlinesvg{.19}{trees_00__4_base.svg}%
+\includeinlinesvg{.19}{trees_00__4_base}%
 \(\Rightarrow\)
-\includeinlinesvg{.19}{trees_00__4.svg}%
-\includeinlinesvg{.19}{trees_00__5.svg}%
-\includeinlinesvg{.19}{trees_00__6.svg}%
-\includeinlinesvg{.19}{trees_00__7.svg}%
+\includeinlinesvg{.19}{trees_00__4}%
+\includeinlinesvg{.19}{trees_00__5}%
+\includeinlinesvg{.19}{trees_00__6}%
+\includeinlinesvg{.19}{trees_00__7}%
 
@@
 
-\includeinlinesvg{.33}{trees_00__2.svg}%
-\includeinlinesvg{.33}{trees_00__3.svg}%
-\includeinlinesvg{.33}{trees_00__7.svg}%
-
-\includeinlinesvg{.33}{trees_00__4.svg}%
-\includeinlinesvg{.33}{trees_00__12.svg}%
-\includeinlinesvg{.33}{trees_00__13.svg}%
-
-\includeinlinesvg{.20}{trees_00__0.svg}%
-\includeinlinesvg{.20}{trees_00__1.svg}%
-\includeinlinesvg{.20}{trees_00__5.svg}%
-\includeinlinesvg{.20}{trees_00__6.svg}%
-\includeinlinesvg{.20}{trees_00__8.svg}%
-
-\includeinlinesvg{.20}{trees_00__9.svg}%
-\includeinlinesvg{.20}{trees_00__10.svg}%
-\includeinlinesvg{.20}{trees_00__11.svg}%
-\includeinlinesvg{.20}{trees_00__14.svg}%
-\includeinlinesvg{.20}{trees_00__15.svg}%
+\includeinlinesvg{.33}{trees_00__2}%
+\includeinlinesvg{.33}{trees_00__3}%
+\includeinlinesvg{.33}{trees_00__7}%
+
+\includeinlinesvg{.33}{trees_00__4}%
+\includeinlinesvg{.33}{trees_00__12}%
+\includeinlinesvg{.33}{trees_00__13}%
+
+\includeinlinesvg{.16}{trees_00__0}%
+\includeinlinesvg{.16}{trees_00__1}%
+\includeinlinesvg{.16}{trees_00__5}%
+\includeinlinesvg{.16}{trees_00__6}%
+\includeinlinesvg{.16}{trees_00__14}%
+\includeinlinesvg{.16}{trees_00__15}%
+
+\includeinlinesvg{.25}{trees_00__8}%
+\includeinlinesvg{.25}{trees_00__9}%
+\includeinlinesvg{.25}{trees_00__10}%
+\includeinlinesvg{.25}{trees_00__11}%
 
@@
 
-\includeinlinesvg{.24}{trees_100__0_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__0.svg}%
-\includeinlinesvg{.24}{trees_100__1_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__1.svg}%
-
-\includeinlinesvg{.24}{trees_100__2_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__2.svg}%
-\includeinlinesvg{.24}{trees_100__3_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__3.svg}%
+\includeinlinesvg{.24}{trees_100__0_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__0}%
+\includeinlinesvg{.24}{trees_100__1_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__1}%
+
+\includeinlinesvg{.24}{trees_100__2_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__2}%
+\includeinlinesvg{.24}{trees_100__3_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__3}%
 
@@
 
+Next, we can take care of the later cases of section \(0, 0\). It can be also expressed using sections \(1, 0\) and \(1, 1\):
+
+\begin{lstlisting}
+c.define_class(1)
+
+c.define_section(0)
+
+# old visitior
+c.append_r_class_subtree_visitor(-1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["l", kind] + left + right + [(None, "*")]
+)
+
+# new visitior
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["l", parent_kind] + [left[0] + ("*",)] + left[1:] + right + [None]
+)
+
+# new visitior
+c.append_r_class_left_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["l", parent_kind] + left + [right[0] + ("*",)] + right[1:] + [None]
+)
+
+c.define_section(1)
+
+# old visitior
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", (None, "*"), parent_kind] + left + right
+)
+
+# new visitior
+c.append_r_class_left_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, parent_kind] + left + [right[0] + ("*",)] + right[1:]
+)
+
+# new visitior
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, parent_kind] + [left[0] + ("*",)] + left[1:] + right
+)
+\end{lstlisting}
+
+Basicaly, for each virtual node not being root (ie.\ having left or right parent), we point it and add \(l\) or \(s\) respectively above the parent.
+
+\includeinlinesvg{.32}{trees_111__1_base}%
+\(\Rightarrow\)
+\includeinlinesvg{.32}{trees_101__0}%
+\includeinlinesvg{.32}{trees_112__0}%
+
+The last row can be generated using section \(2, 0\):
+
+\begin{lstlisting}
+c.define_class(2)
+
+c.define_section(0)
+
+c.append_r_class_subtree_visitor(-1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["a", "o", (None, "*"), None, kind] + left + right
+)
+
+c.append_r_class_subtree_visitor(-1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["a", "o", None, (None, "*"), kind] + left + right
+)
+
+c.append_r_class_subtree_visitor(-1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["a", kind] + left + right + ["o", (None, "*"), None]
+)
+
+c.append_r_class_subtree_visitor(-1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["a", kind] + left + right + ["o", None, (None, "*")]
+)
+\end{lstlisting}
+
+For each actual vertex, we add \(a\) node as its left or right parent and add as a second child \(o\) node as its siblig. We then point left or right virtual child of newly created \(o\) node.
+
+\includeinlinesvg{.20}{trees_200__0_base}%
+\(\Rightarrow\)
+\includeinlinesvg{.20}{trees_200__0}%
+\includeinlinesvg{.20}{trees_201__0}%
+\includeinlinesvg{.20}{trees_202__0}%
+\includeinlinesvg{.20}{trees_203__0}%
+
+After such transformations, we get following statistics:
+
+\begin{lstlisting}
+=== Classes stats ===
+[x]  0,0:      16 of      16 | (k + 1) * Ck              []
+[x]  1,0:     -10 of     -10 | - (2 * k + 1) * Ck        [l]
+[ ]  1,1:      -9 of     -12 | - 2 * (k + 1) * Ck        [s]
+[x]  2,0:      -4 of      -4 | - (4 * k) * Ck            [ao]
+[ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
+[ ]  2,2:       0 of       6 | (4 * k + 2) * Ck          [ls]
+[ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
+[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aos]
+[x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
+[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Ck        [lss]
+[x]  4,0:       0 of       0 | k * Ck                    [llss]
+=== Diff stats ===
+1,0:     4     0
+1,1:     3     0
+\end{lstlisting}
+
+This construction works also for bigger \(N\):
+
+\begin{lstlisting}
+=== Classes stats ===
+[x]  0,0:   39050 of   39050 | (k + 1) * Ck              []
+[x]  1,0:  -23237 of  -23237 | - (2 * k + 1) * Ck        [l]
+[ ]  1,1:  -17799 of  -24460 | - 2 * (k + 1) * Ck        [s]
+[x]  2,0:  -13728 of  -13728 | - (4 * k) * Ck            [ao]
+[ ]  2,1:       0 of    3432 | (k) * Ck                  [ll]
+[ ]  2,2:       0 of   14586 | (4 * k + 2) * Ck          [ls]
+[ ]  2,3:       0 of    3861 | (k + 1) * Ck              [ss]
+[ ]  3,0:       0 of    4620 | 2 * (2 * k + 1) * Ck      [aos]
+[ ]  3,1:       0 of   -2156 | - (2 * k) * Ck            [lls]
+[ ]  3,2:       0 of   -2310 | - (2 * k + 1) * Ck        [lss]
+[ ]  4,0:       0 of     342 | k * Ck                    [llss]
+=== Diff stats ===
+1,0:  7602     0
+1,1:  5832     0
+2,0:  2280     0
+\end{lstlisting}
+
+The process can then be repeated for each section. We have chosen lexicographical order (ie. \(0,0\); \(1,0\); \(1,1\); \(2,0\); \(\ldots\)).
+
+\subsection{Final result}%
+\label{sub:final_result}
+
+After multiple iterations, we managed to come up with following construction:
+
+\begin{lstlisting}
+c.define_class(0)
+
+c.define_section(0)
+
+c.append_r_class_subtree_visitor(1,
+    lambda kind, left, right:
+        None if kind[0] is not None else
+        [kind + ("*", )] + left + right
+)
+
+c.define_class(1)
+
+c.define_section(0)
+
+c.append_r_class_subtree_visitor(-1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["l", kind] + left + right + [(None, "*")]
+)
+
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["l", parent_kind] + [left[0] + ("*",)] + left[1:] + right + [None]
+)
+
+c.append_r_class_left_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["l", parent_kind] + left + [right[0] + ("*",)] + right[1:] + [None]
+)
+
+c.define_section(1)
+
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", (None, "*"), parent_kind] + left + right
+)
+
+c.append_r_class_left_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, parent_kind] + left + [right[0] + ("*",)] + right[1:]
+)
+
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, parent_kind] + [left[0] + ("*",)] + left[1:] + right
+)
+
+c.define_class(2)
+
+c.define_section(0)
+
+c.append_r_class_subtree_visitor(-1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["a", "o", (None, "*"), None, kind] + left + right
+)
+
+c.append_r_class_subtree_visitor(-1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["a", "o", None, (None, "*"), kind] + left + right
+)
+
+c.append_r_class_subtree_visitor(-1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["a", kind] + left + right + ["o", (None, "*"), None]
+)
+
+c.append_r_class_subtree_visitor(-1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["a", kind] + left + right + ["o", None, (None, "*")]
+)
+
+c.define_section(1)
+
+c.append_r_class_subtree_visitor(1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["l", "l", kind] + left + right + [(None, "*"), None]
+)
+
+c.define_section(2)
+
+c.append_r_class_right_parent_subtree_visitor(1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["l", "s", (None, "*"), parent_kind] + left + right + [None]
+)
+
+c.append_r_class_subtree_visitor(1,
+    lambda kind, left, right:
+        None if kind[0] is None else
+        ["s", None, "l", kind] + left + right + [(None, "*")]
+)
+
+c.append_r_class_right_parent_subtree_visitor(1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "l", parent_kind] + left + right + [(None, "*")]
+)
+
+c.append_r_class_right_parent_subtree_visitor(1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "l", parent_kind] + [left[0] + ("*", )] + left[1:] + right + [None]
+)
+
+c.append_r_class_left_parent_subtree_visitor(1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "l", parent_kind] + left + [right[0] + ("*", )] + right[1:] + [None]
+)
+
+c.define_section(3)
+
+c.append_r_class_right_parent_subtree_visitor(1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "s", (None, "*"), parent_kind] + left + right
+)
+
+c.define_class(3)
+
+c.define_section(0)
+
+c.append_r_class_right_parent_subtree_visitor(1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "a", "o", (None, "*"), None, parent_kind] + left + right
+)
+
+c.append_r_class_right_parent_subtree_visitor(1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "a", "o", None, (None, "*"), parent_kind] + left + right
+)
+
+c.append_r_class_right_parent_subtree_visitor(1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "a", parent_kind] + left + right + ["o", (None, "*"), None]
+)
+
+c.append_r_class_right_parent_subtree_visitor(1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "a", parent_kind] + left + right + ["o", None, (None, "*")]
+)
+
+c.define_section(1)
+
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "l", "l", parent_kind] + left + right + [(None, "*"), None]
+)
+
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        ["s", None, "l", "l", parent_kind] + left + right + [(None, "*"), None]
+)
+
+c.define_section(2)
+
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "s", None, "l", parent_kind] + left + right + [(None, "*")]
+)
+
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "l", "s", (None, "*"), parent_kind] + left + right + [None]
+)
+
+c.define_class(4)
+
+c.define_section(0)
+
+c.append_r_class_right_parent_subtree_visitor(1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, "s", None, "l", "l", parent_kind] + left + right + [(None, "*"), None]
+)
+\end{lstlisting}
+
+It resulted in final statistics:
+
+\begin{lstlisting}
+=== Classes stats ===
+[x]  0,0:   39050 of   39050 | (k + 1) * Ck              []
+[x]  1,0:  -23237 of  -23237 | - (2 * k + 1) * Ck        [l]
+[ ]  1,1:  -17799 of  -24460 | - 2 * (k + 1) * Ck        [s]
+[x]  2,0:  -13728 of  -13728 | - (4 * k) * Ck            [ao]
+[x]  2,1:    3432 of    3432 | (k) * Ck                  [ll]
+[ ]  2,2:   10833 of   14586 | (4 * k + 2) * Ck          [ls]
+[ ]  2,3:    1770 of    3861 | (k + 1) * Ck              [ss]
+[ ]  3,0:    2280 of    4620 | 2 * (2 * k + 1) * Ck      [aos]
+[ ]  3,1:   -1648 of   -2156 | - (2 * k) * Ck            [lls]
+[ ]  3,2:   -1140 of   -2310 | - (2 * k + 1) * Ck        [lss]
+[ ]  4,0:     187 of     342 | k * Ck                    [llss]
+=== Diff stats ===
+\end{lstlisting}
+
+As you can see, diff stats are empty, so we managed to generate expected trees on both sides of the equation.
+
+You may also note that we didn't generate all trees suggested by the recurrence. This is due to one cheat we used.
+
 \subsection{The cheat}%
@@
 
-You may ask how we achieved such partial result.
+You may remember our assumptions in section \ref{sub:the_framework} about the discrimination cases.
+We allowed ourselves to apply visitors only to one of left and right child, which isn't handled by our holonomic recurrence as number of such vertices do not depend only on \(n\).
+
+To fix this, one can for example add construction for section \(1, 0\) to generate all expected trees from it and then repeat the iteration in order to generate matching trees on the other side of the equation.
+We can see that we used \(2\) constructions visiting node with right parent and only one visiting node having left parent, so our missing construction should also visit nodes with left parent.
+
+\begin{lstlisting}
+c.define_class(1)
+
+c.define_section(0)
+
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", (None, "*"), parent_kind] + left + right
+)
+
+c.append_r_class_left_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, parent_kind] + left + [right[0] + ("*",)] + right[1:]
+)
+
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, parent_kind] + [left[0] + ("*",)] + left[1:] + right
+)
+
+# example missing construction
+c.append_r_class_left_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", (None, "*"), parent_kind] + left + right
+)
+\end{lstlisting}
+
+Please note that it is only an example of missing construction. It is just the simplest one we could think about, and in that case, simple solution is most often the correct one.
 
@@
 
-\todo{finish interpretation}
-\todo{missing formal proof}
+First thing to be done, that comes to mind immediately, is to finish the construction eliminating the cheat mentioned in section \ref{sub:the_cheat}.
+
+You may also note that we are operating on specific \(N\).
+The probability that we miss some corner case is low, but even if we check large \(N\) values, it is always present.
+The formal algebraic proof would make us sure that the construction works.
+We woulr prioritize finishing the construction first.
+
+The framework also isn't perfect.
+It highly depends on the operator's intuition.
+We believe that the solving process can be automated.
+The simplest method that comes to mind is simply creating heuristic rules that then will be used by the framework to guess at least partial solution.
+
+We believe that one day all of that will be done.
 

### 2021-08-16 article/main.tex
Add more images

@@
 \DeclareUnicodeCharacter{00A0}{ }
+\DeclareUnicodeCharacter{25CF}{\(\n\)}
 
@@
 \RequirePackage{geometry}
+\RequirePackage{tabularx}
 \RequirePackage{graphicx}
@@
 
+\begin{figure}[h]
     \begin{center}
@@
     \end{center}
+    \caption{Binary tree recursive definition}
+    \label{fig:binary_recursion}
+\end{figure}
 
@@
 
-\begin{example}
-    \(\n \n \no \n \no \no \no\)
-    \begin{center}
+\begin{figure}[h]
+    \centering
     \includesvg[scale=.7]{oononnn}
-    \end{center}
-\end{example}
-
-We also can define prefix and suffix of \(T\).
+    \caption{\(\n \n \no \n \no \no \no\)}
+    \label{fig:oononnn}
+\end{figure}
+
+We can also define prefix and suffix of \(T\).
 
@@
 
-\todo{Add some illustration}
+\begin{figure}[h]
+    \centering
+    \begin{minipage}{.25\textwidth}\includesvg[scale=0.35]{remy_base}\end{minipage}%
+    \(\Rightarrow\)
+    \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{remy_left}\end{minipage}%
+    \caption{\(\enc{R_l(T, v)}\)}
+    \label{fig:remy_left}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \begin{minipage}{.25\textwidth}\includesvg[scale=0.35]{remy_base}\end{minipage}%
+    \(\Rightarrow\)
+    \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{remy_right}\end{minipage}%
+    \caption{\(\enc{R_r(T, v)}\)}
+    \label{fig:remy_right}
+\end{figure}
 
@@
 
-\todo{image of transformation unary-binary to full-binary}
+\begin{figure}[h]
+    \centering
+    \includeinlinesvg{.2}{unary_binary_base}%
+    \(\Rightarrow\)%
+    \includeinlinesvg{.3}{unary_binary_full}
+    \caption{Unary-binary tree to full-binary tree transformation}
+    \label{fig:unary_binary_transformation}
+\end{figure}
 
@@
 
-To present the interpretation in bijective language, we will have to introduce several types of the the virtual leaves (you may want to revisit section \ref{sub:notation} Notation):
+To present the interpretation in bijective language, we will have to introduce several types of the the nodes (you may want to revisit section \ref{sub:notation} Notation):
 
@@
             \item VltUra - Vlt which uncle is a right actual node;
-            \item VltUla - Vlt which uncle is a left actual node.
+            \item VltUla - Vlt which uncle is a left actual node;
         \end{enumerate}
+    \item I - Internal node.
 \end{enumerate}
@@
 
-\todo{draw the transformations}
+\begin{center}
+    \begin{tabular}{| c | c | c |}
+        \hline
+
+        \(U(n-2)\) &
+        \(U(n-1)\) &
+        \(U(n)\)\\
+        \hline
+
+        &
+        I \includesvg[scale=0.4]{ub_1si} &
+        Vro \includesvg[scale=0.4]{ub_0fid} \\
+        \hline
+    \end{tabular}
+\end{center}
+\todo{finish the table}
 
@@
 
-\todo{example}
+\begin{figure}[h]
+    \centering
+    \includesvg[scale=0.4]{schroder_1}
+    \includesvg[scale=0.4]{schroder_2}
+    \includesvg[scale=0.4]{schroder_3}
+    \includesvg[scale=0.4]{schroder_4}
+    \(\ldots\)
+    \caption{Schröder tree node}
+    \label{fig:schroder_trees}
+\end{figure}
 

### 2021-08-19 article/main.tex
Fix spelling

@@
 
-\(\tSub(v)\) is implicitly defined as a whole subree rooted with node \(v\).
-
-\(\tLeft(v)\) is implicitly defined as a left subree of node \(v\).
-
-\(\tRight(v)\) is implicitly defined as a right subree of node \(v\).
+\(\tSub(v)\) is implicitly defined as a whole subtree rooted with node \(v\).
+
+\(\tLeft(v)\) is implicitly defined as a left subtree of node \(v\).
+
+\(\tRight(v)\) is implicitly defined as a right subtree of node \(v\).
 
@@
 
-In order to get some intuition on how it works unbeneath, let's take a look on how we can find number of the full binary trees of size \(2\). We can expand the recurrence a bit:
+In order to get some intuition on how it works underneath, let's take a look on how we can find number of the full binary trees of size \(2\). We can expand the recurrence a bit:
 
@@
 \begin{example}
-    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic, ie. none of them satisifies a linear recurrence equation with polynomial coefficients\cite{nonholo}.
+    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic, ie. none of them satisfies a linear recurrence equation with polynomial coefficients\cite{nonholo}.
 \end{example}
@@
 Holonomic recurrences are very useful if we want to count objects of given size.
-Of course, size can be defined in more complex ways, eg.\ we may want to find number of trees with \(n\) internal nodes having exactly \(m\) nodes beging left child of its parent.
+Of course, size can be defined in more complex ways, eg.\ we may want to find number of trees with \(n\) internal nodes having exactly \(m\) nodes being left child of its parent.
 
@@
 Analogically the tree of size \(n + 1\) has \(n + 2\) leaves and \(2n + 3\) nodes in total.
-If you see some resemblence to our holonomic recurrence, you are perfectly right.
+If you see some resemblance to our holonomic recurrence, you are perfectly right.
 
@@
 
-In the second case it is enough to noitice that \(R_l\) generates trees with pointed node being a left child, and \(R_r\) generates trees with pointed node being right child.
+In the second case it is enough to notice that \(R_l\) generates trees with pointed node being a left child, and \(R_r\) generates trees with pointed node being right child.
 That immediately provides us with conclusion that we are generating no duplicates.
@@
 
-The definition above is precise, but introduces a new kind of vertice that we would have to take care of.
+The definition above is precise, but introduces a new kind of node that we would have to take care of.
 We can avoid it by using a trick to make the tree recall binary tree.
@@
 
-When aplying \(L_2\) we achieve following cases respectively:
+When applying \(L_2\) we achieve following cases respectively:
 
@@
 
-To achive trees from \((n - 2) T(n - 1)\), we can simply take trees from case 3.
+To achieve trees from \((n - 2) T(n - 1)\), we can simply take trees from case 3.
 and replace the father of the \(s\) with \(t''\) and point root of \(t''\).
@@
 As you could see in the examples above, most of the solutions base on the simple analysis of number of laves, internal nodes and other similar properties.
-In this section, we've gathered some methods that may be helpful when trying to analyze the problem of interpreting combinatorically some holonomic recurrence.
+In this section, we've gathered some methods that may be helpful when trying to analyze the problem of interpreting combinatorially some holonomic recurrence.
 
@@
 
-First thing that we have to select is defining the size carrefully. We have few standard choices of computing tree sizes:
+First thing that we have to select is defining the size carefully. We have few standard choices of computing tree sizes:
 \begin{itemize}
@@
 
-As the main field of our interest was analyzis of terms of lambda trees in unary de Bruijn notation, we will use it as an example to describe the method.\todo{Add definition}
+As the main field of our interest was analysis of terms of lambda trees in unary de Bruijn notation, we will use it as an example to describe the method.\todo{Add definition}
 
@@
         \item if \(x\) is a variable and \(M \in \Lambda\), then \((\lambda x .
-M) \in \Lambda\) (abstraction, ie.\ creating a function with an argument \(x\) and binding each occurence of \(x\) in \(M\) to this argument)
+M) \in \Lambda\) (abstraction, ie.\ creating a function with an argument \(x\) and binding each occurrence of \(x\) in \(M\) to this argument)
     \end{itemize}
@@
 
-Which leads to following interpreation of \(\Phi\):
+Which leads to following interpretation of \(\Phi\):
 
@@
 
-\subsection{Enhanced holonomic reccurence}%
+\subsection{Enhanced holonomic recurrence}%
 \label{sub:enhanced_holonomic_reccurence}
@@
 
-The latest two are intruduced in order to make the analysis simpler, but do not have immediate interpretation in the world of holonomic recurrences.
+The latest two are introduced in order to make the analysis simpler, but do not have immediate interpretation in the world of holonomic recurrences.
 If we use them both, it sums up to all nodes except root (as root is neither left nor right child).
@@
 
-# old visitior
+# old visitor
 c.append_r_class_subtree_visitor(-1,
@@
 
-# new visitior
+# new visitor
 c.append_r_class_right_parent_subtree_visitor(-1,
@@
 
-# new visitior
+# new visitor
 c.append_r_class_left_parent_subtree_visitor(-1,
@@
 
-# old visitior
+# old visitor
 c.append_r_class_right_parent_subtree_visitor(-1,
@@
 
-Basicaly, for each virtual node not being root (ie.\ having left or right parent), we point it and add \(l\) or \(s\) respectively above the parent.
+Basically, for each virtual node not being root (ie.\ having left or right parent), we point it and add \(l\) or \(s\) respectively above the parent.
 
@@
 
-For each actual vertex, we add \(a\) node as its left or right parent and add as a second child \(o\) node as its siblig. We then point left or right virtual child of newly created \(o\) node.
+For each actual vertex, we add \(a\) node as its left or right parent and add as a second child \(o\) node as its sibling. We then point left or right virtual child of newly created \(o\) node.
 
@@
 The formal algebraic proof would make us sure that the construction works.
-We woulr prioritize finishing the construction first.
+We would prioritize finishing the construction first.
 

### 2021-08-21 article/main.tex
Resolve multiple todos

@@
 \RequirePackage{tabularx}
+\RequirePackage{longtable}
 \RequirePackage{graphicx}
@@
 \RequirePackage{amsmath}
+\RequirePackage{mathtools}
 \RequirePackage{amsfonts}
@@
 
+Dashed edges 
+\begin{minipage}{1.5em}
+\includesvg[width=\textwidth]{intro__dashed_edge}
+\end{minipage}
+depict edges that may or may not exist (eg.\ when we describe transformations and we don't care if the node is root or if it has children).
+
 Green edges 
 \begin{minipage}{1.5em}
-\includesvg[width=\textwidth]{green_edge}
+\includesvg[width=\textwidth]{intro__green_edge}
 \end{minipage}
@@
                 \(B\)\\
-                \includesvg[scale=0.5]{binary_tree_def_1}%
+                \includesvg[scale=0.5]{binary__def_1}%
             \end{center}
@@
                 \(\text{leaf}\)\\
-                \includesvg[scale=0.5]{binary_tree_def_2}%
+                \includesvg[scale=0.5]{binary__def_2}%
             \end{center}
@@
                 \(B^2\)\\
-                \includesvg[scale=0.5]{binary_tree_def_3}%
+                \includesvg[scale=0.5]{binary__def_3}%
             \end{center}
@@
 \begin{center}
-    \includesvg[scale=.7]{iilll}
+    \includesvg[scale=.7]{intro__iilll}
 \end{center}
@@
 \begin{definition}
-    Pre-order notation of \(n\)-ary tree \(T\), \(\enc{T}\), is defined recursively as \(\enc{\troot(T)} \prod_{i=1}^{n} \enc{i\text{-th subtree of } \troot(T)}\), ie.\ catenation of identifier of the root of the tree with encoded its subtrees from left to right.
+    Pre-order notation of \(n\)-ary tree \(T\), \(\enc{T}\), is defined recursively as:
+    \[\enc{T} = \enc{\troot(T)} \prod_{i=1}^{n} \enc{i\text{-th subtree of } \troot(T)}\]
+    ie.\ catenation of identifier of the root of the tree with encoded its subtrees from left to right.
 \end{definition}
@@
     \centering
-    \includesvg[scale=.7]{oononnn}
+    \includesvg[scale=.7]{intro__oononnn}
     \caption{\(\n \n \no \n \no \no \no\)}
@@
     \centering
-    \begin{minipage}{.25\textwidth}\includesvg[scale=0.35]{remy_base}\end{minipage}%
+    \begin{minipage}{.25\textwidth}\includesvg[scale=0.35]{binary__remy_base}\end{minipage}%
     \(\Rightarrow\)
-    \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{remy_left}\end{minipage}%
+    \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{binary__remy_left}\end{minipage}%
     \caption{\(\enc{R_l(T, v)}\)}
@@
     \centering
-    \begin{minipage}{.25\textwidth}\includesvg[scale=0.35]{remy_base}\end{minipage}%
+    \begin{minipage}{.25\textwidth}\includesvg[scale=0.35]{binary__remy_base}\end{minipage}%
     \(\Rightarrow\)
-    \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{remy_right}\end{minipage}%
+    \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{binary__remy_right}\end{minipage}%
     \caption{\(\enc{R_r(T, v)}\)}
@@
     \centering
-    \includeinlinesvg{.2}{unary_binary_base}%
+    \includeinlinesvg{.2}{unary_binary__base}%
     \(\Rightarrow\)%
-    \includeinlinesvg{.3}{unary_binary_full}
+    \includeinlinesvg{.3}{unary_binary__full}
     \caption{Unary-binary tree to full-binary tree transformation}
@@
 \begin{center}
-    \begin{tabular}{| c | c | c |}
+    \begin{longtable}{| c | c | c |}
         \hline
@@
         &
-        I \includesvg[scale=0.4]{ub_1si} &
-        Vro \includesvg[scale=0.4]{ub_0fid} \\
+        I \includesvg[scale=0.4]{unary_binary__1si} &
+        Vro \includesvg[scale=0.4]{unary_binary__0fid} \\
         \hline
-    \end{tabular}
-\end{center}
-\todo{finish the table}
+
+        &
+        Vlt \includesvg[scale=0.4]{unary_binary__1fjg} &
+        VrtUrv \includesvg[scale=0.4]{unary_binary__0fjdOgf} \\
+        \hline
+
+        I \includesvg[scale=0.4]{unary_binary__2i} &
+        &
+        VrtUra \includesvg[scale=0.4]{unary_binary__0fjdOdi} \\
+        \hline
+
+        &
+        Vro \includesvg[scale=0.4]{unary_binary__1fid} &
+        VrtUla \includesvg[scale=0.4]{unary_binary__0fjdOgi} \\
+        \hline
+
+        &
+        Vrt \includesvg[scale=0.4]{unary_binary__1fjd} &
+        VltUrv \includesvg[scale=0.4]{unary_binary__0fjgOdf} \\
+        \hline
+
+        I \includesvg[scale=0.4]{unary_binary__2i} &
+        &
+        VltUra \includesvg[scale=0.4]{unary_binary__0fjgOdi} \\
+        \hline
+
+        I \includesvg[scale=0.4]{unary_binary__2i} &
+        &
+        VltUla \includesvg[scale=0.4]{unary_binary__0fjgOgi} \\
+        \hline
+    \end{longtable}
+\end{center}
 
@@
     \centering
-    \includesvg[scale=0.4]{schroder_1}
-    \includesvg[scale=0.4]{schroder_2}
-    \includesvg[scale=0.4]{schroder_3}
-    \includesvg[scale=0.4]{schroder_4}
+    \includesvg[scale=0.4]{schroder__example_1}
+    \includesvg[scale=0.4]{schroder__example_2}
+    \includesvg[scale=0.4]{schroder__example_3}
+    \includesvg[scale=0.4]{schroder__example_4}
     \(\ldots\)
@@
 
-\todo{image of the transformations}
+\begin{figure}[h]
+    \begin{center}
+    \includeinlinesvg{.16}{schroder__lr_base}%
+    \(\xRightarrow{L_1}\)%
+    \includeinlinesvg{.16}{schroder__l1}%
+    \hspace{.1\textwidth}%
+    \includeinlinesvg{.16}{schroder__lr_base}%
+    \(\xRightarrow{L_2}\)%
+    \includeinlinesvg{.16}{schroder__l2}%
+
+    \includeinlinesvg{.16}{schroder__lr_base}%
+    \(\xRightarrow{R_1}\)%
+    \includeinlinesvg{.16}{schroder__r1}%
+    \end{center}
+    \caption{Transformations \(L_1\), \(L_2\) and \(R_1\)}
+    \label{fig:transformations_L1_L2_R1}
+\end{figure}
 
@@
 
-\todo{image of the problematic cases}
+\begin{center}
+    \begin{minipage}[t]{.3\textwidth}
+        \begin{center}
+            \includesvg[scale=0.5]{schroder__case_a}\\
+            Case 1.
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.3\textwidth}
+        \begin{center}
+            \includesvg[scale=0.5]{schroder__case_b}\\
+            Case 2.
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.3\textwidth}
+        \begin{center}
+            \includesvg[scale=0.5]{schroder__case_c}\\
+            Case 3.
+        \end{center}
+    \end{minipage}%
+\end{center}
 
@@
 
-\todo{images}
-
-In case 1. and 2. we can just swap the labels as follows:
-
-\todo{images}
+\begin{center}
+    \begin{minipage}[t]{.3\textwidth}
+        \begin{center}
+            \includesvg[scale=0.45]{schroder__case_a_l}\\
+            Case 1.
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.3\textwidth}
+        \begin{center}
+            \includesvg[scale=0.45]{schroder__case_b_l}\\
+            Case 2.
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.3\textwidth}
+        \begin{center}
+            \includesvg[scale=0.45]{schroder__case_c_l}\\
+            Case 3.
+        \end{center}
+    \end{minipage}%
+\end{center}
+
+In case 1.\ and 2.\ we can just swap the labels as follows:
+
+\begin{center}
+    \begin{minipage}[t]{.3\textwidth}
+        \begin{center}
+            \includesvg[scale=0.45]{schroder__case_a_l_fixed}\\
+            Case 1.
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.3\textwidth}
+        \begin{center}
+            \includesvg[scale=0.45]{schroder__case_b_l_fixed}\\
+            Case 2.
+        \end{center}
+    \end{minipage}%
+\end{center}
 
@@
 
-To achieve trees from \((n - 2) T(n - 1)\), we can simply take trees from case 3.
-and replace the father of the \(s\) with \(t''\) and point root of \(t''\).
-In this way, we will loose \(2\) leaves and obtain each tree from \((n - 2) T(n - 1)\).
-
-\todo{image}
+To achieve trees from \((n - 2) T(n - 1)\), we can simply take trees from case 3.\ and replace whole subtree with subtree of \(t''\) with its root pointed.
+In this way, we will loose \(2\) leaves and obtain each tree from \((n - 2) T(n - 1)\):
+
+\begin{center}
+    \begin{minipage}[t]{.3\textwidth}
+        \begin{center}
+            \includesvg[scale=0.45]{schroder__case_c_l_fixed}\\
+            Case 3.
+        \end{center}
+    \end{minipage}%
+\end{center}
 
@@
 
-\todo{describe binary trees example}
-
-The method itself has proven to be helpful in order to divide the problem into smaller parts. Unfortunately It does not give any immediate interpretation for applying the inductive step.
+For case of binary trees with size defined as number of leaves, we can define 2 recurrences:
+
+\[\text{Holonomic} := nB(n) = 2 (2n - 3)B(n - 1)\]
+\[\text{Non-linear} := B(n) = \sum_{i=1}^{n - 1} B(i) B(n - i)\]
+
+The non-linear one has very simple interpretation. We can take 2 smaller trees and join them using newly created common root.
+
+We can multiply both sides of Non-linear recurrence by \(n\) and break up \(n = i + (n - i)\) to get two similar sigmas:
+
+\[n B(n) = \sum_{i=1}^{n - 1} i B(i) B(n - i) + \sum_{i=1}^{n - 1} (n - i) B(n - i) B(i)\]
+
+Using our inductive hypothesis, ie.\ holonomic recurrence and moving problematic cases out from the sums (in that case \(B(1)\) needs to be analyzed separately, as we did not define binary trees with no leaves), we can get the right side to use \(B(n - 1)\) and prove that the holonomic recurrence using non-linear one.
+The only part that is left is to translate this proof to the bijective language, which in such simple case as binay trees is almost trivial, especially if one has seen the solution once.
+
+The method itself has proven to be helpful in order to divide the problem into smaller parts and find some corner cases.
+Unfortunately, it does not give any immediate interpretation for applying the inductive step.
 
@@
 
-\includeinlinesvg{.19}{trees_00__4_base}%
+\includeinlinesvg{.19}{lambda__trees_00__4_base}%
 \(\Rightarrow\)
-\includeinlinesvg{.19}{trees_00__4}%
-\includeinlinesvg{.19}{trees_00__5}%
-\includeinlinesvg{.19}{trees_00__6}%
-\includeinlinesvg{.19}{trees_00__7}%
+\includeinlinesvg{.19}{lambda__trees_00__4}%
+\includeinlinesvg{.19}{lambda__trees_00__5}%
+\includeinlinesvg{.19}{lambda__trees_00__6}%
+\includeinlinesvg{.19}{lambda__trees_00__7}%
 
@@
 
-\includeinlinesvg{.33}{trees_00__2}%
-\includeinlinesvg{.33}{trees_00__3}%
-\includeinlinesvg{.33}{trees_00__7}%
-
-\includeinlinesvg{.33}{trees_00__4}%
-\includeinlinesvg{.33}{trees_00__12}%
-\includeinlinesvg{.33}{trees_00__13}%
-
-\includeinlinesvg{.16}{trees_00__0}%
-\includeinlinesvg{.16}{trees_00__1}%
-\includeinlinesvg{.16}{trees_00__5}%
-\includeinlinesvg{.16}{trees_00__6}%
-\includeinlinesvg{.16}{trees_00__14}%
-\includeinlinesvg{.16}{trees_00__15}%
-
-\includeinlinesvg{.25}{trees_00__8}%
-\includeinlinesvg{.25}{trees_00__9}%
-\includeinlinesvg{.25}{trees_00__10}%
-\includeinlinesvg{.25}{trees_00__11}%
+\includeinlinesvg{.33}{lambda__trees_00__2}%
+\includeinlinesvg{.33}{lambda__trees_00__3}%
+\includeinlinesvg{.33}{lambda__trees_00__7}%
+
+\includeinlinesvg{.33}{lambda__trees_00__4}%
+\includeinlinesvg{.33}{lambda__trees_00__12}%
+\includeinlinesvg{.33}{lambda__trees_00__13}%
+
+\includeinlinesvg{.16}{lambda__trees_00__0}%
+\includeinlinesvg{.16}{lambda__trees_00__1}%
+\includeinlinesvg{.16}{lambda__trees_00__5}%
+\includeinlinesvg{.16}{lambda__trees_00__6}%
+\includeinlinesvg{.16}{lambda__trees_00__14}%
+\includeinlinesvg{.16}{lambda__trees_00__15}%
+
+\includeinlinesvg{.25}{lambda__trees_00__8}%
+\includeinlinesvg{.25}{lambda__trees_00__9}%
+\includeinlinesvg{.25}{lambda__trees_00__10}%
+\includeinlinesvg{.25}{lambda__trees_00__11}%
 
@@
 
-\includeinlinesvg{.24}{trees_100__0_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__0}%
-\includeinlinesvg{.24}{trees_100__1_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__1}%
-
-\includeinlinesvg{.24}{trees_100__2_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__2}%
-\includeinlinesvg{.24}{trees_100__3_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__3}%
+\includeinlinesvg{.24}{lambda__trees_100__0_base}\(\Rightarrow\)\includeinlinesvg{.24}{lambda__trees_100__0}%
+\includeinlinesvg{.24}{lambda__trees_100__1_base}\(\Rightarrow\)\includeinlinesvg{.24}{lambda__trees_100__1}%
+
+\includeinlinesvg{.24}{lambda__trees_100__2_base}\(\Rightarrow\)\includeinlinesvg{.24}{lambda__trees_100__2}%
+\includeinlinesvg{.24}{lambda__trees_100__3_base}\(\Rightarrow\)\includeinlinesvg{.24}{lambda__trees_100__3}%
 
@@
 
-\includeinlinesvg{.32}{trees_111__1_base}%
+\includeinlinesvg{.32}{lambda__trees_111__1_base}%
 \(\Rightarrow\)
-\includeinlinesvg{.32}{trees_101__0}%
-\includeinlinesvg{.32}{trees_112__0}%
+\includeinlinesvg{.32}{lambda__trees_101__0}%
+\includeinlinesvg{.32}{lambda__trees_112__0}%
 
@@
 
-\includeinlinesvg{.20}{trees_200__0_base}%
+\includeinlinesvg{.20}{lambda__trees_200__0_base}%
 \(\Rightarrow\)
-\includeinlinesvg{.20}{trees_200__0}%
-\includeinlinesvg{.20}{trees_201__0}%
-\includeinlinesvg{.20}{trees_202__0}%
-\includeinlinesvg{.20}{trees_203__0}%
+\includeinlinesvg{.20}{lambda__trees_200__0}%
+\includeinlinesvg{.20}{lambda__trees_201__0}%
+\includeinlinesvg{.20}{lambda__trees_202__0}%
+\includeinlinesvg{.20}{lambda__trees_203__0}%
 

### 2021-08-21 transformator/context.py
Move transformator out

@@ -1,332 +1,0 @@
-import functools as fn
-
-from collections import defaultdict
-
-
-class cached_property(fn.cached_property):
-    def __set_name__(self, owner, name):
-        if not hasattr(owner, "_cached"):
-            setattr(owner, "_cached", [])
-
-        owner._cached.append(name)
-
-        return super().__set_name__(owner, name)
-
-
-class Context:
-    def __init__(self):
-        self._ns = None
-        self._class_constructor = None
-        self._section_expressions = None
-
-        self._active_class = None
-        self._active_section = None
-
-    @property
-    def ns(self):
-        return self._ns
-
-    @ns.setter
-    def ns(self, value):
-        self._ns = value
-
-        self.clear_cache()
-
-    @property
-    def class_constructor(self):
-        return self._class_constructor
-
-    @class_constructor.setter
-    def class_constructor(self, value):
-        self._class_constructor = value
-
-        self.clear_cache()
-
-    @property
-    def section_expressions(self):
-        return self._section_expressions
-
-    @section_expressions.setter
-    def section_expressions(self, value):
-        self._section_expressions = value
-
-        self.clear_cache()
-
-    @cached_property
-    def classes(self):
-        return [list(self.class_constructor(n)) for n in self.ns]
-
-    @cached_property
-    def section_counts(self):
-        result = []
-        for class_idx, _ in enumerate(self.ns):
-            result.append([])
-            for equation, _ in self.section_expressions[class_idx]:
-                result[-1].append(self.eval_section_equation(equation, class_idx))
-
-        return result
-
-    @cached_property
-    def classes_counts(self):
-        return [sum(k) for k in self.section_counts]
-
-    @cached_property
-    def sections(self):
-        result = []
-        for k in range(len(self.ns)):
-            result.append([[] for _ in range(len(self.section_expressions[k]))])
-
-        return result
-
-    @cached_property
-    def minus(self):
-        return self.get_side(negative=True)
-
-    @cached_property
-    def plus(self):
-        return self.get_side(negative=False)
-
-    @cached_property
-    def diff(self):
-        minus = []
-        plus = []
-
-        p = 0
-        q = 0
-
-        while p < len(self.minus) and q < len(self.plus):
-            minus_key = str(self.minus[p][0])
-            plus_key = str(self.plus[q][0])
-
-            if minus_key < plus_key:
-                minus.append(self.minus[p])
-                p += 1
-            elif minus_key > plus_key:
[…]

### 2021-08-21 transformator/helpers.py

@@ -1,65 +1,0 @@
-def diff_sorted(first, second, key=None, first_label="first", second_label="second"):
-    key = key or (lambda x: x)
-
-    first_generator = iter(first)
-    second_generator = iter(second)
-
-    p = None
-    q = None
-
-    p_sent = True
-    q_sent = True
-
-    try:
-        p = next(first_generator)
-        p_sent = False
-
-        q = next(second_generator)
-        q_sent = False
-
-        while True:
-            k_p = key(p)
-            k_q = key(q)
-
-            if k_p == k_q:
-                p_sent = True
-                q_sent = True
-
-                p = next(first_generator)
-                p_sent = False
-
-                q = next(second_generator)
-                q_sent = False
-
-            elif k_p < k_q:
-                yield first_label, p
-                p_sent = True
-
-                p = next(first_generator)
-                p_sent = False
-            else:
-                yield second_label, q
-                q_sent = True
-
-                q = next(second_generator)
-                q_sent = False
-    except StopIteration:
-        pass
-
-    try:
-        if not p_sent:
-            yield first_label, p
-
-        while True:
-            yield first_label, next(first_generator)
-    except StopIteration:
-        pass
-
-    try:
-        if not q_sent:
-            yield second_label, q
-
-        while True:
-            yield second_label, next(second_generator)
-    except StopIteration:
-        pass

### 2021-08-21 transformator/lambda_tree.py

@@ -1,91 +1,0 @@
-from transformator.tree import Tree
-
-
-class LambdaTree(Tree):
-    kinds = ["l", "a", "s", "o"]
-
-    def __init__(self, *args, **kwargs):
-        super().__init__(*args, **kwargs)
-
-    def validate_vertex(self, kind, children):
-        left, right = children
-
-        sk = kind[0]
-        sl = left[0] if left is not None else None
-        sr = right[0] if right is not None else None
-
-        if sk == "l":
-            if sl is None:
-                return False
-            if sr is not None:
-                return False
-
-        elif sk == "s":
-            if sl is not None:
-                return False
-            if sr not in ("s", "o"):
-                return False
-
-        elif sk == "a":
-            if sl is None:
-                return False
-            if sr is None:
-                return False
-
-        elif sk == "o":
-            if sl is not None:
-                return False
-            if sr is not None:
-                return False
-
-        else:
-            return False
-
-        return True
-
-    @classmethod
-    def generate(cls, n, kinds=None, validate=True):
-        kinds = kinds or cls.kinds
-
-        if n == 0:
-            yield cls([None])
-
-        if n == 1:
-            yield cls(["o", None, None])
-
-        else:
-            for kind in kinds:
-                if kind == "o":
-                    pass
-
-                elif kind == "l" and n >= 2:
-                    for left in cls.generate(n - 1, kinds, validate=False):
-                        result = cls(["l"] + left.pre_order + [None])
-
-                        if validate:
-                            assert result.validate(), result
-
-                        yield result
-
-                elif kind == "s" and n >= 2:
-                    for right in cls.generate(n - 1, ["s", "o"], validate=False):
-                        result = cls(["s", None] + right.pre_order)
-
-                        if validate:
-                            assert result.validate(), result
-
-                        yield result
-
-                elif kind == "a" and n >= 3:
-                    for i in range(1, n - 1):
-                        left_n = n - i - 1
-                        right_n = i
-
-                        for left in cls.generate(left_n, kinds, validate=False):
-                            for right in cls.generate(right_n, kinds, validate=False):
-                                result = cls(["a"] + left.pre_order + right.pre_order)
-
-                                if validate:
-                                    assert result.validate(), result
-
-                                yield result

### 2021-08-21 transformator/main.py

@@ -1,12 +1,0 @@
-from transformator.tree import Tree
-
-
-def main():
-    t = Tree(("@", "l", "0", None, None, None, None))
-    t.graph.view()
-
-    t.visit_subtrees(lambda kind, left, right: ["l", kind] + left + right)
-
-
-if __name__ == '__main__':
-    main()

### 2021-08-21 transformator/tree.py

@@ -1,231 +1,0 @@
-from graphviz import Graph
-
-
-class Tree:
-    shape = "plain"
-    arity = 2
-    kinds = ["o"]
-    pointers = ["*"]
-
-    def __init__(self, pre_order, **extra):
-        self.pre_order = [k if isinstance(k, tuple) else (k, ) for k in pre_order]
-        self.extra = extra
-
-    def __iter__(self):
-        return iter(self.pre_order)
-
-    def _repr_svg_(self):
-        return self.graph._repr_svg_()
-
-    def _repr_html_(self):
-        return self._repr_svg_()
-
-    def get_kind_label(self, kind):
-        if kind[0] is None:
-            return "".join(kind[1:])
-
-        return "".join(kind)
-
-    def get_kind_shape(self, kind):
-        if kind[0] is None:
-            return "none"
-
-        return self.shape
-
-    def get_kind_node_dict(self, kind):
-        result = {}
-
-        result["label"] = self.get_kind_label(kind)
-        result["shape"] = self.get_kind_shape(kind)
-
-        return result
-
-    def get_kind_edge_dict(self, kind, parent_kind):
-        result = {}
-
-        if kind[0] is None:
-            result["color"] = "lightgreen"
-
-        return result
-
-    @property
-    def graph(self):
-        graph = Graph()
-        graph.attr(size="4,4")
-
-        stack = []
-
-        for i, kind in enumerate(self.pre_order):
-            idx = str(i)
-
-            if i == 0:
-                if kind[0] is not None:
-                    graph.node(idx, **self.get_kind_node_dict(kind))
-
-            else:
-                p_idx, p_kind, p_n = stack.pop()
-                p_n -= 1
-
-                graph.node(idx, **self.get_kind_node_dict(kind))
-                graph.edge(p_idx, idx, **self.get_kind_edge_dict(kind, p_kind))
-
-                if p_n > 0:
-                    stack.append((p_idx, p_kind, p_n))
-
-            if kind[0] is not None and self.arity > 0:
-                stack.append((idx, kind, self.arity))
-
-        if len(stack):
-            raise RuntimeError(f"Non-empty stack left: {stack}")
-
-        return graph
-
-    def get_subtree(self, idx):
-        start = idx
-        end = idx
-
-        count = 1
-        while count > 0:
-            if self.pre_order[end][0] is None:
-                count -= 1
-            else:
-                count += 1
-
-            end += 1
-
[…]

### 2021-08-22 article/main.tex
Add Transformator url
Resolve todos

@@
     escapeinside={<@}{@>}
+}
+
+\RequirePackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=black,
+    citecolor=black,
+    filecolor=black,
+    urlcolor=black
 }
@@
 \newcommand{\includeinlinesvg}[2]{\begin{minipage}{#1\textwidth}\includesvg[width=\textwidth]{#2}\end{minipage}}
+\newcommand{\includeinlinescaledsvg}[3]{\begin{minipage}{#1\textwidth}\begin{center}\includesvg[scale=#2]{#3}\end{center}\end{minipage}}
 
@@
 If you had defined the size as number of leaves or null-nodes, the size would be just plain sum of sizes of the smaller trees.
-\todo{Add some example}
 \end{itemize}
@@
 
-\todo{Add some example}
+In section \ref{sub:lambda_terms} we will define trees of lambda terms. If we would assign following weights to nodes:
+
+\[\begin{array}{rcl}
+        a &:& 7\\
+        l &:& 5\\
+        s &:& 3\\
+        o &:& 2\\
+\end{array}\]
+
+we would get significantly smaller classes
+
+\begin{longtable}{| c | c |}
+    \hline
+
+    Size & Trees
+    \\\hline
+
+    2 &
+    \begin{minipage}{.9\textwidth}\centering
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_002_000000}
+    \end{minipage}
+    \\\hline
+
+    5 &
+    \begin{minipage}{.9\textwidth}\centering
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_005_000000}
+    \end{minipage}
+    \\\hline
+
+    7 &
+    \begin{minipage}{.9\textwidth}\centering
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_007_000000}
+    \end{minipage}
+    \\\hline
+
+    8 &
+    \begin{minipage}{.9\textwidth}\centering
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_008_000000}
+    \end{minipage}
+    \\\hline
+
+    10 &
+    \begin{minipage}{.9\textwidth}\centering
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_010_000000}
+    \end{minipage}
+    \\\hline
+
+    11 &
+    \begin{minipage}{.9\textwidth}\centering
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_011_000000}
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_011_000001}
+    \end{minipage}
+    \\\hline
+
+    12 &
+    \begin{minipage}{.9\textwidth}\centering
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_012_000000}
+    \end{minipage}
+    \\\hline
+
+    14 &
+    \begin{minipage}{.9\textwidth}\centering
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_014_000000}
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_014_000001}
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_014_000002}
+    \end{minipage}
+    \\\hline
+
+    15 &
+    \begin{minipage}{.9\textwidth}\centering
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_015_000000}
+    \end{minipage}
+    \\\hline
+
+    16 &
+    \begin{minipage}{.9\textwidth}\centering
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_016_000000}
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_016_000001}
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_016_000002}
+    \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_016_000003}
+    \end{minipage}
+    \\\hline
+
+    % 17 &
+    % \begin{minipage}{.9\textwidth}\centering
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_017_000000}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_017_000001}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_017_000002}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_017_000003}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_017_000004}
+    % \end{minipage}
+    % \\\hline
+
+    % 18 &
+    % \begin{minipage}{.9\textwidth}\centering
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_018_000000}
+    % \end{minipage}
+    % \\\hline
+
+    % 19 &
+    % \begin{minipage}{.9\textwidth}\centering
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_019_000000}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_019_000001}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_019_000002}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_019_000003}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_019_000004}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_019_000005}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_019_000006}
+    % \end{minipage}
+    % \\\hline
+
+    % 20 &
+    % \begin{minipage}{.9\textwidth}\centering
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_020_000000}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_020_000001}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_020_000002}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_020_000003}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_020_000004}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_020_000005}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_020_000006}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_020_000007}
+    % \end{minipage}
+    % \\\hline
+
+    % 21 &
+    % \begin{minipage}{.9\textwidth}\centering
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_021_000000}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_021_000001}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_021_000002}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_021_000003}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_021_000004}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_021_000005}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_021_000006}
+    % \end{minipage}
+    % \\\hline
+
+    % 22 &
+    % \begin{minipage}{.9\textwidth}\centering
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_022_000000}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_022_000001}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_022_000002}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_022_000003}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_022_000004}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_022_000005}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_022_000006}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_022_000007}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_022_000008}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_022_000009}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_022_000010}
+    % \end{minipage}
+    % \\\hline
+
+    % 23 &
+    % \begin{minipage}{.9\textwidth}\centering
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000000}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000001}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000002}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000003}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000004}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000005}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000006}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000007}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000008}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000009}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000010}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000011}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_023_000012}
+    % \end{minipage}
+    % \\\hline
+
+    % 24 &
+    % \begin{minipage}{.9\textwidth}\centering
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000000}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000001}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000002}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000003}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000004}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000005}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000006}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000007}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000008}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000009}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000010}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000011}
+    % \includeinlinescaledsvg{.19}{.5}{lambda__2357__lambda2357_024_000012}
+    % \end{minipage}
+    % \\\hline
+\end{longtable}
+
+Analyzing such small cases is much easier, but on the other side, there are many more classes that have to be considered to get full interpretation.
 
@@
 
-As the main field of our interest was analysis of terms of lambda trees in unary de Bruijn notation, we will use it as an example to describe the method.\todo{Add definition}
+As the main field of our interest was analysis of terms of lambda trees in unary de Bruijn notation, we will use it as an example to describe the method.
 
@@
 In order to make the image cleaner, we will drop the arguments of generating functions, ie. \(\gf{L} := \gf{L}(z, o, l, a, s)\)
-\[\gf{L} = z a \gf{L}^2 + z l \gf{L} + \frac{o z}{1 - z s}\]
-\todo{add some image}
-\todo{describe how the frac is generated}
+
+\begin{center}
+    \begin{minipage}[t]{.2\textwidth}
+        \begin{center}
+            \(\gf{L}\)\\
+            \includesvg[scale=0.5]{lambda__def__1}%
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.05\textwidth}
+        \begin{center}
+            \(=\)\\
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.2\textwidth}
+        \begin{center}
+            \(z a \gf{L}^2\)\\
+            \includesvg[scale=0.5]{lambda__def__2}%
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.05\textwidth}
+        \begin{center}
+            \(+\)\\
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.2\textwidth}
+        \begin{center}
+            \(z l \gf{L}\)\\
+            \includesvg[scale=0.5]{lambda__def__3}%
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.05\textwidth}
+        \begin{center}
+            \(+\)\\
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.2\textwidth}
+        \begin{center}
+            \(\gf{L'}\)\\
+            \includesvg[scale=0.5]{lambda__def__4}%
+        \end{center}
+    \end{minipage}%
+\end{center}
+
+where:
+
+\begin{center}
+    \begin{minipage}[t]{.2\textwidth}
+        \begin{center}
+            \(\gf{L'}\)\\
+            \includesvg[scale=0.5]{lambda__def__5}%
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.05\textwidth}
+        \begin{center}
+            \(=\)\\
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.2\textwidth}
+        \begin{center}
+            \(z s \gf{L'}\)\\
+            \includesvg[scale=0.5]{lambda__def__4}%
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.05\textwidth}
+        \begin{center}
+            \(+\)\\
+        \end{center}
+    \end{minipage}%
+    \begin{minipage}[t]{.2\textwidth}
+        \begin{center}
+            \(z o\)\\
+            \includesvg[scale=0.5]{lambda__def__6}%
+        \end{center}
+    \end{minipage}%
+\end{center}
+
+After solving the equation for \(\gf{L'}\), we get:
+\[\gf{L} = z a \gf{L}^2 + z l \gf{L} + \frac{z o}{1 - z s}\]
 
@@
 
-We also created a framework, called transformator, that may help visualize our work.
+We also created a framework\cite{transformator}, called transformator, that may help visualize our work.
 It is based on the idea that every transformation described using bijective language can be translated to a function transforming node and finite number of its surrounding nodes.
@@
 
-We believe that one day all of that will be done.
+With the proper interpretation, it may be possible to create sampling algorithm similar to Remy's one for binary trees\cite{remy,note}.
+It would have to take under consideration that some trees are being removed by other classes, so the probabilities would have to be set carrefuly.
+
+We believe that one day all of that will be done or proven to be impossible.
 
@@
 \begin{thebibliography}{9}
-    \bibitem{remy}
-    Laurent Alonso Alonso, Jean-Luc Remy, and René Schott,
-    \textit{A Linear-Time Algorithm for the Generation of Trees},
-    Algorithmica 17,
-    1997,
-    p. 162-182
+    \bibitem{gfun}
+    Bruno Salvy, Paul Zimmermann,
+    \textit{GFUN : a maple package for the manipulation of generating and holonomic functions in one variable}
+    [Research Report] RT-0143, INRIA. 1992, pp.14. ffinria-00070025f
+
+    \bibitem{holotoolkit}
+    Manuel Kauers,
+    \textit{The Holonomic Toolkit},
+    in: Carsten Schneider, Johannes Blümlein (eds) Computer Algebra in Quantum Field Theory.
+Texts \& Monographs in Symbolic Computation (A Series of the Research Institute for Symbolic Computation, Johannes Kepler University, Linz, Austria),
+    Springer, Vienna,
+    2013
+
+    \bibitem{nonholo}
+    Stefan Gerhold,
+    \textit{Combinatorial sequences: Non-holonomicity and inequalities. Ph.D. thesis},
+    RISC-Linz, Johannes Kepler Universitat Linz,
+    2005
+
+    \bibitem{complexity}
+    Igor Pak,
+    \textit{Complexity problems in enumerative combinatorics},
+    2018
+
+    \bibitem{binary}
+    Jean-Luc Rémy,
+    \textit{Un procédé itératif de dénombrement d’arbres binaires et son application à leur génération aléatoire}
+    Informatique théorique, tome 19, no 2, 
+    1985,
+    p. 179-195
 
@@
 
-    \bibitem{binary}
-    Jean-Luc Rémy,
-    \textit{Un procédé itératif de dénombrement d’arbres binaires et son application à leur génération aléatoire}
-    Informatique théorique, tome 19, no 2, 
-    1985,
-    p. 179-195
-
     \bibitem{doron}
@@
     2020
+
+    % Non-cited
+
+    \bibitem{remy}
+    Laurent Alonso Alonso, Jean-Luc Remy, and René Schott,
+    \textit{A Linear-Time Algorithm for the Generation of Trees},
+    Algorithmica 17,
+    1997,
+    p. 162-182
 
@@
 
-    \bibitem{complexity}
-    Igor Pak,
-    \textit{Complexity problems in enumerative combinatorics},
-    2018
-
-    \bibitem{gfun}
-    Bruno Salvy, Paul Zimmermann,
-    \textit{GFUN : a maple package for the manipulation of generating and holonomic functions in one variable}
-    [Research Report] RT-0143, INRIA. 1992, pp.14. ffinria-00070025f
-
-    \bibitem{holotoolkit}
-    Manuel Kauers,
-    \textit{The Holonomic Toolkit},
-    in: Carsten Schneider, Johannes Blümlein (eds) Computer Algebra in Quantum Field Theory.
-Texts \& Monographs in Symbolic Computation (A Series of the Research Institute for Symbolic Computation, Johannes Kepler University, Linz, Austria),
-    Springer, Vienna,
-    2013
-
-    \bibitem{nonholo}
-    Stefan Gerhold,
-    \textit{Combinatorial sequences: Non-holonomicity and inequalities. Ph.D. thesis},
-    RISC-Linz, Johannes Kepler Universitat Linz,
-    2005
+    % Additional
+
+    \bibitem{transformator}
+    Bartłomiej Puget,
+    \textit{Transformator framework},
+    \url{https://github.com/Larhard/transformator},
+    2021
 

### 2021-08-22 article/main.tex
Minor fixes

@@
 
-\(u, v\) are implicitly assumed to be a nodes.
+\(u, v\) are implicitly assumed to be nodes.
 
@@
 
-We say that node \(v\) is an oneling \(\textiff\) \(v\) has no sibling. Note that the root is oneling even if it has no parent.
+We say that node \(v\) is an oneling \(\textiff\) \(v\) has no siblings. Note that the root is oneling even if it has no parent.
 
@@
 
-We say that node \(v\) is an virtual-oneling \(\textiff\) \(v\) has no sibling being virtual node.
-
-We say that node \(v\) is virtual-twinling \(\textiff\) \(v\) has at least one sibling being virtual node.
-
 Leaf is a node which has no children.
 
-\(\n\) is implicitly defined as a default identifier a node.
-
-\(\no\) is implicitly defined as a identifier of non-existing node (eg.\ if \(v\) is a leaf, \(\tleft(v) = \n\)).
+\(\n\) is implicitly defined as a default identifier of a node.
+
+\(\no\) is implicitly defined as an identifier of non-existing node (eg.\ if \(v\) is a leaf, \(\tleft(v) = \n\)).
 
@@
 
-We say that node \(v\) is right (left) \(\textiff\) \(v\) is a right (left) child of its parent.
-
-We say that node \(v\) has a right (left) parent \(u\) \(\textiff\) \(v\) is a left (right) child of \(u\).
+We say that node \(v\) is an virtual-oneling \(\textiff\) \(v\) has no siblings being virtual nodes.
+
+We say that node \(v\) is virtual-twinling \(\textiff\) \(v\) has at least one sibling being virtual node.
+
+For binary tree, we say that node \(v\) is right (left) \(\textiff\) \(v\) is a right (left) child of its parent.
+
+For binary tree, we say that node \(v\) has a right (left) parent \(u\) \(\textiff\) \(v\) is a left (right) child of \(u\).
 
@@
 
-\(x_i\) is implicitly assumed to be \(i\)-th element of the sequence \(X\), where \(x\) can be any lower-case letter and \(X\) is upper-case \(x\).
+\(x_i\) is implicitly assumed to be an \(i\)-th element of the sequence \(X\), where \(x\) can be any lower-case letter and \(X\) is upper-case \(x\).
 
@@
 
-We will be analyzing structures that can be expressed using recursive expressions.
+We will be analyzing structures that can be expressed using recursive formulas.
 Eg.\ we can define full binary tree recursively as a node having no children (ie.\ being a leaf) or having exactly two subtrees being full binary trees.
@@
 
-There exist multiple well-known methods and tools that allow us to work with generating functions without need of digging into details.
+There exist multiple well-known methods and tools that allow us to work with generating functions without the need of digging into details.
 The tool we will be using extensively in this work is Maple package called GFUN\cite{gfun}.
@@
     \cite{complexity}
-    Equivalently to definition\ \ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) exists generating function in the following form:
+    Equivalently to definition\ \ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists generating function in the following form:
     \[\sum_{i=0}^{r} p_i(z) \gf{A}^{(i)}(z) = b(z)\]
-    for some fixed \(r \in \N\); \(b, p_0, \ldots, p_r \in \poly\) not all identically zero.
+    for some fixed \(r \in \N\); \(b, p_0, \ldots, p_r \in \poly\) not all identical to zero.
 \end{definition}
@@
 
-In the article we try to gather methods and results that may be helpful for anyone who will try to find such interpretation, as we believe that such interpretation may give better insight into the nature of the structure and make it easier to study its behaviour.
+In the article we try to gather methods and results that may be helpful for anyone trying to find such interpretation, as we believe that such interpretation may give better insight into the nature of the structure and make it easier to study its behaviour.
 
@@
 
-We define the size of tree as a number of internal nodes (ie.\ nodes that are not leaves). Our generating function is therefore:
+We define the size of a tree as a number of internal nodes (ie.\ nodes that are not leaves). Our generating function is therefore:
 
@@
 
-This recurrence describes also Catalan numbers.
-
-It is easy to see that tree of size \(n\) (\(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
+This recurrence also describes Catalan numbers.
+
+It is easy to see that tree of size \(n\) (ie.
+with \(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
 Analogically the tree of size \(n + 1\) has \(n + 2\) leaves and \(2n + 3\) nodes in total.
@@
 
-First case can be also split into 2 subcases. Without loss of the generality we can analyze just one of the operations, let it be \(R_l\). The second case will be symmetric.
+First case can also be split into 2 subcases. Without loss of the generality we can analyze just one of the operations, let it be \(R_l\). The second case is symmetric.
 \begin{itemize}
@@
 
-The next case we will show is case of Schröder trees\cite{schroder}.
+The next case we will show is the case of Schröder trees\cite{schroder}.
 
@@
 
-We can also move \(\gf{T}(z)\) to the other side, ie.:
+We can also move \(T(n)\) to the other side, ie.:
 
@@
 
-Let's define 3 transformations: \(L_1\), \(L_2\) and \(R_1\).
-
-\begin{figure}[h]
+Let's define 3 transformations, \(L_1\), \(L_2\) and \(R_1\):
+
 \begin{center}
@@
 \end{center}
-    \caption{Transformations \(L_1\), \(L_2\) and \(R_1\)}
-    \label{fig:transformations_L1_L2_R1}
-\end{figure}
 
@@
 
-As you could see in the examples above, most of the solutions base on the simple analysis of number of laves, internal nodes and other similar properties.
+As you could see in the examples above, most of the solutions are based on the simple analysis of number of laves, internal nodes and other similar properties.
 In this section, we've gathered some methods that may be helpful when trying to analyze the problem of interpreting combinatorially some holonomic recurrence.
@@
     \item counting null-nodes (ie.\ children of the leaves),
-    \item edges.
+    \item counting edges.
 \end{itemize}
 
-It may seem counter-intuitive at first, that this changes anything crucial, but the holonomic recurrence may change drastically making the problem more difficult than it should be.
+It may seem counter-intuitive at first, that this changes anything crucial, but with a change of the size definition, the holonomic recurrence may complicate itself drastically making the problem more difficult than it should be.
 
@@
     \item we want to join trees using common root and we get many \(\pm1\) in our notes.
-Note that if you count internal nodes, such catenation creates tree of size being sum of sizes of the components increases by 1.
+Note that if you count internal nodes, such catenation creates tree of size being sum of sizes of the components increased by 1.
 If you had defined the size as number of leaves or null-nodes, the size would be just plain sum of sizes of the smaller trees.
@@
 Another method that may help finding the interpretation is inductive translation\cite{doron}.
-The method is based on the idea that most of the time there is easy to find some natural induction (not necessarily holonomic) that has trivial interpretation in bijective language.
+The method is based on the idea that most of the time there is an easy way to find some natural induction (not necessarily holonomic) that has trivial interpretation in bijective language.
 
@@
 Using our inductive hypothesis, ie.\ holonomic recurrence and moving problematic cases out from the sums (in that case \(B(1)\) needs to be analyzed separately, as we did not define binary trees with no leaves), we can get the right side to use \(B(n - 1)\) and prove that the holonomic recurrence using non-linear one.
-The only part that is left is to translate this proof to the bijective language, which in such simple case as binay trees is almost trivial, especially if one has seen the solution once.
+The only part that is left is to translate this proof to the bijective language, which in such simple case as binary trees is almost trivial, especially if one has seen the solution once.
 
@@
 
-If all elaborate methods has failed and the problem is still too big to interpret it by hand, a computer comes handy.
+If all elaborate methods has failed and the problem is still too big to interpret it by hand, a computer comes in handy.
 
@@
 The definition above is quite popular, but introduces several problems.
-One of them is problem of potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction is the variable is bound (or is it even free variable, ie.\ not bound).
+One of them is a problem of potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction is the variable bound (or is it even free variable, ie.\ not bound).
 To address that, we can use de Bruijn indices.
@@
 \begin{definition}
-    \(s\) is a node with just right child.
-\end{definition}
-
-\begin{definition}
-    \(l\) is a node with just left child.
+    \(s\) is a node with only right child.
+\end{definition}
+
+\begin{definition}
+    \(l\) is a node with only left child.
 \end{definition}
@@
 This function can not discriminate nodes on the grounds of their kind.
-The only discrimination that may occur may be connected to the following cases:
+The only discrimination criteria that may occur may be connected to the following cases:
 \begin{itemize}
@@
 
-With the proper interpretation, it may be possible to create sampling algorithm similar to Remy's one for binary trees\cite{remy,note}.
-It would have to take under consideration that some trees are being removed by other classes, so the probabilities would have to be set carrefuly.
+With the proper interpretation, it may be possible to create sampling algorithm similar to Rémy's one for binary trees\cite{remy,note}.
+It would have to take under consideration that some trees are being removed by other classes, so the probabilities would have to be set carefully.
 
@@
     \bibitem{remy}
-    Laurent Alonso Alonso, Jean-Luc Remy, and René Schott,
+    Laurent Alonso Alonso, Jean-Luc Rémy, and René Schott,
     \textit{A Linear-Time Algorithm for the Generation of Trees},

### 2021-08-27 article/main.tex
Add diff support
Create overview

@@
 
-% \date{Kraków, 19 maja 2021}
+\date{\today}
 
@@
 
-We also try to find combinatorial interpretation of holonomic recurrence for trees of lambda terms in de Bruijn notation.
+We also try to find a combinatorial interpretation of the holonomic recurrence for trees of lambda terms in the de Bruijn notation.
 
@@
 \tableofcontents
+\clearpage
+
+\section{Overview}%
+Initial inspiration for the thesis came from \textit{A natural counting of lambda terms}\cite{zigzag} publication, which shows bijection between seemingly different tree structures, which are lambda trees, black-white trees nad zigzag free trees.
+\todo{Finish the overview section}
+
 \clearpage
@@
 \begin{thebibliography}{9}
+    \bibitem{zigzag}
+    Maciej Bendkowski, Katarzyna Grygiel, Pierre Lescanne, Marek Zaionc,
+    \textit{A natural counting of lambda terms},
+    2016
+
     \bibitem{gfun}
     Bruno Salvy, Paul Zimmermann,
-    \textit{GFUN : a maple package for the manipulation of generating and holonomic functions in one variable}
+    \textit{GFUN : a maple package for the manipulation of generating and holonomic functions in one variable},
     [Research Report] RT-0143, INRIA. 1992, pp.14. ffinria-00070025f

### 2021-08-28 article/main.tex
Add overview

@@
 \section{Overview}%
-Initial inspiration for the thesis came from \textit{A natural counting of lambda terms}\cite{zigzag} publication, which shows bijection between seemingly different tree structures, which are lambda trees, black-white trees nad zigzag free trees.
-\todo{Finish the overview section}
+
+Every recursive structure can be described using generating function, which then can be transformed into holonomic recurrences.
+It allows us to quickly compute number of objects of given structure with of given size.
+At first glance, the recurrence seems to be closely related to the structure itself.
+It just seems like it should describe simple transformations, like adding some vertices to the smaller trees.
+Although, there is no known way of interpreting it in the language of the combinatorial structures.
+
+Initial inspiration for the thesis came from publication \textit{A natural counting of lambda terms}\cite{zigzag}, which shows bijection between seemingly different tree structures, which are lambda trees, black-white trees nad zigzag free trees.
+They share the same holonomic recurrence, but there is no known immediate connection between the holonomic recurrence and the structure itself.
+
+In the thesis we try to accumulate known results and techniques that may help solving the problem of finding combinatorial interpretations.
+We also propose approach that helped us to find intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of lambda trees in the unary de Bruijn notation.
+
+In the section\ \ref{sec:introduction} we establish notation nad introduce concepts that will be using throughout the thesis.
+
+Next, in the section \ref{sec:known_results}, we present known results. They demonstrate combinatorial interpretations that resemble different approaches.
+
+In the section\ \ref{sec:approaches} we show approaches to the problem that helped people achieving their results.
+All of them were tried in order to find the answer to the original problem of interpreting holonomic recurrence of trees of lambda terms in the unary de Bruijn notation.
+Unfortunately none of them helped us enough to get the final result.
+They are proven to be helpful when we were stuck though as most of them are able to divide problem into smaller parts and detect corner cases.
+
+Section\ \ref{sec:brutal_iterative_approach} presents our final approach to the original problem, ie.\ computer-aided iterative approach that allowed us to find the intermediate solution.
+We belive that it is able to provide us with the full solution, but we were not able to achieve that due to the limited time that was available to us.
+
+At last, in section\ \ref{sec:further_work}, we present our view on what can be done with the problem in the future.
+We belive that one day the problem will be fully solved and more generic approach to interpreting holonomic recurrences will emerge.
 
@@
 The tool we will be using extensively in this work is Maple package called GFUN\cite{gfun}.
+If you want to learn more about algorithms used in the package, we strongly encourage reading the referenced article.
 
@@
 
-And with a bit of Maple magic, we immediately get following recurrence:
+And with a bit of Maple magic\cite{gfun}, we immediately get following recurrence:
 
@@
 
-Using a little bit of Maple magic, we can easily achieve following holonomic recurrence.
+Using a little bit of Maple magic\cite{gfun}, we can easily achieve following holonomic recurrence.
 

### 2021-08-29 article/main.tex
Apply auto-grammar fixes

@@
 
-Every recursive structure can be described using generating function, which then can be transformed into holonomic recurrences.
-It allows us to quickly compute number of objects of given structure with of given size.
+Every recursive structure can be described using a generating function, which can be then transformed into holonomic recurrence.
+It allows us to quickly count objects of given structure with of given size.
 At first glance, the recurrence seems to be closely related to the structure itself.
 It just seems like it should describe simple transformations, like adding some vertices to the smaller trees.
-Although, there is no known way of interpreting it in the language of the combinatorial structures.
-
-Initial inspiration for the thesis came from publication \textit{A natural counting of lambda terms}\cite{zigzag}, which shows bijection between seemingly different tree structures, which are lambda trees, black-white trees nad zigzag free trees.
+Although, there is no known method of interpreting it in the language of the combinatorial structures.
+
+Initial inspiration for the thesis came from publication \textit{A natural counting of lambda terms}\cite{zigzag}, which shows bijection between seemingly different tree structures, which are lambda trees, black-white trees and zigzag free trees.
 They share the same holonomic recurrence, but there is no known immediate connection between the holonomic recurrence and the structure itself.
@@
 In the thesis we try to accumulate known results and techniques that may help solving the problem of finding combinatorial interpretations.
-We also propose approach that helped us to find intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of lambda trees in the unary de Bruijn notation.
+We also propose an approach that helped us to find an intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of lambda trees in the unary de Bruijn notation.
 
@@
 
-In the section\ \ref{sec:approaches} we show approaches to the problem that helped people achieving their results.
+In the section\ \ref{sec:approaches} we show approaches to the problem that helped people achieve their results.
 All of them were tried in order to find the answer to the original problem of interpreting holonomic recurrence of trees of lambda terms in the unary de Bruijn notation.
 Unfortunately none of them helped us enough to get the final result.
-They are proven to be helpful when we were stuck though as most of them are able to divide problem into smaller parts and detect corner cases.
+They are proven to be helpful when we are stuck though as most of them are able to divide problems into smaller parts and detect corner cases.
 
 Section\ \ref{sec:brutal_iterative_approach} presents our final approach to the original problem, ie.\ computer-aided iterative approach that allowed us to find the intermediate solution.
-We belive that it is able to provide us with the full solution, but we were not able to achieve that due to the limited time that was available to us.
-
-At last, in section\ \ref{sec:further_work}, we present our view on what can be done with the problem in the future.
-We belive that one day the problem will be fully solved and more generic approach to interpreting holonomic recurrences will emerge.
+We believe that it is able to provide us with the full solution, but we were not able to achieve that due to the limited time that was available to us.
+
+Finally, in section\ \ref{sec:further_work}, we present our view on what can be done with the problem in the future.
+We believe that one day the problem will be fully solved and a more generic approach to interpreting holonomic recurrences will emerge.
 
@@
 
-In order to make reading of this article easier, let's fix some notation and make some assumptions.
+In order to make reading this article easier, let's fix some notation and make some assumptions.
 Any deviation from this will be clearly stated.
@@
 
-Uncle of node \(v\) is defined as sibling of the parent of \(v\).
+Uncle of node \(v\) is defined as a sibling of the parent of \(v\).
 
@@
 
-\(\no\) is implicitly defined as an identifier of non-existing node (eg.\ if \(v\) is a leaf, \(\tleft(v) = \n\)).
+\(\no\) is implicitly defined as an identifier of a non-existing node (eg.\ if \(v\) is a leaf, \(\tleft(v) = \n\)).
 
@@
 
-Virtual node is artificially defined node that does not affect the structure definition (eg.\ we can define virtual leafs that are children of actual leaves of the binary tree.
-Such virtual leaves are not included when counting number of children of the node, so the actual leaves are still called leaves).
+Virtual node is an artificially defined node that does not affect the structure definition (eg.\ we can define virtual leafs that are children of actual leaves of the binary tree.
+Such virtual leaves are not included when counting the number of children of the node, so the actual leaves are still called leaves).
 
@@
 
-For binary tree, we say that node \(v\) is right (left) \(\textiff\) \(v\) is a right (left) child of its parent.
-
-For binary tree, we say that node \(v\) has a right (left) parent \(u\) \(\textiff\) \(v\) is a left (right) child of \(u\).
-
-\(\pointed{v}\) is implicitly defined as a pointed node \(v\). We can treat it as node with additional label \(\pointed{}\).
+For a binary tree, we say that node \(v\) is right (left) \(\textiff\) \(v\) is a right (left) child of its parent.
+
+For a binary tree, we say that node \(v\) has a right (left) parent \(u\) \(\textiff\) \(v\) is a left (right) child of \(u\).
+
+\(\pointed{v}\) is implicitly defined as a pointed node \(v\). We can treat it as a node with an additional label \(\pointed{}\).
 
@@
 
-\(\size{X}\) is implicitly defined as a size of the object \(X\).
-
-eg.\ stands for Latin exampli gratia, which means \textit{for example}.
+\(\size{X}\) is implicitly defined as the size of the object \(X\).
+
+eg.\ stands for Latin exempli gratia, which means \textit{for example}.
 
@@
 We will be analyzing structures that can be expressed using recursive formulas.
-Eg.\ we can define full binary tree recursively as a node having no children (ie.\ being a leaf) or having exactly two subtrees being full binary trees.
+Eg.\ we can define a full binary tree recursively as a node having no children (ie.\ being a leaf) or having exactly two subtrees being full binary trees.
 To express the alternative in the construction rule, we use \(+\).
@@
 
-Note that in order to compute \(k\)-th element of the sequence, \(a_k\), we just need to find constant corresponding to indeterminate \(z^k\).
+Note that in order to compute \(k\)-th element of the sequence, \(a_k\), we just need to find a constant corresponding to indeterminate \(z^k\).
 
@@
     Having our recursive definition of the object, we can easily construct a generating function for it.
-Let's create generating function that will count number of full binary trees consisting of exactly \(k\) internal nodes.
+Let's create a generating function that will count the number of full binary trees consisting of exactly \(k\) internal nodes.
 
@@
 
-In order to get some intuition on how it works underneath, let's take a look on how we can find number of the full binary trees of size \(2\). We can expand the recurrence a bit:
+In order to get some intuition on how it works underneath, let's take a look at how we can find the number of full binary trees of size \(2\). We can expand the recurrence a bit:
 
@@
 There exist multiple well-known methods and tools that allow us to work with generating functions without the need of digging into details.
-The tool we will be using extensively in this work is Maple package called GFUN\cite{gfun}.
+The tool we will be using extensively in this work is the Maple package called GFUN\cite{gfun}.
 If you want to learn more about algorithms used in the package, we strongly encourage reading the referenced article.
@@
 
-Note that the sum can only take finite number of subsequent elements of the sequence \(A\) into the relation.
+Note that the sum can only take a finite number of subsequent elements of the sequence \(A\) into the relation.
 
@@
 
-    For our purposes we will often ignore the initial conditions, as they can be easily described by exact number of the objects.
+    For our purposes we will often ignore the initial conditions, as they can be easily described by the exact number of the objects.
 The most interesting part for us is the relation between the finite number consecutive elements.
@@
 
-Combinatorial interpretation is just fancy name for something you probably know and use.
+Combinatorial interpretation is just a fancy name for something you probably know and use.
 Eg.\ if you know the binomial coefficient \(\binom{n}{k}\), I bet it was introduced to you as something like: "let's assume you have \(n\) distinguishable balls.
@@
 Holonomic recurrences are very useful if we want to count objects of given size.
-Of course, size can be defined in more complex ways, eg.\ we may want to find number of trees with \(n\) internal nodes having exactly \(m\) nodes being left child of its parent.
-
-Unfortunately, as for the most of auto-generated code, they almost never come with intuitive interpretation.
-They are just some recurrences, but there is no commonly known method to find, how they correspond to the structures they describe.
+Of course, size can be defined in more complex ways, eg.\ we may want to find the number of trees with \(n\) internal nodes having exactly \(m\) nodes being left child of its parent.
+
+Unfortunately, as for most auto-generated code, they almost never come with intuitive interpretation.
+They are just some recurrences, but there is no commonly known method to find how they correspond to the structures they describe.
 
@@
     \[\enc{T} = \enc{\troot(T)} \prod_{i=1}^{n} \enc{i\text{-th subtree of } \troot(T)}\]
-    ie.\ catenation of identifier of the root of the tree with encoded its subtrees from left to right.
+    ie.\ catenation of the identifier of the root of the tree with encoded its subtrees from left to right.
 \end{definition}
@@
 
-We can also define prefix and suffix of \(T\).
+We can also define prefixes and suffixes of \(T\).
 
@@
 
-In the article we define some operations using its notation. As pre-order notation is bijective, you can obtain the structure the notation describe by reversing the process of encoding.
+In the article we define some operations using its notation. As pre-order notation is bijective, you can obtain the structure the notation describes by reversing the process of encoding.
 
@@
 
-It is easy to see that tree of size \(n\) (ie.
+It is easy to see that a tree of size \(n\) (ie.
 with \(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
@@
 
-We are going to create bijection between left and right side of the recurrence.
-We will be using term \textit{bijective language} to describe talking about the recurrence using the objects it describes and their transformations.
+We are going to create a bijection between the left and right side of the recurrence.
+We will be using the term \textit{bijective language} to talk about the recurrence using the objects it describes and their transformations.
 
@@
     \item \((2n + 1) B(n)\) is set of all full binary trees of size \(n\) with one of the nodes pointed (remember that the node can be internal node or leaf),
-    \item \(2\) at the beginning of \(2 (2n + 1) B(n)\) means that we will be using \(2\) copies of the set defined in previous bullet.
+    \item \(2\) at the beginning of \(2 (2n + 1) B(n)\) means that we will be using \(2\) copies of the set defined in the previous bullet.
 \end{itemize}
 
-At the moment left side of the recurrence describe set of trees of size \(n + 1\), the right, on the other hand, of size \(n\). Therefore, we need to apply some transformation to make the sets equal.
+At the moment the left side of the recurrence describes a set of trees of size \(n + 1\), the right, on the other hand, of size \(n\).
+Therefore, we need to apply some transformation to make the sets equal.
 
@@
 We can now take the bijective interpretation of \((2n + 1) B(n)\), ie.
-trees of size \(n\) with single node pointed.
+trees of size \(n\) with a single node pointed.
 For each of such trees, \(T\) we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a node that is pointed in \(T\).
@@
 
-The only thing that's left for us to verify is if we generate all trees of size \(n + 1\) with pointed leaf.
+The only thing that's left for us to verify is if we generate all trees of size \(n + 1\) with pointed leaves.
 As from the recursion, we know that \(2 (2n + 1) B(n)\) is total number of trees with single leaf pointed, it is enough to check if we do not generate any duplicate using \(R_l\) and \(R_r\).
@@
 
-First case can also be split into 2 subcases. Without loss of the generality we can analyze just one of the operations, let it be \(R_l\). The second case is symmetric.
+First case can also be split into 2 subcases. Without loss of generality we can analyze just one of the operations, let it be \(R_l\). The second case is symmetric.
 \begin{itemize}
@@
 
-In the second case it is enough to notice that \(R_l\) generates trees with pointed node being a left child, and \(R_r\) generates trees with pointed node being right child.
-That immediately provides us with conclusion that we are generating no duplicates.
+In the second case it is enough to notice that \(R_l\) generates trees with pointed nodes being a left child, and \(R_r\) generates trees with pointed nodes being right child.
+That immediately provides us with the conclusion that we are generating no duplicates.
 
@@
 
-Let's think, what would have changed if we introduce unary nodes to the binary case\cite{motzkin}. We will be counting edges. Note that tree having \(n\) edges has exactly \(n + 1\) nodes.
+Let's think, what would have changed if we introduce unary nodes to the binary case\cite{motzkin}. We will be counting edges. Note that a tree having \(n\) edges has exactly \(n + 1\) nodes.
 
@@
 The definition above is precise, but introduces a new kind of node that we would have to take care of.
-We can avoid it by using a trick to make the tree recall binary tree.
+We can avoid it by using a trick to make the tree recall binary trees.
 We don't change the structure, just the notation.
@@
     \label{def:unary_binary_2}
-    Left-leaning binary tree\todo{find official name; skewed binary tree is something different} is a binary tree with following constraint added: if a node has right child, it also have a left child.
+    Left-leaning binary tree\todo{find official name; skewed binary tree is something different} is a binary tree with the following constraint added: if a node has a right child, it also has a left child.
 \end{definition}
@@
 The bijection between unary-binary and left-leaning binary trees is very simple.
-We just represent unary nodes as nodes with just left child of left-leaning binary tree.
+We just represent unary nodes as nodes with just the left child of the left-leaning binary tree.
 The other cases translate immediately to corresponding ones.
@@
 \begin{definition}
-    Virtual leaf is a virtual node added to the node in place of non-existing child.
-\end{definition}
-
-As we have added \(n + 2\) virtual nodes, we have added as much virtual edges.
+    Virtual leaf is a virtual node added to the node in place of a non-existing child.
+\end{definition}
+
+As we have added \(n + 2\) virtual nodes, we have added as many virtual edges.
 
@@
         \end{enumerate}
-    \item Vlt - virtual leaf left virtual-twinling. Note that from definition \ref{def:unary_binary_2}, left virtual leave can not have sibling being a actual node. We can divide also this case into:
+    \item Vlt - virtual leaf left virtual-twinling.
+Note that from definition \ref{def:unary_binary_2}, left virtual leave can not have a sibling being an actual node.
+We can divide also this case into:
         \begin{enumerate}
@@
 
-Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point any node, as in a tree having \(n - 1\) edges, we have \(n\) actual and \(n + 1\) virtual ones.
+Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point to any node, as in a tree having \(n - 1\) edges, we have \(n\) actual and \(n + 1\) virtual ones.
 
@@
 
-Simply speaking, node can have zero or strictly more than one children.
+Simply speaking, nodes can have zero or strictly more than one child.
 
@@
         \item internal nodes can have weight either \(1\) or \(2\);
-        \item if internal node has weight 2, then its right child is not a leaf.
+        \item if the internal node has weight 2, then its right child is not a leaf.
     \end{itemize}
@@
 
-This may seem counterintuitive, as by default we want to describe how to generate larger case from the smaller ones, but it will make the interpretation simpler.
+This may seem counterintuitive, as by default we want to describe how to generate larger cases from the smaller ones, but it will make the interpretation simpler.
 
@@
 To achieve trees from \((n - 2) T(n - 1)\), we can simply take trees from case 3.\ and replace whole subtree with subtree of \(t''\) with its root pointed.
-In this way, we will loose \(2\) leaves and obtain each tree from \((n - 2) T(n - 1)\):
+In this way, we will lose \(2\) leaves and obtain each tree from \((n - 2) T(n - 1)\):
 
@@
 
-As you could see in the examples above, most of the solutions are based on the simple analysis of number of laves, internal nodes and other similar properties.
+As you could see in the examples above, most of the solutions are based on the simple analysis of number of leaves, internal nodes and other similar properties.
 In this section, we've gathered some methods that may be helpful when trying to analyze the problem of interpreting combinatorially some holonomic recurrence.
@@
 
-It may seem counter-intuitive at first, that this changes anything crucial, but with a change of the size definition, the holonomic recurrence may complicate itself drastically making the problem more difficult than it should be.
+It may seem counterintuitive at first, that this changes anything crucial, but with a change of the size definition, the holonomic recurrence may complicate itself drastically making the problem more difficult than it should be.
 
@@
     \item we get empty classes of the objects, eg.\ if we analyze problem of full binary trees and define size as number of all existing nodes, we can not generate tree of even size, therefore half of our classes are empty;
-    \item we want to join trees using common root and we get many \(\pm1\) in our notes.
-Note that if you count internal nodes, such catenation creates tree of size being sum of sizes of the components increased by 1.
-If you had defined the size as number of leaves or null-nodes, the size would be just plain sum of sizes of the smaller trees.
+    \item we want to join trees using common roots and we get many \(\pm1\) in our notes.
+Note that if you count internal nodes, such catenation creates a tree of size being the sum of sizes of the components increased by 1.
+If you had defined the size as the number of leaves or null-nodes, the size would be just a simple sum of the sizes of the smaller trees.
 \end{itemize}
@@
 
-As the most common trees are binary ones, it may be worth an effort to find the some structure based on binary trees that can represent original structure (see section~\ref{sub:unary_binary_trees}).
-
-\subsection{Weights variablization}%
+As the most common trees are binary ones, it may be worth an effort to find some structure based on binary trees that can represent the original structure (see section~\ref{sub:unary_binary_trees}).
+
+\subsection{Weights variabilization}%
 \label{sub:weights_variablization}
@@
 
-Unfortunately, decreasing size of the classes increases number of the sizes we need to analyze to get full result.
+Unfortunately, decreasing the size of the classes increases the number of the sizes we need to analyze to get a full result.
 
@@
 
-Analyzing such small cases is much easier, but on the other side, there are many more classes that have to be considered to get full interpretation.
+Analyzing such small cases is much easier, but on the other hand, there are many more classes that have to be considered to get full interpretation.
 
@@
 
-The non-linear one has very simple interpretation. We can take 2 smaller trees and join them using newly created common root.
+The non-linear one has a very simple interpretation. We can take 2 smaller trees and join them using newly created common root.
 
@@
 Using our inductive hypothesis, ie.\ holonomic recurrence and moving problematic cases out from the sums (in that case \(B(1)\) needs to be analyzed separately, as we did not define binary trees with no leaves), we can get the right side to use \(B(n - 1)\) and prove that the holonomic recurrence using non-linear one.
-The only part that is left is to translate this proof to the bijective language, which in such simple case as binary trees is almost trivial, especially if one has seen the solution once.
+The only part that is left is to translate this proof to the bijective language, which in such a simple case as binary trees is almost trivial, especially if one has seen the solution once.
 
@@
 
-If all elaborate methods has failed and the problem is still too big to interpret it by hand, a computer comes in handy.
+If all elaborate methods have failed and the problem is still too big to interpret it by hand, a computer comes in handy.
 
@@
 The definition above is quite popular, but introduces several problems.
-One of them is a problem of potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction is the variable bound (or is it even free variable, ie.\ not bound).
+One of them is a problem of potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction is the variable bound (or is it even a free variable, ie.\ not bound).
 To address that, we can use de Bruijn indices.
@@
 
-As you can see, we managed to eliminate the arbitrary variables. We can also easily check if given variable is bound by checking its depth.
+As you can see, we managed to eliminate the arbitrary variables. We can also easily check if a given variable is bound by checking its depth.
 
@@
 \begin{definition}
-    \(s\) is a node with only right child.
-\end{definition}
-
-\begin{definition}
-    \(l\) is a node with only left child.
+    \(s\) is a node with only the right child.
+\end{definition}
+
+\begin{definition}
+    \(l\) is a node with only the left child.
 \end{definition}
@@
 
-You can note that not every binary tree represents valid term.
+You can note that not every binary tree represents a valid term.
 
 \begin{example}
-    \(\n\; \no\; \n\; \n\; \no\; \no\; \no\) does not represent valid lambda term.
+    \(\n\; \no\; \n\; \n\; \no\; \no\; \no\) does not represent a valid lambda term.
 \end{example}
@@
 
-\(s\) represents successor which can be applied only to \(n \in \N\), but is applied to lambda-abstracted term.
+\(s\) represents the successor which can be applied only to \(n \in \N\), but is applied to the lambda-abstracted term.
 
@@
 
-As we have our structure defined, let's create generating functions that will keep track of more than just number of nodes, but also counts of each kind of nodes in the tree.
+As we have our structure defined, let's create generating functions that will keep track of more than just the number of nodes, but also counts of each kind of node in the tree.
 The generating function will be parameterized then using following arguments:
@@
 
-Using a little bit of Maple magic\cite{gfun}, we can easily achieve following holonomic recurrence.
+Using a little bit of Maple magic\cite{gfun}, we can easily achieve the following holonomic recurrence.
 
@@
 
-Appearing in the recurrence node kinds mean that we extend trees of given size using nodes of that kinds.
+Appearing in the recurrence node kinds means that we extend trees of given size using nodes of that kind.
 
@@
 
-You may notice that some potentially trivial terms are more complex that it seems. If we didn't count different types of nodes, we would achieve following holonomic recurrence:
+You may notice that some potentially trivial terms are more complex than they seem. If we didn't count different types of nodes, we would achieve following holonomic recurrence:
 
@@
 It is based on the idea that every transformation described using bijective language can be translated to a function transforming node and finite number of its surrounding nodes.
-This function can not discriminate nodes on the grounds of their kind.
+This function can not discriminate between nodes on the grounds of their kind.
 The only discrimination criteria that may occur may be connected to the following cases:
@@
     \item node has its parent on the left, ie.~is right child of its parent;
-    \item node has its parent on the right, ie.~is left child of its parent.
+    \item node has its parent on the right, ie.~is the left child of its parent.
 \end{itemize}
@@
 \begin{definition}
-    Class \(T_i\) is defined as set of transformations of trees of size \((n - i)\) into trees of size \(n\).
-\end{definition}
-
-\begin{definition}
-    Section \(T_{i,j}\) is defined as subset of \(T_i\) adding specific set of nodes. We assign \(j\) according to the lexicographical order of lexicographically sorted node types.
-\end{definition}
-
-\begin{definition}
-    Part \(T_{i,j,k}\) is defined as single transformation in section \(T_{i,j}\). \(k\) is assigned according to the order of discovering the transformation.
+    Class \(T_i\) is defined as a set of transformations of trees of size \((n - i)\) into trees of size \(n\).
+\end{definition}
+
+\begin{definition}
+    Section \(T_{i,j}\) is defined as a subset of \(T_i\) adding a specific set of nodes. Webassign \(j\) according to the lexicographical order of lexicographically sorted node types.
+\end{definition}
+
+\begin{definition}
+    Part \(T_{i,j,k}\) is defined as a single transformation in section \(T_{i,j}\). \(k\) is assigned according to the order of discovering the transformation.
 \end{definition}
@@
 \begin{definition}
-    In context of \(T_i\), \(k\) is defined as \((n - i)\).
-\end{definition}
-
-\begin{definition}
-    In context of \(T_i\), \(C_k\) is defined as \(L(n - i)\), ie.\ number of trees transformations from \(T_i\) are working on.
-\end{definition}
-
-\begin{definition}
-    Section equation \(E_{i, j}\) is an equation defined in context of \(T_i\) that evaluates to a total number of trees that should be generated by transformations from \(T_{i, j}\).
-\end{definition}
-
-\begin{definition}
-    Section expression \(S_{i, j}\) is pair of section equation and set of kinds of nodes the transformation introduces.
+    In the context of \(T_i\), \(k\) is defined as \((n - i)\).
+\end{definition}
+
+\begin{definition}
+    In the context of \(T_i\), \(C_k\) is defined as \(L(n - i)\), ie.\ number of tree transformations from \(T_i\) are working on.
+\end{definition}
+
+\begin{definition}
+    Section equation \(E_{i, j}\) is an equation defined in the context of \(T_i\) that evaluates to a total number of trees that should be generated by transformations from \(T_{i, j}\).
+\end{definition}
+
+\begin{definition}
+    Section expression \(S_{i, j}\) is a pair of section equations and a set of kinds of nodes the transformation introduces.
 \end{definition}
@@
 
-Using context-based variables makes the equation simpler to interpret, as we can immediately see relation between \(k\) and multiplier.
+Using context-based variables makes the equation simpler to interpret, as we can immediately see the relation between \(k\) and multiplier.
 
@@
 
-As we want to make our work kind of organized, we are going to divide the process into iterations. Each iteration should be a small step into direction of solving the original problem.
+As we want to make our work kind of organized, we are going to divide the process into iterations. Each iteration should be a small step into the direction of solving the original problem.
 
@@
 Positive and negative ones.
-When computing total number of trees, we count positive tree is counted as \(1\), negative as \(-1\).
+When computing the total number of trees, we count positive trees as \(1\), negative as \(-1\).
 Our goal is to generate \(E_{i, j}\) trees for each section \(T_{i, j}\).
@@
 
-This statistic tells us for each section, how many trees have been generated of expected total number of trees in that section. \verb|[x]| means that we generated enough trees for such section.
-
-We start with interpreting \(E_{0,0} = (k + 1) C_k\). From statistics above, we see that we should generate \(16\) trees. \((k + 1)\) suggests pointing virtual leaf. Let's do so.
+This statistic tells us for each section, how many trees have been generated of the expected total number of trees in that section. \verb|[x]| means that we generated enough trees for such a section.
+
+We start with interpreting \(E_{0,0} = (k + 1) C_k\). From statistics above, we see that we should generate \(16\) trees. \((k + 1)\) suggests pointing to a virtual leaf. Let's do so.
 
@@
 The order may be a bit suggestive.
-Section \(1,0\) adds single \(l\) node, whereas section \(1,1\) adds single \(s\) node.
-It actually suggests how can we can try to generate first and second line of the trees above.
+Section \(1,0\) adds a single \(l\) node, whereas section \(1,1\) adds a single \(s\) node.
+It actually suggests how we can try to generate the first and second line of the trees above.
 The first one is simple.
@@
 
-It addresses all cases from the first line, but also introduces incorrect lambda tree in which \(s\) is parent of \(l\), which can not happen.
+It addresses all cases from the first line, but also introduces an incorrect lambda tree in which \(s\) is the parent of \(l\), which can not happen.
 We will fix it with the section \(2,2\) generating positive trees, which introduces one \(l\) node and one \(s\) by extending the tree with \(2\) nodes where \(s\) is parent of \(l\).
@@
 
-For each actual vertex, we add \(a\) node as its left or right parent and add as a second child \(o\) node as its sibling. We then point left or right virtual child of newly created \(o\) node.
+For each actual vertex, we add \(a\) node as its left or right parent and add as a second child \(o\) node as its sibling.
+We then point to the left or right virtual child of the newly created \(o\) node.
 
@@
 You may remember our assumptions in section \ref{sub:the_framework} about the discrimination cases.
-We allowed ourselves to apply visitors only to one of left and right child, which isn't handled by our holonomic recurrence as number of such vertices do not depend only on \(n\).
+We allowed ourselves to apply visitors only to one of the left and right children, which isn't handled by our holonomic recurrence as the number of such vertices does not depend only on \(n\).
 
 To fix this, one can for example add construction for section \(1, 0\) to generate all expected trees from it and then repeat the iteration in order to generate matching trees on the other side of the equation.
-We can see that we used \(2\) constructions visiting node with right parent and only one visiting node having left parent, so our missing construction should also visit nodes with left parent.
+We can see that we used \(2\) constructions visiting nodes with right parent and only one visiting node having left parent, so our missing construction should also visit nodes with left parent.
 
@@
 
-Please note that it is only an example of missing construction. It is just the simplest one we could think about, and in that case, simple solution is most often the correct one.
+Please note that it is only an example of missing construction. It is just the simplest one we could think about, and in that case, a simple solution is most often the correct one.
 
@@
 We believe that the solving process can be automated.
-The simplest method that comes to mind is simply creating heuristic rules that then will be used by the framework to guess at least partial solution.
-
-With the proper interpretation, it may be possible to create sampling algorithm similar to Rémy's one for binary trees\cite{remy,note}.
+The simplest method that comes to mind is simply creating heuristic rules that then will be used by the framework to guess at least partial solutions.
+
+With the proper interpretation, it may be possible to create a sampling algorithm similar to Rémy's one for binary trees\cite{remy,note}.
 It would have to take under consideration that some trees are being removed by other classes, so the probabilities would have to be set carefully.

### 2021-08-29 article/main.tex
Make minor fixes

@@
 Every recursive structure can be described using a generating function, which can be then transformed into holonomic recurrence.
-It allows us to quickly count objects of given structure with of given size.
+It allows us to quickly count objects of given structure with given size.
 At first glance, the recurrence seems to be closely related to the structure itself.
@@
 
-In the thesis we try to accumulate known results and techniques that may help solving the problem of finding combinatorial interpretations.
+Throughout the thesis we try to accumulate known results and techniques that may help solving the problem of finding combinatorial interpretations.
 We also propose an approach that helped us to find an intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of lambda trees in the unary de Bruijn notation.
@@
 
-Section\ \ref{sec:brutal_iterative_approach} presents our final approach to the original problem, ie.\ computer-aided iterative approach that allowed us to find the intermediate solution.
+Section\ \ref{sec:brutal_iterative_approach} presents our final approach to the original problem, i.e.\ computer-aided iterative approach that allowed us to find the intermediate solution.
 We believe that it is able to provide us with the full solution, but we were not able to achieve that due to the limited time that was available to us.
@@
 
-In order to make reading this article easier, let's fix some notation and make some assumptions.
+In order to make reading this thesis easier, let's fix some notation and make some assumptions.
 Any deviation from this will be clearly stated.
@@
 
-\(\no\) is implicitly defined as an identifier of a non-existing node (eg.\ if \(v\) is a leaf, \(\tleft(v) = \n\)).
+\(\no\) is implicitly defined as an identifier of a non-existing node (e.g.\ if \(v\) is a leaf, \(\tleft(v) = \n\)).
 
@@
 \end{minipage}
-depict edges that may or may not exist (eg.\ when we describe transformations and we don't care if the node is root or if it has children).
+depict edges that may or may not exist (e.g.\ when we describe transformations and we do not care if the node is root or if it has children).
 
@@
 
-Virtual node is an artificially defined node that does not affect the structure definition (eg.\ we can define virtual leafs that are children of actual leaves of the binary tree.
+Virtual node is an artificially defined node that does not affect the structure definition (e.g.\ we can define virtual leafs that are children of actual leaves of the binary tree.
 Such virtual leaves are not included when counting the number of children of the node, so the actual leaves are still called leaves).
@@
 
-eg.\ stands for Latin exempli gratia, which means \textit{for example}.
-
-ie.\ stands for Latin id est, which means \textit{that is}.
+e.g.\ stands for Latin exempli gratia, which means \textit{for example}.
+
+i.e.\ stands for Latin id est, which means \textit{that is}.
+\todo{It should be obvious, but people mix them up}
 
@@
 We will be analyzing structures that can be expressed using recursive formulas.
-Eg.\ we can define a full binary tree recursively as a node having no children (ie.\ being a leaf) or having exactly two subtrees being full binary trees.
+Eg.\ we can define a full binary tree recursively as a node having no children (i.e.\ being a leaf) or having exactly two subtrees being full binary trees.
 To express the alternative in the construction rule, we use \(+\).
@@
 
-In the article we use ordinary generating functions to describe and count structures.
+Throughout the thesis we use ordinary generating functions to describe and count structures.
 
@@
 
-The highlighted terms are describing following tree:
+The highlighted terms describe following tree:
 
@@
 
-\begin{definition}
+\begin{definition}[\cite{holotoolkit}]
     \label{def:holo_1}
-    \cite{holotoolkit}
-    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) exists holonomic recurrence for it, ie.:
+    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) there exists a holonomic recurrence for it, i.e.:
 
@@
 \begin{example}
-    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic, ie. none of them satisfies a linear recurrence equation with polynomial coefficients\cite{nonholo}.
+    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic, i.e.\ none of them satisfies a linear recurrence equation with polynomial coefficients\cite{nonholo}.
 \end{example}
 
-\begin{definition}
+\begin{definition}[\cite{complexity}]
     \label{def:holo_2}
-    \cite{complexity}
     Equivalently to definition\ \ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists generating function in the following form:
@@
     \label{ex:gfun-rec}
-    For generating function full binary trees defined in example\ \ref{ex:bin_gf}, ie.:
+    For generating function full binary trees defined in example\ \ref{ex:bin_gf}, i.e.:
     \[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
@@
 Holonomic recurrences are very useful if we want to count objects of given size.
-Of course, size can be defined in more complex ways, eg.\ we may want to find the number of trees with \(n\) internal nodes having exactly \(m\) nodes being left child of its parent.
+Of course, size can be defined in more complex ways, e.g.\ we may want to find the number of trees with \(n\) internal nodes having exactly \(m\) nodes being left child of its parent.
 
@@
 
-In the article we try to gather methods and results that may be helpful for anyone trying to find such interpretation, as we believe that such interpretation may give better insight into the nature of the structure and make it easier to study its behaviour.
+In the thesis we try to gather methods and results that may be helpful for anyone trying to find such interpretation, as we believe that such interpretation may give better insight into the nature of the structure and make it easier to study its behaviour.
 
@@
     \[\enc{T} = \enc{\troot(T)} \prod_{i=1}^{n} \enc{i\text{-th subtree of } \troot(T)}\]
-    ie.\ catenation of the identifier of the root of the tree with encoded its subtrees from left to right.
+    i.e.\ catenation of the identifier of the root of the tree with encoded its subtrees from left to right.
 \end{definition}
@@
 
-In the article we define some operations using its notation. As pre-order notation is bijective, you can obtain the structure the notation describes by reversing the process of encoding.
+Throughout thesis we define some operations using this notation. As pre-order notation is bijective, you can obtain the structure the notation describes by reversing the process of encoding.
 
@@
 
-We define the size of a tree as a number of internal nodes (ie.\ nodes that are not leaves). Our generating function is therefore:
+We define the size of a tree as a number of internal nodes (i.e.\ nodes that are not leaves). Our generating function is therefore:
 
@@
 
-It is easy to see that a tree of size \(n\) (ie.
-with \(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
+It is easy to see that a tree of size \(n\) (i.e.\ with \(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
 Analogically the tree of size \(n + 1\) has \(n + 2\) leaves and \(2n + 3\) nodes in total.
@@
 Let's define two local operations: \(R_l(T, v)\) and \(R_r(T, v)\).
-The term \textit{local} means that the operation can operate on just some finite fragment of tree with predefined size (eg.\ node and its 2 children, but can not traverse the whole tree).
+The term \textit{local} means that the operation can operate on just some finite fragment of tree with predefined size (e.g.\ node and its 2 children, but can not traverse the whole tree).
 
@@
 
-We can now take the bijective interpretation of \((2n + 1) B(n)\), ie.
-trees of size \(n\) with a single node pointed.
+We can now take the bijective interpretation of \((2n + 1) B(n)\), i.e.\ trees of size \(n\) with a single node pointed.
 For each of such trees, \(T\) we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a node that is pointed in \(T\).
@@
 We can avoid it by using a trick to make the tree recall binary trees.
-We don't change the structure, just the notation.
+We do not change the structure, just the notation.
 
@@
 The other cases translate immediately to corresponding ones.
-Please note that this transformation keeps the size of the tree (ie.~number of edges).
+Please note that this transformation keeps the size of the tree (i.e.~number of edges).
 
@@
 
-All we need to show are the transformations from the smaller cases, ie. \(U(n-1)\) and \(U(n-2)\).
+All we need to show are the transformations from the smaller cases, i.e.\ \(U(n-1)\) and \(U(n-2)\).
 
@@
 
-This definition is quite precise, but is difficult to implement as a structural recursion. Let's transform it into something more manageable, ie.~of finite arity.
+This definition is quite precise, but is difficult to implement as a structural recursion. Let's transform it into something more manageable, i.e.~of finite arity.
 
@@
 
-We can also move \(T(n)\) to the other side, ie.:
+We can also move \(T(n)\) to the other side, i.e.:
 
@@
 \begin{itemize}
-    \item \((2 n - 1) T(n)\) describes well-weighted binary plane trees of size \(n\) (ie. with \(n\) leaves) with some node pointed (internal or leaf),
+    \item \((2 n - 1) T(n)\) describes well-weighted binary plane trees of size \(n\) (i.e.\ with \(n\) leaves) with some node pointed (internal or leaf),
     \item \((n + 1) T(n + 1)\) describes well-weighted binary plane trees of size \(n - 1\) with some leaf pointed,
@@
     \item counting leaves,
-    \item counting null-nodes (ie.\ children of the leaves),
+    \item counting null-nodes (i.e.\ children of the leaves),
     \item counting edges.
@@
 \begin{itemize}
-    \item we get empty classes of the objects, eg.\ if we analyze problem of full binary trees and define size as number of all existing nodes, we can not generate tree of even size, therefore half of our classes are empty;
+    \item we get empty classes of the objects, e.g.\ if we analyze problem of full binary trees and define size as number of all existing nodes, we can not generate tree of even size, therefore half of our classes are empty;
     \item we want to join trees using common roots and we get many \(\pm1\) in our notes.
@@
 
-If we describe some structure we may be tempted to use multiple kinds of nodes, eg.~unary and binary nodes.
+If we describe some structure we may be tempted to use multiple kinds of nodes, e.g.~unary and binary nodes.
 Having multiple kinds of nodes may cause problems, both in creating holonomic recurrence and finding the interpretation, as we have to keep track of how they can transform.
@@
 
-Most of the time we are operating on trees with some nodes of weight \(0\) and some of weight \(1\). We may as well try to make them variable or assign some other values (eg.\ small prime numbers).
+Most of the time we are operating on trees with some nodes of weight \(0\) and some of weight \(1\). We may as well try to make them variable or assign some other values (e.g.\ small prime numbers).
 
@@
 
-Using our inductive hypothesis, ie.\ holonomic recurrence and moving problematic cases out from the sums (in that case \(B(1)\) needs to be analyzed separately, as we did not define binary trees with no leaves), we can get the right side to use \(B(n - 1)\) and prove that the holonomic recurrence using non-linear one.
+Using our inductive hypothesis, i.e.\ holonomic recurrence and moving problematic cases out from the sums (in that case \(B(1)\) needs to be analyzed separately, as we did not define binary trees with no leaves), we can get the right side to use \(B(n - 1)\) and prove that the holonomic recurrence using non-linear one.
 The only part that is left is to translate this proof to the bijective language, which in such a simple case as binary trees is almost trivial, especially if one has seen the solution once.
@@
         \item if \(x\) is a variable and \(M \in \Lambda\), then \((\lambda x .
-M) \in \Lambda\) (abstraction, ie.\ creating a function with an argument \(x\) and binding each occurrence of \(x\) in \(M\) to this argument)
+M) \in \Lambda\) (abstraction, i.e.\ creating a function with an argument \(x\) and binding each occurrence of \(x\) in \(M\) to this argument)
     \end{itemize}
@@
 The definition above is quite popular, but introduces several problems.
-One of them is a problem of potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction is the variable bound (or is it even a free variable, ie.\ not bound).
+One of them is a problem of potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction is the variable bound (or is it even a free variable, i.e.\ not bound).
 To address that, we can use de Bruijn indices.
@@
 
-In order to make the image cleaner, we will drop the arguments of generating functions, ie. \(\gf{L} := \gf{L}(z, o, l, a, s)\)
+In order to make the image cleaner, we will drop the arguments of generating functions, i.e.\ \(\gf{L} := \gf{L}(z, o, l, a, s)\)
 
@@
 
-You may notice that some potentially trivial terms are more complex than they seem. If we didn't count different types of nodes, we would achieve following holonomic recurrence:
+You may notice that some potentially trivial terms are more complex than they seem. If we did not count different types of nodes, we would achieve following holonomic recurrence:
 
@@
 \begin{itemize}
-    \item node has no children, ie.~is a virtual leaf (which corresponds to the size of the tree, \(n\));
-    \item node has has children, ie.~is not a virtual leaf (which corresponds to \(n - 1\));
+    \item node has no children, i.e.~is a virtual leaf (which corresponds to the size of the tree, \(n\));
+    \item node has has children, i.e.~is not a virtual leaf (which corresponds to \(n - 1\));
     \item node is a root (which corresponds to \(1\));
-    \item node has its parent on the left, ie.~is right child of its parent;
-    \item node has its parent on the right, ie.~is the left child of its parent.
+    \item node has its parent on the left, i.e.~is right child of its parent;
+    \item node has its parent on the right, i.e.~is the left child of its parent.
 \end{itemize}
@@
 \begin{definition}
-    In the context of \(T_i\), \(C_k\) is defined as \(L(n - i)\), ie.\ number of tree transformations from \(T_i\) are working on.
+    In the context of \(T_i\), \(C_k\) is defined as \(L(n - i)\), i.e.\ number of tree transformations from \(T_i\) are working on.
 \end{definition}
@@
 Positive and negative ones.
-When computing the total number of trees, we count positive trees as \(1\), negative as \(-1\).
+When computing the total number of trees, we count positive trees as \(1\) and negative as \(-1\).
 Our goal is to generate \(E_{i, j}\) trees for each section \(T_{i, j}\).
@@
 c.append_r_class_subtree_visitor(1,       # we define positive trees
-                                          # ie. that count as 1
+                                          # i.e. that count as 1
     lambda kind, left, right:
@@
 
-Basically, for each virtual node not being root (ie.\ having left or right parent), we point it and add \(l\) or \(s\) respectively above the parent.
+Basically, for each virtual node not being root (i.e.\ having left or right parent), we point it and add \(l\) or \(s\) respectively above the parent.
 
@@
 
-The process can then be repeated for each section. We have chosen lexicographical order (ie. \(0,0\); \(1,0\); \(1,1\); \(2,0\); \(\ldots\)).
+The process can then be repeated for each section. We have chosen lexicographical order (i.e.\ \(0,0\); \(1,0\); \(1,1\); \(2,0\); \(\ldots\)).
 
@@
 
-You may also note that we didn't generate all trees suggested by the recurrence. This is due to one cheat we used.
+You may also note that we did not generate all trees suggested by the recurrence. This is due to one cheat we used.
 
@@
 You may remember our assumptions in section \ref{sub:the_framework} about the discrimination cases.
-We allowed ourselves to apply visitors only to one of the left and right children, which isn't handled by our holonomic recurrence as the number of such vertices does not depend only on \(n\).
+We allowed ourselves to apply visitors only to one of the left and right children, which is not handled by our holonomic recurrence as the number of such vertices does not depend only on \(n\).
 
@@
 
-The framework also isn't perfect.
+The framework also is not perfect.
 It highly depends on the operator's intuition.

### 2021-08-29 article/main.tex
Add minor fixes

@@
 \label{sub:generating_functions}
+\todo{Make the section simpler}
 
@@
 
-Note that in order to compute \(k\)-th element of the sequence, \(a_k\), we just need to find a constant corresponding to indeterminate \(z^k\).
+Note that in order to compute the \(k\)-th element of the sequence, namely \(a_k\), we just need to find a constant corresponding to indeterminate \(z^k\).
 
@@
     Having our recursive definition of the object, we can easily construct a generating function for it.
-Let's create a generating function that will count the number of full binary trees consisting of exactly \(k\) internal nodes.
+Let's create a generating function that will count the number of full binary trees consisting of exactly \(k\) internal nodes.\todo{define sequence for the structure}
 
@@
 
-Note that we used \(z\) to count internal nodes and left the leaf part as \(1\).
+Note that we used \(z\) to mark internal nodes. Leaves are of size \(0\), so they are marked using \(z^0 = 1\).
 
@@
 \label{sub:holonomic_recurrences}
+\todo{Extend the section}
 
@@
 \begin{example}
-    \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because:
+    The sequence \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because it satisifies:
     \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0\]
@@
     \label{def:holo_2}
-    Equivalently to definition\ \ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists generating function in the following form:
+    Equivalently to definition\ \ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists a generating function in the following form:
     \[\sum_{i=0}^{r} p_i(z) \gf{A}^{(i)}(z) = b(z)\]
@@
 
-Equivalence of these two definitions assures us that if we find generating function describing the desired objects satisfying definition\ \ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def:holo_1}.\cite{complexity}
+The equivalence of these two definitions assures us that if we find generating function describing the desired objects satisfying definition\ \ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def:holo_1}.\cite{complexity}
 

### 2021-09-04 article/main.tex
Add unary-binary proof
Fixups

@@
 \newcommand{\mhl}[1]{{\tikzmarkin[set fill color=red!30,set border color=red]{highlight-\arabic{highlightid}}(0.02,-0.15)(-0.02,0.35){#1}\tikzmarkend{highlight-\arabic{highlightid}}\stepcounter{highlightid}}}
+
+\newcommand{\mhlr}[1]{{\tikzmarkin[set fill color=red!30,set border color=red]{highlight-\arabic{highlightid}}(0.02,-0.15)(-0.02,0.35){#1}\tikzmarkend{highlight-\arabic{highlightid}}\stepcounter{highlightid}}}
+\newcommand{\mhlg}[1]{{\tikzmarkin[set fill color=green!30,set border color=green]{highlight-\arabic{highlightid}}(0.02,-0.15)(-0.02,0.35){#1}\tikzmarkend{highlight-\arabic{highlightid}}\stepcounter{highlightid}}}
+\newcommand{\mhlb}[1]{{\tikzmarkin[set fill color=blue!30,set border color=blue]{highlight-\arabic{highlightid}}(0.02,-0.15)(-0.02,0.35){#1}\tikzmarkend{highlight-\arabic{highlightid}}\stepcounter{highlightid}}}
 
@@
 
-Next, in the section \ref{sec:known_results}, we present known results. They demonstrate combinatorial interpretations that resemble different approaches.
+Next, in the section \ref{sec:known_results}, we present known results. They demonstrate combinatorial interpretations that reflect different approaches.
 
@@
 \begin{center}
-    \begin{longtable}{| c | c | c |}
+    \begin{longtable}{| c | c | c | c |}
         \hline
@@
         \(U(n-1)\) &
+               &
         \(U(n)\)\\
@@
         I \includesvg[scale=0.4]{unary_binary__1si} &
+        \(\Rightarrow\)&
         Vro \includesvg[scale=0.4]{unary_binary__0fid} \\
@@
         Vlt \includesvg[scale=0.4]{unary_binary__1fjg} &
+        \(\Rightarrow\)&
         VrtUrv \includesvg[scale=0.4]{unary_binary__0fjdOgf} \\
@@
         &
+        \(\Rightarrow\)&
         VrtUra \includesvg[scale=0.4]{unary_binary__0fjdOdi} \\
@@
         Vro \includesvg[scale=0.4]{unary_binary__1fid} &
+        \(\Rightarrow\)&
         VrtUla \includesvg[scale=0.4]{unary_binary__0fjdOgi} \\
@@
         Vrt \includesvg[scale=0.4]{unary_binary__1fjd} &
+        \(\Rightarrow\)&
         VltUrv \includesvg[scale=0.4]{unary_binary__0fjgOdf} \\
@@
         &
+        \(\Rightarrow\)&
         VltUra \includesvg[scale=0.4]{unary_binary__0fjgOdi} \\
@@
         &
+        \(\Rightarrow\)&
         VltUla \includesvg[scale=0.4]{unary_binary__0fjgOgi} \\
@@
 
-It is easy to show that it constructs bijection between \((n + 1) T(n + 1)\) and subset of \(\{L_1, L_2, R_1\} \times (2 n - 1) T(n)\) not falling into case 3.
+It is easy to show that it constructs bijection between \((n + 1) T(n + 1)\) and subset of \(\{L_1, L_2, R_1\} \times (2 n - 1) T(n)\) not falling into case 3. We will show that in a moment.
 
@@
 \end{center}
+
+To see the bijection, we can just draw all possible cases:
+
+\begin{center}
+    \begin{longtable}{| c | c | c | c | c |}
+        \hline
+        &
+        \(\Rightarrow\)&
+        \(R_1\) &
+        \(L_1\) &
+        \(L_2\) \\
+        \hline
+
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__21} &
+        \(\Rightarrow\)&
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__23} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__22} &
+        \begin{minipage}{.23\textwidth}
+            \begin{center}
+                \includeinlinescaledsvg{1}{.35}{schroder__proof__24}
+                \(\Downarrow\)
+                \includeinlinescaledsvg{1}{.35}{schroder__proof__24b}
+            \end{center}
+        \end{minipage}
+        \\
+        \hline
+
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__11} &
+        \(\Rightarrow\)&
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__13} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__12} &
+        \begin{minipage}{.23\textwidth}
+            \begin{center}
+                \includeinlinescaledsvg{1}{.35}{schroder__proof__14}
+                \(\Downarrow\)
+                \includeinlinescaledsvg{1}{.35}{schroder__proof__14b}
+            \end{center}
+        \end{minipage}
+        \\
+        \hline
+
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__31} &
+        \(\Rightarrow\)&
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__33} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__32} &
+        \begin{minipage}{.23\textwidth}
+            \begin{center}
+                \includeinlinescaledsvg{1}{.35}{schroder__proof__34}
+                \(\Downarrow\)
+                \includeinlinescaledsvg{1}{.35}{schroder__proof__34b}
+            \end{center}
+        \end{minipage}
+        \\
+        \hline
+
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__51} &
+        \(\Rightarrow\)&
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__53} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__52} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__54} \\
+        \hline
+
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__41} &
+        \(\Rightarrow\)&
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__43} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__42} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__44} \\
+        \hline
+
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__61} &
+        \(\Rightarrow\)&
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__63} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__62} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__64} \\
+        \hline
+
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__71} &
+        \(\Rightarrow\)&
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__73} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__72} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__74} \\
+        \hline
+
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__81} &
+        \(\Rightarrow\)&
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__83} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__82} &
+        \includeinlinescaledsvg{.23}{.35}{schroder__proof__84} \\
+        \hline
+
+    \end{longtable}
+\end{center}
+
+In the left column you can see all possibilities of selecting \(s\) from a tree of size \(n\).
+In \(R_1\), \(L_1\) and \(L_2\) columns we show how they are then transformed.
+It covers all possible cases of selecting leaf from a tree of size \(n + 1\) and selecting an internal from a tree of size \(n - 1\).
 

### 2021-09-04 article/main.tex
Fixups

@@
 \section{Overview}%
-
-Every recursive structure can be described using a generating function, which can be then transformed into holonomic recurrence.
+\todo{generating functions}
+\todo{holonomic recurrences}
+\todo{publications about Motzkin, etc.}
+\todo{Lambda terms}
+\todo{zigzag free}
+
+Every recursive structure can be described using a generating function, which can be then transformed into a holonomic recurrence.
 It allows us to quickly count objects of given structure with given size.
 At first glance, the recurrence seems to be closely related to the structure itself.
-It just seems like it should describe simple transformations, like adding some vertices to the smaller trees.
-Although, there is no known method of interpreting it in the language of the combinatorial structures.
-
-Initial inspiration for the thesis came from publication \textit{A natural counting of lambda terms}\cite{zigzag}, which shows bijection between seemingly different tree structures, which are lambda trees, black-white trees and zigzag free trees.
-They share the same holonomic recurrence, but there is no known immediate connection between the holonomic recurrence and the structure itself.
+It just seems like it should describe simple transformations resulting in constructing bigger objects from slightly smaller ones.
+In case of trees it could be for example adding vertices.
+However, there is no known method of interpreting it in the language of the combinatorial structures.
+
+The initial inspiration for the thesis came from the publication \textit{A natural counting of lambda terms}~\cite{zigzag}, which shows bijections among seemingly different tree structures, which are lambda trees, black-white trees\todo{cite} and zigzag free trees\todo{cite}.
+They share the same holonomic recurrence, but there is no known immediate connection between the holonomic recurrence and the structures itself.
 
@@
 We also propose an approach that helped us to find an intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of lambda trees in the unary de Bruijn notation.
-
-In the section\ \ref{sec:introduction} we establish notation nad introduce concepts that will be using throughout the thesis.
-
-Next, in the section \ref{sec:known_results}, we present known results. They demonstrate combinatorial interpretations that reflect different approaches.
-
-In the section\ \ref{sec:approaches} we show approaches to the problem that helped people achieve their results.
+We use the de Bruijn indices in order to get rid of letter-based variable names.
+Unary notation allows us to connect size of the tree to the values of the de Bruijn indices.
+
+In Section~\ref{sec:introduction} we establish notation nad introduce concepts that will be used throughout the thesis.
+
+Next, in Section~\ref{sec:known_results}, we present known results, ie.
+binary trees, unary-binary trees and Schröder trees.
+They demonstrate combinatorial interpretations that reflect different approaches.
+
+In Section~\ref{sec:approaches} we show approaches to the problem that helped to achieve the aforementioned results.
 All of them were tried in order to find the answer to the original problem of interpreting holonomic recurrence of trees of lambda terms in the unary de Bruijn notation.
-Unfortunately none of them helped us enough to get the final result.
-They are proven to be helpful when we are stuck though as most of them are able to divide problems into smaller parts and detect corner cases.
-
-Section\ \ref{sec:brutal_iterative_approach} presents our final approach to the original problem, i.e.\ computer-aided iterative approach that allowed us to find the intermediate solution.
-We believe that it is able to provide us with the full solution, but we were not able to achieve that due to the limited time that was available to us.
-
-Finally, in section\ \ref{sec:further_work}, we present our view on what can be done with the problem in the future.
+Unfortunately, none of them helped us enough to get the final result.
+Anyway, they are proven to be helpful when we are stuck, as most of them are able to divide problems into smaller parts and detect corner cases.
+
+Section~\ref{sec:brutal_iterative_approach} presents our final approach to the original problem, i.e.\ computer-aided iterative approach that allowed us to find the intermediate solution.
+We believe that it is possible to extend this idea in order to obtain the full solution, but we were not able to achieve that due to the limited time that was available to us.
+
+Finally, in Section~\ref{sec:further_work}, we present our view on what can be done with the problem in the future.
 We believe that one day the problem will be fully solved and a more generic approach to interpreting holonomic recurrences will emerge.
@@
 If you have trouble guessing what some letter or word means, this should be your primary place to look for the answer.
+
+e.g.\ stands for Latin exempli gratia, which means \textit{for example}.
+
+i.e.\ stands for Latin id est, which means \textit{that is}.
 
@@
 
-e.g.\ stands for Latin exempli gratia, which means \textit{for example}.
-
-i.e.\ stands for Latin id est, which means \textit{that is}.
-\todo{It should be obvious, but people mix them up}
-
 \subsection{Structurally recursive objects}%
@@
 We will be analyzing structures that can be expressed using recursive formulas.
-Eg.\ we can define a full binary tree recursively as a node having no children (i.e.\ being a leaf) or having exactly two subtrees being full binary trees.
-To express the alternative in the construction rule, we use \(+\).
+For example we can define a full binary tree recursively as a node having no children (i.e.\ being a leaf) or having exactly two subtrees being full binary trees.
+To express the disjoint alternative in the construction rule, we use \(+\).
 The reason will become obvious soon.
@@
 \label{sub:generating_functions}
+\todo{Source}
 \todo{Make the section simpler}
@@
 \begin{definition}
-The ordinary generating function of sequence \(A = (a_i)_{i=0}^{\infty}\) is defined as:
-\[\gf{A}(z) = \sum_{i=0}^{\infty} a_i z^i\]
+The ordinary generating function of sequence \(A = (a_i)_{i=0}^{\infty}\) is defined as a formal power series:
+\[\gf{A}(z) = \sum_{i=0}^{\infty} a_i z^i .\]
 \end{definition}
@@
 There exist multiple well-known methods and tools that allow us to work with generating functions without the need of digging into details.
-The tool we will be using extensively in this work is the Maple package called GFUN\cite{gfun}.
+The tool we will be using extensively in this work is the Maple package called GFUN~\cite{gfun}.
 If you want to learn more about algorithms used in the package, we strongly encourage reading the referenced article.
@@
 \begin{example}
-    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic, i.e.\ none of them satisfies a linear recurrence equation with polynomial coefficients\cite{nonholo}.
+    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic, i.e.\ none of them satisfies a linear recurrence equation with polynomial coefficients~\cite{nonholo}.
 \end{example}
@@
 
-The equivalence of these two definitions assures us that if we find generating function describing the desired objects satisfying definition\ \ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def:holo_1}.\cite{complexity}
+The equivalence of these two definitions assures us that if we find generating function describing the desired objects satisfying definition\ \ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def:holo_1}~\cite{complexity}.
 
@@
     \[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
-    we can use GFUN\cite{gfun} to immediately find holonomic recurrence of our interest:
+    we can use GFUN~\cite{gfun} to immediately find holonomic recurrence of our interest:
 
@@
 Combinatorial interpretation is just a fancy name for something you probably know and use.
-Eg.\ if you know the binomial coefficient \(\binom{n}{k}\), I bet it was introduced to you as something like: "let's assume you have \(n\) distinguishable balls.
+For example if you know the binomial coefficient \(\binom{n}{k}\), I bet it was introduced to you as something like: "let's assume you have \(n\) distinguishable balls.
 If you want to choose \(k\) from them, then you can do it in \(\binom{n}{k}\) ways" and now, whenever you see the term \(\binom{n}{k}\) you interpret it as number of ways to choose \(k\) objects from the set of size \(n\).
@@
 
-Let's start with probably the most known result, full binary trees\cite{binary}.
+Let's start with probably the most known result, full binary trees~\cite{binary}.
 
@@
 
-Let's think, what would have changed if we introduce unary nodes to the binary case\cite{motzkin}. We will be counting edges. Note that a tree having \(n\) edges has exactly \(n + 1\) nodes.
+Let's think, what would have changed if we introduce unary nodes to the binary case~\cite{motzkin}. We will be counting edges. Note that a tree having \(n\) edges has exactly \(n + 1\) nodes.
 
@@
 
-And with a bit of Maple magic\cite{gfun}, we immediately get following recurrence:
+And with a bit of Maple magic~\cite{gfun}, we immediately get following recurrence:
 
@@
 
-To present the interpretation in bijective language, we will have to introduce several types of the the nodes (you may want to revisit section \ref{sub:notation} Notation):
+To present the interpretation in bijective language, we will have to introduce several types of the the nodes (you may want to revisit Section~\ref{sub:notation} Notation):
 
@@
 
-The next case we will show is the case of Schröder trees\cite{schroder}.
+The next case we will show is the case of Schröder trees~\cite{schroder}.
 
@@
 
-As the most common trees are binary ones, it may be worth an effort to find some structure based on binary trees that can represent the original structure (see section~\ref{sub:unary_binary_trees}).
+As the most common trees are binary ones, it may be worth an effort to find some structure based on binary trees that can represent the original structure (see Section~\ref{sub:unary_binary_trees}).
 
@@
 
-In section \ref{sub:lambda_terms} we will define trees of lambda terms. If we would assign following weights to nodes:
+In Section~\ref{sub:lambda_terms} we will define trees of lambda terms. If we would assign following weights to nodes:
 
@@
 
-Another method that may help finding the interpretation is inductive translation\cite{doron}.
+Another method that may help finding the interpretation is inductive translation~\cite{doron}.
 The method is based on the idea that most of the time there is an easy way to find some natural induction (not necessarily holonomic) that has trivial interpretation in bijective language.
@@
 
-Using a little bit of Maple magic\cite{gfun}, we can easily achieve the following holonomic recurrence.
+Using a little bit of Maple magic~\cite{gfun}, we can easily achieve the following holonomic recurrence.
 
@@
 
-We also created a framework\cite{transformator}, called transformator, that may help visualize our work.
+We also created a framework~\cite{transformator}, called transformator, that may help visualize our work.
 It is based on the idea that every transformation described using bijective language can be translated to a function transforming node and finite number of its surrounding nodes.
@@
 
-You may remember our assumptions in section \ref{sub:the_framework} about the discrimination cases.
+You may remember our assumptions in Section~\ref{sub:the_framework} about the discrimination cases.
 We allowed ourselves to apply visitors only to one of the left and right children, which is not handled by our holonomic recurrence as the number of such vertices does not depend only on \(n\).
@@
 
-First thing to be done, that comes to mind immediately, is to finish the construction eliminating the cheat mentioned in section \ref{sub:the_cheat}.
+First thing to be done, that comes to mind immediately, is to finish the construction eliminating the cheat mentioned in Section~\ref{sub:the_cheat}.
 
@@
 
-With the proper interpretation, it may be possible to create a sampling algorithm similar to Rémy's one for binary trees\cite{remy,note}.
+With the proper interpretation, it may be possible to create a sampling algorithm similar to Rémy's one for binary trees~\cite{remy,note}.
 It would have to take under consideration that some trees are being removed by other classes, so the probabilities would have to be set carefully.

### 2021-09-04 article/main.tex
Unify bibliography

@@
 \svgpath{images/}
+
+\RequirePackage[maxbibnames=99]{biblatex}
+\addbibresource{bibliography.bib}
 
@@
 
-The initial inspiration for the thesis came from the publication \textit{A natural counting of lambda terms}~\cite{zigzag}, which shows bijections among seemingly different tree structures, which are lambda trees, black-white trees\todo{cite} and zigzag free trees\todo{cite}.
+The initial inspiration for the thesis came from the publication \textit{A natural counting of lambda terms}~\cite{inspiration}, which shows bijections among seemingly different tree structures, which are lambda trees, black-white trees~\cite{blackwhite} and zigzag free trees\todo{cite}.
 They share the same holonomic recurrence, but there is no known immediate connection between the holonomic recurrence and the structures itself.
@@
 
-\begin{thebibliography}{9}
-    \bibitem{zigzag}
-    Maciej Bendkowski, Katarzyna Grygiel, Pierre Lescanne, Marek Zaionc,
-    \textit{A natural counting of lambda terms},
-    2016
-
-    \bibitem{gfun}
-    Bruno Salvy, Paul Zimmermann,
-    \textit{GFUN : a maple package for the manipulation of generating and holonomic functions in one variable},
-    [Research Report] RT-0143, INRIA. 1992, pp.14. ffinria-00070025f
-
-    \bibitem{holotoolkit}
-    Manuel Kauers,
-    \textit{The Holonomic Toolkit},
-    in: Carsten Schneider, Johannes Blümlein (eds) Computer Algebra in Quantum Field Theory.
-Texts \& Monographs in Symbolic Computation (A Series of the Research Institute for Symbolic Computation, Johannes Kepler University, Linz, Austria),
-    Springer, Vienna,
-    2013
-
-    \bibitem{nonholo}
-    Stefan Gerhold,
-    \textit{Combinatorial sequences: Non-holonomicity and inequalities. Ph.D. thesis},
-    RISC-Linz, Johannes Kepler Universitat Linz,
-    2005
-
-    \bibitem{complexity}
-    Igor Pak,
-    \textit{Complexity problems in enumerative combinatorics},
-    2018
-
-    \bibitem{binary}
-    Jean-Luc Rémy,
-    \textit{Un procédé itératif de dénombrement d’arbres binaires et son application à leur génération aléatoire}
-    Informatique théorique, tome 19, no 2, 
-    1985,
-    p. 179-195
-
-    \bibitem{motzkin}
-    Serge Dulucq, Jean-Guy Penaud,
-    \textit{Interprétation bijective d'une récurrence des nombres de Motzkin},
-    Discrete Mathematics,
-    Volume 256, Issue 3,
-    2002,
-    p. 671-676
-
-    \bibitem{schroder}
-    Dominique Foata, Doron Zeilberger,
-    \textit{A Classic Proof of a Recurrence for a Very Classical Sequence}
-    J. Comb., Ser. A, 80,
-    1997, 380-384
-
-    \bibitem{doron}
-    Doron Zeilberger,
-    \textit{e-mail conversation},
-    2020
-
-    % Non-cited
-
-    \bibitem{remy}
-    Laurent Alonso Alonso, Jean-Luc Rémy, and René Schott,
-    \textit{A Linear-Time Algorithm for the Generation of Trees},
-    Algorithmica 17,
-    1997,
-    p. 162-182
-
-    \bibitem{note}
-    Jarmo Siltaneva, Erkki Mäkinen,
-    \textit{A Note on Rémy's Algorithm for Generating Random Binary Trees},
-    Missouri Journal of Mathematical Sciences. 15. 103-109. 10.35834/2003/1502103,
-    2003
-
-    \bibitem{bodini}
-    Axel Bacher, Olivier Bodini, Alice Jacquot,
-    Efficient random sampling of binary and unary-binary trees via holonomic equations,
-    2014
-
-    % Additional
-
-    \bibitem{transformator}
-    Bartłomiej Puget,
-    \textit{Transformator framework},
-    \url{https://github.com/Larhard/transformator},
-    2021
-
-\end{thebibliography}
+\printbibliography
 

### 2021-09-05 article/main.tex
Add fixups

@@
 \RequirePackage{svg}
+\RequirePackage{float}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \begin{center}
@@
 
+If we have sequence counting some objects and corresponding generating function, we say that this function counts the objects.
+
 \begin{example}
     \label{ex:bin_gf}
-    Having our recursive definition of the object, we can easily construct a generating function for it.
-Let's create a generating function that will count the number of full binary trees consisting of exactly \(k\) internal nodes.\todo{define sequence for the structure}
-
-\[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
-
-Note that we used \(z\) to mark internal nodes. Leaves are of size \(0\), so they are marked using \(z^0 = 1\).
+    Let's consider recursive definition of binary trees shown in Figure~\ref{fig:binary_recursion}.
+We can create a functional equation to count trees with exactly n internal nodes.
+To do so, we make internal nodes contribute to the generating function with \(z^1 = z\) and leaves with \(z^0 = 1\):
+
+\[\gf{B}(z) = 1 + z\gf{B}^2(z).\]
 
@@
 
-\[\begin{array}{rcl}
+\[\begin{array}{rclr}
         \gf{B}(z) &=& 1 + z\gf{B}^2(z)\\
                   &=& 1 + z\bigg(1 + z\gf{B}^2(z)\bigg)\bigg(1 + z\gf{B}^2(z)\bigg)\\
-                  &=& 1 + \mhl{z}\bigg(1 + \mhl{z}\Big(\mhl{1} + z\gf{B}^2(z)\Big)\Big(\mhl{1} + z\gf{B}^2(z)\Big)\bigg)\bigg(\mhl{1} + z\gf{B}^2(z)\bigg)
+                  &=& 1 + \mhl{z}\bigg(1 + \mhl{z}\Big(\mhl{1} + z\gf{B}^2(z)\Big)\Big(\mhl{1} + z\gf{B}^2(z)\Big)\bigg)\bigg(\mhl{1} + z\gf{B}^2(z)\bigg) &(*)\\
+                  &=& 1 + z\bigg(1 + z\Big(1 + z\gf{B}^2(z)\Big)\Big(1 + z\gf{B}^2(z)\Big)\bigg)\bigg(1 + z\Big(1 + z\gf{B}^2(z)\Big)\Big(1 + z\gf{B}^2(z)\Big)\bigg)\\
+                  &=& 1 + z + 2 z^2 + \bigg(2 \gf{B}^2(z) + \Big(1 + z \gf{B}^2(z)\Big)^2\bigg) z^3
 \end{array}\]
 
-The highlighted terms describe following tree:
-
+It is enough, as the term \(\bigg(2 \gf{B}^2(z) + \Big(1 + z \gf{B}^2(z)\Big)^2\bigg) z^3\) will contribute only to \(z^k\) where \(k > 2\).
+Therefore, we can see that there are \(2\) trees with exactly \(2\) internal nodes, as multiplier next to \(z^2\) is \(2\).
+
+To visualize even more, let's take a look at the line marked with \((*)\). The highlighted terms describe following tree:
+
+\begin{figure}[H]
     \begin{center}
@@
     \end{center}
+    \caption{Tree corresponding to highlighted terms in \((*)\)}
+    \label{fig:tree_corresponding_to_mhl}
+\end{figure}
+
 \end{example}
@@
 
-Most of the time we will be working with holonomic recurrences, let's introduce them.
+Since most of the time we will be working with holonomic recurrences, let's introduce them.
 
@@
     \label{def:holo_1}
-    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) there exists a holonomic recurrence for it, i.e.:
-
-\[\exists_{r \in \N} \exists_{p_0, \ldots, p_r \in \poly} \forall_{n \in \N} \sum_{i=0}^r p_i(n)a_{n+i} = 0\]
+    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) there exists a holonomic recurrence for it, i.e.
+
+\[\exists_{r \in \N} \exists_{p_0, \ldots, p_r \in \poly} \forall_{n \in \N} \sum_{i=0}^r p_i(n)a_{n+i} = 0 .\]
 \end{definition}
@@
 \begin{example}
-    The sequence \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because it satisifies:
-    \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0\]
+    The sequence \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because it satisifies
+    \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0 .\]
 \end{example}
@@
 
+\todo{Continue}
 The equivalence of these two definitions assures us that if we find generating function describing the desired objects satisfying definition\ \ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def:holo_1}~\cite{complexity}.
@@
     \label{ex:gfun-rec}
-    For generating function full binary trees defined in example\ \ref{ex:bin_gf}, i.e.:
+    For generating function full binary trees defined in Example~\ref{ex:bin_gf}, i.e.:
     \[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering

### 2021-09-05 article/main.tex
Add presuf_custom

@@
     \label{def:holo_2}
-    Equivalently to definition\ \ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists a generating function in the following form:
+    Equivalently to Definition~\ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists a generating function in the following form:
     \[\sum_{i=0}^{r} p_i(z) \gf{A}^{(i)}(z) = b(z)\]
@@
 
-\todo{Continue}
-The equivalence of these two definitions assures us that if we find generating function describing the desired objects satisfying definition\ \ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in definition\ \ref{def:holo_1}~\cite{complexity}.
+The equivalence of these two definitions assures us that if we find an generating function equation describing the desired objects satisfying Definition~\ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in Definition~\ref{def:holo_1}~\cite{complexity}.
 
@@
     \label{ex:gfun-rec}
-    For generating function full binary trees defined in Example~\ref{ex:bin_gf}, i.e.:
+    For generating function counting full binary trees defined in Example~\ref{ex:bin_gf}, i.e.:
     \[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
-    we can use GFUN~\cite{gfun} to immediately find holonomic recurrence of our interest:
+    we can use GFUN~\cite{gfun} to immediately find a holonomic recurrence of our interest:
 
@@
 
-    Our holonomic recurrence is then:
+    Our holonomic recurrence is then
     \[\left\{\begin{array}{rcl}
-                B(0) &=& 1\\
-                (2 + 4 n) B(n) + (-2 - n) B(n + 1) &=& 0
-    \end{array}\right.\]
-
-    For our purposes we will often ignore the initial conditions, as they can be easily described by the exact number of the objects.
-The most interesting part for us is the relation between the finite number consecutive elements.
-
+                b_0 &=& 1\\
+                (2 + 4 n) b_n + (-2 - n) b_{n + 1} &=& 0
+    \end{array}\right. .\]
+
+    The most interesting part for us is the relation among the finite number of consecutive elements of the sequence.
 \end{example}
@@
 For example if you know the binomial coefficient \(\binom{n}{k}\), I bet it was introduced to you as something like: "let's assume you have \(n\) distinguishable balls.
-If you want to choose \(k\) from them, then you can do it in \(\binom{n}{k}\) ways" and now, whenever you see the term \(\binom{n}{k}\) you interpret it as number of ways to choose \(k\) objects from the set of size \(n\).
+If you want to choose \(k\) from them, then you can do it in \(\binom{n}{k}\) ways" and now, whenever you see the term \(\binom{n}{k}\), you interpret it as the number of ways to choose \(k\) objects from the set of size \(n\).
 This is the combinatorial interpretation of the binomial coefficient.
 
-Holonomic recurrences are very useful if we want to count objects of given size.
-Of course, size can be defined in more complex ways, e.g.\ we may want to find the number of trees with \(n\) internal nodes having exactly \(m\) nodes being left child of its parent.
-
-Unfortunately, as for most auto-generated code, they almost never come with intuitive interpretation.
-They are just some recurrences, but there is no commonly known method to find how they correspond to the structures they describe.
-
-In the thesis we try to gather methods and results that may be helpful for anyone trying to find such interpretation, as we believe that such interpretation may give better insight into the nature of the structure and make it easier to study its behaviour.
+Holonomic recurrences are very useful if we want to count objects of a given size.
+Of course, size can be defined in more complex ways, e.g.\ we may want to find the number of binary trees with \(n\) internal nodes having exactly \(m\) nodes being left child of its parent.
+Unfortunately, there is no commonly known method to find their intuitive interpretation in the world of the objects they describe.
+
+In the thesis we try to gather methods and results that may be helpful for anyone trying to find such an interpretation, as we believe that it may give better insight into the nature of the structure and make it easier to study the structure's properties.
 
@@
 
-In order to make notation easier and unambiguous, we also introduce pre-order notation of \(n\)-ary tree.
-
-\begin{definition}
-    \(\enc{v}\) is an identifier of node \(v\). 
-\end{definition}
-
-\begin{definition}
-    Pre-order notation of \(n\)-ary tree \(T\), \(\enc{T}\), is defined recursively as:
+In the thesis, if not stated otherwise, we will be working on rooted ordered unlabeled \(n\)-ary trees. To understand the terms, let's define them:
+\begin{itemize}
+    \item rooted tree is a tree with single vertex marked as root. This allows us to define hierarchy of nodes using such terms as parent and child;
+    \item ordered trees introduce order on children from the leftmost to the rightmost;
+    \item unlabeled trees have nodes that are not distinguishable by their label.
+We will introduce soon kinds of nodes, but you shouldn't treat them as labels, but rather way to describe the structure of the node that is already present (e.g.\ we can call node with just left child an \(l\) node, but it is not its label.
+If the right child was added to the \(l\) node, it would not be an \(l\) node anymore).
+\end{itemize}
+Additionally we allow that \(n\)-ary node has some of its children unset (e.g.\ we can define a binary node with just left child set, but not right one).
+
+In order to make notation easier and unambiguous, we introduce pre-order notation of an \(n\)-ary tree.
+
+\begin{definition}
+    For single vertex \(v\), the pre-order notation is defined as \(\enc{v}\).
+\end{definition}
+
+Here, \(\enc{v}\) is defined as follows:
+\begin{itemize}
+    \item if \(v\) is an existing node, \(\enc{v} = \n\);
+    \item if \(v\) is a non-existing node (i.e.\ we describe non-existing child of some node), \(\enc{v} = \no\).
+\end{itemize}
+
+\begin{definition}
+    Pre-order notation of \(n\)-ary tree \(T\), namely \(\enc{T}\), is defined recursively as:
     \[\enc{T} = \enc{\troot(T)} \prod_{i=1}^{n} \enc{i\text{-th subtree of } \troot(T)}\]
@@
     \includesvg[scale=.7]{intro__oononnn}
-    \caption{\(\n \n \no \n \no \no \no\)}
+    \caption{Tree described in the pre-order notation as: \(\n \n \no \n \no \no \no\).}
     \label{fig:oononnn}
@@
 
-We can also define prefixes and suffixes of \(T\).
-
-\begin{definition}
-    Let \(k\) be the index of its identifier in \enc{T}. Notation of prefix of \(T\) in relation to \(v\), \(\enc{\tPre(T, v)}\), is defined as a prefix of \enc{T} of size \(k - 1\).
-\end{definition}
-
-\begin{definition}
-    Let \(n\) be the size of \enc{T}.
-Notation of suffix of \(T\) in relation to \(v\), \(\enc{\tSuf(T, v)}\), is defined as a suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
-\end{definition}
-
-Throughout thesis we define some operations using this notation. As pre-order notation is bijective, you can obtain the structure the notation describes by reversing the process of encoding.
+We use green edges 
+\begin{minipage}{1.5em}
+\includesvg[width=\textwidth]{intro__green_edge}
+\end{minipage}
+to depict edges to \(\no\) nodes.
+
+You can note that the encoding of a given tree is unique. Unfortunately, not every sequence encodes proper tree.
+
+We can also define prefixes and suffixes of \(T\) in relation to a node \(v\).
+
+\begin{definition}
+    \(\tSub(v)\) is defined as a whole subtree rooted with node \(v\).
+\end{definition}
+
+\begin{definition}
+    Let \(v\) be a node described using \(k\)-th symbol of \(\enc{T}\).
+Notation of the prefix of \(T\) in relation to \(v\), namely \(\enc{\tPre(T, v)}\), is defined as a prefix of \enc{T} of size \(k - 1\).
+\end{definition}
+
+\begin{definition}
+    Let \(n\) be the length of the sequence \(\enc{T}\).
+Notation of suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined as a suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
+\end{definition}
+
+In other words, prefix of the tree \(T\) in relation to \(v\) describes a part of the tree that appears before subtree rooted in \(v\) in pre-order notation.
+Suffix describes part of the tree that appears after it.
+
+\begin{figure}[H]
+    \centering
+    \includesvg[scale=.7]{intro__presuf_custom}
+    \caption{Visualization of prefixes and sufixes}
+    \label{fig:presuf}
+\end{figure}
+
+Throughout thesis we define some operations using this notation.
+Valid pre-order notation of \(n\)-ary tree (note that not all sequences are valid pre-order notations) can be easily translated back into a tree.
+In order to do so, we just take first symbol of the notation and create the root accordingly.
+Then for each of the \(n\) children of the root, in sequence, we decode it recursively as if it was whole tree.
+Each such operation consumes some prefix of the notation.
+At the end we should be left with no symbols in the sequence.
 
@@
 Let's define two local operations: \(R_l(T, v)\) and \(R_r(T, v)\).
-The term \textit{local} means that the operation can operate on just some finite fragment of tree with predefined size (e.g.\ node and its 2 children, but can not traverse the whole tree).
+The term \textit{local} means that the operation can operate on just some finite fragment of tree with predefined size (e.g.\ node and its 2 children, but cannot traverse the whole tree).
 
@@
     \item Vlt - virtual leaf left virtual-twinling.
-Note that from definition \ref{def:unary_binary_2}, left virtual leave can not have a sibling being an actual node.
+Note that from definition \ref{def:unary_binary_2}, left virtual leave cannot have a sibling being an actual node.
 We can divide also this case into:
@@
 
-As we can not use division to get \(\gf{T}_2(z)\), let's multiply the first equation by \(1 - \gf{T}(z)\).
+As we cannot use division to get \(\gf{T}_2(z)\), let's multiply the first equation by \(1 - \gf{T}(z)\).
 
@@
 
-where \(t'\) can be any tree and \(t''\) can not be a leaf.
+where \(t'\) can be any tree and \(t''\) cannot be a leaf.
 
@@
 \begin{itemize}
-    \item we get empty classes of the objects, e.g.\ if we analyze problem of full binary trees and define size as number of all existing nodes, we can not generate tree of even size, therefore half of our classes are empty;
+    \item we get empty classes of the objects, e.g.\ if we analyze problem of full binary trees and define size as number of all existing nodes, we cannot generate tree of even size, therefore half of our classes are empty;
     \item we want to join trees using common roots and we get many \(\pm1\) in our notes.
@@
 
-You can note that not every binary tree represents a valid term.
+You cannote that not every binary tree represents a valid term.
 
@@
 It is based on the idea that every transformation described using bijective language can be translated to a function transforming node and finite number of its surrounding nodes.
-This function can not discriminate between nodes on the grounds of their kind.
+This function cannot discriminate between nodes on the grounds of their kind.
 The only discrimination criteria that may occur may be connected to the following cases:
@@
 
-It addresses all cases from the first line, but also introduces an incorrect lambda tree in which \(s\) is the parent of \(l\), which can not happen.
+It addresses all cases from the first line, but also introduces an incorrect lambda tree in which \(s\) is the parent of \(l\), which cannot happen.
 We will fix it with the section \(2,2\) generating positive trees, which introduces one \(l\) node and one \(s\) by extending the tree with \(2\) nodes where \(s\) is parent of \(l\).

### 2021-09-05 article/main.tex
Add fixups

@@
 \newtheorem{definition}{Definition}[subsection]
+
+\theoremstyle{definition}
+\newtheorem{interpretation}{Interpretation}[subsection]
 
@@
     \includesvg[scale=.7]{intro__presuf_custom}
-    \caption{Visualization of prefixes and sufixes}
+    \caption{Visualization of prefixes, suffixes and subtrees}
     \label{fig:presuf}
@@
 
+As \(T\) and \(\enc{T}\) describe the same structures, notation of trees \(T\) and its encoding \(\enc{T}\) will be used interchangeably.
+
 \section{Known results}%
 \label{sec:known_results}
+\todo{Add introduction}
 
@@
 
-Let's start with probably the most known result, full binary trees~\cite{binary}.
-
-We define the size of a tree as a number of internal nodes (i.e.\ nodes that are not leaves). Our generating function is therefore:
+Let's start with probably the most known interpretation, full binary trees~\cite{binary}.
+
+We define the size of a tree as the number of its internal nodes (i.e.\ nodes that are not leaves). Our generating function is therefore a solution of the following equation
 
@@
 
-After a quick transformation, we get following holonomic recurrence:
-
-\[(n + 2)B(n + 1) = 2 (2n + 1)B(n)\]
-
-This recurrence also describes Catalan numbers.
+After a quick transformation, we get the following holonomic recurrence:
+
+\[\left\{\begin{array}{rcl}
+            b_0 &=& 1\\
+            (n + 2)b_{n + 1} &=& 2 (2n + 1)b_n
+\end{array}\right.\]
+
+This equation actually have \(2\) solutions, but we can eliminate one of them due to assumption that we are counting objects, i.e.\ we are interested only in solutions that give us natural numbers.
+
+Numbers defined as above are also known as Catalan numbers.
 
@@
 We will be using the term \textit{bijective language} to talk about the recurrence using the objects it describes and their transformations.
-
-Let's translate the recurrence to the bijective language then.
+\todo{rewrite}
+
+\begin{interpretation}
+Let's translate the recurrence to the bijective language.
 \begin{itemize}
-    \item \(B(n)\) is simply set of all full binary trees of size \(n\),
-    \item \((n + 2) B(n + 1)\) is set of all full binary trees of size \(n + 1\) with one of the leaves pointed,
-    \item \((2n + 1) B(n)\) is set of all full binary trees of size \(n\) with one of the nodes pointed (remember that the node can be internal node or leaf),
-    \item \(2\) at the beginning of \(2 (2n + 1) B(n)\) means that we will be using \(2\) copies of the set defined in the previous bullet.
+    \item \(b_n\) is simply the set of all full binary trees of size \(n\),
+    \item \((n + 2) b_{n + 1}\) is the set of all full binary trees of size \(n + 1\) with one of the leaves pointed,
+    \item \((2n + 1) b_{n}\) is the set of all full binary trees of size \(n\) with one of the nodes (either internal or a leaf) pointed (i.e.\ distinguished),
+    \item \(2\) at the beginning of \(2 (2n + 1) b_{n}\) indicates that we will be using \(2\) copies of the set defined in the previous bullet.
 \end{itemize}
 
-At the moment the left side of the recurrence describes a set of trees of size \(n + 1\), the right, on the other hand, of size \(n\).
-Therefore, we need to apply some transformation to make the sets equal.
-
-Let's define two local operations: \(R_l(T, v)\) and \(R_r(T, v)\).
-The term \textit{local} means that the operation can operate on just some finite fragment of tree with predefined size (e.g.\ node and its 2 children, but cannot traverse the whole tree).
+At the moment the left side of the recurrence is related to trees of size \(n + 1\), the right, on the other hand, of size \(n\). Therefore, we need to apply some transformations on trees.
+
+Let's define two local operations for tree \(T\) with a single node \(v\) pointed: \(R_l(T, v)\) and \(R_r(T, v)\).
+The term \textit{local} means that the operation can operate on just some finite fragment of a tree with predefined size (e.g.\ node and its 2 children, but cannot traverse the whole tree).
 
@@
     \(\enc{R_l(T, v)} = \enc{\tPre(T, v)} \n \pointed{\n} \no \no \enc{\tSub(v)} \enc{\tSuf(T, v)}\)
-\end{definition}
-
-\begin{definition}
-    \(\enc{R_r(T, v)} = \enc{\tPre(T, v)} \n \enc{\tSub(v)} \pointed{\n} \no \no \enc{\tSuf(T, v)} \)
 \end{definition}
@@
     \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{binary__remy_left}\end{minipage}%
-    \caption{\(\enc{R_l(T, v)}\)}
+    \caption{Visualization of \(\enc{R_l(T, v)}\)}
     \label{fig:remy_left}
 \end{figure}
+
+\begin{definition}
+    \(\enc{R_r(T, v)} = \enc{\tPre(T, v)} \n \enc{\tSub(v)} \pointed{\n} \no \no \enc{\tSuf(T, v)} \)
+\end{definition}
 
@@
     \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{binary__remy_right}\end{minipage}%
-    \caption{\(\enc{R_r(T, v)}\)}
+    \caption{Visualization of \(\enc{R_r(T, v)}\)}
     \label{fig:remy_right}
@@
 For each of such trees, \(T\) we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a node that is pointed in \(T\).
-Therefore we generate \(2(2n + 1) B(n)\) trees of size \(n + 1\)
+Therefore we generate \(2(2n + 1) B(n)\) trees of size \(n + 1\).
+\todo{rewrite}
 
@@
 
+\qed
+\end{interpretation}
+
 \subsection{Unary-binary trees}%
@@
 
-Let's think, what would have changed if we introduce unary nodes to the binary case~\cite{motzkin}. We will be counting edges. Note that a tree having \(n\) edges has exactly \(n + 1\) nodes.
-
-\begin{definition}
-    Unary-binary tree is such tree of which any node can have either 0, 1 or 2 children.
-\end{definition}
+Let's think, what would have changed if we introduce unary nodes to the binary case~\cite{motzkin}.
+
+\begin{definition}
+    \label{def:unary_binary_tree}
+    An unary-binary tree is an ordered tree in which any node can have either 0, 1 or 2 children.
+\end{definition}
+
+We do not allow nodes with gaps here, e.g.\ a binary node with just one child or unary node with no children.
+
+We will define size as number of edges. Note that a tree having \(n\) edges has exactly \(n + 1\) nodes.
 
@@
 
-And with a bit of Maple magic~\cite{gfun}, we immediately get following recurrence:
-
-\[(n + 2)U(n) = (2n + 1)U(n - 1) + 3(n - 1)U(n - 2)\]
-
-The definition above is precise, but introduces a new kind of node that we would have to take care of.
-We can avoid it by using a trick to make the tree recall binary trees.
+And with a bit of Maple magic~\cite{gfun}, we immediately get the following recurrence:
+
+\[(n + 2)u_{n} = (2n + 1)u_{n - 1} + 3(n - 1)u_{n - 2}\]
+
+\[\left\{\begin{array}{rcl}
+            u_0 &=& 1\\
+            u_1 &=& 1\\
+            (n + 2)u_{n} &=& (2n + 1)u_{n - 1} + 3(n - 1)u_{n - 2}
+\end{array}\right.\]
+
+Definition~\ref{def:unary_binary_tree} is precise, but introduces a new kind of node that we would have to take care of.
+We can avoid it by using a trick to make unary-binary trees recall binary trees.
 We do not change the structure, just the notation.
@@
     \label{def:unary_binary_2}
-    Left-leaning binary tree\todo{find official name; skewed binary tree is something different} is a binary tree with the following constraint added: if a node has a right child, it also has a left child.
-\end{definition}
-
-The bijection between unary-binary and left-leaning binary trees is very simple.
-We just represent unary nodes as nodes with just the left child of the left-leaning binary tree.
-The other cases translate immediately to corresponding ones.
-Please note that this transformation keeps the size of the tree (i.e.~number of edges).
-
-The next step is to make binary trees full. Let's just define virtual leaves.
-
-\begin{definition}
-    Virtual leaf is a virtual node added to the node in place of a non-existing child.
-\end{definition}
-
-As we have added \(n + 2\) virtual nodes, we have added as many virtual edges.
+    A left-leaning binary tree is a binary tree with the following constraint added: if a node has a right child, it also has a left child. It can have just the left child.
+\end{definition}
+
+The bijection between unary-binary trees and left-leaning binary ones is very simple.
+We just represent unary nodes as nodes with just a left child.
+The other cases translate immediately to themselves.
+Please note that this transformation preserves the size of the tree (i.e.~number of edges).
+
+The next step is to make binary trees full. Let's define virtual leaves.
+
+\begin{definition}
+    Virtual node is an artificially defined node that does not affect the structure definition (i.e.\ they are not included when counting the number of children of the node).
+\end{definition}
+
+\begin{definition}
+    Actual node is a node that is not virtual.
+\end{definition}
+
+\begin{definition}
+    A virtual leaf is a virtual node added to the node in place of a non-existing child.
+\end{definition}
+
+As we have added \(n + 2\) virtual nodes, we have added as many virtual edges.\todo{notes?}
 
@@
 
-Please note that \(n + 2\) matches the multiplier of \(U(n)\). Let's point the virtual leaves then.
-
-To present the interpretation in bijective language, we will have to introduce several types of the the nodes (you may want to revisit Section~\ref{sub:notation} Notation):
+Please note that \(n + 2\) matches the multiplier of \(u_n\) in holonomic equation. The set \((n + 2) U(n)\) corresponds to trees of size \(n\) with single virtual leaf pointed.
+
+\begin{definition}
+    We say that node \(v\) is an virtual-oneling \(\textiff\) \(v\) has no virtual siblings. Note that the root is oneling even if it has no parent.
+\end{definition}
+
+\begin{definition}
+    We say that node \(v\) is virtual-twinling \(\textiff\) \(v\) has at least one virtual sibling.
+\end{definition}
+
+\begin{definition}
+    If \(u\) is parent of \(v\), we say that sibling of \(u\) is an uncle of \(v\).
+\end{definition}
+
+\begin{interpretation}
+To present the interpretation in bijective language, we will have to introduce several types of the nodes.
 
@@
         \end{enumerate}
-    \item I - Internal node.
+    \item A - Actual node.
 \end{enumerate}
 
-Note that it covers all possible cases of pointing virtual leaf and all the cases are mutually disjoint.
-
-All we need to show are the transformations from the smaller cases, i.e.\ \(U(n-1)\) and \(U(n-2)\).
-
-Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point to any node, as in a tree having \(n - 1\) edges, we have \(n\) actual and \(n + 1\) virtual ones.
-
-In case of \(U(n-2)\), the multiplier is \(3(n-1)\), that suggests that we should perform \(3\) transformations on the trees with a pointed actual node.
+Note that it covers all possible cases of nodes and all the cases are mutually disjoint. There is no such thing as VrtUlv, VltUlv nor Vlo due to Definition~\ref{def:unary_binary_2}.
+
+All we need to show are transformations from the smaller cases, i.e.\ pointed trees from \(U(n-1)\) and \(U(n-2)\) to \(U(n)\).
+
+Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point to any node, as in a tree having \(n - 1\) actual edges, we have \(n\) actual and \(n + 1\) virtual nodes.
+
+In the case of \(U(n-2)\), the multiplier is \(3(n-1)\), which suggests that we should perform \(3\) distinct types of transformations on the trees with a pointed actual node.
+
+In the table below we show transformations that are applied to trees from \(U(n-1)\) and \(U(n-2)\) in order to achieve trees from \(U(n)\).
+We mark pointed node with \(\pointed{}\).
+You can find the case name in the buttom left corners of cells.
 
@@
         &
-        I \includesvg[scale=0.4]{unary_binary__1si} &
+        A \includesvg[scale=0.4]{unary_binary__1si} &
         \(\Rightarrow\)&
@@
 
-        I \includesvg[scale=0.4]{unary_binary__2i} &
+        A \includesvg[scale=0.4]{unary_binary__2i} &
         &
@@
 
-As you can see, we have satisfied all of the cases of \(U(n)\) with no repetitions, which concludes the construction.
+As you can see, we have satisfied all of the cases of trees from \(U(n-2)\), \(U(n-1)\) and \(U(n)\) with no repetitions, which concludes the construction.
+
+\qed
+\end{interpretation}
 
@@
 \begin{definition}
-    Schröder tree is a tree with no unary nodes.
+    \label{def:schroder_tree}
+    A Schröder tree is a tree with no unary nodes. We do not allow empty children here (e.g.\ binary node with just one child).
 \end{definition}
@@
     \(\ldots\)
-    \caption{Schröder tree node}
+    \caption{Possible cases of Schröder tree nodes}
     \label{fig:schroder_trees}
@@
 
-This definition is quite precise, but is difficult to implement as a structural recursion. Let's transform it into something more manageable, i.e.~of finite arity.
-
-\begin{definition}
-    Well-weighted binary plane tree is a weighted tree such that:
+This definition is precise, but is difficult to implement as a structural recursion. Let's define binary structure that will allow us to encode all Schröder trees.
+
+\begin{definition}
+    \label{def:well_weighted}
+    A well-weighted full binary tree is a weighted tree such that:
     \begin{itemize}
@@
         \item internal nodes can have weight either \(1\) or \(2\);
-        \item if the internal node has weight 2, then its right child is not a leaf.
+        \item if an internal node has weight 2, then its right child is not a leaf.
     \end{itemize}
@@
 
-We can easily define the bijection \(\Phi\) between these two models using pre-order notation:
+Let's represent node \(v\) with a weight \(n\) as \(v\weighted{n}\).
+
+We can easily define the bijection \(\Phi\) between models from Definition~\ref{def:schroder_tree} and~\ref{def:well_weighted} using pre-order notation:
 \[\Phi(T) = \left\{\begin{array}{lcl}
@@
 \end{array}\right.\]
+\todo{image}
+\todo{continue}
 
@@
 \begin{itemize}
-    \item \((2 n - 1) T(n)\) describes well-weighted binary plane trees of size \(n\) (i.e.\ with \(n\) leaves) with some node pointed (internal or leaf),
-    \item \((n + 1) T(n + 1)\) describes well-weighted binary plane trees of size \(n - 1\) with some leaf pointed,
-    \item \((n - 2) T(n - 1)\) describes well-weighted binary plane trees of size \(n - 1\) with some internal node pointed.
+    \item \((2 n - 1) T(n)\) describes well-weighted binary trees of size \(n\) (i.e.\ with \(n\) leaves) with some node pointed (internal or leaf),
+    \item \((n + 1) T(n + 1)\) describes well-weighted binary trees of size \(n - 1\) with some leaf pointed,
+    \item \((n - 2) T(n - 1)\) describes well-weighted binary trees of size \(n - 1\) with some internal node pointed.
 \end{itemize}

### 2021-09-06 article/main.tex
Fix known results

@@
 
-We also try to find a combinatorial interpretation of the holonomic recurrence for trees of lambda terms in the de Bruijn notation.
+We also try to find~a combinatorial interpretation of the holonomic recurrence for trees of lambda terms in the de Bruijn notation.
 
@@
 
-Every recursive structure can be described using a generating function, which can be then transformed into a holonomic recurrence.
+Every recursive structure can be described using~a generating function, which can be then transformed into~a holonomic recurrence.
 It allows us to quickly count objects of given structure with given size.
@@
 Throughout the thesis we try to accumulate known results and techniques that may help solving the problem of finding combinatorial interpretations.
-We also propose an approach that helped us to find an intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of lambda trees in the unary de Bruijn notation.
+We also propose~an approach that helped us to find~an intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of lambda trees in the unary de Bruijn notation.
 We use the de Bruijn indices in order to get rid of letter-based variable names.
@@
 
-Section~\ref{sec:brutal_iterative_approach} presents our final approach to the original problem, i.e.\ computer-aided iterative approach that allowed us to find the intermediate solution.
+Section~\ref{sec:brutal_iterative_approach} presents our final approach to the original problem, i.e.~computer-aided iterative approach that allowed us to find the intermediate solution.
 We believe that it is possible to extend this idea in order to obtain the full solution, but we were not able to achieve that due to the limited time that was available to us.
@@
 Finally, in Section~\ref{sec:further_work}, we present our view on what can be done with the problem in the future.
-We believe that one day the problem will be fully solved and a more generic approach to interpreting holonomic recurrences will emerge.
+We believe that one day the problem will be fully solved and~a more generic approach to interpreting holonomic recurrences will emerge.
 
@@
 
-e.g.\ stands for Latin exempli gratia, which means \textit{for example}.
-
-i.e.\ stands for Latin id est, which means \textit{that is}.
+e.g.~stands for Latin exempli gratia, which means \textit{for example}.
+
+i.e.~stands for Latin id est, which means \textit{that is}.
 
@@
 
-\(\poly\) is a set of all polynomials.
+\(\poly\) is~a set of all polynomials.
 
@@
 
-\(V(T)\) is implicitly defined as a set of nodes of the tree \(T\).
-
-\(E(T)\) is implicitly defined as a set of edges of the tree \(T\).
+\(V(T)\) is implicitly defined as~a set of nodes of the tree \(T\).
+
+\(E(T)\) is implicitly defined as~a set of edges of the tree \(T\).
 
@@
 
-\(e\) is implicitly assumed to be an edge.
-
-\(\troot(T)\) is implicitly defined as a root of tree \(T\).
-
-\(\tleft(v)\) is implicitly defined as a left child of node \(v\).
-
-\(\tright(v)\) is implicitly defined as a right child of node \(v\).
-
-\(\tSub(v)\) is implicitly defined as a whole subtree rooted with node \(v\).
-
-\(\tLeft(v)\) is implicitly defined as a left subtree of node \(v\).
-
-\(\tRight(v)\) is implicitly defined as a right subtree of node \(v\).
+\(e\) is implicitly assumed to be~an edge.
+
+\(\troot(T)\) is implicitly defined as~a root of tree \(T\).
+
+\(\tleft(v)\) is implicitly defined as~a left child of node \(v\).
+
+\(\tright(v)\) is implicitly defined as~a right child of node \(v\).
+
+\(\tSub(v)\) is implicitly defined as~a whole subtree rooted with node \(v\).
+
+\(\tLeft(v)\) is implicitly defined as~a left subtree of node \(v\).
+
+\(\tRight(v)\) is implicitly defined as~a right subtree of node \(v\).
 
@@
 
-Uncle of node \(v\) is defined as a sibling of the parent of \(v\).
-
-We say that node \(v\) is an oneling \(\textiff\) \(v\) has no siblings. Note that the root is oneling even if it has no parent.
+Uncle of node \(v\) is defined as~a sibling of the parent of \(v\).
+
+We say that node \(v\) is~an oneling \(\textiff\) \(v\) has no siblings. Note that the root is oneling even if it has no parent.
 
@@
 
-Leaf is a node which has no children.
-
-\(\n\) is implicitly defined as a default identifier of a node.
-
-\(\no\) is implicitly defined as an identifier of a non-existing node (e.g.\ if \(v\) is a leaf, \(\tleft(v) = \n\)).
+Leaf is~a node which has no children.
+
+\(\n\) is implicitly defined as~a default identifier of~a node.
+
+\(\no\) is implicitly defined as~an identifier of~a non-existing node (e.g.~if \(v\) is~a leaf, \(\tleft(v) = \n\)).
 
@@
 \end{minipage}
-depict edges that may or may not exist (e.g.\ when we describe transformations and we do not care if the node is root or if it has children).
+depict edges that may or may not exist (e.g.~when we describe transformations and we do not care if the node is root or if it has children).
 
@@
 
-Virtual node is an artificially defined node that does not affect the structure definition (e.g.\ we can define virtual leafs that are children of actual leaves of the binary tree.
+Virtual node is~an artificially defined node that does not affect the structure definition (e.g.~we can define virtual leafs that are children of actual leaves of the binary tree.
 Such virtual leaves are not included when counting the number of children of the node, so the actual leaves are still called leaves).
 
-Actual node is a node that is not virtual.
-
-We say that node \(v\) is an virtual-oneling \(\textiff\) \(v\) has no siblings being virtual nodes.
+Actual node is~a node that is not virtual.
+
+We say that node \(v\) is~an virtual-oneling \(\textiff\) \(v\) has no siblings being virtual nodes.
 
@@
 
-For a binary tree, we say that node \(v\) is right (left) \(\textiff\) \(v\) is a right (left) child of its parent.
-
-For a binary tree, we say that node \(v\) has a right (left) parent \(u\) \(\textiff\) \(v\) is a left (right) child of \(u\).
-
-\(\pointed{v}\) is implicitly defined as a pointed node \(v\). We can treat it as a node with an additional label \(\pointed{}\).
-
-\(v\weighted{n}\) is implicitly defined as a weighted node \(v\) with weight \(n\).
-
-\(x_i\) is implicitly assumed to be an \(i\)-th element of the sequence \(X\), where \(x\) can be any lower-case letter and \(X\) is upper-case \(x\).
-
-Calligraphic \(\gf{X}\) is implicitly assumed to be a generating function of the sequence \(X\) where \(X\) is any upper-case letter.
+For~a binary tree, we say that node \(v\) is right (left) \(\textiff\) \(v\) is~a right (left) child of its parent.
+
+For~a binary tree, we say that node \(v\) has~a right (left) parent \(u\) \(\textiff\) \(v\) is~a left (right) child of \(u\).
+
+\(\pointed{v}\) is implicitly defined as~a pointed node \(v\). We can treat it as~a node with~an additional label \(\pointed{}\).
+
+\(v\weighted{n}\) is implicitly defined as~a weighted node \(v\) with weight \(n\).
+
+\(x_i\) is implicitly assumed to be~an \(i\)-th element of the sequence \(X\), where \(x\) can be any lower-case letter and \(X\) is upper-case \(x\).
+
+Calligraphic \(\gf{X}\) is implicitly assumed to be~a generating function of the sequence \(X\) where \(X\) is any upper-case letter.
 
@@
 We will be analyzing structures that can be expressed using recursive formulas.
-For example we can define a full binary tree recursively as a node having no children (i.e.\ being a leaf) or having exactly two subtrees being full binary trees.
+For example we can define~a full binary tree recursively as~a node having no children (i.e.~being~a leaf) or having exactly two subtrees being full binary trees.
 To express the disjoint alternative in the construction rule, we use \(+\).
@@
 \begin{definition}
-The ordinary generating function of sequence \(A = (a_i)_{i=0}^{\infty}\) is defined as a formal power series:
+The ordinary generating function of sequence \(A = (a_i)_{i=0}^{\infty}\) is defined as~a formal power series:
 \[\gf{A}(z) = \sum_{i=0}^{\infty} a_i z^i .\]
@@
 
-Note that in order to compute the \(k\)-th element of the sequence, namely \(a_k\), we just need to find a constant corresponding to indeterminate \(z^k\).
+Note that in order to compute the \(k\)-th element of the sequence, namely \(a_k\), we just need to find~a constant corresponding to indeterminate \(z^k\).
 
@@
     Let's consider recursive definition of binary trees shown in Figure~\ref{fig:binary_recursion}.
-We can create a functional equation to count trees with exactly n internal nodes.
+We can create~a functional equation to count trees with exactly n internal nodes.
 To do so, we make internal nodes contribute to the generating function with \(z^1 = z\) and leaves with \(z^0 = 1\):
@@
 
-In order to get some intuition on how it works underneath, let's take a look at how we can find the number of full binary trees of size \(2\). We can expand the recurrence a bit:
+In order to get some intuition on how it works underneath, let's take~a look at how we can find the number of full binary trees of size \(2\). We can expand the recurrence~a bit:
 
@@
 
-To visualize even more, let's take a look at the line marked with \((*)\). The highlighted terms describe following tree:
+To visualize even more, let's take~a look at the line marked with \((*)\). The highlighted terms describe following tree:
 
@@
     \label{def:holo_1}
-    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) there exists a holonomic recurrence for it, i.e.
+    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) there exists~a holonomic recurrence for it, i.e.
 
@@
 
-Note that the sum can only take a finite number of subsequent elements of the sequence \(A\) into the relation.
+Note that the sum can only take~a finite number of subsequent elements of the sequence \(A\) into the relation.
 
@@
 \begin{example}
-    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic, i.e.\ none of them satisfies a linear recurrence equation with polynomial coefficients~\cite{nonholo}.
+    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic, i.e.~none of them satisfies~a linear recurrence equation with polynomial coefficients~\cite{nonholo}.
 \end{example}
@@
     \label{def:holo_2}
-    Equivalently to Definition~\ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists a generating function in the following form:
+    Equivalently to Definition~\ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists~a generating function in the following form:
     \[\sum_{i=0}^{r} p_i(z) \gf{A}^{(i)}(z) = b(z)\]
@@
 
-The equivalence of these two definitions assures us that if we find an generating function equation describing the desired objects satisfying Definition~\ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in Definition~\ref{def:holo_1}~\cite{complexity}.
+The equivalence of these two definitions assures us that if we find~an generating function equation describing the desired objects satisfying Definition~\ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in Definition~\ref{def:holo_1}~\cite{complexity}.
 
@@
     \[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
-    we can use GFUN~\cite{gfun} to immediately find a holonomic recurrence of our interest:
+    we can use GFUN~\cite{gfun} to immediately find~a holonomic recurrence of our interest:
 
@@
 
-Combinatorial interpretation is just a fancy name for something you probably know and use.
+Combinatorial interpretation is just~a fancy name for something you probably know and use.
 For example if you know the binomial coefficient \(\binom{n}{k}\), I bet it was introduced to you as something like: "let's assume you have \(n\) distinguishable balls.
@@
 
-Holonomic recurrences are very useful if we want to count objects of a given size.
-Of course, size can be defined in more complex ways, e.g.\ we may want to find the number of binary trees with \(n\) internal nodes having exactly \(m\) nodes being left child of its parent.
+Holonomic recurrences are very useful if we want to count objects of~a given size.
+Of course, size can be defined in more complex ways, e.g.~we may want to find the number of binary trees with \(n\) internal nodes having exactly \(m\) nodes being left child of its parent.
 Unfortunately, there is no commonly known method to find their intuitive interpretation in the world of the objects they describe.
 
-In the thesis we try to gather methods and results that may be helpful for anyone trying to find such an interpretation, as we believe that it may give better insight into the nature of the structure and make it easier to study the structure's properties.
+In the thesis we try to gather methods and results that may be helpful for anyone trying to find such~an interpretation, as we believe that it may give better insight into the nature of the structure and make it easier to study the structure's properties.
 
@@
 \begin{itemize}
-    \item rooted tree is a tree with single vertex marked as root. This allows us to define hierarchy of nodes using such terms as parent and child;
+    \item rooted tree is~a tree with single vertex marked as root. This allows us to define hierarchy of nodes using such terms as parent and child;
     \item ordered trees introduce order on children from the leftmost to the rightmost;
     \item unlabeled trees have nodes that are not distinguishable by their label.
-We will introduce soon kinds of nodes, but you shouldn't treat them as labels, but rather way to describe the structure of the node that is already present (e.g.\ we can call node with just left child an \(l\) node, but it is not its label.
-If the right child was added to the \(l\) node, it would not be an \(l\) node anymore).
+We will introduce soon kinds of nodes, but you shouldn't treat them as labels, but rather way to describe the structure of the node that is already present (e.g.~we can call node with just left child~an \(l\) node, but it is not its label.
+If the right child was added to the \(l\) node, it would not be~an \(l\) node anymore).
 \end{itemize}
-Additionally we allow that \(n\)-ary node has some of its children unset (e.g.\ we can define a binary node with just left child set, but not right one).
-
-In order to make notation easier and unambiguous, we introduce pre-order notation of an \(n\)-ary tree.
+Additionally we allow that \(n\)-ary node has some of its children unset (e.g.~we can define~a binary node with just left child set, but not right one).
+
+In order to make notation easier and unambiguous, we introduce pre-order notation of~an \(n\)-ary tree.
 
@@
 \begin{itemize}
-    \item if \(v\) is an existing node, \(\enc{v} = \n\);
-    \item if \(v\) is a non-existing node (i.e.\ we describe non-existing child of some node), \(\enc{v} = \no\).
+    \item if \(v\) is~an existing node, \(\enc{v} = \n\);
+    \item if \(v\) is~a non-existing node (i.e.~we describe non-existing child of some node), \(\enc{v} = \no\).
 \end{itemize}
@@
     \[\enc{T} = \enc{\troot(T)} \prod_{i=1}^{n} \enc{i\text{-th subtree of } \troot(T)}\]
-    i.e.\ catenation of the identifier of the root of the tree with encoded its subtrees from left to right.
+    i.e.~catenation of the identifier of the root of the tree with encoded its subtrees from left to right.
 \end{definition}
@@
 
-You can note that the encoding of a given tree is unique. Unfortunately, not every sequence encodes proper tree.
-
-We can also define prefixes and suffixes of \(T\) in relation to a node \(v\).
-
-\begin{definition}
-    \(\tSub(v)\) is defined as a whole subtree rooted with node \(v\).
-\end{definition}
-
-\begin{definition}
-    Let \(v\) be a node described using \(k\)-th symbol of \(\enc{T}\).
-Notation of the prefix of \(T\) in relation to \(v\), namely \(\enc{\tPre(T, v)}\), is defined as a prefix of \enc{T} of size \(k - 1\).
+You can note that the encoding of~a given tree is unique. Unfortunately, not every sequence encodes proper tree.
+
+We can also define prefixes and suffixes of \(T\) in relation to~a node \(v\).
+
+\begin{definition}
+    \(\tSub(v)\) is defined as~a whole subtree rooted with node \(v\).
+\end{definition}
+
+\begin{definition}
+    Let \(v\) be~a node described using \(k\)-th symbol of \(\enc{T}\).
+Notation of the prefix of \(T\) in relation to \(v\), namely \(\enc{\tPre(T, v)}\), is defined as~a prefix of \enc{T} of size \(k - 1\).
 \end{definition}
@@
     Let \(n\) be the length of the sequence \(\enc{T}\).
-Notation of suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined as a suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
-\end{definition}
-
-In other words, prefix of the tree \(T\) in relation to \(v\) describes a part of the tree that appears before subtree rooted in \(v\) in pre-order notation.
+Notation of suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined as~a suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
+\end{definition}
+
+In other words, prefix of the tree \(T\) in relation to \(v\) describes~a part of the tree that appears before subtree rooted in \(v\) in pre-order notation.
 Suffix describes part of the tree that appears after it.
@@
 Throughout thesis we define some operations using this notation.
-Valid pre-order notation of \(n\)-ary tree (note that not all sequences are valid pre-order notations) can be easily translated back into a tree.
+Valid pre-order notation of \(n\)-ary tree (note that not all sequences are valid pre-order notations) can be easily translated back into~a tree.
 In order to do so, we just take first symbol of the notation and create the root accordingly.
@@
 
-We define the size of a tree as the number of its internal nodes (i.e.\ nodes that are not leaves). Our generating function is therefore a solution of the following equation
+We define the size of~a tree as the number of its internal nodes (i.e.~nodes that are not leaves). Our generating function is therefore~a solution of the following equation
 
@@
 
-After a quick transformation, we get the following holonomic recurrence:
+After~a quick transformation, we get the following holonomic recurrence:
 
@@
 
-This equation actually have \(2\) solutions, but we can eliminate one of them due to assumption that we are counting objects, i.e.\ we are interested only in solutions that give us natural numbers.
+This equation actually have \(2\) solutions, but we can eliminate one of them due to assumption that we are counting objects, i.e.~we are interested only in solutions that give us natural numbers.
 
@@
 
-It is easy to see that a tree of size \(n\) (i.e.\ with \(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
+It is easy to see that~a tree of size \(n\) (i.e.~with \(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
 Analogically the tree of size \(n + 1\) has \(n + 2\) leaves and \(2n + 3\) nodes in total.
@@
 
-We are going to create a bijection between the left and right side of the recurrence.
+We are going to create~a bijection between the left and right side of the recurrence.
 We will be using the term \textit{bijective language} to talk about the recurrence using the objects it describes and their transformations.
@@
     \item \((n + 2) b_{n + 1}\) is the set of all full binary trees of size \(n + 1\) with one of the leaves pointed,
-    \item \((2n + 1) b_{n}\) is the set of all full binary trees of size \(n\) with one of the nodes (either internal or a leaf) pointed (i.e.\ distinguished),
+    \item \((2n + 1) b_{n}\) is the set of all full binary trees of size \(n\) with one of the nodes (either internal or~a leaf) pointed (i.e.~distinguished),
     \item \(2\) at the beginning of \(2 (2n + 1) b_{n}\) indicates that we will be using \(2\) copies of the set defined in the previous bullet.
@@
 
-Let's define two local operations for tree \(T\) with a single node \(v\) pointed: \(R_l(T, v)\) and \(R_r(T, v)\).
-The term \textit{local} means that the operation can operate on just some finite fragment of a tree with predefined size (e.g.\ node and its 2 children, but cannot traverse the whole tree).
+Let's define two local operations for tree \(T\) with~a single node \(v\) pointed: \(R_l(T, v)\) and \(R_r(T, v)\).
+The term \textit{local} means that the operation can operate on just some finite fragment of~a tree with predefined size (e.g.~node and its 2 children, but cannot traverse the whole tree).
 
@@
 
-We can now take the bijective interpretation of \((2n + 1) B(n)\), i.e.\ trees of size \(n\) with a single node pointed.
-For each of such trees, \(T\) we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a node that is pointed in \(T\).
+We can now take the bijective interpretation of \((2n + 1) B(n)\), i.e.~trees of size \(n\) with~a single node pointed.
+For each of such trees, \(T\) we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is~a node that is pointed in \(T\).
 Therefore we generate \(2(2n + 1) B(n)\) trees of size \(n + 1\).
@@
 
-In the second case it is enough to notice that \(R_l\) generates trees with pointed nodes being a left child, and \(R_r\) generates trees with pointed nodes being right child.
+In the second case it is enough to notice that \(R_l\) generates trees with pointed nodes being~a left child, and \(R_r\) generates trees with pointed nodes being right child.
 That immediately provides us with the conclusion that we are generating no duplicates.
@@
     \label{def:unary_binary_tree}
-    An unary-binary tree is an ordered tree in which any node can have either 0, 1 or 2 children.
-\end{definition}
-
-We do not allow nodes with gaps here, e.g.\ a binary node with just one child or unary node with no children.
-
-We will define size as number of edges. Note that a tree having \(n\) edges has exactly \(n + 1\) nodes.
+    An unary-binary tree is~an ordered tree in which any node can have either 0, 1 or 2 children.
+\end{definition}
+
+We do not allow nodes with gaps here, e.g.~a binary node with just one child or unary node with no children.
+
+We will define size as number of edges. Note that~a tree having \(n\) edges has exactly \(n + 1\) nodes.
 
@@
 
-And with a bit of Maple magic~\cite{gfun}, we immediately get the following recurrence:
+And with~a bit of Maple magic~\cite{gfun}, we immediately get the following recurrence:
 
@@
 
-Definition~\ref{def:unary_binary_tree} is precise, but introduces a new kind of node that we would have to take care of.
-We can avoid it by using a trick to make unary-binary trees recall binary trees.
+Definition~\ref{def:unary_binary_tree} is precise, but introduces~a new kind of node that we would have to take care of.
+We can avoid it by using~a trick to make unary-binary trees recall binary trees.
 We do not change the structure, just the notation.
@@
     \label{def:unary_binary_2}
-    A left-leaning binary tree is a binary tree with the following constraint added: if a node has a right child, it also has a left child. It can have just the left child.
+    A left-leaning binary tree is~a binary tree with the following constraint added: if~a node has~a right child, it also has~a left child. It can have just the left child.
 \end{definition}
@@
 The bijection between unary-binary trees and left-leaning binary ones is very simple.
-We just represent unary nodes as nodes with just a left child.
+We just represent unary nodes as nodes with just~a left child.
 The other cases translate immediately to themselves.
@@
 \begin{definition}
-    Virtual node is an artificially defined node that does not affect the structure definition (i.e.\ they are not included when counting the number of children of the node).
-\end{definition}
-
-\begin{definition}
-    Actual node is a node that is not virtual.
-\end{definition}
-
-\begin{definition}
-    A virtual leaf is a virtual node added to the node in place of a non-existing child.
+    Virtual node is~an artificially defined node that does not affect the structure definition (i.e.~they are not included when counting the number of children of the node).
+\end{definition}
+
+\begin{definition}
+    Actual node is~a node that is not virtual.
+\end{definition}
+
+\begin{definition}
+    A virtual leaf is~a virtual node added to the node in place of~a non-existing child.
 \end{definition}
@@
 \begin{definition}
-    We say that node \(v\) is an virtual-oneling \(\textiff\) \(v\) has no virtual siblings. Note that the root is oneling even if it has no parent.
+    We say that node \(v\) is~an virtual-oneling \(\textiff\) \(v\) has no virtual siblings. Note that the root is oneling even if it has no parent.
 \end{definition}
@@
 \begin{definition}
-    If \(u\) is parent of \(v\), we say that sibling of \(u\) is an uncle of \(v\).
+    If \(u\) is parent of \(v\), we say that sibling of \(u\) is~an uncle of \(v\).
 \end{definition}
@@
         \begin{enumerate}
-            \item VrtUrv - Vri which uncle is a right virtual leaf;
-            \item VrtUra - Vri which uncle is a right actual node;
-            \item VrtUla - Vri which uncle is a left actual node.
+            \item VrtUrv - Vri which uncle is~a right virtual leaf;
+            \item VrtUra - Vri which uncle is~a right actual node;
+            \item VrtUla - Vri which uncle is~a left actual node.
         \end{enumerate}
     \item Vlt - virtual leaf left virtual-twinling.
-Note that from definition \ref{def:unary_binary_2}, left virtual leave cannot have a sibling being an actual node.
+Note that from definition \ref{def:unary_binary_2}, left virtual leave cannot have~a sibling being~an actual node.
 We can divide also this case into:
         \begin{enumerate}
-            \item VltUrv - Vlt which uncle is a right virtual leaf;
-            \item VltUra - Vlt which uncle is a right actual node;
-            \item VltUla - Vlt which uncle is a left actual node;
+            \item VltUrv - Vlt which uncle is~a right virtual leaf;
+            \item VltUra - Vlt which uncle is~a right actual node;
+            \item VltUla - Vlt which uncle is~a left actual node;
         \end{enumerate}
@@
 
-All we need to show are transformations from the smaller cases, i.e.\ pointed trees from \(U(n-1)\) and \(U(n-2)\) to \(U(n)\).
-
-Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point to any node, as in a tree having \(n - 1\) actual edges, we have \(n\) actual and \(n + 1\) virtual nodes.
-
-In the case of \(U(n-2)\), the multiplier is \(3(n-1)\), which suggests that we should perform \(3\) distinct types of transformations on the trees with a pointed actual node.
+All we need to show are transformations from the smaller cases, i.e.~pointed trees from \(U(n-1)\) and \(U(n-2)\) to \(U(n)\).
+
+Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point to any node, as in~a tree having \(n - 1\) actual edges, we have \(n\) actual and \(n + 1\) virtual nodes.
+
+In the case of \(U(n-2)\), the multiplier is \(3(n-1)\), which suggests that we should perform \(3\) distinct types of transformations on the trees with~a pointed actual node.
 
@@
     \label{def:schroder_tree}
-    A Schröder tree is a tree with no unary nodes. We do not allow empty children here (e.g.\ binary node with just one child).
+    A Schröder tree is~a tree with no unary nodes. We do not allow empty children here (e.g.~binary node with just one child).
 \end{definition}
@@
 
-This definition is precise, but is difficult to implement as a structural recursion. Let's define binary structure that will allow us to encode all Schröder trees.
+This definition is precise, but is difficult to implement as~a structural recursion. Let's define binary structure that will allow us to encode all Schröder trees.
 
@@
     \label{def:well_weighted}
-    A well-weighted full binary tree is a weighted tree such that:
+    A well-weighted full binary tree is~a weighted tree such that:
     \begin{itemize}
@@
         \item internal nodes can have weight either \(1\) or \(2\);
-        \item if an internal node has weight 2, then its right child is not a leaf.
+        \item if~an internal node has weight 2, then its right child is not~a leaf.
     \end{itemize}
@@
 
-Let's represent node \(v\) with a weight \(n\) as \(v\weighted{n}\).
+Let's represent node \(v\) with~a weight \(n\) as \(v\weighted{n}\).
 
@@
 \todo{image}
-\todo{continue}
-
-Let's define size as a number of leaves. Note that the size is independent from which construction we use, as the leaf is translated to leaf and the internal node to internal nodes.
+
+Let's define the size of the tree as~a number of its leaves. As leaves is translated to leaves and internal nodes to internal nodes, the bijection \(\Phi\) is size-preserving.
 
@@
 
-To be able to use Maple to generate the recurrence, we need to transform this system of equations to a single one. We can eliminate \(\gf{T}_1(z)\) first.
+\(\gf{T}_1\) and \(\gf{T}_1\) are generating functions of trees rooted in nodes of weight \(1\) and \(2\) respectively. \(\gf{T}\) is generating function for the whole well-weighted full binary tree.
+
+To be able to use Maple to generate the corresponding recurrence, we need to transform this system of equations to~a single one. We can eliminate \(\gf{T}_1(z)\) first.
 
@@
 > algeqtodiffeq(%, T(z));
-                               2            /d      \                    2
+                               2            /d      ~                   2
     {z - 1 + (-z + 3) T(z) + (z  - 6 z + 1) |-- T(z)|, T(0) = RootOf(2 _Z  - _Z)}
@@
 
-We can also move \(T(n)\) to the other side, i.e.:
-
-\[3 (2 n - 1) T(n) = (n - 2) T(n - 1) + (n + 1) T(n + 1)\]
+We can also move \(t_n\) to the other side, i.e.:
+
+\[\left\{\begin{array}{rcl}
+            t_1 &=& 1\\
+            t_2 &=& 1\\
+            3 (2 n - 1) t_n &=& (n - 2) t_{n - 1} + (n + 1) t_{n + 1}
+\end{array}\right.\]
 
@@
 \begin{itemize}
-    \item \((2 n - 1) T(n)\) describes well-weighted binary trees of size \(n\) (i.e.\ with \(n\) leaves) with some node pointed (internal or leaf),
-    \item \((n + 1) T(n + 1)\) describes well-weighted binary trees of size \(n - 1\) with some leaf pointed,
+    \item \((2 n - 1) T(n)\) describes well-weighted binary trees of size \(n\) (i.e.~with \(n\) leaves) with some node pointed (internal or leaf),
+    \item \((n + 1) T(n + 1)\) describes well-weighted binary trees of size \(n + 1\) with some leaf pointed,
     \item \((n - 2) T(n - 1)\) describes well-weighted binary trees of size \(n - 1\) with some internal node pointed.
@@
 We will transform each tree from \((2 n - 1) T(n)\) in three ways in order to achieve all trees from \((n + 1) T(n + 1)\).
-We will get some extra ones which are not well-weighted, but we will deal with them in a minute.
-
-Let's define 3 transformations, \(L_1\), \(L_2\) and \(R_1\):
-
-\begin{center}
-    \includeinlinesvg{.16}{schroder__lr_base}%
+We will get some extra ones which are not well-weighted, but we will deal with them in~a minute.
+
+Let's define three transformations, \(L_1\), \(L_2\), and \(R_1\) that transform tree with~a pointed node \(s\) into bigger tree, as follows. We use dashed edges 
+\begin{minipage}{1.5em}
+\includesvg[width=\textwidth]{intro__dashed_edge}
+\end{minipage}
+to depict edges that may or may not exist (i.e.~when the node can have parent or child, but it does not have to). Whenewer we use solid edge, we expect this edge to actually exist.
+
+\begin{center}
+    \includeinlinescaledsvg{.16}{.5}{schroder__lr_base}%
     \(\xRightarrow{L_1}\)%
-    \includeinlinesvg{.16}{schroder__l1}%
+    \includeinlinescaledsvg{.16}{.5}{schroder__l1}%
     \hspace{.1\textwidth}%
-    \includeinlinesvg{.16}{schroder__lr_base}%
+    \includeinlinescaledsvg{.16}{.5}{schroder__lr_base}%
     \(\xRightarrow{L_2}\)%
-    \includeinlinesvg{.16}{schroder__l2}%
-
-    \includeinlinesvg{.16}{schroder__lr_base}%
+    \includeinlinescaledsvg{.16}{.5}{schroder__l2}%
+
+    \includeinlinescaledsvg{.16}{.5}{schroder__lr_base}%
     \(\xRightarrow{R_1}\)%
-    \includeinlinesvg{.16}{schroder__r1}%
-\end{center}
-
-You can see that trees generated by \(L_1\) and \(R_1\) are always well-weighted. The problem appears when applying \(L_2\) when \(s\) is a leaf.
-
-When \(s\) is a leaf, we will look at the \(s\)'s parent. It can fall into one of following cases:
+    \includeinlinescaledsvg{.16}{.5}{schroder__r1}%
+\end{center}
+
+You can see that trees generated by \(L_1\) and \(R_1\) are always well-weighted. The problem appears when applying \(L_2\) when \(s\) is~a leaf.
+
+When \(s\) is~a leaf, we will look at its parent. It can fall into one of following cases, where \(t'\) can be any tree and \(t''\) cannot be~a leaf.
 
@@
 
-where \(t'\) can be any tree and \(t''\) cannot be a leaf.
-
 When applying \(L_2\) we achieve following cases respectively:
@@
 
-In case 1.\ and 2.\ we can just swap the labels as follows:
+In case 1.~and 2.~we can just swap the labels as follows:
 
@@
 
-It is easy to show that it constructs bijection between \((n + 1) T(n + 1)\) and subset of \(\{L_1, L_2, R_1\} \times (2 n - 1) T(n)\) not falling into case 3. We will show that in a moment.
-
-To achieve trees from \((n - 2) T(n - 1)\), we can simply take trees from case 3.\ and replace whole subtree with subtree of \(t''\) with its root pointed.
+It is easy to show that it constructs a bijection between \((n + 1) T(n + 1)\) and subset of \((2 n - 1) T(n)\) with \(L_1\), \(L_2\) and \(R_1\) applied, not falling into case 3.
+We will show that in~a moment.
+
+To achieve trees from \((n - 2) T(n - 1)\), we can simply take trees from case 3.~and replace whole subtree with subtree of \(t''\) with its root pointed.
 In this way, we will lose \(2\) leaves and obtain each tree from \((n - 2) T(n - 1)\):
@@
 
-In the left column you can see all possibilities of selecting \(s\) from a tree of size \(n\).
+In the left column you can see all possibilities of selecting \(s\) from~a tree of size \(n\).
 In \(R_1\), \(L_1\) and \(L_2\) columns we show how they are then transformed.
-It covers all possible cases of selecting leaf from a tree of size \(n + 1\) and selecting an internal from a tree of size \(n - 1\).
+It covers all possible cases of selecting leaf from~a tree of size \(n + 1\) and selecting~an internal from~a tree of size \(n - 1\).
 
@@
 
-\subsection{Introduction}%
-\label{sub:introduction}
-
-As you could see in the examples above, most of the solutions are based on the simple analysis of number of leaves, internal nodes and other similar properties.
-In this section, we've gathered some methods that may be helpful when trying to analyze the problem of interpreting combinatorially some holonomic recurrence.
+As you could see in the examples above, most of the solutions are based on the simple analysis of the number of leaves, internal nodes and some of their special types.
+In this section, we will gather some methods that may be helpful when trying to analyze the problem of interpreting combinatorially some holonomic recurrences.
 
@@
     \item counting leaves,
-    \item counting null-nodes (i.e.\ children of the leaves),
+    \item counting null-nodes (i.e.~children of the leaves),
     \item counting edges.
@@
 
-It may seem counterintuitive at first, that this changes anything crucial, but with a change of the size definition, the holonomic recurrence may complicate itself drastically making the problem more difficult than it should be.
+It may seem counterintuitive at first, that this changes anything crucial, but with~a change of the size definition, the holonomic recurrence may complicate itself drastically making the problem more difficult than it should be.
 
@@
 \begin{itemize}
-    \item we get empty classes of the objects, e.g.\ if we analyze problem of full binary trees and define size as number of all existing nodes, we cannot generate tree of even size, therefore half of our classes are empty;
+    \item we get empty classes of the objects, e.g.~if we analyze problem of full binary trees and define size as number of all existing nodes, we cannot generate tree of even size, therefore half of our classes are empty;
     \item we want to join trees using common roots and we get many \(\pm1\) in our notes.
-Note that if you count internal nodes, such catenation creates a tree of size being the sum of sizes of the components increased by 1.
-If you had defined the size as the number of leaves or null-nodes, the size would be just a simple sum of the sizes of the smaller trees.
+Note that if you count internal nodes, such catenation creates~a tree of size being the sum of sizes of the components increased by 1.
+If you had defined the size as the number of leaves or null-nodes, the size would be just~a simple sum of the sizes of the smaller trees.
 \end{itemize}
@@
 
-As the most common trees are binary ones, it may be worth an effort to find some structure based on binary trees that can represent the original structure (see Section~\ref{sub:unary_binary_trees}).
+As the most common trees are binary ones, it may be worth~an effort to find some structure based on binary trees that can represent the original structure (see Section~\ref{sub:unary_binary_trees}).
 
@@
 
-Most of the time we are operating on trees with some nodes of weight \(0\) and some of weight \(1\). We may as well try to make them variable or assign some other values (e.g.\ small prime numbers).
+Most of the time we are operating on trees with some nodes of weight \(0\) and some of weight \(1\). We may as well try to make them variable or assign some other values (e.g.~small prime numbers).
 
@@
 
-Unfortunately, decreasing the size of the classes increases the number of the sizes we need to analyze to get a full result.
+Unfortunately, decreasing the size of the classes increases the number of the sizes we need to analyze to get~a full result.
 
@@
 \[\begin{array}{rcl}
-        a &:& 7\\
+       ~a &:& 7\\
         l &:& 5\\
@@
 Another method that may help finding the interpretation is inductive translation~\cite{doron}.
-The method is based on the idea that most of the time there is an easy way to find some natural induction (not necessarily holonomic) that has trivial interpretation in bijective language.
+The method is based on the idea that most of the time there is~an easy way to find some natural induction (not necessarily holonomic) that has trivial interpretation in bijective language.
 
@@
 
-The non-linear one has a very simple interpretation. We can take 2 smaller trees and join them using newly created common root.
+The non-linear one has~a very simple interpretation. We can take 2 smaller trees and join them using newly created common root.
 
@@
 
-Using our inductive hypothesis, i.e.\ holonomic recurrence and moving problematic cases out from the sums (in that case \(B(1)\) needs to be analyzed separately, as we did not define binary trees with no leaves), we can get the right side to use \(B(n - 1)\) and prove that the holonomic recurrence using non-linear one.
-The only part that is left is to translate this proof to the bijective language, which in such a simple case as binary trees is almost trivial, especially if one has seen the solution once.
+Using our inductive hypothesis, i.e.~holonomic recurrence and moving problematic cases out from the sums (in that case \(B(1)\) needs to be analyzed separately, as we did not define binary trees with no leaves), we can get the right side to use \(B(n - 1)\) and prove that the holonomic recurrence using non-linear one.
+The only part that is left is to translate this proof to the bijective language, which in such~a simple case as binary trees is almost trivial, especially if one has seen the solution once.
 
@@
 
-If all elaborate methods have failed and the problem is still too big to interpret it by hand, a computer comes in handy.
-
-As the main field of our interest was analysis of terms of lambda trees in unary de Bruijn notation, we will use it as an example to describe the method.
+If all elaborate methods have failed and the problem is still too big to interpret it by hand,~a computer comes in handy.
+
+As the main field of our interest was analysis of terms of lambda trees in unary de Bruijn notation, we will use it as~an example to describe the method.
 
@@
     \begin{itemize}
-        \item if \(x\) is a variable, \(x \in \Lambda\)
-        \item if \(M, N \in \Lambda\), then \((M N) \in \Lambda\) (application of function \(M\) to an argument \(N\))
-        \item if \(x\) is a variable and \(M \in \Lambda\), then \((\lambda x .
-M) \in \Lambda\) (abstraction, i.e.\ creating a function with an argument \(x\) and binding each occurrence of \(x\) in \(M\) to this argument)
+        \item if \(x\) is~a variable, \(x \in \Lambda\)
+        \item if \(M, N \in \Lambda\), then \((M N) \in \Lambda\) (application of function \(M\) to~an argument \(N\))
+        \item if \(x\) is~a variable and \(M \in \Lambda\), then \((\lambda x .
+M) \in \Lambda\) (abstraction, i.e.~creating~a function with~an argument \(x\) and binding each occurrence of \(x\) in \(M\) to this argument)
     \end{itemize}
@@
 The definition above is quite popular, but introduces several problems.
-One of them is a problem of potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction is the variable bound (or is it even a free variable, i.e.\ not bound).
+One of them is~a problem of potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction is the variable bound (or is it even~a free variable, i.e.~not bound).
 To address that, we can use de Bruijn indices.
@@
     \begin{itemize}
-        \item if \(n \in \N\), \(n \in \LambdadB\) (\(n\) is a variable bound to lambda abstraction \(n\) levels above)
+        \item if \(n \in \N\), \(n \in \LambdadB\) (\(n\) is~a variable bound to lambda abstraction \(n\) levels above)
         \item if \(M, N \in \LambdadB\), then \((M N) \in \LambdadB\) (application)
@@
 
-As you can see, we managed to eliminate the arbitrary variables. We can also easily check if a given variable is bound by checking its depth.
+As you can see, we managed to eliminate the arbitrary variables. We can also easily check if~a given variable is bound by checking its depth.
 
@@
 
-To simplify the interpretation, we can introduce several kinds of the nodes: \(o\), \(s\), \(l\) and \(a\). They do not change the structure, but make the reading a bit easier:
-
-\begin{definition}
-    \(o\) is a leaf.
-\end{definition}
-
-\begin{definition}
-    \(s\) is a node with only the right child.
-\end{definition}
-
-\begin{definition}
-    \(l\) is a node with only the left child.
-\end{definition}
-
-\begin{definition}
-    \(a\) is a node with both children.
+To simplify the interpretation, we can introduce several kinds of the nodes: \(o\), \(s\), \(l\) and \(a\). They do not change the structure, but make the reading~a bit easier:
+
+\begin{definition}
+    \(o\) is~a leaf.
+\end{definition}
+
+\begin{definition}
+    \(s\) is~a node with only the right child.
+\end{definition}
+
+\begin{definition}
+    \(l\) is~a node with only the left child.
+\end{definition}
+
+\begin{definition}
+    \(a\) is~a node with both children.
 \end{definition}
@@
 
-You cannote that not every binary tree represents a valid term.
+You cannote that not every binary tree represents~a valid term.
 
 \begin{example}
-    \(\n\; \no\; \n\; \n\; \no\; \no\; \no\) does not represent a valid lambda term.
+    \(\n\; \no\; \n\; \n\; \no\; \no\; \no\) does not represent~a valid lambda term.
 \end{example}
 
-To see that, we can take a look at this tree with our node kinds used:
+To see that, we can take~a look at this tree with our node kinds used:
     \[s\; \no\; l\; o\; \no\; \no\; \no\]
@@
 
-In order to make the image cleaner, we will drop the arguments of generating functions, i.e.\ \(\gf{L} := \gf{L}(z, o, l, a, s)\)
+In order to make the image cleaner, we will drop the arguments of generating functions, i.e.~\(\gf{L} := \gf{L}(z, o, l, a, s)\)
 
@@
         \begin{center}
-            \(z a \gf{L}^2\)\\
+            \(z~a \gf{L}^2\)\\
             \includesvg[scale=0.5]{lambda__def__2}%
@@
 After solving the equation for \(\gf{L'}\), we get:
-\[\gf{L} = z a \gf{L}^2 + z l \gf{L} + \frac{z o}{1 - z s}\]
-
-Using a little bit of Maple magic~\cite{gfun}, we can easily achieve the following holonomic recurrence.
+\[\gf{L} = z~a \gf{L}^2 + z l \gf{L} + \frac{z o}{1 - z s}\]
+
+Using~a little bit of Maple magic~\cite{gfun}, we can easily achieve the following holonomic recurrence.
 
@@
         0 =& (n - 4) l^2 s^2 L(n - 4)\\
-        +& ((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) L(n - 3)\\
-        +& ((-4 n + 8) a o + (n - 2) l^2 + (4 n - 6) l s + (n - 1) s^2) L(n - 2)\\
+        +& ((4 n - 10)~a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) L(n - 3)\\
+        +& ((-4 n + 8)~a o + (n - 2) l^2 + (4 n - 6) l s + (n - 1) s^2) L(n - 2)\\
         +& ((-2 n + 1) l - 2 n s) L(n - 1)\\
@@
 \begin{example}
-    \(L(n-3)\) is expanded into \(((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) L(n - 3)\).
+    \(L(n-3)\) is expanded into \(((4 n - 10)~a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) L(n - 3)\).
 \end{example}
@@
 
-We also created a framework~\cite{transformator}, called transformator, that may help visualize our work.
-It is based on the idea that every transformation described using bijective language can be translated to a function transforming node and finite number of its surrounding nodes.
+We also created~a framework~\cite{transformator}, called transformator, that may help visualize our work.
+It is based on the idea that every transformation described using bijective language can be translated to~a function transforming node and finite number of its surrounding nodes.
 This function cannot discriminate between nodes on the grounds of their kind.
@@
 \begin{itemize}
-    \item node has no children, i.e.~is a virtual leaf (which corresponds to the size of the tree, \(n\));
-    \item node has has children, i.e.~is not a virtual leaf (which corresponds to \(n - 1\));
-    \item node is a root (which corresponds to \(1\));
+    \item node has no children, i.e.~is~a virtual leaf (which corresponds to the size of the tree, \(n\));
+    \item node has has children, i.e.~is not~a virtual leaf (which corresponds to \(n - 1\));
+    \item node is~a root (which corresponds to \(1\));
     \item node has its parent on the left, i.e.~is right child of its parent;
@@
 \begin{definition}
-    Class \(T_i\) is defined as a set of transformations of trees of size \((n - i)\) into trees of size \(n\).
-\end{definition}
-
-\begin{definition}
-    Section \(T_{i,j}\) is defined as a subset of \(T_i\) adding a specific set of nodes. Webassign \(j\) according to the lexicographical order of lexicographically sorted node types.
-\end{definition}
-
-\begin{definition}
-    Part \(T_{i,j,k}\) is defined as a single transformation in section \(T_{i,j}\). \(k\) is assigned according to the order of discovering the transformation.
+    Class \(T_i\) is defined as~a set of transformations of trees of size \((n - i)\) into trees of size \(n\).
+\end{definition}
+
+\begin{definition}
+    Section \(T_{i,j}\) is defined as~a subset of \(T_i\) adding~a specific set of nodes. Webassign \(j\) according to the lexicographical order of lexicographically sorted node types.
+\end{definition}
+
+\begin{definition}
+    Part \(T_{i,j,k}\) is defined as~a single transformation in section \(T_{i,j}\). \(k\) is assigned according to the order of discovering the transformation.
 \end{definition}
@@
 \begin{definition}
-    In the context of \(T_i\), \(C_k\) is defined as \(L(n - i)\), i.e.\ number of tree transformations from \(T_i\) are working on.
-\end{definition}
-
-\begin{definition}
-    Section equation \(E_{i, j}\) is an equation defined in the context of \(T_i\) that evaluates to a total number of trees that should be generated by transformations from \(T_{i, j}\).
-\end{definition}
-
-\begin{definition}
-    Section expression \(S_{i, j}\) is a pair of section equations and a set of kinds of nodes the transformation introduces.
+    In the context of \(T_i\), \(C_k\) is defined as \(L(n - i)\), i.e.~number of tree transformations from \(T_i\) are working on.
+\end{definition}
+
+\begin{definition}
+    Section equation \(E_{i, j}\) is~an equation defined in the context of \(T_i\) that evaluates to~a total number of trees that should be generated by transformations from \(T_{i, j}\).
+\end{definition}
+
+\begin{definition}
+    Section expression \(S_{i, j}\) is~a pair of section equations and~a set of kinds of nodes the transformation introduces.
 \end{definition}
@@
 
-As we want to make our work kind of organized, we are going to divide the process into iterations. Each iteration should be a small step into the direction of solving the original problem.
+As we want to make our work kind of organized, we are going to divide the process into iterations. Each iteration should be~a small step into the direction of solving the original problem.
 
@@
 
-This statistic tells us for each section, how many trees have been generated of the expected total number of trees in that section. \verb|[x]| means that we generated enough trees for such a section.
-
-We start with interpreting \(E_{0,0} = (k + 1) C_k\). From statistics above, we see that we should generate \(16\) trees. \((k + 1)\) suggests pointing to a virtual leaf. Let's do so.
+This statistic tells us for each section, how many trees have been generated of the expected total number of trees in that section. \verb|[x]| means that we generated enough trees for such~a section.
+
+We start with interpreting \(E_{0,0} = (k + 1) C_k\). From statistics above, we see that we should generate \(16\) trees. \((k + 1)\) suggests pointing to~a virtual leaf. Let's do so.
 
@@
 
-If we take a look at more examples from class \(0\), we can start seeing some patterns:
+If we take~a look at more examples from class \(0\), we can start seeing some patterns:
 
@@
 
-The order may be a bit suggestive.
-Section \(1,0\) adds a single \(l\) node, whereas section \(1,1\) adds a single \(s\) node.
+The order may be~a bit suggestive.
+Section \(1,0\) adds~a single \(l\) node, whereas section \(1,1\) adds~a single \(s\) node.
 It actually suggests how we can try to generate the first and second line of the trees above.
@@
                                                     # l node with right virtual
-                                                    # node pointed as a parent
+                                                    # node pointed as~a parent
 )
@@
 
-It addresses all cases from the first line, but also introduces an incorrect lambda tree in which \(s\) is the parent of \(l\), which cannot happen.
+It addresses all cases from the first line, but also introduces~an incorrect lambda tree in which \(s\) is the parent of \(l\), which cannot happen.
 We will fix it with the section \(2,2\) generating positive trees, which introduces one \(l\) node and one \(s\) by extending the tree with \(2\) nodes where \(s\) is parent of \(l\).
@@
 
-Basically, for each virtual node not being root (i.e.\ having left or right parent), we point it and add \(l\) or \(s\) respectively above the parent.
+Basically, for each virtual node not being root (i.e.~having left or right parent), we point it and add \(l\) or \(s\) respectively above the parent.
 
@@
 
-For each actual vertex, we add \(a\) node as its left or right parent and add as a second child \(o\) node as its sibling.
+For each actual vertex, we add \(a\) node as its left or right parent and add as~a second child \(o\) node as its sibling.
 We then point to the left or right virtual child of the newly created \(o\) node.
@@
 
-The process can then be repeated for each section. We have chosen lexicographical order (i.e.\ \(0,0\); \(1,0\); \(1,1\); \(2,0\); \(\ldots\)).
+The process can then be repeated for each section. We have chosen lexicographical order (i.e.~\(0,0\); \(1,0\); \(1,1\); \(2,0\); \(\ldots\)).
 
@@
 
-Please note that it is only an example of missing construction. It is just the simplest one we could think about, and in that case, a simple solution is most often the correct one.
+Please note that it is only~an example of missing construction. It is just the simplest one we could think about, and in that case,~a simple solution is most often the correct one.
 
@@
 
-With the proper interpretation, it may be possible to create a sampling algorithm similar to Rémy's one for binary trees~\cite{remy,note}.
+With the proper interpretation, it may be possible to create~a sampling algorithm similar to Rémy's one for binary trees~\cite{remy,note}.
 It would have to take under consideration that some trees are being removed by other classes, so the probabilities would have to be set carefully.

### 2021-09-08 article/main.tex
Fix lambda

@@
 
-We also try to find~a combinatorial interpretation of the holonomic recurrence for trees of lambda terms in the de Bruijn notation.
+We also try to find a~combinatorial interpretation of the holonomic recurrence for trees of lambda terms in the de Bruijn notation.
 
@@
 
-Every recursive structure can be described using~a generating function, which can be then transformed into~a holonomic recurrence.
+Every recursive structure can be described using a~generating function, which can be then transformed into a~holonomic recurrence.
 It allows us to quickly count objects of given structure with given size.
@@
 Throughout the thesis we try to accumulate known results and techniques that may help solving the problem of finding combinatorial interpretations.
-We also propose~an approach that helped us to find~an intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of lambda trees in the unary de Bruijn notation.
+We also propose an~approach that helped us to find an~intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of lambda trees in the unary de Bruijn notation.
 We use the de Bruijn indices in order to get rid of letter-based variable names.
@@
 Finally, in Section~\ref{sec:further_work}, we present our view on what can be done with the problem in the future.
-We believe that one day the problem will be fully solved and~a more generic approach to interpreting holonomic recurrences will emerge.
+We believe that one day the problem will be fully solved and a~more generic approach to interpreting holonomic recurrences will emerge.
 
@@
 
-\(\poly\) is~a set of all polynomials.
+\(\poly\) is a~set of all polynomials.
 
@@
 
-\(V(T)\) is implicitly defined as~a set of nodes of the tree \(T\).
-
-\(E(T)\) is implicitly defined as~a set of edges of the tree \(T\).
+\(V(T)\) is implicitly defined as a~set of nodes of the tree \(T\).
+
+\(E(T)\) is implicitly defined as a~set of edges of the tree \(T\).
 
@@
 
-\(e\) is implicitly assumed to be~an edge.
-
-\(\troot(T)\) is implicitly defined as~a root of tree \(T\).
-
-\(\tleft(v)\) is implicitly defined as~a left child of node \(v\).
-
-\(\tright(v)\) is implicitly defined as~a right child of node \(v\).
-
-\(\tSub(v)\) is implicitly defined as~a whole subtree rooted with node \(v\).
-
-\(\tLeft(v)\) is implicitly defined as~a left subtree of node \(v\).
-
-\(\tRight(v)\) is implicitly defined as~a right subtree of node \(v\).
+\(e\) is implicitly assumed to be an~edge.
+
+\(\troot(T)\) is implicitly defined as a~root of tree \(T\).
+
+\(\tleft(v)\) is implicitly defined as a~left child of node \(v\).
+
+\(\tright(v)\) is implicitly defined as a~right child of node \(v\).
+
+\(\tSub(v)\) is implicitly defined as a~whole subtree rooted with node \(v\).
+
+\(\tLeft(v)\) is implicitly defined as a~left subtree of node \(v\).
+
+\(\tRight(v)\) is implicitly defined as a~right subtree of node \(v\).
 
@@
 
-Uncle of node \(v\) is defined as~a sibling of the parent of \(v\).
-
-We say that node \(v\) is~an oneling \(\textiff\) \(v\) has no siblings. Note that the root is oneling even if it has no parent.
+Uncle of node \(v\) is defined as a~sibling of the parent of \(v\).
+
+We say that node \(v\) is an~oneling \(\textiff\) \(v\) has no siblings. Note that the root is oneling even if it has no parent.
 
@@
 
-Leaf is~a node which has no children.
-
-\(\n\) is implicitly defined as~a default identifier of~a node.
-
-\(\no\) is implicitly defined as~an identifier of~a non-existing node (e.g.~if \(v\) is~a leaf, \(\tleft(v) = \n\)).
+Leaf is a~node which has no children.
+
+\(\n\) is implicitly defined as a~default identifier of a~node.
+
+\(\no\) is implicitly defined as an~identifier of a~non-existing node (e.g.~if \(v\) is a~leaf, \(\tleft(v) = \n\)).
 
@@
 
-Virtual node is~an artificially defined node that does not affect the structure definition (e.g.~we can define virtual leafs that are children of actual leaves of the binary tree.
+Virtual node is an~artificially defined node that does not affect the structure definition (e.g.~we can define virtual leafs that are children of actual leaves of the binary tree.
 Such virtual leaves are not included when counting the number of children of the node, so the actual leaves are still called leaves).
 
-Actual node is~a node that is not virtual.
-
-We say that node \(v\) is~an virtual-oneling \(\textiff\) \(v\) has no siblings being virtual nodes.
+Actual node is a~node that is not virtual.
+
+We say that node \(v\) is an~virtual-oneling \(\textiff\) \(v\) has no siblings being virtual nodes.
 
@@
 
-For~a binary tree, we say that node \(v\) is right (left) \(\textiff\) \(v\) is~a right (left) child of its parent.
-
-For~a binary tree, we say that node \(v\) has~a right (left) parent \(u\) \(\textiff\) \(v\) is~a left (right) child of \(u\).
-
-\(\pointed{v}\) is implicitly defined as~a pointed node \(v\). We can treat it as~a node with~an additional label \(\pointed{}\).
-
-\(v\weighted{n}\) is implicitly defined as~a weighted node \(v\) with weight \(n\).
-
-\(x_i\) is implicitly assumed to be~an \(i\)-th element of the sequence \(X\), where \(x\) can be any lower-case letter and \(X\) is upper-case \(x\).
-
-Calligraphic \(\gf{X}\) is implicitly assumed to be~a generating function of the sequence \(X\) where \(X\) is any upper-case letter.
+For a~binary tree, we say that node \(v\) is right (left) \(\textiff\) \(v\) is a~right (left) child of its parent.
+
+For a~binary tree, we say that node \(v\) has a~right (left) parent \(u\) \(\textiff\) \(v\) is a~left (right) child of \(u\).
+
+\(\pointed{v}\) is implicitly defined as a~pointed node \(v\). We can treat it as a~node with an~additional label \(\pointed{}\).
+
+\(v\weighted{n}\) is implicitly defined as a~weighted node \(v\) with weight \(n\).
+
+\(x_i\) is implicitly assumed to be an~\(i\)-th element of the sequence \(X\), where \(x\) can be any lower-case letter and \(X\) is upper-case \(x\).
+
+Calligraphic \(\gf{X}\) is implicitly assumed to be a~generating function of the sequence \(X\) where \(X\) is any upper-case letter.
 
@@
 We will be analyzing structures that can be expressed using recursive formulas.
-For example we can define~a full binary tree recursively as~a node having no children (i.e.~being~a leaf) or having exactly two subtrees being full binary trees.
+For example we can define a~full binary tree recursively as a~node having no children (i.e.~being a~leaf) or having exactly two subtrees being full binary trees.
 To express the disjoint alternative in the construction rule, we use \(+\).
@@
 \begin{definition}
-The ordinary generating function of sequence \(A = (a_i)_{i=0}^{\infty}\) is defined as~a formal power series:
+The ordinary generating function of sequence \(A = (a_i)_{i=0}^{\infty}\) is defined as a~formal power series:
 \[\gf{A}(z) = \sum_{i=0}^{\infty} a_i z^i .\]
@@
 
-Note that in order to compute the \(k\)-th element of the sequence, namely \(a_k\), we just need to find~a constant corresponding to indeterminate \(z^k\).
-
-If we have sequence counting some objects and corresponding generating function, we say that this function counts the objects.
+Note that in order to compute the \(k\)-th element of the sequence, namely \(a_k\), we just need to find a~constant corresponding to indeterminate \(z^k\).
+
+If we have a sequence counting some objects and a corresponding generating function, we say that this function counts the objects.
 
@@
     Let's consider recursive definition of binary trees shown in Figure~\ref{fig:binary_recursion}.
-We can create~a functional equation to count trees with exactly n internal nodes.
+We can create a~functional equation to count trees with exactly n internal nodes.
 To do so, we make internal nodes contribute to the generating function with \(z^1 = z\) and leaves with \(z^0 = 1\):
@@
 
-In order to get some intuition on how it works underneath, let's take~a look at how we can find the number of full binary trees of size \(2\). We can expand the recurrence~a bit:
+In order to get some intuition on how it works underneath, let's take a~look at how we can find the number of full binary trees of size \(2\). We can expand the recurrence a~bit:
 
@@
 
-To visualize even more, let's take~a look at the line marked with \((*)\). The highlighted terms describe following tree:
+To visualize even more, let's take a~look at the line marked with \((*)\). The highlighted terms describe following tree:
 
@@
     \label{def:holo_1}
-    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) there exists~a holonomic recurrence for it, i.e.
+    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) there exists a~holonomic recurrence for it, i.e.
 
@@
 
-Note that the sum can only take~a finite number of subsequent elements of the sequence \(A\) into the relation.
+Note that the sum can only take a~finite number of subsequent elements of the sequence \(A\) into the relation.
 
@@
 \begin{example}
-    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic, i.e.~none of them satisfies~a linear recurrence equation with polynomial coefficients~\cite{nonholo}.
+    Sequences \(a_n = \sqrt{n}\), \(b_n = n^n\) are \textbf{not} holonomic, i.e.~none of them satisfies a~linear recurrence equation with polynomial coefficients~\cite{nonholo}.
 \end{example}
@@
     \label{def:holo_2}
-    Equivalently to Definition~\ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists~a generating function in the following form:
+    Equivalently to Definition~\ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists a~generating function in the following form:
     \[\sum_{i=0}^{r} p_i(z) \gf{A}^{(i)}(z) = b(z)\]
@@
 
-The equivalence of these two definitions assures us that if we find~an generating function equation describing the desired objects satisfying Definition~\ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in Definition~\ref{def:holo_1}~\cite{complexity}.
+The equivalence of these two definitions assures us that if we find an~generating function equation describing the desired objects satisfying Definition~\ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in Definition~\ref{def:holo_1}~\cite{complexity}.
 
@@
     \[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
-    we can use GFUN~\cite{gfun} to immediately find~a holonomic recurrence of our interest:
+    we can use GFUN~\cite{gfun} to immediately find a~holonomic recurrence of our interest:
 
@@
 
-Combinatorial interpretation is just~a fancy name for something you probably know and use.
+Combinatorial interpretation is just a~fancy name for something you probably know and use.
 For example if you know the binomial coefficient \(\binom{n}{k}\), I bet it was introduced to you as something like: "let's assume you have \(n\) distinguishable balls.
@@
 
-Holonomic recurrences are very useful if we want to count objects of~a given size.
+Holonomic recurrences are very useful if we want to count objects of a~given size.
 Of course, size can be defined in more complex ways, e.g.~we may want to find the number of binary trees with \(n\) internal nodes having exactly \(m\) nodes being left child of its parent.
@@
 
-In the thesis we try to gather methods and results that may be helpful for anyone trying to find such~an interpretation, as we believe that it may give better insight into the nature of the structure and make it easier to study the structure's properties.
+In the thesis we try to gather methods and results that may be helpful for anyone trying to find such an~interpretation, as we believe that it may give better insight into the nature of the structure and make it easier to study the structure's properties.
 
@@
 \begin{itemize}
-    \item rooted tree is~a tree with single vertex marked as root. This allows us to define hierarchy of nodes using such terms as parent and child;
+    \item rooted tree is a~tree with single vertex marked as root. This allows us to define hierarchy of nodes using such terms as parent and child;
     \item ordered trees introduce order on children from the leftmost to the rightmost;
     \item unlabeled trees have nodes that are not distinguishable by their label.
-We will introduce soon kinds of nodes, but you shouldn't treat them as labels, but rather way to describe the structure of the node that is already present (e.g.~we can call node with just left child~an \(l\) node, but it is not its label.
-If the right child was added to the \(l\) node, it would not be~an \(l\) node anymore).
+We will introduce soon kinds of nodes, but you shouldn't treat them as labels, but rather way to describe the structure of the node that is already present (e.g.~we can call node with just left child an~\(l\) node, but it is not its label.
+If the right child was added to the \(l\) node, it would not be an~\(l\) node anymore).
 \end{itemize}
-Additionally we allow that \(n\)-ary node has some of its children unset (e.g.~we can define~a binary node with just left child set, but not right one).
-
-In order to make notation easier and unambiguous, we introduce pre-order notation of~an \(n\)-ary tree.
+Additionally we allow that \(n\)-ary node has some of its children unset (e.g.~we can define a~binary node with just left child set, but not right one).
+
+In order to make notation easier and unambiguous, we introduce pre-order notation of an~\(n\)-ary tree.
 
@@
 \begin{itemize}
-    \item if \(v\) is~an existing node, \(\enc{v} = \n\);
-    \item if \(v\) is~a non-existing node (i.e.~we describe non-existing child of some node), \(\enc{v} = \no\).
+    \item if \(v\) is an~existing node, \(\enc{v} = \n\);
+    \item if \(v\) is a~non-existing node (i.e.~we describe non-existing child of some node), \(\enc{v} = \no\).
 \end{itemize}
@@
 
-You can note that the encoding of~a given tree is unique. Unfortunately, not every sequence encodes proper tree.
-
-We can also define prefixes and suffixes of \(T\) in relation to~a node \(v\).
-
-\begin{definition}
-    \(\tSub(v)\) is defined as~a whole subtree rooted with node \(v\).
-\end{definition}
-
-\begin{definition}
-    Let \(v\) be~a node described using \(k\)-th symbol of \(\enc{T}\).
-Notation of the prefix of \(T\) in relation to \(v\), namely \(\enc{\tPre(T, v)}\), is defined as~a prefix of \enc{T} of size \(k - 1\).
+You can note that the encoding of a~given tree is unique. Unfortunately, not every sequence encodes proper tree.
+
+We can also define prefixes and suffixes of \(T\) in relation to a~node \(v\).
+
+\begin{definition}
+    \(\tSub(v)\) is defined as a~whole subtree rooted with node \(v\).
+\end{definition}
+
+\begin{definition}
+    Let \(v\) be a~node described using \(k\)-th symbol of \(\enc{T}\).
+Notation of the prefix of \(T\) in relation to \(v\), namely \(\enc{\tPre(T, v)}\), is defined as a~prefix of \enc{T} of size \(k - 1\).
 \end{definition}
@@
     Let \(n\) be the length of the sequence \(\enc{T}\).
-Notation of suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined as~a suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
-\end{definition}
-
-In other words, prefix of the tree \(T\) in relation to \(v\) describes~a part of the tree that appears before subtree rooted in \(v\) in pre-order notation.
+Notation of suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined as a~suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
+\end{definition}
+
+In other words, prefix of the tree \(T\) in relation to \(v\) describes a~part of the tree that appears before subtree rooted in \(v\) in pre-order notation.
 Suffix describes part of the tree that appears after it.
@@
 Throughout thesis we define some operations using this notation.
-Valid pre-order notation of \(n\)-ary tree (note that not all sequences are valid pre-order notations) can be easily translated back into~a tree.
+Valid pre-order notation of \(n\)-ary tree (note that not all sequences are valid pre-order notations) can be easily translated back into a~tree.
 In order to do so, we just take first symbol of the notation and create the root accordingly.
@@
 
-We define the size of~a tree as the number of its internal nodes (i.e.~nodes that are not leaves). Our generating function is therefore~a solution of the following equation
+We define the size of a~tree as the number of its internal nodes (i.e.~nodes that are not leaves). Our generating function is therefore a~solution of the following equation
 
@@
 
-After~a quick transformation, we get the following holonomic recurrence:
+After a~quick transformation, we get the following holonomic recurrence:
 
@@
 
-It is easy to see that~a tree of size \(n\) (i.e.~with \(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
+It is easy to see that a~tree of size \(n\) (i.e.~with \(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
 Analogically the tree of size \(n + 1\) has \(n + 2\) leaves and \(2n + 3\) nodes in total.
@@
 
-We are going to create~a bijection between the left and right side of the recurrence.
+We are going to create a~bijection between the left and right side of the recurrence.
 We will be using the term \textit{bijective language} to talk about the recurrence using the objects it describes and their transformations.
@@
     \item \((n + 2) b_{n + 1}\) is the set of all full binary trees of size \(n + 1\) with one of the leaves pointed,
-    \item \((2n + 1) b_{n}\) is the set of all full binary trees of size \(n\) with one of the nodes (either internal or~a leaf) pointed (i.e.~distinguished),
+    \item \((2n + 1) b_{n}\) is the set of all full binary trees of size \(n\) with one of the nodes (either internal or a~leaf) pointed (i.e.~distinguished),
     \item \(2\) at the beginning of \(2 (2n + 1) b_{n}\) indicates that we will be using \(2\) copies of the set defined in the previous bullet.
@@
 
-Let's define two local operations for tree \(T\) with~a single node \(v\) pointed: \(R_l(T, v)\) and \(R_r(T, v)\).
-The term \textit{local} means that the operation can operate on just some finite fragment of~a tree with predefined size (e.g.~node and its 2 children, but cannot traverse the whole tree).
+Let's define two local operations for tree \(T\) with a~single node \(v\) pointed: \(R_l(T, v)\) and \(R_r(T, v)\).
+The term \textit{local} means that the operation can operate on just some finite fragment of a~tree with predefined size (e.g.~node and its 2 children, but cannot traverse the whole tree).
 
@@
 
-We can now take the bijective interpretation of \((2n + 1) B(n)\), i.e.~trees of size \(n\) with~a single node pointed.
-For each of such trees, \(T\) we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is~a node that is pointed in \(T\).
+We can now take the bijective interpretation of \((2n + 1) B(n)\), i.e.~trees of size \(n\) with a~single node pointed.
+For each of such trees, \(T\) we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a~node that is pointed in \(T\).
 Therefore we generate \(2(2n + 1) B(n)\) trees of size \(n + 1\).
@@
 
-In the second case it is enough to notice that \(R_l\) generates trees with pointed nodes being~a left child, and \(R_r\) generates trees with pointed nodes being right child.
+In the second case it is enough to notice that \(R_l\) generates trees with pointed nodes being a~left child, and \(R_r\) generates trees with pointed nodes being right child.
 That immediately provides us with the conclusion that we are generating no duplicates.
@@
     \label{def:unary_binary_tree}
-    An unary-binary tree is~an ordered tree in which any node can have either 0, 1 or 2 children.
-\end{definition}
-
-We do not allow nodes with gaps here, e.g.~a binary node with just one child or unary node with no children.
-
-We will define size as number of edges. Note that~a tree having \(n\) edges has exactly \(n + 1\) nodes.
+    An unary-binary tree is an~ordered tree in which any node can have either 0, 1 or 2 children.
+\end{definition}
+
+We do not allow nodes with gaps here, e.g. a~binary node with just one child or unary node with no children.
+
+We will define size as number of edges. Note that a~tree having \(n\) edges has exactly \(n + 1\) nodes.
 
@@
 
-And with~a bit of Maple magic~\cite{gfun}, we immediately get the following recurrence:
+And with a~bit of Maple magic~\cite{gfun}, we immediately get the following recurrence:
 
@@
 
-Definition~\ref{def:unary_binary_tree} is precise, but introduces~a new kind of node that we would have to take care of.
-We can avoid it by using~a trick to make unary-binary trees recall binary trees.
+Definition~\ref{def:unary_binary_tree} is precise, but introduces a~new kind of node that we would have to take care of.
+We can avoid it by using a~trick to make unary-binary trees recall binary trees.
 We do not change the structure, just the notation.
@@
     \label{def:unary_binary_2}
-    A left-leaning binary tree is~a binary tree with the following constraint added: if~a node has~a right child, it also has~a left child. It can have just the left child.
+    A left-leaning binary tree is a~binary tree with the following constraint added: if a~node has a~right child, it also has a~left child.
+Of course a node with just a left child can appear in such tree.
 \end{definition}
@@
 The bijection between unary-binary trees and left-leaning binary ones is very simple.
-We just represent unary nodes as nodes with just~a left child.
+We just represent unary nodes as nodes with just a~left child.
 The other cases translate immediately to themselves.
@@
 \begin{definition}
-    Virtual node is~an artificially defined node that does not affect the structure definition (i.e.~they are not included when counting the number of children of the node).
-\end{definition}
-
-\begin{definition}
-    Actual node is~a node that is not virtual.
-\end{definition}
-
-\begin{definition}
-    A virtual leaf is~a virtual node added to the node in place of~a non-existing child.
+    Virtual node is an~artificially defined node that does not affect the structure definition (i.e.~they are not included when counting the number of children of the node).
+\end{definition}
+
+\begin{definition}
+    Actual node is a~node that is not virtual.
+\end{definition}
+
+\begin{definition}
+    A virtual leaf is a~virtual node added to the node in place of a~non-existing child.
 \end{definition}
@@
 
-Please note that \(n + 2\) matches the multiplier of \(u_n\) in holonomic equation. The set \((n + 2) U(n)\) corresponds to trees of size \(n\) with single virtual leaf pointed.
-
-\begin{definition}
-    We say that node \(v\) is~an virtual-oneling \(\textiff\) \(v\) has no virtual siblings. Note that the root is oneling even if it has no parent.
+Please note that \(n + 2\) matches the multiplier of \(u_n\) in holonomic equation.
+
+We will be using \(U(n)\) to describe sets of trees corresponding to \(u_n\) from the holonomic recurrence.
+The set \((n + 2) U(n)\) can be interpreted as trees of size \(n\) with single virtual leaf pointed.
+
+\begin{definition}
+    We say that node \(v\) is an~virtual-oneling \(\textiff\) \(v\) has no virtual siblings. Note that the root is an oneling even if it has no parent.
 \end{definition}
@@
 \begin{definition}
-    If \(u\) is parent of \(v\), we say that sibling of \(u\) is~an uncle of \(v\).
+    If \(u\) is parent of \(v\), we say that sibling of \(u\) is an~uncle of \(v\).
 \end{definition}
@@
         \begin{enumerate}
-            \item VrtUrv - Vri which uncle is~a right virtual leaf;
-            \item VrtUra - Vri which uncle is~a right actual node;
-            \item VrtUla - Vri which uncle is~a left actual node.
+            \item VrtUrv - Vri which uncle is a~right virtual leaf;
+            \item VrtUra - Vri which uncle is a~right actual node;
+            \item VrtUla - Vri which uncle is a~left actual node.
         \end{enumerate}
     \item Vlt - virtual leaf left virtual-twinling.
-Note that from definition \ref{def:unary_binary_2}, left virtual leave cannot have~a sibling being~an actual node.
+Note that from definition \ref{def:unary_binary_2}, left virtual leave cannot have a~sibling being an~actual node.
 We can divide also this case into:
         \begin{enumerate}
-            \item VltUrv - Vlt which uncle is~a right virtual leaf;
-            \item VltUra - Vlt which uncle is~a right actual node;
-            \item VltUla - Vlt which uncle is~a left actual node;
+            \item VltUrv - Vlt which uncle is a~right virtual leaf;
+            \item VltUra - Vlt which uncle is a~right actual node;
+            \item VltUla - Vlt which uncle is a~left actual node;
         \end{enumerate}
@@
 
-Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point to any node, as in~a tree having \(n - 1\) actual edges, we have \(n\) actual and \(n + 1\) virtual nodes.
-
-In the case of \(U(n-2)\), the multiplier is \(3(n-1)\), which suggests that we should perform \(3\) distinct types of transformations on the trees with~a pointed actual node.
+Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point to any node, as in a~tree having \(n - 1\) actual edges, we have \(n\) actual and \(n + 1\) virtual nodes.
+
+In the case of \(U(n-2)\), the multiplier is \(3(n-1)\), which suggests that we should perform \(3\) distinct types of transformations on the trees with a~pointed actual node.
 
@@
 We mark pointed node with \(\pointed{}\).
-You can find the case name in the buttom left corners of cells.
+You can find the case name in the bottom left corners of cells.
 
@@
     \label{def:schroder_tree}
-    A Schröder tree is~a tree with no unary nodes. We do not allow empty children here (e.g.~binary node with just one child).
+    A Schröder tree is a~tree with no unary nodes. Empty children are not allowed (e.g.~binary node with just one child).
 \end{definition}
@@
 
-This definition is precise, but is difficult to implement as~a structural recursion. Let's define binary structure that will allow us to encode all Schröder trees.
+This definition is precise, but is difficult to implement as a~structural recursion. Let's define binary structure that will allow us to encode all Schröder trees.
 
@@
     \label{def:well_weighted}
-    A well-weighted full binary tree is~a weighted tree such that:
+    A well-weighted full binary tree is a~weighted tree such that:
     \begin{itemize}
@@
         \item internal nodes can have weight either \(1\) or \(2\);
-        \item if~an internal node has weight 2, then its right child is not~a leaf.
+        \item if an~internal node has weight 2, then its right child is not a~leaf.
     \end{itemize}
@@
 
-Let's represent node \(v\) with~a weight \(n\) as \(v\weighted{n}\).
+Let's represent node \(v\) with a~weight \(n\) as \(v\weighted{n}\).
 
@@
 
-Let's define the size of the tree as~a number of its leaves. As leaves is translated to leaves and internal nodes to internal nodes, the bijection \(\Phi\) is size-preserving.
+Let's define the size of the tree as a~number of its leaves. As leaves are translated to leaves and internal nodes to internal nodes, the bijection \(\Phi\) is size-preserving.
 
@@
 
-\(\gf{T}_1\) and \(\gf{T}_1\) are generating functions of trees rooted in nodes of weight \(1\) and \(2\) respectively. \(\gf{T}\) is generating function for the whole well-weighted full binary tree.
-
-To be able to use Maple to generate the corresponding recurrence, we need to transform this system of equations to~a single one. We can eliminate \(\gf{T}_1(z)\) first.
+\(\gf{T}_1\) and \(\gf{T}_1\) are generating functions of trees rooted in nodes of weight \(1\) and \(2\) respectively.
+\(\gf{T}\) is a generating function for the whole well-weighted full binary tree.
+
+To be able to use Maple to generate the corresponding recurrence, we need to transform this system of equations to a~single one. We can eliminate \(\gf{T}_1(z)\) first.
 
@@
 > algeqtodiffeq(%, T(z));
-                               2            /d      ~                   2
+                               2            /d      \                   2
     {z - 1 + (-z + 3) T(z) + (z  - 6 z + 1) |-- T(z)|, T(0) = RootOf(2 _Z  - _Z)}
@@
 We will transform each tree from \((2 n - 1) T(n)\) in three ways in order to achieve all trees from \((n + 1) T(n + 1)\).
-We will get some extra ones which are not well-weighted, but we will deal with them in~a minute.
-
-Let's define three transformations, \(L_1\), \(L_2\), and \(R_1\) that transform tree with~a pointed node \(s\) into bigger tree, as follows. We use dashed edges 
+We will get some extra ones which are not well-weighted, but we will deal with them in a~minute.
+
+Let's define three transformations, \(L_1\), \(L_2\), and \(R_1\) that transform tree with a~pointed node \(s\) into bigger tree, as follows. We use dashed edges 
 \begin{minipage}{1.5em}
@@
 \end{minipage}
-to depict edges that may or may not exist (i.e.~when the node can have parent or child, but it does not have to). Whenewer we use solid edge, we expect this edge to actually exist.
+to depict edges that may or may not exist (i.e.~when the node can have parent or child, but it does not have to). Whenever we use solid edge, we expect this edge to actually exist.
 
@@
 
-You can see that trees generated by \(L_1\) and \(R_1\) are always well-weighted. The problem appears when applying \(L_2\) when \(s\) is~a leaf.
-
-When \(s\) is~a leaf, we will look at its parent. It can fall into one of following cases, where \(t'\) can be any tree and \(t''\) cannot be~a leaf.
+You can see that trees generated by \(L_1\) and \(R_1\) are always well-weighted. The problem appears when applying \(L_2\) when \(s\) is a~leaf.
+
+When \(s\) is a~leaf, we will look at its parent. It can fall into one of following cases, where \(t'\) can be any tree and \(t''\) cannot be a~leaf.
 
@@
 It is easy to show that it constructs a bijection between \((n + 1) T(n + 1)\) and subset of \((2 n - 1) T(n)\) with \(L_1\), \(L_2\) and \(R_1\) applied, not falling into case 3.
-We will show that in~a moment.
+We will show that in a~moment.
 
@@
 
-In the left column you can see all possibilities of selecting \(s\) from~a tree of size \(n\).
+In the left column you can see all possibilities of selecting \(s\) from a~tree of size \(n\).
 In \(R_1\), \(L_1\) and \(L_2\) columns we show how they are then transformed.
-It covers all possible cases of selecting leaf from~a tree of size \(n + 1\) and selecting~an internal from~a tree of size \(n - 1\).
+It covers all possible cases of selecting leaf from a~tree of size \(n + 1\) and selecting an~internal node from a~tree of size \(n - 1\).
 
@@
 
-First thing that we have to select is defining the size carefully. We have few standard choices of computing tree sizes:
+First thing to be done is to define the size carefully. We have a few standard choices for specifying the size of trees:
 \begin{itemize}
@@
     \item counting leaves,
-    \item counting null-nodes (i.e.~children of the leaves),
+    \item counting virtual leaves (i.e.~virtual nodes being children of actual leaves),
     \item counting edges.
@@
 
-It may seem counterintuitive at first, that this changes anything crucial, but with~a change of the size definition, the holonomic recurrence may complicate itself drastically making the problem more difficult than it should be.
-
-There are 2 most common symptoms that we may want to choose different method of counting the size:
+It may seem counterintuitive at first that this changes anything crucial, but the definition changes the shape of the holonomic recurrence.
+Sometimes changing the definition can drastically reduce the number of cases we have to consider.
+
+There are two most common symptoms indicating that we may want to choose a different method of counting the size:
 \begin{itemize}
-    \item we get empty classes of the objects, e.g.~if we analyze problem of full binary trees and define size as number of all existing nodes, we cannot generate tree of even size, therefore half of our classes are empty;
-    \item we want to join trees using common roots and we get many \(\pm1\) in our notes.
-Note that if you count internal nodes, such catenation creates~a tree of size being the sum of sizes of the components increased by 1.
-If you had defined the size as the number of leaves or null-nodes, the size would be just~a simple sum of the sizes of the smaller trees.
+    \item we get empty classes of objects, e.g.~if we analyze the problem of full binary trees and define the size as the number of all existing nodes, we cannot generate a tree of even size, therefore every second class is empty;
+    \item we want to join trees using a newly created node, which will become the root of the new object and our equations are getting complicated.
+For example if we define the size as the number of internal nodes, such catenation creates a~tree of size being the sum of sizes of the components increased by \(1\).
+This \(+1\) can drastically clutter the holonomic recurrence.
+If we had defined the size as the number of leaves, the size of the new object would be just a~simple sum of the sizes of the smaller trees.
 \end{itemize}
@@
 
-As the most common trees are binary ones, it may be worth~an effort to find some structure based on binary trees that can represent the original structure (see Section~\ref{sub:unary_binary_trees}).
-
-\subsection{Weights variabilization}%
+As the most common trees are binary ones, it may be worth an~effort to find some structure based on binary trees that can represent the original structure (see Section~\ref{sub:unary_binary_trees}).
+
+\subsection{Custom weights assignment}%
 \label{sub:weights_variablization}
@@
 
-This method gives us some suggestion which kind of nodes are being modified in the operation
-
-Another benefit of this method is decreasing the sizes of particular classes, so we have less objects to look at.
-
-Unfortunately, decreasing the size of the classes increases the number of the sizes we need to analyze to get~a full result.
-
+\todo{rewrite to unary-binary}
 In Section~\ref{sub:lambda_terms} we will define trees of lambda terms. If we would assign following weights to nodes:
@@
 \[\begin{array}{rcl}
-       ~a &:& 7\\
+        a~&:& 7\\
         l &:& 5\\
@@
 
-Analyzing such small cases is much easier, but on the other hand, there are many more classes that have to be considered to get full interpretation.
+This method gives us some suggestion which kind of nodes are modified in the operation
+
+Another benefit of this method is decreasing the cardinalities of sets of objects of a given size, so we have less objects to look at.
+
+Unfortunately, decreasing the cardinalities of the classes increases the number of sets we need to analyze to get a~full interpretation.
 
@@
 
-Another method that may help finding the interpretation is inductive translation~\cite{doron}.
-The method is based on the idea that most of the time there is~an easy way to find some natural induction (not necessarily holonomic) that has trivial interpretation in bijective language.
-
-For case of binary trees with size defined as number of leaves, we can define 2 recurrences:
-
-\[\text{Holonomic} := nB(n) = 2 (2n - 3)B(n - 1)\]
-\[\text{Non-linear} := B(n) = \sum_{i=1}^{n - 1} B(i) B(n - i)\]
-
-The non-linear one has~a very simple interpretation. We can take 2 smaller trees and join them using newly created common root.
-
-We can multiply both sides of Non-linear recurrence by \(n\) and break up \(n = i + (n - i)\) to get two similar sigmas:
-
-\[n B(n) = \sum_{i=1}^{n - 1} i B(i) B(n - i) + \sum_{i=1}^{n - 1} (n - i) B(n - i) B(i)\]
-
-Using our inductive hypothesis, i.e.~holonomic recurrence and moving problematic cases out from the sums (in that case \(B(1)\) needs to be analyzed separately, as we did not define binary trees with no leaves), we can get the right side to use \(B(n - 1)\) and prove that the holonomic recurrence using non-linear one.
-The only part that is left is to translate this proof to the bijective language, which in such~a simple case as binary trees is almost trivial, especially if one has seen the solution once.
+Another method that may help us finding the interpretation is inductive translation~\cite{doron}.
+The method is based on the idea that most of the time there is an~easy way to find some natural recurrence (not necessarily holonomic) that has simple interpretation in bijective language.
+
+In the case of binary trees with size defined as the number of leaves, we can define 2 recurrences:
+
+\[\text{Holonomic recurrence} : n b_{n} = 2 (2n - 3) b_{n - 1}\]
+\[\text{Non-linear recurrence} : b_{n} = \sum_{i=1}^{n - 1} b_{i} b_{n - i}\]
+
+The non-linear one has a~very simple interpretation. We can take two smaller trees and join them using a newly created common root.
+
+We can multiply both sides of non-linear recurrence by \(n\) and break up \(n = i + (n - i)\) to get two similar sums
+
+\[n b_{n} = \sum_{i=1}^{n - 1} i b_{i} b_{n - i} + \sum_{i=1}^{n - 1} (n - i) b_{n - i} b_{i}\]
+
+Using our inductive hypothesis, i.e.~holonomic recurrence and moving problematic boundary cases out from the sums (in this case \(b_{1}\) needs to be analyzed separately, as we did not define binary trees with no leaves), we can get the right side to use \(b_{n - 1}\) and prove that the holonomic recurrence using non-linear one.
+The only part that is left is to translate this inductive proof to the bijective language, which in such a~simple case as binary trees is quite simple, especially if one has seen the solution once.
 
@@
 Unfortunately, it does not give any immediate interpretation for applying the inductive step.
+\todo{fill the gaps}
+\todo{add reconstruction images}
 
@@
 
-If all elaborate methods have failed and the problem is still too big to interpret it by hand,~a computer comes in handy.
-
-As the main field of our interest was analysis of terms of lambda trees in unary de Bruijn notation, we will use it as~an example to describe the method.
+If all manual methods have failed and the problem is still too complex to interpret it by hand, a~computer comes in handy.
+
+As our inspiration and main field of interest is an analysis of trees of lambda terms in unary de Bruijn notation, we will introduce them and use them as an~example to describe the method.
 
@@
 
+\todo{add story}
+Let a countable set of variables be given.
+
 \begin{definition}
@@
     \begin{itemize}
-        \item if \(x\) is~a variable, \(x \in \Lambda\)
-        \item if \(M, N \in \Lambda\), then \((M N) \in \Lambda\) (application of function \(M\) to~an argument \(N\))
-        \item if \(x\) is~a variable and \(M \in \Lambda\), then \((\lambda x .
-M) \in \Lambda\) (abstraction, i.e.~creating~a function with~an argument \(x\) and binding each occurrence of \(x\) in \(M\) to this argument)
+        \item if \(x\) is a~variable, then \(x \in \Lambda\)
+        \item if \(M, N \in \Lambda\), then \((M N) \in \Lambda\) (it can be interpreted as an application of function \(M\) to an~argument \(N\))
+        \item if \(x\) is a~variable and \(M \in \Lambda\), then \((\lambda x .
+M) \in \Lambda\) (it can be interpreted as an~abstraction, i.e.~creating a~function with an~argument \(x\) and binding each occurrence of \(x\) in \(M\) to this argument.
+We say that variable \(x\) is abstracted by this \(lambda\)-abstraction)
     \end{itemize}
@@
 
+\todo{introduce trees}
 The definition above is quite popular, but introduces several problems.
-One of them is~a problem of potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction is the variable bound (or is it even~a free variable, i.e.~not bound).
+One of them is a~problem of a potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction the variable is bound (or is it even a~free variable, i.e.~not bound).
 To address that, we can use de Bruijn indices.
@@
     \begin{itemize}
-        \item if \(n \in \N\), \(n \in \LambdadB\) (\(n\) is~a variable bound to lambda abstraction \(n\) levels above)
+        \item if \(n \in \N\), then \(n \in \LambdadB\) (\(n\) is a~variable bound to lambda abstraction \(n\) levels above)
         \item if \(M, N \in \LambdadB\), then \((M N) \in \LambdadB\) (application)
@@
 
-As you can see, we managed to eliminate the arbitrary variables. We can also easily check if~a given variable is bound by checking its depth.
+As you can see, we managed to eliminate name-based variables. We can also easily check if a~given variable is bound by checking its depth.
 
@@
 
-It also allows us to define tree representation of the terms.
-
-\begin{definition}
-    Injection from lambda terms in de Bruijn notation to binary trees \(\Phi\) is defined as follows:
+It also allows us to define tree representation of the terms from \(\LambdadB\).
+\todo{introduce unary notation; correlation between n and the size}
+
+\begin{definition}
+    Translation from lambda terms in de Bruijn notation to binary trees \(\Phi\) is defined as follows:
     \begin{itemize}
@@
 
-To simplify the interpretation, we can introduce several kinds of the nodes: \(o\), \(s\), \(l\) and \(a\). They do not change the structure, but make the reading~a bit easier:
-
-\begin{definition}
-    \(o\) is~a leaf.
-\end{definition}
-
-\begin{definition}
-    \(s\) is~a node with only the right child.
-\end{definition}
-
-\begin{definition}
-    \(l\) is~a node with only the left child.
-\end{definition}
-
-\begin{definition}
-    \(a\) is~a node with both children.
-\end{definition}
-
-Which leads to following interpretation of \(\Phi\):
+\todo{add note about injectiveness}
+\todo{add image}
+To simplify the interpretation, we can introduce several kinds of the nodes: \(o\), \(s\), \(l\) and \(a\). They do not change the structure, but make the reading a~bit easier:
+
+\begin{definition}
+    \(o\) is a~leaf.
+\end{definition}
+
+\begin{definition}
+    \(s\) is a~node with only a right child.
+\end{definition}
+
+\begin{definition}
+    \(l\) is a~node with only a left child.
+\end{definition}
+
+\begin{definition}
+    \(a\) is a~node with both children.
+\end{definition}
+
+This leads to the following interpretation of \(\Phi\):
 
@@
 
-You cannote that not every binary tree represents~a valid term.
+You cannote that not every binary tree represents a~valid term.
 
 \begin{example}
-    \(\n\; \no\; \n\; \n\; \no\; \no\; \no\) does not represent~a valid lambda term.
+    \(\n\; \no\; \n\; \n\; \no\; \no\; \no\) does represent a~valid tree, but not a~valid lambda term.
+
+To see that, we can take a~look at this tree with our node kinds used:
+
+\todo{add image}
+\[s\; \no\; l\; o\; \no\; \no\; \no\]
+
+Here \(s\) represents the successor which can be applied only to \(n \in \N\), but is applied to the lambda-abstracted term.
 \end{example}
-
-To see that, we can take~a look at this tree with our node kinds used:
-    \[s\; \no\; l\; o\; \no\; \no\; \no\]
-
-\(s\) represents the successor which can be applied only to \(n \in \N\), but is applied to the lambda-abstracted term.
 
@@
 
-As we have our structure defined, let's create generating functions that will keep track of more than just the number of nodes, but also counts of each kind of node in the tree.
-The generating function will be parameterized then using following arguments:
+As we have our structure defined, let's create a generating function that will keep track of more than just the number of nodes, but also counts the number of each kind of node in the tree.
+The generating function \(\gf{T}(z, o, l, a, s)\) will be parameterized then using the following arguments:
 \begin{itemize}
-    \item \(z\) counting total number of virtual leaves
-    \item \(o\) counting number of bound variable nodes
-    \item \(l\) counting number of lambda abstraction nodes
-    \item \(a\) counting number of application nodes
-    \item \(s\) counting number of successors of bound variable nodes
+    \item \(z\) marking total number of virtual leaves
+    \item \(o\) marking number of variable nodes
+    \item \(l\) marking number of lambda abstraction nodes
+    \item \(a\) marking number of application nodes
+    \item \(s\) marking number of successors of variable nodes
 \end{itemize}
 
-In order to make the image cleaner, we will drop the arguments of generating functions, i.e.~\(\gf{L} := \gf{L}(z, o, l, a, s)\)
+In order to make the image cleaner, we will drop the arguments of generating functions, i.e.~\(\gf{T} := \gf{T}(z, o, l, a, s)\).
 
@@
         \begin{center}
-            \(\gf{L}\)\\
+            \(\gf{T}\)\\
             \includesvg[scale=0.5]{lambda__def__1}%
@@
         \begin{center}
-            \(z~a \gf{L}^2\)\\
+            \(z a~\gf{T}^2\)\\
             \includesvg[scale=0.5]{lambda__def__2}%
@@
         \begin{center}
-            \(z l \gf{L}\)\\
+            \(z l \gf{T}\)\\
             \includesvg[scale=0.5]{lambda__def__3}%
@@
         \begin{center}
-            \(\gf{L'}\)\\
+            \(\gf{S}\)\\
             \includesvg[scale=0.5]{lambda__def__4}%
@@
 
-where:
+where \(V\) represents part of the tree being variable (i.e.~\(o\) node, potentially with some \(s\) successor nodes applied):
 
@@
         \begin{center}
-            \(\gf{L'}\)\\
+            \(\gf{V}\)\\
             \includesvg[scale=0.5]{lambda__def__5}%
@@
         \begin{center}
-            \(z s \gf{L'}\)\\
+            \(z s \gf{V}\)\\
             \includesvg[scale=0.5]{lambda__def__4}%
@@
 
-After solving the equation for \(\gf{L'}\), we get:
-\[\gf{L} = z~a \gf{L}^2 + z l \gf{L} + \frac{z o}{1 - z s}\]
-
-Using~a little bit of Maple magic~\cite{gfun}, we can easily achieve the following holonomic recurrence.
+After solving the equation for \(\gf{V}\), we get:
+\[\gf{T} = z a~\gf{T}^2 + z l \gf{T} + \frac{z o}{1 - z s}\]
+
+If we treat \(z\) as the only variable and make \(o\), \(l\), \(a\), and \(s\) constants, we can use a~little bit of Maple magic~\cite{gfun} to achieve the following holonomic recurrence.
 
 \[\begin{array}{rl}
-        0 =& (n - 4) l^2 s^2 L(n - 4)\\
-        +& ((4 n - 10)~a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) L(n - 3)\\
-        +& ((-4 n + 8)~a o + (n - 2) l^2 + (4 n - 6) l s + (n - 1) s^2) L(n - 2)\\
-        +& ((-2 n + 1) l - 2 n s) L(n - 1)\\
-        +& (n + 1) L(n)
-\end{array}\]
-
-Appearing in the recurrence node kinds means that we extend trees of given size using nodes of that kind.
+        0 =& (n - 4) l^2 s^2 t_{n - 4}\\
+        +& ((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) t_{n - 3}\\
+        +& ((-4 n + 8) a o + (n - 2) l^2 + (4 n - 6) l s + (n - 1) s^2) t_{n - 2}\\
+        +& ((-2 n + 1) l - 2 n s) t_{n - 1}\\
+        +& (n + 1) t_{n}
+\end{array} .\]
+
+Terms \(o\), \(l\), \(a\), and \(s\) appearing in the holonomic recurrence can be interpreted as list of kinds of nodes we need to use to extend smaller tree into bigger one.
 
 \begin{example}
-    \((2n - 5) l s^2 L(n - 3)\) mean extending each tree of size \((n - 3)\) pointed in \((2n - 5)\) ways using single \(l\) node and two \(s\) nodes.
+    Let's consider one of the summands, \((2n - 5) l s^2 t_{n - 3}\).
+We can interpret it as extending trees of size \((n - 3)\).
+In total we want to have \((2n - 5) t_{n - 3}\) of them and each of them should have some node pointed (we allow duplicates).
+To extend the tree we need to use exactly one \(l\) node and two \(s\) nodes.
 \end{example}
 
-You may notice that some potentially trivial terms are more complex than they seem. If we did not count different types of nodes, we would achieve following holonomic recurrence:
+If we forget about kinds of nodes, we get following recurrence:
 
 \[\begin{array}{rl}
-        0 =& (n - 4) L(n - 4)\\
-        +& L(n - 3)\\
-        +& (2 n - 1) L(n - 2)\\
-        +& (-4 n + 1) L(n - 1)\\
-        +& (1 + n) L(n)
-\end{array}\]
-
-\begin{example}
-    \(L(n-3)\) is expanded into \(((4 n - 10)~a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) L(n - 3)\).
-\end{example}
-
-\subsection{The Transformator framework}%
+        0 =& (n - 4) t_{n - 4}\\
+        +& t_{n - 3}\\
+        +& (2 n - 1) t_{n - 2}\\
+        +& (-4 n + 1) t_{n - 1}\\
+        +& (1 + n) t_{n}
+\end{array} .\]
+
+You may notice that some summands have become oversimplified.
+For example \(((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) t_{n - 3}\) has become \(t_{n-3}\), which could be interpreted as simply set of trees of size \(n - 3\) without any pointing.
+
+\subsection{Transformator framework}%
 \label{sub:the_framework}
 
-We also created~a framework~\cite{transformator}, called transformator, that may help visualize our work.
-It is based on the idea that every transformation described using bijective language can be translated to~a function transforming node and finite number of its surrounding nodes.
-This function cannot discriminate between nodes on the grounds of their kind.
+We also created a~framework~\cite{transformator}, called Transformator, that may help visualize our work on binary trees.
+It is based on the idea that every transformation expressed in bijective language can be seen as a~function transforming some node and a finite number of its surrounding nodes.
+\todo{Fix it}This function cannot discriminate between nodes on the grounds of their kind.
 The only discrimination criteria that may occur may be connected to the following cases:
 \begin{itemize}
-    \item node has no children, i.e.~is~a virtual leaf (which corresponds to the size of the tree, \(n\));
-    \item node has has children, i.e.~is not~a virtual leaf (which corresponds to \(n - 1\));
-    \item node is~a root (which corresponds to \(1\));
+    \item node has no children, i.e.~is a~virtual leaf (which corresponds to the size of the tree, \(n\));
+    \item node has has children, i.e.~is not a~virtual leaf (which corresponds to \(n - 1\));
+    \item node is a~root (which corresponds to \(1\));
     \item node has its parent on the left, i.e.~is right child of its parent;
@@
 \end{itemize}
+\todo{Fix it}
 
@@
 
+\todo{Introduce contexts with holes}
 We will be operating on transformation classes, sections and parts. Let's define them:
@@
 \begin{definition}
-    Class \(T_i\) is defined as~a set of transformations of trees of size \((n - i)\) into trees of size \(n\).
-\end{definition}
-
-\begin{definition}
-    Section \(T_{i,j}\) is defined as~a subset of \(T_i\) adding~a specific set of nodes. Webassign \(j\) according to the lexicographical order of lexicographically sorted node types.
-\end{definition}
-
-\begin{definition}
-    Part \(T_{i,j,k}\) is defined as~a single transformation in section \(T_{i,j}\). \(k\) is assigned according to the order of discovering the transformation.
+    Class \(T_i\) is defined as a~set of transformations of trees of size \((n - i)\) into trees of size \(n\).
+\end{definition}
+
+\begin{definition}
+    Section \(T_{i,j}\) is defined as a~subset of \(T_i\) adding a~specific set of nodes. Webassign \(j\) according to the lexicographical order of lexicographically sorted node types.
+\end{definition}
+
+\begin{definition}
+    Part \(T_{i,j,k}\) is defined as a~single transformation in section \(T_{i,j}\). \(k\) is assigned according to the order of discovering the transformation.
 \end{definition}
@@
 \begin{definition}
-    In the context of \(T_i\), \(C_k\) is defined as \(L(n - i)\), i.e.~number of tree transformations from \(T_i\) are working on.
-\end{definition}
-
-\begin{definition}
-    Section equation \(E_{i, j}\) is~an equation defined in the context of \(T_i\) that evaluates to~a total number of trees that should be generated by transformations from \(T_{i, j}\).
-\end{definition}
-
-\begin{definition}
-    Section expression \(S_{i, j}\) is~a pair of section equations and~a set of kinds of nodes the transformation introduces.
+    In the context of \(T_i\), \(C_k\) is defined as \(T(n - i)\), i.e.~number of tree transformations from \(T_i\) are working on.
+\end{definition}
+
+\begin{definition}
+    Section equation \(E_{i, j}\) is an~equation defined in the context of \(T_i\) that evaluates to a~total number of trees that should be generated by transformations from \(T_{i, j}\).
+\end{definition}
+
+\begin{definition}
+    Section expression \(S_{i, j}\) is a~pair of section equations and a~set of kinds of nodes the transformation introduces.
 \end{definition}
@@
 
-As we want to make our work kind of organized, we are going to divide the process into iterations. Each iteration should be~a small step into the direction of solving the original problem.
-
-We are going to generate two kinds of trees.
-Positive and negative ones.
-When computing the total number of trees, we count positive trees as \(1\) and negative as \(-1\).
+As we want to make our work kind of organized, we are going to divide the process of finding interpretation into iterations.
+Each iteration should be a~small step into the direction of solving the original problem.
+
+We are going to generate two kinds of trees: positive and negative ones.
+When computing the total number of trees of a given size, we count positive trees as \(1\) and negative as \(-1\).
 Our goal is to generate \(E_{i, j}\) trees for each section \(T_{i, j}\).
@@
 
-This statistic tells us for each section, how many trees have been generated of the expected total number of trees in that section. \verb|[x]| means that we generated enough trees for such~a section.
-
-We start with interpreting \(E_{0,0} = (k + 1) C_k\). From statistics above, we see that we should generate \(16\) trees. \((k + 1)\) suggests pointing to~a virtual leaf. Let's do so.
+This statistic tells us for each section, how many trees have been generated of the expected total number of trees in that section. \verb|[x]| means that we generated enough trees for such a~section.
+
+We start with interpreting \(E_{0,0} = (k + 1) C_k\). From statistics above, we see that we should generate \(16\) trees. \((k + 1)\) suggests pointing to a~virtual leaf. Let's do so.
 
@@
 
-If we take~a look at more examples from class \(0\), we can start seeing some patterns:
-
-\includeinlinesvg{.33}{lambda__trees_00__2}%
-\includeinlinesvg{.33}{lambda__trees_00__3}%
-\includeinlinesvg{.33}{lambda__trees_00__7}%
-
-\includeinlinesvg{.33}{lambda__trees_00__4}%
-\includeinlinesvg{.33}{lambda__trees_00__12}%
-\includeinlinesvg{.33}{lambda__trees_00__13}%
-
-\includeinlinesvg{.16}{lambda__trees_00__0}%
-\includeinlinesvg{.16}{lambda__trees_00__1}%
-\includeinlinesvg{.16}{lambda__trees_00__5}%
-\includeinlinesvg{.16}{lambda__trees_00__6}%
-\includeinlinesvg{.16}{lambda__trees_00__14}%
-\includeinlinesvg{.16}{lambda__trees_00__15}%
-
-\includeinlinesvg{.25}{lambda__trees_00__8}%
-\includeinlinesvg{.25}{lambda__trees_00__9}%
-\includeinlinesvg{.25}{lambda__trees_00__10}%
-\includeinlinesvg{.25}{lambda__trees_00__11}%
-
-The order may be~a bit suggestive.
-Section \(1,0\) adds~a single \(l\) node, whereas section \(1,1\) adds~a single \(s\) node.
+If we take a~look at more examples from class \(0\), we can start seeing some patterns:
+
+(1)%
+\begin{minipage}{.98\textwidth}\begin{center}%
+\includeinlinescaledsvg{.33}{.4}{lambda__trees_00__2}%
+\includeinlinescaledsvg{.33}{.4}{lambda__trees_00__3}%
+\includeinlinescaledsvg{.33}{.4}{lambda__trees_00__7}%
+\end{center}\end{minipage}
+
+(2)%
+\begin{minipage}{.98\textwidth}\begin{center}%
+\includeinlinescaledsvg{.33}{.4}{lambda__trees_00__4}%
+\includeinlinescaledsvg{.33}{.4}{lambda__trees_00__12}%
+\includeinlinescaledsvg{.33}{.4}{lambda__trees_00__13}%
+\end{center}\end{minipage}
+
+(3)%
+\begin{minipage}{.98\textwidth}\begin{center}%
+\includeinlinescaledsvg{.16}{.4}{lambda__trees_00__0}%
+\includeinlinescaledsvg{.16}{.4}{lambda__trees_00__1}%
+\includeinlinescaledsvg{.16}{.4}{lambda__trees_00__5}%
+\includeinlinescaledsvg{.16}{.4}{lambda__trees_00__6}%
+\includeinlinescaledsvg{.16}{.4}{lambda__trees_00__14}%
+\includeinlinescaledsvg{.16}{.4}{lambda__trees_00__15}%
+\end{center}\end{minipage}
+
+(4)%
+\begin{minipage}{.98\textwidth}\begin{center}%
+\includeinlinescaledsvg{.25}{.4}{lambda__trees_00__8}%
+\includeinlinescaledsvg{.25}{.4}{lambda__trees_00__9}%
+\includeinlinescaledsvg{.25}{.4}{lambda__trees_00__10}%
+\includeinlinescaledsvg{.25}{.4}{lambda__trees_00__11}%
+\end{center}\end{minipage}
+
+The order may be a~bit suggestive.
+Section \(1,0\) adds a~single \(l\) node, whereas section \(1,1\) adds a~single \(s\) node.
 It actually suggests how we can try to generate the first and second line of the trees above.
 The first one is simple.
-Let's add \(l\) node with pointed right virtual node to each actual node:
+Let's add \(l\) node with pointed right virtual leaf above each actual node:
 
@@
                                                     # l node with right virtual
-                                                    # node pointed as~a parent
+                                                    # node pointed as a~parent
 )
 \end{lstlisting}
+\todo{Repeat in natural language}
 
 It creates following trees:
+\todo{Mark transformed nodes}
 
@@
 
-It addresses all cases from the first line, but also introduces~an incorrect lambda tree in which \(s\) is the parent of \(l\), which cannot happen.
+It addresses all cases from the first line, but also introduces an~incorrect lambda tree in which \(s\) is the parent of \(l\), which cannot happen.
 We will fix it with the section \(2,2\) generating positive trees, which introduces one \(l\) node and one \(s\) by extending the tree with \(2\) nodes where \(s\) is parent of \(l\).
 
-Next, we can take care of the later cases of section \(0, 0\). It can be also expressed using sections \(1, 0\) and \(1, 1\):
+Next, we can take care of next cases of section \(0, 0\). It can be also expressed using sections \(1, 0\) and \(1, 1\):
 
@@
 
-Basically, for each virtual node not being root (i.e.~having left or right parent), we point it and add \(l\) or \(s\) respectively above the parent.
+Basically, for each virtual leaf not being root (i.e.~having left or right parent), we point it and add \(l\) or \(s\) respectively above the parent.
 
@@
 
-For each actual vertex, we add \(a\) node as its left or right parent and add as~a second child \(o\) node as its sibling.
+For each actual vertex, we add \(a\) node as its left or right parent and add as a~second child \(o\) node as its sibling.
 We then point to the left or right virtual child of the newly created \(o\) node.
@@
 
-Please note that it is only~an example of missing construction. It is just the simplest one we could think about, and in that case,~a simple solution is most often the correct one.
+Please note that it is only an~example of missing construction. It is just the simplest one we could think about, and in that case, a~simple solution is most often the correct one.
 
@@
 
-With the proper interpretation, it may be possible to create~a sampling algorithm similar to Rémy's one for binary trees~\cite{remy,note}.
+With the proper interpretation, it may be possible to create a~sampling algorithm similar to Rémy's one for binary trees~\cite{remy,note}.
 It would have to take under consideration that some trees are being removed by other classes, so the probabilities would have to be set carefully.

### 2021-09-08 article/main.tex
Add more stories

@@
 \section{Overview}%
-\todo{generating functions}
-\todo{holonomic recurrences}
-\todo{publications about Motzkin, etc.}
-\todo{Lambda terms}
-\todo{zigzag free}
-
-Every recursive structure can be described using a~generating function, which can be then transformed into a~holonomic recurrence.
+
+Generating functions is a way of describing infinite sequences using formal power series, where coefficients are encoding the the consecutive elements.
+It allows us to incorporate many advanced methods of analysis of encoded objects.
+
+Every recursive structure can be described using a~generating function equation, which can be then solved and transformed into a~holonomic recurrence, i.e.~recurrence that in order to define \(n\)-th element of the sequence requires just finite number of previous ones and coefficients that are polynomials of \(n\).
+
 It allows us to quickly count objects of given structure with given size.
@@
 
-The initial inspiration for the thesis came from the publication \textit{A natural counting of lambda terms}~\cite{inspiration}, which shows bijections among seemingly different tree structures, which are lambda trees, black-white trees~\cite{blackwhite} and zigzag free trees\todo{cite}.
+Up to today only a few interpretations of holonomic recurrences on trees have been found, including interpretation of holonomic recurrences for binary trees~\cite{binary}, unary-binary trees~\cite{motzkin}, and Schröder trees~\cite{schroder}.
+Unfortunately, the mentioned interpretations do not come with a method of finding them that could be generatlized to more complex cases.
+
+The initial inspiration for the thesis came from the publication \textit{A natural counting of lambda terms}~\cite{inspiration}, which shows bijections among seemingly different tree structures, which are lambda trees, black-white trees~\cite{blackwhite} and zigzag free trees~\cite{inspiration}\todo{Find better cite}.
 They share the same holonomic recurrence, but there is no known immediate connection between the holonomic recurrence and the structures itself.
+
+Lambda terms are very popular structures used for analyzing functions and programming languages.
+Their very simple recursive definition makes them very attractive.
+Better understanding them could allow us improving programming language compilers and in consequence improve every aspect of our lives.
+The interpretation of holonomic recurrence for lambda trees itself could allow us to discover new ways of generating random lambda terms via extending smaller ones in similar way to Rémy's algorithm for sampling binary trees~\cite{remy,note}.
 
@@
 
-Next, in Section~\ref{sec:known_results}, we present known results, ie.
-binary trees, unary-binary trees and Schröder trees.
+Next, in Section~\ref{sec:known_results}, we present known results, i.e.~binary trees, unary-binary trees and Schröder trees.
 They demonstrate combinatorial interpretations that reflect different approaches.
@@
     \end{center}
-    \caption{Binary tree recursive definition}
+    \caption{Binary tree recursive definition}%
     \label{fig:binary_recursion}
@@
 \begin{definition}
-The ordinary generating function of sequence \(A = (a_i)_{i=0}^{\infty}\) is defined as a~formal power series:
-\[\gf{A}(z) = \sum_{i=0}^{\infty} a_i z^i .\]
+    The ordinary generating function of sequence \(A = {(a_i)}_{i=0}^{\infty}\) is defined as a~formal power series:
+\[\gf{A}(z) = \sum_{i=0}^{\infty} a_i z^i.\]
 \end{definition}
@@
 
-\begin{example}
+\begin{example}%
     \label{ex:bin_gf}
@@
                   &=& 1 + z\bigg(1 + z\Big(1 + z\gf{B}^2(z)\Big)\Big(1 + z\gf{B}^2(z)\Big)\bigg)\bigg(1 + z\Big(1 + z\gf{B}^2(z)\Big)\Big(1 + z\gf{B}^2(z)\Big)\bigg)\\
-                  &=& 1 + z + 2 z^2 + \bigg(2 \gf{B}^2(z) + \Big(1 + z \gf{B}^2(z)\Big)^2\bigg) z^3
+                  &=& 1 + z + 2 z^2 + \bigg(2 \gf{B}^2(z) + {\Big(1 + z \gf{B}^2(z)\Big)}^2\bigg) z^3
 \end{array}\]

### 2021-09-08 article/main.tex
Fix ALE

@@
 
-It is enough, as the term \(\bigg(2 \gf{B}^2(z) + \Big(1 + z \gf{B}^2(z)\Big)^2\bigg) z^3\) will contribute only to \(z^k\) where \(k > 2\).
+It is enough, as the term \(\bigg(2 \gf{B}^2(z) + {\Big(1 + z \gf{B}^2(z)\Big)}^2\bigg) z^3\) will contribute only to \(z^k\) where \(k > 2\).
 Therefore, we can see that there are \(2\) trees with exactly \(2\) internal nodes, as multiplier next to \(z^2\) is \(2\).
@@
     \end{center}
-    \caption{Tree corresponding to highlighted terms in \((*)\)}
+    \caption{Tree corresponding to highlighted terms in \((*)\)}%
     \label{fig:tree_corresponding_to_mhl}
@@
 
-\begin{definition}[\cite{holotoolkit}]
+\begin{definition}[\cite{holotoolkit}]%
     \label{def:holo_1}
-    An infinite sequence \(A = (a_i)_{i=0}^{\infty}\) is holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) there exists a~holonomic recurrence for it, i.e.
-
-\[\exists_{r \in \N} \exists_{p_0, \ldots, p_r \in \poly} \forall_{n \in \N} \sum_{i=0}^r p_i(n)a_{n+i} = 0 .\]
+    An infinite sequence \(A = {(a_i)}_{i=0}^{\infty}\) is holonomic (aka. P-finite, P-recursive or D-recursive) \(\textiff\) there exists a~holonomic recurrence for it, i.e.
+
+\[\exists_{r \in \N} \exists_{p_0, \ldots, p_r \in \poly} \forall_{n \in \N} \sum_{i=0}^r p_i(n)a_{n+i} = 0.\]
 \end{definition}
@@
     The sequence \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because it satisifies
-    \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0 .\]
+    \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0.\]
 \end{example}
@@
 
-\begin{definition}[\cite{complexity}]
+\begin{definition}[\cite{complexity}]%
     \label{def:holo_2}
-    Equivalently to Definition~\ref{def:holo_1}, \(A = (a_i)_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists a~generating function in the following form:
+    Equivalently to Definition~\ref{def:holo_1}, \(A = {(a_i)}_{i=0}^{\infty}\) is holonomic \(\textiff\) there exists a~generating function in the following form:
     \[\sum_{i=0}^{r} p_i(z) \gf{A}^{(i)}(z) = b(z)\]
@@
 
-\begin{example}
+\begin{example}%
     \label{ex:gfun-rec}
@@
                 (2 + 4 n) b_n + (-2 - n) b_{n + 1} &=& 0
-    \end{array}\right. .\]
+    \end{array}\right..\]
 
@@
 Combinatorial interpretation is just a~fancy name for something you probably know and use.
-For example if you know the binomial coefficient \(\binom{n}{k}\), I bet it was introduced to you as something like: "let's assume you have \(n\) distinguishable balls.
-If you want to choose \(k\) from them, then you can do it in \(\binom{n}{k}\) ways" and now, whenever you see the term \(\binom{n}{k}\), you interpret it as the number of ways to choose \(k\) objects from the set of size \(n\).
+For example if you know the binomial coefficient \(\binom{n}{k}\), I bet it was introduced to you as something like: ``let's assume you have \(n\) distinguishable balls.
+If you want to choose \(k\) from them, then you can do it in \(\binom{n}{k}\) ways'' and now, whenever you see the term \(\binom{n}{k}\), you interpret it as the number of ways to choose \(k\) objects from the set of size \(n\).
 This is the combinatorial interpretation of the binomial coefficient.
@@
     \includesvg[scale=.7]{intro__oononnn}
-    \caption{Tree described in the pre-order notation as: \(\n \n \no \n \no \no \no\).}
+    \caption{Tree described in the pre-order notation as: \(\n \n \no \n \no \no \no\).}%
     \label{fig:oononnn}
@@
     \includesvg[scale=.7]{intro__presuf_custom}
-    \caption{Visualization of prefixes, suffixes and subtrees}
+    \caption{Visualization of prefixes, suffixes and subtrees}%
     \label{fig:presuf}
@@
     \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{binary__remy_left}\end{minipage}%
-    \caption{Visualization of \(\enc{R_l(T, v)}\)}
+    \caption{Visualization of \(\enc{R_l(T, v)}\)}%
     \label{fig:remy_left}
@@
     \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{binary__remy_right}\end{minipage}%
-    \caption{Visualization of \(\enc{R_r(T, v)}\)}
+    \caption{Visualization of \(\enc{R_r(T, v)}\)}%
     \label{fig:remy_right}
@@
 
-\qed
+\qed%
 \end{interpretation}
@@
 
-\begin{definition}
+\begin{definition}%
     \label{def:unary_binary_tree}
@@
 
-We do not allow nodes with gaps here, e.g. a~binary node with just one child or unary node with no children.
+We do not allow nodes with gaps here, e.g.~a~binary node with just one child or unary node with no children.
 
@@
 
-\begin{definition}
+\begin{definition}%
     \label{def:unary_binary_2}
@@
     \includeinlinesvg{.3}{unary_binary__full}
-    \caption{Unary-binary tree to full-binary tree transformation}
+    \caption{Unary-binary tree to full-binary tree transformation}%
     \label{fig:unary_binary_transformation}
@@
 \begin{enumerate}
-    \item Vro - virtual leaf being right virtual-oneling;
-    \item Vrt - virtual leaf being right virtual-twinling. We will divide this case into:
+    \item Vro --- virtual leaf being right virtual-oneling;
+    \item Vrt --- virtual leaf being right virtual-twinling. We will divide this case into:
         \begin{enumerate}
-            \item VrtUrv - Vri which uncle is a~right virtual leaf;
-            \item VrtUra - Vri which uncle is a~right actual node;
-            \item VrtUla - Vri which uncle is a~left actual node.
+            \item VrtUrv --- Vri which uncle is a~right virtual leaf;
+            \item VrtUra --- Vri which uncle is a~right actual node;
+            \item VrtUla --- Vri which uncle is a~left actual node.
         \end{enumerate}
-    \item Vlt - virtual leaf left virtual-twinling.
-Note that from definition \ref{def:unary_binary_2}, left virtual leave cannot have a~sibling being an~actual node.
+    \item Vlt --- virtual leaf left virtual-twinling.
+Note that from definition~\ref{def:unary_binary_2}, left virtual leave cannot have a~sibling being an~actual node.
 We can divide also this case into:
         \begin{enumerate}
-            \item VltUrv - Vlt which uncle is a~right virtual leaf;
-            \item VltUra - Vlt which uncle is a~right actual node;
-            \item VltUla - Vlt which uncle is a~left actual node;
+            \item VltUrv --- Vlt which uncle is a~right virtual leaf;
+            \item VltUra --- Vlt which uncle is a~right actual node;
+            \item VltUla --- Vlt which uncle is a~left actual node;
         \end{enumerate}
-    \item A - Actual node.
+    \item A --- Actual node.
 \end{enumerate}
@@
 
-\begin{definition}
+\begin{definition}%
     \label{def:schroder_tree}
@@
     \(\ldots\)
-    \caption{Possible cases of Schröder tree nodes}
+    \caption{Possible cases of Schröder tree nodes}%
     \label{fig:schroder_trees}
@@
 
-\begin{definition}
+\begin{definition}%
     \label{def:well_weighted}
@@
         \item if \(M, N \in \Lambda\), then \((M N) \in \Lambda\) (it can be interpreted as an application of function \(M\) to an~argument \(N\))
-        \item if \(x\) is a~variable and \(M \in \Lambda\), then \((\lambda x .
+        \item if \(x\) is a~variable and \(M \in \Lambda\), then \((\lambda x.
 M) \in \Lambda\) (it can be interpreted as an~abstraction, i.e.~creating a~function with an~argument \(x\) and binding each occurrence of \(x\) in \(M\) to this argument.
@@
 \begin{example}
-    \(\lambda x . \lambda y . x\) is equivalent to \(\lambda \lambda 1\)
+    \(\lambda x.\lambda y.x\) is equivalent to \(\lambda \lambda 1\)
 \end{example}
@@
 \begin{example}
-    \(\lambda x . (\lambda y . x) (\lambda y . y)\) is equivalent to \(\lambda (\lambda 1) (\lambda 0)\)
+    \(\lambda x. (\lambda y.x) (\lambda y.y)\) is equivalent to \(\lambda (\lambda 1) (\lambda 0)\)
 \end{example}
@@
         +& (n + 1) t_{n}
-\end{array} .\]
+\end{array}.\]
 
@@
         +& (1 + n) t_{n}
-\end{array} .\]
+\end{array}.\]
 
@@
 
-\printbibliography
+\printbibliography%
 

### 2021-09-08 article/main.tex
Spellcheck

@@
 Up to today only a few interpretations of holonomic recurrences on trees have been found, including interpretation of holonomic recurrences for binary trees~\cite{binary}, unary-binary trees~\cite{motzkin}, and Schröder trees~\cite{schroder}.
-Unfortunately, the mentioned interpretations do not come with a method of finding them that could be generatlized to more complex cases.
+Unfortunately, the mentioned interpretations do not come with a method of finding them that could be generalized to more complex cases.
 
@@
 
-In Section~\ref{sec:introduction} we establish notation nad introduce concepts that will be used throughout the thesis.
+In Section~\ref{sec:introduction} we establish notation and introduce concepts that will be used throughout the thesis.
 
@@
 \begin{example}
-    The sequence \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because it satisifies
+    The sequence \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because it satisfies
     \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0.\]
@@
         \end{enumerate}
-    \item A --- Actual node.
+    \item A --- actual node.
 \end{enumerate}
@@
 
-You cannote that not every binary tree represents a~valid term.
+You can note that not every binary tree represents a~valid term.
 
@@
 \begin{definition}
-    Section \(T_{i,j}\) is defined as a~subset of \(T_i\) adding a~specific set of nodes. Webassign \(j\) according to the lexicographical order of lexicographically sorted node types.
+    Section \(T_{i,j}\) is defined as a~subset of \(T_i\) adding a~specific set of nodes. We assign \(j\) according to the lexicographical order of lexicographically sorted node types.
 \end{definition}

### 2021-09-08 article/main.tex
Fix typo in lstlisting

@@
                                                     # l node with right virtual
-                                                    # node pointed as a~parent
+                                                    # node pointed as a parent
 )

### 2021-09-09 article/main.tex
Minor fix

@@
 
-Next, in Section~\ref{sec:known_results}, we present known results, i.e.~binary trees, unary-binary trees and Schröder trees.
-They demonstrate combinatorial interpretations that reflect different approaches.
+Next, in Section~\ref{sec:known_results}, we present known results, i.e.~interpretations for binary trees, unary-binary trees and Schröder trees.
+They demonstrate few different approaches to the problem.
 

### 2021-09-12 article/main.tex
Add contexts

@@
 \newcommand{\mhl}[1]{{\tikzmarkin[set fill color=red!30,set border color=red]{highlight-\arabic{highlightid}}(0.02,-0.15)(-0.02,0.35){#1}\tikzmarkend{highlight-\arabic{highlightid}}\stepcounter{highlightid}}}
+\newcommand{\mhll}[1]{{\tikzmarkin[set fill color=red!30,set border color=red]{highlight-\arabic{highlightid}}(0.15,-0.15)(-0.15,0.35){#1}\tikzmarkend{highlight-\arabic{highlightid}}\stepcounter{highlightid}}}
 
@@
     \end{center}
-    \caption{Binary tree recursive definition}%
+    \caption{Binary tree recursive definition.}%
     \label{fig:binary_recursion}
@@
     \end{center}
-    \caption{Tree corresponding to highlighted terms in \((*)\)}%
+    \caption{Tree corresponding to highlighted terms in \((*)\).}%
     \label{fig:tree_corresponding_to_mhl}
@@
 \label{sec:known_results}
-\todo{Add introduction}
+
+In this section we show combinatorial interpretations of holonomic recurrences for binary trees, unary-binary trees and Schröder trees.
+As to our knowledge these are only tree classes that have commonly known interpretations.
+Also the thought process leading to these interpretations is not obvious.
+
+Each of these interpretations has its unique character, like different selection of the size definition or different approach to arranging the terms of the holonomic recurrence.
+
+These interpretations have been source of ideas that that we were incorporating in order to make our partial interpretation for the case of lambda trees in unary de Bruijn notation.
 
@@
 
-\todo{add story}
+Lambda calculus is a formal system that allows expressing computable functions introduced by Alonzo Church.
+It is widely used in computer science and mathematics to study functions and their properties.
+
 Let a countable set of variables be given.
@@
 M) \in \Lambda\) (it can be interpreted as an~abstraction, i.e.~creating a~function with an~argument \(x\) and binding each occurrence of \(x\) in \(M\) to this argument.
-We say that variable \(x\) is abstracted by this \(lambda\)-abstraction)
+We say that variable \(x\) is abstracted by this lambda-abstraction)
     \end{itemize}
@@
 
-\todo{introduce trees}
-The definition above is quite popular, but introduces several problems.
-One of them is a~problem of a potential collision of lambda-abstracted variables and difficulty of finding to which lambda abstraction the variable is bound (or is it even a~free variable, i.e.~not bound).
+This definition resembles tree-based structure of lambda terms, where:
+\begin{itemize}
+    \item lambda abstraction is represented as an unary node holding name of lambda-abstracted variable;
+    \item application is represented as a binary node;
+    \item variable is represented as a leaf holding name of the variable.
+\end{itemize}
+
+\begin{figure}[H]
+    \centering
+    \includesvg[scale=.7]{lambda__tree_structure__example_custom}
+    \caption{Tree representation of the term \(\lambda x. (\lambda y.x) (\lambda y.y)\).}%
+    \label{fig:lambda_tree_example}
+\end{figure}
+
+We have used dashed arrows to point lambda-abstraction binding particular variables.
+It is also possible that a variable is unbound, i.e.~there is no lambda-abstraction that abstracts the variable.
+We are perfectly fine with that.
+
+The definition using named variables is quite popular, but introduces several problems.
+One of them is a~problem of a potential collision of lambda-abstracted variable names and difficulty of finding to which lambda abstraction the variable is bound (or is it even a~free variable, i.e.~not bound).
 To address that, we can use de Bruijn indices.
@@
     \begin{itemize}
-        \item if \(n \in \N\), then \(n \in \LambdadB\) (\(n\) is a~variable bound to lambda abstraction \(n\) levels above)
+        \item if \(n \in \N\), then \(n \in \LambdadB\) (\(n\) is a~variable bound to lambda abstraction \(n\) levels above, i.e.~if you traverse the tree of the lambda term upwards, we have to ignore \(n\) lambda-abstraction nodes and the \((n+1)\)-st one is the one binding the variable.
+If we would have to go beyond the root of the tree, we say that the variable is free, i.e.~not bound)
         \item if \(M, N \in \LambdadB\), then \((M N) \in \LambdadB\) (application)
@@
 
-It also allows us to define tree representation of the terms from \(\LambdadB\).
-\todo{introduce unary notation; correlation between n and the size}
+We can define tree representation of the terms from \(\LambdadB\). In order to encode natural numbers, we use unary notation. This allows us to connect the size of the tree to de Bruijn index values.
 
@@
         \item \(\Phi(0) = \n\; \no\; \no\)
-        \item \(\Phi(n) = \n\; \no\; \Phi(n - 1)\)
+        \item \(\Phi(n) = \n\; \no\; \Phi(n - 1)\) (this node acts as a successor in unary notation, i.e.~function incrementing natural number by \(1\))
         \item \(\Phi(\lambda M) = \n\; \Phi(M)\; \no\)
@@
 
-\todo{add note about injectiveness}
-\todo{add image}
+\begin{figure}[H]
+    \centering
+    \includesvg[scale=.7]{lambda__tree_structure__deBruijn_001_custom}
+    \caption{Tree representation of the term \(\lambda (\lambda 1) (\lambda 0)\).}%
+    \label{fig:lambda_tree_example_2}
+\end{figure}
+
+We use green edges to express the non-existing child of the node. Note that in order to get the exact value of the variable we had to take a look at a leaf with all successor nodes above it.
+
 To simplify the interpretation, we can introduce several kinds of the nodes: \(o\), \(s\), \(l\) and \(a\). They do not change the structure, but make the reading a~bit easier:
@@
 
-You can note that not every binary tree represents a~valid term.
+\begin{figure}[H]
+    \centering
+    \includesvg[scale=.7]{lambda__tree_structure__deBruijn_002_custom}
+    \caption{Tree representation of the term \(\lambda (\lambda 1) (\lambda 0)\) with node kinds.}%
+    \label{fig:lambda_tree_example_3}
+\end{figure}
+
+You can note that every tree has its own binary tree representation, but not every binary tree represents a~valid term.
 
@@
 
-\todo{add image}
-\[s\; \no\; l\; o\; \no\; \no\; \no\]
-
-Here \(s\) represents the successor which can be applied only to \(n \in \N\), but is applied to the lambda-abstracted term.
+\begin{figure}[H]
+    \centering
+    \includesvg[scale=.7]{lambda__tree_structure__deBruijn_invalid}
+    \caption{Visualization of the tree \(\n\; \no\; \n\; \n\; \no\; \no\; \no\) with node kinds.}%
+    \label{fig:lambda_tree_invalid}
+\end{figure}
+
+As \(s\) represents the successor, it can be applied only to \(n \in \N\), but is applied to the lambda-abstracted term.
 \end{example}
@@
 \begin{itemize}
-    \item \(z\) marking total number of virtual leaves
-    \item \(o\) marking number of variable nodes
-    \item \(l\) marking number of lambda abstraction nodes
-    \item \(a\) marking number of application nodes
-    \item \(s\) marking number of successors of variable nodes
+    \item \(z\) marking all actual nodes
+    \item \(o\) marking variable nodes
+    \item \(l\) marking lambda abstraction nodes
+    \item \(a\) marking application nodes
+    \item \(s\) marking successors of variable nodes
 \end{itemize}
@@
 
-We also created a~framework~\cite{transformator}, called Transformator, that may help visualize our work on binary trees.
-It is based on the idea that every transformation expressed in bijective language can be seen as a~function transforming some node and a finite number of its surrounding nodes.
-\todo{Fix it}This function cannot discriminate between nodes on the grounds of their kind.
-The only discrimination criteria that may occur may be connected to the following cases:
+We also created a~framework~\cite{transformator}, called Transformator, that may help visualize our work.
+It operates on binary trees and is based on the idea that every transformation expressed in bijective language is local, i.e.~transforms some node and a finite number of its surrounding nodes.
+
+To show the idea of such transformations, let's define transformation context with holes.
+The context specifies shape of the fragment of the tree.
+It can have holes that specify whole subtree.
+We can also specify whether the root of the context has parent and is it the left or right child of its parent.
+
+\begin{example}
+    We want to modify a node being right a child of its parent.
+We do not care what is below that node (i.e.~if that is a leaf or if it has children).
+We want to add a new node of which the original one is left child.
+We do not want the new node to have a right child.
+Additionally we want to swap potential children of the original node.
+We can define following transformation:
+    \begin{center}
+        \includeinlinescaledsvg{.4}{.7}{lambda__contexts__def_001}%
+        \(\Rightarrow\)
+        \includeinlinescaledsvg{.4}{.7}{lambda__contexts__def_002}%
+    \end{center}
+\end{example}
+
+We marked the node being transformed to clarify the picture.
+
+We support following starting contexts of the transformations:
+
 \begin{itemize}
-    \item node has no children, i.e.~is a~virtual leaf (which corresponds to the size of the tree, \(n\));
-    \item node has has children, i.e.~is not a~virtual leaf (which corresponds to \(n - 1\));
-    \item node is a~root (which corresponds to \(1\));
-    \item node has its parent on the left, i.e.~is right child of its parent;
-    \item node has its parent on the right, i.e.~is the left child of its parent.
+    \item node is a~virtual leaf (each tree with \(n\) actual nodes has exactly \((n + 1)\) places where such contex apply):\\
+        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_001}%
+    \item node is an~actual node (tree with \(n\) actual nodes has excatly \(n\) places where such context apply):\\
+        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_002}%
+    \item node is a~root (each tree has exactly \(1\) place where such context apply):\\
+        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_003}%
+    \item node has its parent on the left, i.e.~is right child of its parent:\\
+        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_004}%
+    \item node has its parent on the right, i.e.~is the left child of its parent:\\
+        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_005}%
 \end{itemize}
-\todo{Fix it}
 
 The latest two are introduced in order to make the analysis simpler, but do not have immediate interpretation in the world of holonomic recurrences.
-If we use them both, it sums up to all nodes except root (as root is neither left nor right child).
+However, if we use them both, it sums up to all nodes except root (as root is neither left nor right child), so in total there are \((n - 1)\) places where such a pair of contexts apply.
+
+The target of the transformation can be any context preserving all holes. This allows us to specify number of nodes added by the transformation.
 
@@
 
-\todo{Introduce contexts with holes}
 We will be operating on transformation classes, sections and parts. Let's define them:

### 2021-09-13 article/main.tex
Fix brutal approach

@@
 
-\title{Combinatorial interpretations of holonomic recurrences}
+\title{Combinatorial interpretations of~holonomic recurrences}
 \author{Bartłomiej Puget}
@@
 \DeclareMathOperator{\tSuf}{\text{Suf}}
+\DeclareMathOperator{\tClass}{\text{Class}}
+\DeclareMathOperator{\tSection}{\text{Section}}
+\DeclareMathOperator{\tPart}{\text{Part}}
 \DeclareMathOperator{\n}{\bullet}
@@
 
-Generating functions is a way of describing infinite sequences using formal power series, where coefficients are encoding the the consecutive elements.
+Generating functions is a way of describing infinite sequences using formal power series, where coefficients encode the consecutive elements.
 It allows us to incorporate many advanced methods of analysis of encoded objects.
 
-Every recursive structure can be described using a~generating function equation, which can be then solved and transformed into a~holonomic recurrence, i.e.~recurrence that in order to define \(n\)-th element of the sequence requires just finite number of previous ones and coefficients that are polynomials of \(n\).
+Most recursive structure can be described using a~generating function equation, which can be then solved and transformed into a~holonomic recurrence, i.e.~recurrence that in order to define \(n\)-th element of the sequence requires just finite number of previous ones and coefficients that are polynomials in \(n\).
 
@@
 It just seems like it should describe simple transformations resulting in constructing bigger objects from slightly smaller ones.
-In case of trees it could be for example adding vertices.
+In case of trees it could be for example adding nodes.
 However, there is no known method of interpreting it in the language of the combinatorial structures.
@@
 The initial inspiration for the thesis came from the publication \textit{A natural counting of lambda terms}~\cite{inspiration}, which shows bijections among seemingly different tree structures, which are lambda trees, black-white trees~\cite{blackwhite} and zigzag free trees~\cite{inspiration}\todo{Find better cite}.
-They share the same holonomic recurrence, but there is no known immediate connection between the holonomic recurrence and the structures itself.
+They share the same holonomic recurrence, but there is no known immediate connection between the holonomic recurrence and the structures themselves.
 
@@
 Their very simple recursive definition makes them very attractive.
-Better understanding them could allow us improving programming language compilers and in consequence improve every aspect of our lives.
+A better understanding of them could allow us improving programming language compilers and in consequence improve every aspect of our lives.
 The interpretation of holonomic recurrence for lambda trees itself could allow us to discover new ways of generating random lambda terms via extending smaller ones in similar way to Rémy's algorithm for sampling binary trees~\cite{remy,note}.
@@
 Section~\ref{sec:brutal_iterative_approach} presents our final approach to the original problem, i.e.~computer-aided iterative approach that allowed us to find the intermediate solution.
-We believe that it is possible to extend this idea in order to obtain the full solution, but we were not able to achieve that due to the limited time that was available to us.
+We believe that it is possible to extend this idea in order to obtain the full solution, but we were not able to achieve this due to the limited time that was available to us.
 
@@
 
-\(\troot(T)\) is implicitly defined as a~root of tree \(T\).
-
-\(\tleft(v)\) is implicitly defined as a~left child of node \(v\).
-
-\(\tright(v)\) is implicitly defined as a~right child of node \(v\).
-
-\(\tSub(v)\) is implicitly defined as a~whole subtree rooted with node \(v\).
-
-\(\tLeft(v)\) is implicitly defined as a~left subtree of node \(v\).
-
-\(\tRight(v)\) is implicitly defined as a~right subtree of node \(v\).
-
-Sibling of node \(v\) is defined as node \(u\) having the same parent as \(v\).
-
-Uncle of node \(v\) is defined as a~sibling of the parent of \(v\).
+\(\troot(T)\) is implicitly defined as the~root of the~tree \(T\).
+
+\(\tleft(v)\) is implicitly defined as the~left child of the~node \(v\).
+
+\(\tright(v)\) is implicitly defined as the~right child of the~node \(v\).
+
+\(\tSub(v)\) is implicitly defined as the~whole subtree rooted with the~node \(v\).
+
+\(\tLeft(v)\) is implicitly defined as the~left subtree of the~node \(v\).
+
+\(\tRight(v)\) is implicitly defined as the~right subtree of the~node \(v\).
+
+Sibling of the node \(v\) is defined as the node \(u\) having the same parent as \(v\).
+
+Uncle of the node \(v\) is defined as the~sibling of the parent of \(v\).
 
@@
 
-We say that node \(v\) is twinling \(\textiff\) \(v\) has at least one sibling.
+We say that node \(v\) is a~twinling \(\textiff\) \(v\) has at least one sibling.
 
@@
 
-\(x_i\) is implicitly assumed to be an~\(i\)-th element of the sequence \(X\), where \(x\) can be any lower-case letter and \(X\) is upper-case \(x\).
+\(x_i\) is implicitly assumed to be the~\(i\)-th element of a sequence \(X\), where \(x\) can be any lower-case letter and \(X\) is upper-case \(x\).
 
@@
 \begin{definition}
-    The ordinary generating function of sequence \(A = {(a_i)}_{i=0}^{\infty}\) is defined as a~formal power series:
+    The ordinary generating function of a sequence \(A = {(a_i)}_{i=0}^{\infty}\) is defined as the following formal power series:
 \[\gf{A}(z) = \sum_{i=0}^{\infty} a_i z^i.\]
@@
 
-Note that in order to compute the \(k\)-th element of the sequence, namely \(a_k\), we just need to find a~constant corresponding to indeterminate \(z^k\).
+Note that in order to compute the \(k\)-th element of the sequence, namely \(a_k\), we just need to find the~constant corresponding to indeterminate \(z^k\).
 
@@
     \label{ex:bin_gf}
-    Let's consider recursive definition of binary trees shown in Figure~\ref{fig:binary_recursion}.
-We can create a~functional equation to count trees with exactly n internal nodes.
+    Let's consider the recursive definition of binary trees shown in Figure~\ref{fig:binary_recursion}.
+We can create a~functional equation to count trees with exactly \(n\) internal nodes.
 To do so, we make internal nodes contribute to the generating function with \(z^1 = z\) and leaves with \(z^0 = 1\):
@@
 \begin{itemize}
-    \item rooted tree is a~tree with single vertex marked as root. This allows us to define hierarchy of nodes using such terms as parent and child;
+    \item rooted tree is a~tree with single node marked as root. This allows us to define hierarchy of nodes using such terms as parent and child;
     \item ordered trees introduce order on children from the leftmost to the rightmost;
@@
 \begin{definition}
-    For single vertex \(v\), the pre-order notation is defined as \(\enc{v}\).
+    For single node \(v\), the pre-order notation is defined as \(\enc{v}\).
 \end{definition}
@@
 Notation of suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined as a~suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
+Note that the suffix may be an ordered forest.\todo{add to the example}
 \end{definition}
@@
 
-These interpretations have been source of ideas that that we were incorporating in order to make our partial interpretation for the case of lambda trees in unary de Bruijn notation.
+These interpretations have been source of ideas that we were incorporating in order to make our partial interpretation for the case of lambda trees in unary de Bruijn notation.
 
@@
 
-Most of the time we are operating on trees with some nodes of weight \(0\) and some of weight \(1\). We may as well try to make them variable or assign some other values (e.g.~small prime numbers).
+Most of the time we are operating on trees, we define the size as a count of some objects (nodes or edges).
+We can assign weights to these objects and make the size a weighted sum.
+The weights can be variable or we can assign some other constant values (e.g.~small prime numbers).
 
@@
 To show the idea of such transformations, let's define transformation context with holes.
-The context specifies shape of the fragment of the tree.
-It can have holes that specify whole subtree.
-We can also specify whether the root of the context has parent and is it the left or right child of its parent.
-
-\begin{example}
+
+\begin{definition}
+    The transformation context is a rooted tree.
+Some of nodes can be left as holes, that may be later filled with trees.
+It also specifies type of the edge above the root of the context (i.e.~if that is actual edge, optional actual edge, virtual edge, or if there is no edge at all).
+\end{definition}
+
+\begin{example}%
+    \label{ex:transformation}%
     We want to modify a node being right a child of its parent.
@@
 
-We marked the node being transformed to clarify the picture.
+\(H_1\), \(H_2\), and \(H_3\) are holes.
+Edge crossing the box around the context defines type of edge the context is connect to the rest of the tree (i.e.~optional actual edge).
+We marked the node being described to clarify the picture.
 
@@
         \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_003}%
-    \item node has its parent on the left, i.e.~is right child of its parent:\\
-        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_004}%
-    \item node has its parent on the right, i.e.~is the left child of its parent:\\
-        \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_005}%
+    \item node has its parent on the left, i.e.~is right child of its parent (the node can be specified to be actual or virtual):\\
+        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_004}%
+        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_004b}%
+    \item node has its parent on the right, i.e.~is the left child of its parent (the node can be specified to be actual or virtual):\\
+        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_005}%
+        \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_005b}%
 \end{itemize}
@@
 
-We will be operating on transformation classes, sections and parts. Let's define them:
-
-\begin{definition}
-    Class \(T_i\) is defined as a~set of transformations of trees of size \((n - i)\) into trees of size \(n\).
-\end{definition}
-
-\begin{definition}
-    Section \(T_{i,j}\) is defined as a~subset of \(T_i\) adding a~specific set of nodes. We assign \(j\) according to the lexicographical order of lexicographically sorted node types.
-\end{definition}
-
-\begin{definition}
-    Part \(T_{i,j,k}\) is defined as a~single transformation in section \(T_{i,j}\). \(k\) is assigned according to the order of discovering the transformation.
-\end{definition}
-
-In order to make interpretation more human readable, we will be using local notation:
-
-\begin{definition}
-    In the context of \(T_i\), \(k\) is defined as \((n - i)\).
-\end{definition}
-
-\begin{definition}
-    In the context of \(T_i\), \(C_k\) is defined as \(T(n - i)\), i.e.~number of tree transformations from \(T_i\) are working on.
-\end{definition}
-
-\begin{definition}
-    Section equation \(E_{i, j}\) is an~equation defined in the context of \(T_i\) that evaluates to a~total number of trees that should be generated by transformations from \(T_{i, j}\).
-\end{definition}
-
-\begin{definition}
-    Section expression \(S_{i, j}\) is a~pair of section equations and a~set of kinds of nodes the transformation introduces.
-\end{definition}
-
-For the problem of interpreting trees of lambda terms we define following section expressions:
-
-\[\begin{array}{rccrlc}
-        S_{0,0} &=& (& (k + 1) C_k,& \emptyset &)\\
-        S_{1,0} &=& (& - (2 k + 1) C_k,& \{l\} &)\\
-        S_{1,1} &=& (& - 2 (k + 1) C_k,& \{s\} &)\\
-        S_{2,0} &=& (& - (4 k) C_k,& \{ao\} &)\\
-        S_{2,1} &=& (& (k) C_k,& \{ll\} &)\\
-        S_{2,2} &=& (& (4 k + 2) C_k,& \{ls\} &)\\
-        S_{2,3} &=& (& (k + 1) C_k,& \{ss\} &)\\
-        S_{3,0} &=& (& 2 (2 k + 1) C_k,& \{aos\} &)\\
-        S_{3,1} &=& (& - (2 k) C_k,& \{lls\} &)\\
-        S_{3,2} &=& (& - (2 k + 1) C_k,& \{lss\} &)\\
-        S_{4,0} &=& (& k C_k,& \{llss\} &)\\
+Note that for each transformation we can specify number and kinds of the nodes added to the tree. Let's take a look at the transformation from Example~\ref{ex:transformation}:
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__contexts__def_001}%
+    \(\Rightarrow\)
+    \includeinlinescaledsvg{.4}{.7}{lambda__contexts__def_002_with_l}%
+\end{center}
+It adds single \(l\) node.
+
+We will be operating on transformation classes, sections. They will start being empty and we will be adding tranformations to them.
+
+\(\tSection_\tau\), where \(\tau\) is list constructed from \(\{a, l, o, s\}\) (you can treat is as a~set, but with potential repetitions), stores transformation extending the tree with nodes \(\tau\).
+
+\(\tClass_i\), where \(i \in \N\) is defined as \(\bigcup_{\tau : |\tau| = i} \tSection_\tau\) (i.e.~set of all transformations adding exactly \(i\)~nodes to the tree).
+
+We will be also talking about trees generated by the transformation.
+Let's consider constant \(n \in \N\).
+List of trees generated by the transformation from \(\tSection_\tau\) is defined as all trees generated by applying the transformation to all trees of size \((n - |\tau|)\).
+
+Analogically, we can specify list of trees generated by the \(\tSection_\tau\) and \(\tClass_i\) as list of trees generated by all transformations from them.
+
+Each section is associated with an expression coming from the holonomic recurrence.
+It defines expected number of trees that will be generated by each of them.
+Let \(k = n - |\tau|\) for each \(\tSection_\tau\).
+In the case of trees of lambda terms, we get following expressions associated to each section:
+
+\[\begin{array}{lcr}
+        \tSection_{\emptyset} &:& (k + 1) t_k\\
+        \tSection_{\{l\}} &:& - (2 k + 1) t_k\\
+        \tSection_{\{s\}} &:& - 2 (k + 1) t_k\\
+        \tSection_{\{ao\}} &:& - (4 k) t_k\\
+        \tSection_{\{ll\}} &:& (k) t_k\\
+        \tSection_{\{ls\}} &:& (4 k + 2) t_k\\
+        \tSection_{\{ss\}} &:& (k + 1) t_k\\
+        \tSection_{\{aos\}} &:& 2 (2 k + 1) t_k\\
+        \tSection_{\{lls\}} &:& - (2 k) t_k\\
+        \tSection_{\{lss\}} &:& - (2 k + 1) t_k\\
+        \tSection_{\{llss\}} &:& (k) t_k\\
 \end{array}\]
 
-Using context-based variables makes the equation simpler to interpret, as we can immediately see the relation between \(k\) and multiplier.
+Using \(k\) instead of \(n\) makes it easier to interpret, as we immediately see number of trees that should be generated by each section.
+For example \(\tSection_{\{ll\}}\) should generate \(k t_k\) trees from trees of size \(k\), which can be interpreted as taking each actual node and adding two \(l\) nodes above it.
+
+Note that some of these expressions will evaluate to negative numbers.
+It is because of the fact that sum of all sections is equal to zero.
+We will be generating two kinds of trees then: positive (contributing to the total number of trees being generated as \(1\)) and negative ones (contributing as \(-1\)).
 
@@
 
-As we want to make our work kind of organized, we are going to divide the process of finding interpretation into iterations.
-Each iteration should be a~small step into the direction of solving the original problem.
-
-We are going to generate two kinds of trees: positive and negative ones.
-When computing the total number of trees of a given size, we count positive trees as \(1\) and negative as \(-1\).
-Our goal is to generate \(E_{i, j}\) trees for each section \(T_{i, j}\).
-
-Our brains like small examples, so we will consider small \(n = 3\). This will cause some classes to be empty at the beginning, but it's ok. That's less trees to look at.
+As we want to make our work kind of organized, we are going to divide the process of finding interpretation into iterations. Each iteration should be a~small step towards solving the original problem.
+
+Our brains like small examples, so we will consider small constant \(n = 3\).
+It will be describing size of the trees we want to generate.
+Because we start with such small \(n\), some of expressions associated with some sections will be empty, but it is ok.
+That's less trees to look at and soon we will increase \(n\).
+
+We will be still using \(k = n - |\tau|\) when considering sections to make the view simpler.
+
+Let's take a look at the number of trees we should generate:
 
@@
 === Classes stats ===
-[ ]  0,0:       0 of      16 | (k + 1) * Ck              []
-[ ]  1,0:       0 of     -10 | - (2 * k + 1) * Ck        [l]
-[ ]  1,1:       0 of     -12 | - 2 * (k + 1) * Ck        [s]
-[ ]  2,0:       0 of      -4 | - (4 * k) * Ck            [ao]
-[ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
-[ ]  2,2:       0 of       6 | (4 * k + 2) * Ck          [ls]
-[ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
-[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aos]
-[x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
-[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Ck        [lss]
-[x]  4,0:       0 of       0 | k * Ck                    [llss]
+[ ]  0,0:       0 of      16 | (k + 1) * Tk              []
+[ ]  1,0:       0 of     -10 | - (2 * k + 1) * Tk        [l]
+[ ]  1,1:       0 of     -12 | - 2 * (k + 1) * Tk        [s]
+[ ]  2,0:       0 of      -4 | - (4 * k) * Tk            [ao]
+[ ]  2,1:       0 of       1 | (k) * Tk                  [ll]
+[ ]  2,2:       0 of       6 | (4 * k + 2) * Tk          [ls]
+[ ]  2,3:       0 of       2 | (k + 1) * Tk              [ss]
+[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Tk      [aos]
+[x]  3,1:       0 of       0 | - (2 * k) * Tk            [lls]
+[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Tk        [lss]
+[x]  4,0:       0 of       0 | k * Tk                    [llss]
 \end{lstlisting}
 
-This statistic tells us for each section, how many trees have been generated of the expected total number of trees in that section. \verb|[x]| means that we generated enough trees for such a~section.
-
-We start with interpreting \(E_{0,0} = (k + 1) C_k\). From statistics above, we see that we should generate \(16\) trees. \((k + 1)\) suggests pointing to a~virtual leaf. Let's do so.
+The listing above is statistics view from Transformator framework. Let's analyze the first line:
+\begin{itemize}
+    \item \verb|[ ]| at the beginning means that we still need to generate some more trees. If we have generated all of them, it would be \verb|[x]|;
+    \item \verb|0,0| is class and section identifier, i.e. \(|\tau|\) and arbitrarily assigned section identifier;
+    \item \verb|0 of 16| means that we have generated \(0\) trees from \(16\) expected;
+    \item \verb|(k + 1) * Tk| is just the expression associated with the section;
+    \item \verb|[]| at the end is \(\tau\), which in this case is equal to \(\emptyset\).
+\end{itemize}
+
+We start with interpreting \(\tSection_\emptyset\).
+From statistics above, we see that we should generate \(16\) trees.
+\((k + 1)\) suggests pointing to a~virtual leaf.
+Let's do so.
+We do that by defining following transformation:
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__001a}%
+    \(\xRightarrow{+1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__001b}%
+\end{center}
+
+Here \(\xRightarrow{+1}\) means that we are generating positive trees.
+
+In the language of Transformator framework it would be:
 
@@
 
+After such operation we get following statistics:
+
 \begin{lstlisting}
-# define 0,0: (k + 1) * Ck []
+# define 0,0: (k + 1) * Tk []
 === Classes stats ===
-[x]  0,0:      16 of      16 | (k + 1) * Ck              []
-[ ]  1,0:       0 of     -10 | - (2 * k + 1) * Ck        [l]
-[ ]  1,1:       0 of     -12 | - 2 * (k + 1) * Ck        [s]
-[ ]  2,0:       0 of      -4 | - (4 * k) * Ck            [ao]
-[ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
-[ ]  2,2:       0 of       6 | (4 * k + 2) * Ck          [ls]
-[ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
-[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aos]
-[x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
-[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Ck        [lss]
-[x]  4,0:       0 of       0 | k * Ck                    [llss]
+[x]  0,0:      16 of      16 | (k + 1) * Tk              []
+[ ]  1,0:       0 of     -10 | - (2 * k + 1) * Tk        [l]
+[ ]  1,1:       0 of     -12 | - 2 * (k + 1) * Tk        [s]
+[ ]  2,0:       0 of      -4 | - (4 * k) * Tk            [ao]
+[ ]  2,1:       0 of       1 | (k) * Tk                  [ll]
+[ ]  2,2:       0 of       6 | (4 * k + 2) * Tk          [ls]
+[ ]  2,3:       0 of       2 | (k + 1) * Tk              [ss]
+[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Tk      [aos]
+[x]  3,1:       0 of       0 | - (2 * k) * Tk            [lls]
+[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Tk        [lss]
+[x]  4,0:       0 of       0 | k * Tk                    [llss]
 === Diff stats ===
@@
 
-The framework informs us that we have generated all trees for section \(0,0\) for \(n = 3\). It also can provide us with the visualization of the trees we have generated. For example:
+Note that we have generated all expected trees associated with \(\tSection_\emptyset\) (it is indicated by \verb|[x]|).
+
+We also get the \verb|Diff stats|.
+It shows us information about how we have unbalanced the positive and negative side of our equation.
+At the end we want to generate the same list of trees at the negative and positive site.
+
+The framework also can provide us with the visualization of the trees we have generated. For example, from the tree on the left side of \(\xRightarrow{+1}\) we have generated four trees:
 
 \includeinlinesvg{.19}{lambda__trees_00__4_base}%
-\(\Rightarrow\)
+\(\xRightarrow{+1}\)%
 \includeinlinesvg{.19}{lambda__trees_00__4}%
@@
 
-If we take a~look at more examples from class \(0\), we can start seeing some patterns:
+You can see that there are four virtual leaves matching left side of the transformation we have defined.
+
+We can also query Transformator framework to visualize the trees that are unbalanced. For \(\tClass_0\) those are:
 
@@
 
-The order may be a~bit suggestive.
-Section \(1,0\) adds a~single \(l\) node, whereas section \(1,1\) adds a~single \(s\) node.
-It actually suggests how we can try to generate the first and second line of the trees above.
-The first one is simple.
-Let's add \(l\) node with pointed right virtual leaf above each actual node:
+We have ordered the trees and enumerated the lines to make the analysis clearer.
+
+We need to generate all of these trees on the negative side of the equation.
+Let's take a look at the line (1).
+All of these trees share the same property, that the virtual leaf being pointed is child of \(l\)~node.
+Analogically at the line (2) pointed virtual leaves are children of \(s\) nodes.
+To generate such trees on the negative side we will use \(\tSection_{\{l\}}\) and \(\tSection_{\{s\}}\).
+
+The transformation to resolve case of the line (1) is simple:
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__002a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__002b}%
+\end{center}
 
 \begin{lstlisting}
-c.define_class(1)
-
-c.define_section(0)
-
 c.append_r_class_subtree_visitor(-1,                # negative node
@@
 \end{lstlisting}
-\todo{Repeat in natural language}
+
+We just add an \(l\) node above each actual one and point its right child being virtual leaf.
 
 It creates following trees:
-\todo{Mark transformed nodes}
-
-\includeinlinesvg{.24}{lambda__trees_100__0_base}\(\Rightarrow\)\includeinlinesvg{.24}{lambda__trees_100__0}%
-\includeinlinesvg{.24}{lambda__trees_100__1_base}\(\Rightarrow\)\includeinlinesvg{.24}{lambda__trees_100__1}%
-
-\includeinlinesvg{.24}{lambda__trees_100__2_base}\(\Rightarrow\)\includeinlinesvg{.24}{lambda__trees_100__2}%
-\includeinlinesvg{.24}{lambda__trees_100__3_base}\(\Rightarrow\)\includeinlinesvg{.24}{lambda__trees_100__3}%
-
-It addresses all cases from the first line, but also introduces an~incorrect lambda tree in which \(s\) is the parent of \(l\), which cannot happen.
-We will fix it with the section \(2,2\) generating positive trees, which introduces one \(l\) node and one \(s\) by extending the tree with \(2\) nodes where \(s\) is parent of \(l\).
-
-Next, we can take care of next cases of section \(0, 0\). It can be also expressed using sections \(1, 0\) and \(1, 1\):
+
+\includeinlinesvg{.24}{lambda__trees_100__0_base}\(\xRightarrow{-1}\)\includeinlinesvg{.24}{lambda__trees_100__0}%
+\includeinlinesvg{.24}{lambda__trees_100__1_base}\(\xRightarrow{-1}\)\includeinlinesvg{.24}{lambda__trees_100__1}%
+
+\includeinlinesvg{.24}{lambda__trees_100__2_base}\(\xRightarrow{-1}\)\includeinlinesvg{.24}{lambda__trees_100__2}%
+\includeinlinesvg{.24}{lambda__trees_100__3_base}\(\xRightarrow{-1}\)\includeinlinesvg{.24}{lambda__trees_100__3}%
+
+It addresses all cases from the line (1), but also introduces an~incorrect lambda tree in which \(s\) node is the parent of \(l\) node, which cannot happen (i.e.~such tree does not correspond to valid lambda term).
+To mitigate this problem we will later use \(\tSection_{\{ls\}}\) and generate positive trees where \(s\) node is parent of \(l\) node.
+
+To generate negative trees corresponding to the line (2), create following transformation for \(\tSection_{\{s\}}\).
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__003a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__003b}%
+\end{center}
 
 \begin{lstlisting}
-c.define_class(1)
-
-c.define_section(0)
-
-# old visitor
-c.append_r_class_subtree_visitor(-1,
-    lambda kind, left, right:
-        None if kind[0] is None else
-        ["l", kind] + left + right + [(None, "*")]
-)
-
-# new visitor
 c.append_r_class_right_parent_subtree_visitor(-1,
@@
         None if kind[0] is not None else
+        ["s", (None, "*"), parent_kind] + left + right
+)
+\end{lstlisting}
+
+It generates exactly the trees we need:
+
+\begin{center}
+    \includeinlinescaledsvg{.24}{.4}{lambda__trees_110__0_base}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.24}{.4}{lambda__trees_110__0}%
+
+    \includeinlinescaledsvg{.24}{.4}{lambda__trees_110__1_base}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.24}{.4}{lambda__trees_110__1}%
+    \includeinlinescaledsvg{.24}{.4}{lambda__trees_110__2_base}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.24}{.4}{lambda__trees_110__2}%
+\end{center}
+
+Next, we can take care of cases from line (3). To do so, we will use both \(\tSection_{\{l\}}\) and \(\tSection_{\{s\}}\).
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__004a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__004b}%
+\end{center}
+
+\begin{lstlisting}
+c.append_r_class_right_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
         ["l", parent_kind] + [left[0] + ("*",)] + left[1:] + right + [None]
 )
-
-# new visitor
+\end{lstlisting}
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__005a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__005b}%
+\end{center}
+
+\begin{lstlisting}
 c.append_r_class_left_parent_subtree_visitor(-1,
@@
 )
-
-c.define_section(1)
-
-# old visitor
+\end{lstlisting}
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__006a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__006b}%
+\end{center}
+
+\begin{lstlisting}
+c.append_r_class_left_parent_subtree_visitor(-1,
+    lambda kind, parent_kind, left, right:
+        None if kind[0] is not None else
+        ["s", None, parent_kind] + left + [right[0] + ("*",)] + right[1:]
+)
+\end{lstlisting}
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__007a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__007b}%
+\end{center}
+
+\begin{lstlisting}
 c.append_r_class_right_parent_subtree_visitor(-1,
@@
         None if kind[0] is not None else
-        ["s", (None, "*"), parent_kind] + left + right
-)
-
-# new visitor
-c.append_r_class_left_parent_subtree_visitor(-1,
-    lambda kind, parent_kind, left, right:
-        None if kind[0] is not None else
-        ["s", None, parent_kind] + left + [right[0] + ("*",)] + right[1:]
-)
-
-# new visitor
-c.append_r_class_right_parent_subtree_visitor(-1,
-    lambda kind, parent_kind, left, right:
-        None if kind[0] is not None else
         ["s", None, parent_kind] + [left[0] + ("*",)] + left[1:] + right
@@
 \includeinlinesvg{.32}{lambda__trees_111__1_base}%
-\(\Rightarrow\)
+\(\xRightarrow{-1}\)%
 \includeinlinesvg{.32}{lambda__trees_101__0}%
@@
 
-The last row can be generated using section \(2, 0\):
+The last row can be generated using \(\tSection_{\{ao\}}\):
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__008a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__008b}%
+\end{center}
 
 \begin{lstlisting}
-c.define_class(2)
-
-c.define_section(0)
-
 c.append_r_class_subtree_visitor(-1,
@@
 )
-
+\end{lstlisting}
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__009a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__009b}%
+\end{center}
+
+\begin{lstlisting}
 c.append_r_class_subtree_visitor(-1,
@@
 )
-
+\end{lstlisting}
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__010a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__010b}%
+\end{center}
+
+\begin{lstlisting}
 c.append_r_class_subtree_visitor(-1,
@@
 )
-
+\end{lstlisting}
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__011a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__011b}%
+\end{center}
+
+\begin{lstlisting}
 c.append_r_class_subtree_visitor(-1,
@@
 
-For each actual vertex, we add \(a\) node as its left or right parent and add as a~second child \(o\) node as its sibling.
-We then point to the left or right virtual child of the newly created \(o\) node.
+In other words, for each actual node, we add an \(a\) node as its left or right parent and add as a~second child \(o\) node as its sibling.
+We then point to the left or right virtual child of the newly created \(o\)~node:
 
 \includeinlinesvg{.20}{lambda__trees_200__0_base}%
-\(\Rightarrow\)
+\(\xRightarrow{-1}\)%
 \includeinlinesvg{.20}{lambda__trees_200__0}%
@@
 === Classes stats ===
-[x]  0,0:      16 of      16 | (k + 1) * Ck              []
-[x]  1,0:     -10 of     -10 | - (2 * k + 1) * Ck        [l]
-[ ]  1,1:      -9 of     -12 | - 2 * (k + 1) * Ck        [s]
-[x]  2,0:      -4 of      -4 | - (4 * k) * Ck            [ao]
-[ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
-[ ]  2,2:       0 of       6 | (4 * k + 2) * Ck          [ls]
-[ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
-[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aos]
-[x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
-[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Ck        [lss]
-[x]  4,0:       0 of       0 | k * Ck                    [llss]
+[x]  0,0:      16 of      16 | (k + 1) * Tk              []
+[x]  1,0:     -10 of     -10 | - (2 * k + 1) * Tk        [l]
+[ ]  1,1:      -9 of     -12 | - 2 * (k + 1) * Tk        [s]
+[x]  2,0:      -4 of      -4 | - (4 * k) * Tk            [ao]
+[ ]  2,1:       0 of       1 | (k) * Tk                  [ll]
+[ ]  2,2:       0 of       6 | (4 * k + 2) * Tk          [ls]
+[ ]  2,3:       0 of       2 | (k + 1) * Tk              [ss]
+[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Tk      [aos]
+[x]  3,1:       0 of       0 | - (2 * k) * Tk            [lls]
+[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Tk        [lss]
+[x]  4,0:       0 of       0 | k * Tk                    [llss]
 === Diff stats ===
@@
 
-This construction works also for bigger \(N\):
+Note that we have gotten rid of the \(\tSection_\emptyset\) in \verb|Diff stats|. It means that we have generated all negative counterpart of the trees generated by that.
+
+If we increase \(n\) (i.e.~target size of the trees), this construction still works:
 
@@
 === Classes stats ===
-[x]  0,0:   39050 of   39050 | (k + 1) * Ck              []
-[x]  1,0:  -23237 of  -23237 | - (2 * k + 1) * Ck        [l]
-[ ]  1,1:  -17799 of  -24460 | - 2 * (k + 1) * Ck        [s]
-[x]  2,0:  -13728 of  -13728 | - (4 * k) * Ck            [ao]
-[ ]  2,1:       0 of    3432 | (k) * Ck                  [ll]
-[ ]  2,2:       0 of   14586 | (4 * k + 2) * Ck          [ls]
-[ ]  2,3:       0 of    3861 | (k + 1) * Ck              [ss]
-[ ]  3,0:       0 of    4620 | 2 * (2 * k + 1) * Ck      [aos]
-[ ]  3,1:       0 of   -2156 | - (2 * k) * Ck            [lls]
-[ ]  3,2:       0 of   -2310 | - (2 * k + 1) * Ck        [lss]
-[ ]  4,0:       0 of     342 | k * Ck                    [llss]
+[x]  0,0:   39050 of   39050 | (k + 1) * Tk              []
+[x]  1,0:  -23237 of  -23237 | - (2 * k + 1) * Tk        [l]
+[ ]  1,1:  -17799 of  -24460 | - 2 * (k + 1) * Tk        [s]
+[x]  2,0:  -13728 of  -13728 | - (4 * k) * Tk            [ao]
+[ ]  2,1:       0 of    3432 | (k) * Tk                  [ll]
+[ ]  2,2:       0 of   14586 | (4 * k + 2) * Tk          [ls]
+[ ]  2,3:       0 of    3861 | (k + 1) * Tk              [ss]
+[ ]  3,0:       0 of    4620 | 2 * (2 * k + 1) * Tk      [aos]
+[ ]  3,1:       0 of   -2156 | - (2 * k) * Tk            [lls]
+[ ]  3,2:       0 of   -2310 | - (2 * k + 1) * Tk        [lss]
+[ ]  4,0:       0 of     342 | k * Tk                    [llss]
 === Diff stats ===
@@
 
-The process can then be repeated for each section. We have chosen lexicographical order (i.e.~\(0,0\); \(1,0\); \(1,1\); \(2,0\); \(\ldots\)).
+The process can then be repeated for each section.
+We have chosen lexicographical order (i.e.~\(\tSection_\emptyset\); \(\tSection_{\{l\}}\); \(\tSection_{\{s\}}\); \(\tSection_{\{ao\}}\); \(\tSection_{\{ll\}}\); \(\ldots\)).
 
@@
 === Classes stats ===
-[x]  0,0:   39050 of   39050 | (k + 1) * Ck              []
-[x]  1,0:  -23237 of  -23237 | - (2 * k + 1) * Ck        [l]
-[ ]  1,1:  -17799 of  -24460 | - 2 * (k + 1) * Ck        [s]
-[x]  2,0:  -13728 of  -13728 | - (4 * k) * Ck            [ao]
-[x]  2,1:    3432 of    3432 | (k) * Ck                  [ll]
-[ ]  2,2:   10833 of   14586 | (4 * k + 2) * Ck          [ls]
-[ ]  2,3:    1770 of    3861 | (k + 1) * Ck              [ss]
-[ ]  3,0:    2280 of    4620 | 2 * (2 * k + 1) * Ck      [aos]
-[ ]  3,1:   -1648 of   -2156 | - (2 * k) * Ck            [lls]
-[ ]  3,2:   -1140 of   -2310 | - (2 * k + 1) * Ck        [lss]
-[ ]  4,0:     187 of     342 | k * Ck                    [llss]
+[x]  0,0:   39050 of   39050 | (k + 1) * Tk              []
+[x]  1,0:  -23237 of  -23237 | - (2 * k + 1) * Tk        [l]
+[ ]  1,1:  -17799 of  -24460 | - 2 * (k + 1) * Tk        [s]
+[x]  2,0:  -13728 of  -13728 | - (4 * k) * Tk            [ao]
+[x]  2,1:    3432 of    3432 | (k) * Tk                  [ll]
+[ ]  2,2:   10833 of   14586 | (4 * k + 2) * Tk          [ls]
+[ ]  2,3:    1770 of    3861 | (k + 1) * Tk              [ss]
+[ ]  3,0:    2280 of    4620 | 2 * (2 * k + 1) * Tk      [aos]
+[ ]  3,1:   -1648 of   -2156 | - (2 * k) * Tk            [lls]
+[ ]  3,2:   -1140 of   -2310 | - (2 * k + 1) * Tk        [lss]
+[ ]  4,0:     187 of     342 | k * Tk                    [llss]
 === Diff stats ===
@@
 
-As you can see, diff stats are empty, so we managed to generate expected trees on both sides of the equation.
+As you can see, \verb|Diff stats| are empty, so we managed to generate expected trees on both sides of the equation.
 
@@
 You may remember our assumptions in Section~\ref{sub:the_framework} about the discrimination cases.
-We allowed ourselves to apply visitors only to one of the left and right children, which is not handled by our holonomic recurrence as the number of such vertices does not depend only on \(n\).
-
-To fix this, one can for example add construction for section \(1, 0\) to generate all expected trees from it and then repeat the iteration in order to generate matching trees on the other side of the equation.
+We allowed ourselves to apply visitors only to one of the left and right children, which is not handled by our holonomic recurrence as the number of such nodes does not depend only on \(n\).
+
+To fix this, one can for example add construction for \(\tSection_{\{s\}}\) to generate all expected trees from it and then repeat the iteration in order to generate matching trees on the other side of the equation.
 We can see that we used \(2\) constructions visiting nodes with right parent and only one visiting node having left parent, so our missing construction should also visit nodes with left parent.
 
+We already have defined following transformations:
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__003a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__003b}%
+\end{center}
+
 \begin{lstlisting}
-c.define_class(1)
-
-c.define_section(0)
-
 c.append_r_class_right_parent_subtree_visitor(-1,
@@
 )
-
+\end{lstlisting}
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__012a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__012b}%
+\end{center}
+
+\begin{lstlisting}
 c.append_r_class_left_parent_subtree_visitor(-1,
@@
 )
-
+\end{lstlisting}
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__013a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__013b}%
+\end{center}
+
+\begin{lstlisting}
 c.append_r_class_right_parent_subtree_visitor(-1,
@@
 )
-
-# example missing construction
+\end{lstlisting}
+
+An example of transformation we would like to add can be:
+
+\begin{center}
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__014a}%
+    \(\xRightarrow{-1}\)%
+    \includeinlinescaledsvg{.4}{.7}{lambda__transformations__014b}%
+\end{center}
+
+\begin{lstlisting}
 c.append_r_class_left_parent_subtree_visitor(-1,

### 2021-09-13 article/main.tex
Remove done todo
Spellcheck

@@
 Notation of suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined as a~suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
-Note that the suffix may be an ordered forest.\todo{add to the example}
+Note that the suffix may be an ordered forest.
 \end{definition}
@@
 \begin{itemize}
-    \item node is a~virtual leaf (each tree with \(n\) actual nodes has exactly \((n + 1)\) places where such contex apply):\\
+    \item node is a~virtual leaf (each tree with \(n\) actual nodes has exactly \((n + 1)\) places where such context apply):\\
         \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_001}%
-    \item node is an~actual node (tree with \(n\) actual nodes has excatly \(n\) places where such context apply):\\
+    \item node is an~actual node (tree with \(n\) actual nodes has exactly \(n\) places where such context apply):\\
         \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_002}%
@@
 
-We will be operating on transformation classes, sections. They will start being empty and we will be adding tranformations to them.
+We will be operating on transformation classes, sections. They will start being empty and we will be adding transformations to them.
 

### 2021-09-13 article/main.tex
Minor fix
Fix bB in UB

@@
 \begin{itemize}
-    \item \(b_n\) is simply the set of all full binary trees of size \(n\),
-    \item \((n + 2) b_{n + 1}\) is the set of all full binary trees of size \(n + 1\) with one of the leaves pointed,
-    \item \((2n + 1) b_{n}\) is the set of all full binary trees of size \(n\) with one of the nodes (either internal or a~leaf) pointed (i.e.~distinguished),
-    \item \(2\) at the beginning of \(2 (2n + 1) b_{n}\) indicates that we will be using \(2\) copies of the set defined in the previous bullet.
+    \item \(B(n)\) is simply the set of all full binary trees of size \(n\),
+    \item \((n + 2) B(n + 1)\) is the set of all full binary trees of size \(n + 1\) with one of the leaves pointed,
+    \item \((2n + 1) B(n)\) is the set of all full binary trees of size \(n\) with one of the nodes (either internal or a~leaf) pointed (i.e.~distinguished),
+    \item \(2\) at the beginning of \(2 (2n + 1) B(n)\) indicates that we will be using \(2\) copies of the set defined in the previous bullet.
 \end{itemize}
@@
 We can now take the bijective interpretation of \((2n + 1) B(n)\), i.e.~trees of size \(n\) with a~single node pointed.
-For each of such trees, \(T\) we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a~node that is pointed in \(T\).
-Therefore we generate \(2(2n + 1) B(n)\) trees of size \(n + 1\).
+For each of such trees, namely \(T\), we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a~node that is pointed in \(T\).
+Therefore we generate all trees from \(2(2n + 1) B(n)\).
 \todo{rewrite}
@@
 The only thing that's left for us to verify is if we generate all trees of size \(n + 1\) with pointed leaves.
-As from the recursion, we know that \(2 (2n + 1) B(n)\) is total number of trees with single leaf pointed, it is enough to check if we do not generate any duplicate using \(R_l\) and \(R_r\).
+As from the recursion, we know that \(2 (2n + 1) B(n)\) describe trees with single leaf pointed, it is enough to check if we do not generate any duplicate using \(R_l\) and \(R_r\).
 It can happen in 2 ways:
@@
 
-An example of transformation we would like to add can be:
+An example of transformation we may want to add can be:
 

### 2021-09-14 article/main.tex
Minor fixes

@@
 
-Generating functions is a way of describing infinite sequences using formal power series, where coefficients encode the consecutive elements.
+Generating functions are a way of describing infinite sequences using formal power series, where coefficients encode the consecutive elements.
 It allows us to incorporate many advanced methods of analysis of encoded objects.
 
-Most recursive structure can be described using a~generating function equation, which can be then solved and transformed into a~holonomic recurrence, i.e.~recurrence that in order to define \(n\)-th element of the sequence requires just finite number of previous ones and coefficients that are polynomials in \(n\).
+Most recursive structures can be described using a~generating function equation, which can be then solved and transformed into a~holonomic recurrence, i.e.~recurrence that in order to define \(n\)-th element of the sequence requires just finite number of previous ones and coefficients that are polynomials in \(n\).
 
@@
 
-Lambda terms are very popular structures used for analyzing functions and programming languages.
-Their very simple recursive definition makes them very attractive.
-A better understanding of them could allow us improving programming language compilers and in consequence improve every aspect of our lives.
-The interpretation of holonomic recurrence for lambda trees itself could allow us to discover new ways of generating random lambda terms via extending smaller ones in similar way to Rémy's algorithm for sampling binary trees~\cite{remy,note}.
+Lambda terms are extremely popular structures used for analyzing functions and programming languages.
+Their simple recursive definition makes them very attractive.
+A better understanding of them could allow us to improve programming language compilers and in consequence improve every aspect of our lives.
+The interpretation of holonomic recurrence for trees of lambda terms itself could allow us to discover new ways of generating random lambda terms via extending smaller ones in similar way to Rémy's algorithm for sampling binary trees~\cite{remy,note}.
 
 Throughout the thesis we try to accumulate known results and techniques that may help solving the problem of finding combinatorial interpretations.
-We also propose an~approach that helped us to find an~intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of lambda trees in the unary de Bruijn notation.
+We also propose an~approach that helped us finding an~intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of trees of lambda terms in the unary de Bruijn notation.
 We use the de Bruijn indices in order to get rid of letter-based variable names.
-Unary notation allows us to connect size of the tree to the values of the de Bruijn indices.
+Unary notation allows us to connect the size of the tree to the values of the de Bruijn indices.
 
@@
 Next, in Section~\ref{sec:known_results}, we present known results, i.e.~interpretations for binary trees, unary-binary trees and Schröder trees.
-They demonstrate few different approaches to the problem.
+They demonstrate a few different approaches to the problem.
 
@@
 
-\(V(T)\) is implicitly defined as a~set of nodes of the tree \(T\).
-
-\(E(T)\) is implicitly defined as a~set of edges of the tree \(T\).
-
 \(u, v\) are implicitly assumed to be nodes.
@@
 
-We say that node \(v\) is an~oneling \(\textiff\) \(v\) has no siblings. Note that the root is oneling even if it has no parent.
+We say that node \(v\) is an~oneling \(\textiff\) \(v\) has no siblings. Note that the root is an oneling even if it has no parent.
 
@@
 \end{minipage}
-depict edges that may or may not exist (e.g.~when we describe transformations and we do not care if the node is root or if it has children).
+depict edges that may or may not exist (e.g.~when we describe transformations and we do not care if the node is a root or if it has children).
 
@@
 
-To visualize even more, let's take a~look at the line marked with \((*)\). The highlighted terms describe following tree:
+To visualize it even more, let's take a~look at the line marked with \((*)\). The highlighted terms describe following tree:
 
@@
 
-The equivalence of these two definitions assures us that if we find an~generating function equation describing the desired objects satisfying Definition~\ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in Definition~\ref{def:holo_1}~\cite{complexity}.
+The equivalence of these two definitions assures us that if we find a~generating function equation describing the desired objects satisfying Definition~\ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in Definition~\ref{def:holo_1}~\cite{complexity}.
 
@@
 \begin{itemize}
-    \item rooted tree is a~tree with single node marked as root. This allows us to define hierarchy of nodes using such terms as parent and child;
+    \item rooted tree is a~tree with single node marked as the root. This allows us to define a hierarchy of nodes using such terms as parent and child;
     \item ordered trees introduce order on children from the leftmost to the rightmost;
     \item unlabeled trees have nodes that are not distinguishable by their label.
-We will introduce soon kinds of nodes, but you shouldn't treat them as labels, but rather way to describe the structure of the node that is already present (e.g.~we can call node with just left child an~\(l\) node, but it is not its label.
-If the right child was added to the \(l\) node, it would not be an~\(l\) node anymore).
+We will introduce soon kinds of nodes, but you shouldn't treat them as labels, but rather way to describe the structure of the node that is already present (e.g.~we can call node with just left child an~\(l\)~node, but it is not its label.
+If the right child was added to the \(l\)~node, it would not be an~\(l\)~node anymore).
 \end{itemize}
-Additionally we allow that \(n\)-ary node has some of its children unset (e.g.~we can define a~binary node with just left child set, but not right one).
-
-In order to make notation easier and unambiguous, we introduce pre-order notation of an~\(n\)-ary tree.
+Additionally we allow that an \(n\)-ary node has some of its children unset (e.g.~we can define a~binary node with just the left child set, but not the right one).
+
+In order to make the notation easier and unambiguous, we introduce a pre-order notation of an~\(n\)-ary tree.
 
 \begin{definition}
-    For single node \(v\), the pre-order notation is defined as \(\enc{v}\).
+    For a single node \(v\), the pre-order notation is defined as \(\enc{v}\).
 \end{definition}
@@
     \[\enc{T} = \enc{\troot(T)} \prod_{i=1}^{n} \enc{i\text{-th subtree of } \troot(T)}\]
-    i.e.~catenation of the identifier of the root of the tree with encoded its subtrees from left to right.
+    i.e.~catenation of the identifier of the root of the tree with its subtrees encoded from left to right.
 \end{definition}
@@
 
-You can note that the encoding of a~given tree is unique. Unfortunately, not every sequence encodes proper tree.
+You can note that the encoding of a~given tree is unique. Unfortunately, not every sequence encodes a proper tree.
 
@@
 \begin{definition}
-    \(\tSub(v)\) is defined as a~whole subtree rooted with node \(v\).
+    \(\tSub(v)\) is defined as a~whole subtree rooted with the node \(v\).
 \end{definition}
@@
 \begin{definition}
-    Let \(v\) be a~node described using \(k\)-th symbol of \(\enc{T}\).
-Notation of the prefix of \(T\) in relation to \(v\), namely \(\enc{\tPre(T, v)}\), is defined as a~prefix of \enc{T} of size \(k - 1\).
+    Let \(v\) be a~node described using the \(k\)-th symbol of\;\(\enc{T}\).
+The prefix of \(T\) in relation to \(v\), namely \(\tPre(T, v)\), is defined using pre-order notation as a~prefix of \enc{T} of size \((k - 1)\).
 \end{definition}
@@
     Let \(n\) be the length of the sequence \(\enc{T}\).
-Notation of suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined as a~suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
+The suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined using pre-order notation as a~suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
 Note that the suffix may be an ordered forest.
@@
 
-In other words, prefix of the tree \(T\) in relation to \(v\) describes a~part of the tree that appears before subtree rooted in \(v\) in pre-order notation.
-Suffix describes part of the tree that appears after it.
+In other words, the prefix of the tree \(T\) in relation to \(v\) describes a~part of the tree that appears before the subtree rooted in \(v\) in pre-order notation.
+Suffix describes a part of the tree that appears after it.
 
@@
 
-Throughout thesis we define some operations using this notation.
-Valid pre-order notation of \(n\)-ary tree (note that not all sequences are valid pre-order notations) can be easily translated back into a~tree.
-In order to do so, we just take first symbol of the notation and create the root accordingly.
-Then for each of the \(n\) children of the root, in sequence, we decode it recursively as if it was whole tree.
+Throughout the thesis we define some operations using this notation.
+Valid pre-order notation of an \(n\)-ary tree (note that not all sequences are valid pre-order notations) can be easily translated back into a~tree.
+In order to do so, we just take the first symbol of the notation and create the root accordingly.
+Then for each of the \(n\) children of the root, in sequence, we decode it recursively as if it was a whole tree.
 Each such operation consumes some prefix of the notation.
@@
 In this section we show combinatorial interpretations of holonomic recurrences for binary trees, unary-binary trees and Schröder trees.
-As to our knowledge these are only tree classes that have commonly known interpretations.
+As to our knowledge these are the only tree classes that have commonly known combinatorial interpretations.
 Also the thought process leading to these interpretations is not obvious.
 
-Each of these interpretations has its unique character, like different selection of the size definition or different approach to arranging the terms of the holonomic recurrence.
-
-These interpretations have been source of ideas that we were incorporating in order to make our partial interpretation for the case of lambda trees in unary de Bruijn notation.
+Each of these interpretations has its unique character, like a different selection of the size definition or a different approach to arranging the terms of the holonomic recurrence.
+
+These interpretations have been a source of ideas that we were incorporating in order to make our partial interpretation for the case of trees of lambda terms in unary de Bruijn notation.
 
@@
 
-We are going to create a~bijection between the left and right side of the recurrence.
+We are going to create a~bijection between the left and the right side of the recurrence.
 We will be using the term \textit{bijective language} to talk about the recurrence using the objects it describes and their transformations.
@@
     \item \(B(n)\) is simply the set of all full binary trees of size \(n\),
-    \item \((n + 2) B(n + 1)\) is the set of all full binary trees of size \(n + 1\) with one of the leaves pointed,
-    \item \((2n + 1) B(n)\) is the set of all full binary trees of size \(n\) with one of the nodes (either internal or a~leaf) pointed (i.e.~distinguished),
+    \item \((n + 2) B(n + 1)\) is the set of all full binary trees of size \(n + 1\) with one of the leaves pointed (i.e.~distinguished),
+    \item \((2n + 1) B(n)\) is the set of all full binary trees of size \(n\) with one of the nodes (either internal or a~leaf) pointed,
     \item \(2\) at the beginning of \(2 (2n + 1) B(n)\) indicates that we will be using \(2\) copies of the set defined in the previous bullet.
@@
 
-At the moment the left side of the recurrence is related to trees of size \(n + 1\), the right, on the other hand, of size \(n\). Therefore, we need to apply some transformations on trees.
-
-Let's define two local operations for tree \(T\) with a~single node \(v\) pointed: \(R_l(T, v)\) and \(R_r(T, v)\).
+At the moment the left side of the recurrence is related to the trees of size \(n + 1\), the right, on the other hand, of size \(n\). Therefore, we need to apply some transformations on the trees.
+
+Let's define two local operations for a tree \(T\) with a~single node \(v\) pointed: \(R_l(T, v)\) and \(R_r(T, v)\).
 The term \textit{local} means that the operation can operate on just some finite fragment of a~tree with predefined size (e.g.~node and its 2 children, but cannot traverse the whole tree).
@@
 We can now take the bijective interpretation of \((2n + 1) B(n)\), i.e.~trees of size \(n\) with a~single node pointed.
-For each of such trees, namely \(T\), we create new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a~node that is pointed in \(T\).
+For each of such trees, namely \(T\), we create a new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a~node that is pointed in \(T\).
 Therefore we generate all trees from \(2(2n + 1) B(n)\).
@@
 
-The only thing that's left for us to verify is if we generate all trees of size \(n + 1\) with pointed leaves.
-As from the recursion, we know that \(2 (2n + 1) B(n)\) describe trees with single leaf pointed, it is enough to check if we do not generate any duplicate using \(R_l\) and \(R_r\).
-It can happen in 2 ways:
+The only thing that's left for us to verify is if we generate all the trees of size \(n + 1\) with pointed leaves.
+As from the recursion, we know that \(2 (2n + 1) B(n)\) describe trees with a single leaf pointed.
+It is enough to check if we do not generate any duplicate using \(R_l\) and \(R_r\).
+It can happen in only 2 ways:
 \begin{enumerate}
@@
 
-In the second case it is enough to notice that \(R_l\) generates trees with pointed nodes being a~left child, and \(R_r\) generates trees with pointed nodes being right child.
+In the second case it is enough to notice that \(R_l\) generates trees with pointed nodes being a~left child, and \(R_r\) generates trees with pointed nodes being a right child.
 That immediately provides us with the conclusion that we are generating no duplicates.
@@
 
-Let's think, what would have changed if we introduce unary nodes to the binary case~\cite{motzkin}.
+Let's think, what would have changed if we had introduced unary nodes to the binary case~\cite{motzkin}.
 
@@
 
-We will define size as number of edges. Note that a~tree having \(n\) edges has exactly \(n + 1\) nodes.
+We will define the size as a number of edges. Note that a~tree having \(n\) edges has exactly \(n + 1\) nodes.
 
@@
 
-Definition~\ref{def:unary_binary_tree} is precise, but introduces a~new kind of node that we would have to take care of.
+Though Definition~\ref{def:unary_binary_tree} is precise, it introduces a~new kind of node that we would have to take care of.
 We can avoid it by using a~trick to make unary-binary trees recall binary trees.
@@
 
-As we have added \(n + 2\) virtual nodes, we have added as many virtual edges.\todo{notes?}
+As we have added \(n + 2\) virtual leaves, we have added as many virtual edges.
 
@@
 
-Please note that \(n + 2\) matches the multiplier of \(u_n\) in holonomic equation.
+Please note that \(n + 2\) matches the multiplier of \(u_n\) in the holonomic equation.
 
 We will be using \(U(n)\) to describe sets of trees corresponding to \(u_n\) from the holonomic recurrence.
-The set \((n + 2) U(n)\) can be interpreted as trees of size \(n\) with single virtual leaf pointed.
+The set \((n + 2) U(n)\) can be interpreted as trees of size \(n\) with a single virtual leaf pointed.
 
 \begin{definition}
-    We say that node \(v\) is an~virtual-oneling \(\textiff\) \(v\) has no virtual siblings. Note that the root is an oneling even if it has no parent.
+    We say that a node \(v\) is a~virtual-oneling \(\textiff\) \(v\) has no virtual siblings. Note that the root is a~virtual-oneling even if it has no parent.
 \end{definition}
@@
 \begin{definition}
-    We say that node \(v\) is virtual-twinling \(\textiff\) \(v\) has at least one virtual sibling.
+    We say that a node \(v\) is a~virtual-twinling \(\textiff\) \(v\) has at least one virtual sibling.
 \end{definition}
@@
 \begin{definition}
-    If \(u\) is parent of \(v\), we say that sibling of \(u\) is an~uncle of \(v\).
+    If \(u\) is a parent of \(v\), we say that a sibling of \(u\) is an~uncle of \(v\).
 \end{definition}

### 2021-09-14 article/main.tex
Minor fixes

@@
         \begin{enumerate}
-            \item VrtUrv --- Vri which uncle is a~right virtual leaf;
-            \item VrtUra --- Vri which uncle is a~right actual node;
-            \item VrtUla --- Vri which uncle is a~left actual node.
+            \item VrtUrv --- Vrt which uncle is a~right virtual leaf;
+            \item VrtUra --- Vrt which uncle is a~right actual node;
+            \item VrtUla --- Vrt which uncle is a~left actual node.
         \end{enumerate}
-    \item Vlt --- virtual leaf left virtual-twinling.
-Note that from definition~\ref{def:unary_binary_2}, left virtual leave cannot have a~sibling being an~actual node.
-We can divide also this case into:
+    \item Vlt --- virtual leaf left virtual-twinling. We can divide also this case into:
         \begin{enumerate}
@@
 
-Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point to any node, as in a~tree having \(n - 1\) actual edges, we have \(n\) actual and \(n + 1\) virtual nodes.
+Let's start from \(U(n-1)\). Its multiplier is \(2n + 1\). It suggests that we can point any node, as in a~tree having \(n - 1\) actual edges, we have \(n\) actual and \(n + 1\) virtual nodes.
 
@@
 We mark pointed node with \(\pointed{}\).
-You can find the case name in the bottom left corners of cells.
+You can find the case name in the bottom left corners of the cells.
 
@@
 
-As you can see, we have satisfied all of the cases of trees from \(U(n-2)\), \(U(n-1)\) and \(U(n)\) with no repetitions, which concludes the construction.
+As you can see, we have satisfied all of the cases of trees from \(U(n-2)\), \(U(n-1)\) and \(U(n)\) with no repetitions, which concludes the interpretation.
 
@@
 
-This definition is precise, but is difficult to implement as a~structural recursion. Let's define binary structure that will allow us to encode all Schröder trees.
+This definition is precise, but it is difficult to implement as a~structural recursion. Let's define a binary structure that will allow us to encode all Schröder trees.
 
@@
         \item leaves are unweighted;
-        \item internal nodes can have weight either \(1\) or \(2\);
-        \item if an~internal node has weight 2, then its right child is not a~leaf.
+        \item internal nodes can have a weight of either \(1\) or \(2\);
+        \item if an~internal node has a weight of 2, then its right child is not a~leaf.
     \end{itemize}
@@
 
-\(\gf{T}_1\) and \(\gf{T}_1\) are generating functions of trees rooted in nodes of weight \(1\) and \(2\) respectively.
-\(\gf{T}\) is a generating function for the whole well-weighted full binary tree.
+\(\gf{T}_1(z)\) and \(\gf{T}_2(z)\) are generating functions of trees rooted in nodes of weight \(1\) and \(2\) respectively.
+\(\gf{T}(z)\) is a~generating function for the whole well-weighted full binary tree.
 
@@
 
-As we cannot use division to get \(\gf{T}_2(z)\), let's multiply the first equation by \(1 - \gf{T}(z)\).
+As we cannot use division to get \(\gf{T}_2(z)\), let's multiply the first equation by \((1 - \gf{T}(z))\).
 
@@
 
+\todo{XXX DANGEROUS NEWLINES}
 \begin{lstlisting}
@@
     \item \((2 n - 1) T(n)\) describes well-weighted binary trees of size \(n\) (i.e.~with \(n\) leaves) with some node pointed (internal or leaf),
-    \item \((n + 1) T(n + 1)\) describes well-weighted binary trees of size \(n + 1\) with some leaf pointed,
-    \item \((n - 2) T(n - 1)\) describes well-weighted binary trees of size \(n - 1\) with some internal node pointed.
+    \item \((n + 1) T(n + 1)\) describes well-weighted binary trees of size \((n + 1)\) with some leaf pointed,
+    \item \((n - 2) T(n - 1)\) describes well-weighted binary trees of size \((n - 1)\) with some internal node pointed.
 \end{itemize}
@@
 
-Let's define three transformations, \(L_1\), \(L_2\), and \(R_1\) that transform tree with a~pointed node \(s\) into bigger tree, as follows. We use dashed edges 
+Let's define three transformations, \(L_1\), \(L_2\), and \(R_1\) that transform tree with a~pointed node \(s\) into a bigger tree, as follows. We use dashed edges 
 \begin{minipage}{1.5em}
@@
 \end{minipage}
-to depict edges that may or may not exist (i.e.~when the node can have parent or child, but it does not have to). Whenever we use solid edge, we expect this edge to actually exist.
+to depict edges that may or may not exist (i.e.~when the node can have a parent or a child, but it does not have to). Whenever we use solid edge, we expect this edge to actually exist.
 
@@
 
-It is easy to show that it constructs a bijection between \((n + 1) T(n + 1)\) and subset of \((2 n - 1) T(n)\) with \(L_1\), \(L_2\) and \(R_1\) applied, not falling into case 3.
+It is easy to show that it constructs a bijection between \((n + 1) T(n + 1)\) and a subset of \((2 n - 1) T(n)\) with \(L_1\), \(L_2\) and \(R_1\) applied, not falling into case 3.
 We will show that in a~moment.
 
-To achieve trees from \((n - 2) T(n - 1)\), we can simply take trees from case 3.~and replace whole subtree with subtree of \(t''\) with its root pointed.
+To achieve trees from \((n - 2) T(n - 1)\), we can simply take trees from case 3.~and replace the whole subtree with the subtree of \(t''\) with its root pointed.
 In this way, we will lose \(2\) leaves and obtain each tree from \((n - 2) T(n - 1)\):
@@
 
-In the left column you can see all possibilities of selecting \(s\) from a~tree of size \(n\).
+In the left column you can see all the possibilities of selecting \(s\) from a~tree of size \(n\).
 In \(R_1\), \(L_1\) and \(L_2\) columns we show how they are then transformed.
-It covers all possible cases of selecting leaf from a~tree of size \(n + 1\) and selecting an~internal node from a~tree of size \(n - 1\).
+It covers all the possible cases of selecting a~leaf from a~tree of size \(n + 1\) and selecting an~internal node from a~tree of size \(n - 1\).
 
@@
 This \(+1\) can drastically clutter the holonomic recurrence.
-If we had defined the size as the number of leaves, the size of the new object would be just a~simple sum of the sizes of the smaller trees.
+If we had defined the size as the number of leaves, the size of the new object would have been just a~simple sum of the sizes of the smaller trees.
 \end{itemize}
@@
 If we describe some structure we may be tempted to use multiple kinds of nodes, e.g.~unary and binary nodes.
-Having multiple kinds of nodes may cause problems, both in creating holonomic recurrence and finding the interpretation, as we have to keep track of how they can transform.
+Having multiple kinds of nodes may cause problems, both in creating a holonomic recurrence and finding the interpretation, as we have to keep track of how they can transform.
 
@@
 We can assign weights to these objects and make the size a weighted sum.
-The weights can be variable or we can assign some other constant values (e.g.~small prime numbers).
+The weights can be variable or we can assign some constant values (e.g.~small prime numbers).
 
@@
 Another method that may help us finding the interpretation is inductive translation~\cite{doron}.
-The method is based on the idea that most of the time there is an~easy way to find some natural recurrence (not necessarily holonomic) that has simple interpretation in bijective language.
-
-In the case of binary trees with size defined as the number of leaves, we can define 2 recurrences:
+The~method is based on the idea that most of the time there is an~easy way to find some natural recurrence (not necessarily holonomic) that has simple interpretation in bijective language.
+
+In the case of binary trees with the size defined as a number of leaves, we can define 2 recurrences:
 
@@
 
-Using our inductive hypothesis, i.e.~holonomic recurrence and moving problematic boundary cases out from the sums (in this case \(b_{1}\) needs to be analyzed separately, as we did not define binary trees with no leaves), we can get the right side to use \(b_{n - 1}\) and prove that the holonomic recurrence using non-linear one.
+Using our inductive hypothesis, i.e.~holonomic recurrence and moving problematic boundary cases out from the sums (in this case \(b_{1}\) needs to be analyzed separately, as we did not define binary trees with no leaves), we can get the right side to use \(b_{n - 1}\) and prove the holonomic recurrence using non-linear one.
 The only part that is left is to translate this inductive proof to the bijective language, which in such a~simple case as binary trees is quite simple, especially if one has seen the solution once.
@@
 
-As our inspiration and main field of interest is an analysis of trees of lambda terms in unary de Bruijn notation, we will introduce them and use them as an~example to describe the method.
+As our inspiration and main field of interest is an analysis of trees of lambda terms in unary de~Bruijn notation, we will introduce them and use them as an~example to describe the method.
 
@@
 
-Lambda calculus is a formal system that allows expressing computable functions introduced by Alonzo Church.
+Lambda calculus is a formal system introduced by Alonzo Church that allows expressing computable functions.
 It is widely used in computer science and mathematics to study functions and their properties.
@@
 \begin{definition}
-    Set of lambda terms \(\Lambda\) is defined recursively:
+    The set of lambda terms \(\Lambda\) is defined recursively:
     \begin{itemize}
         \item if \(x\) is a~variable, then \(x \in \Lambda\)
-        \item if \(M, N \in \Lambda\), then \((M N) \in \Lambda\) (it can be interpreted as an application of function \(M\) to an~argument \(N\))
+        \item if \(M, N \in \Lambda\), then \((M N) \in \Lambda\) (it can be interpreted as an application of a~function \(M\) to an~argument \(N\))
         \item if \(x\) is a~variable and \(M \in \Lambda\), then \((\lambda x.
 M) \in \Lambda\) (it can be interpreted as an~abstraction, i.e.~creating a~function with an~argument \(x\) and binding each occurrence of \(x\) in \(M\) to this argument.
-We say that variable \(x\) is abstracted by this lambda-abstraction)
+We say that a variable \(x\) is abstracted by this lambda-abstraction)
     \end{itemize}
@@
 
-The definition using named variables is quite popular, but introduces several problems.
+The definition using named variables is quite popular, but it introduces several problems.
 One of them is a~problem of a potential collision of lambda-abstracted variable names and difficulty of finding to which lambda abstraction the variable is bound (or is it even a~free variable, i.e.~not bound).
@@
     \begin{itemize}
-        \item if \(n \in \N\), then \(n \in \LambdadB\) (\(n\) is a~variable bound to lambda abstraction \(n\) levels above, i.e.~if you traverse the tree of the lambda term upwards, we have to ignore \(n\) lambda-abstraction nodes and the \((n+1)\)-st one is the one binding the variable.
+        \item if \(n \in \N\), then \(n \in \LambdadB\) (\(n\) is a~variable bound to a lambda abstraction \(n\) levels above, i.e.~if you traverse the tree of the lambda term upwards, we have to ignore \(n\) lambda-abstraction nodes and the \((n+1)\)-st one is the one binding the variable.
 If we would have to go beyond the root of the tree, we say that the variable is free, i.e.~not bound)
@@
 
-As you can see, we managed to eliminate name-based variables. We can also easily check if a~given variable is bound by checking its depth.
+As you can see, we have managed to eliminate name-based variables. We can also easily check if a~given variable is bound by checking its depth.
 
@@
 \begin{definition}
-    Translation from lambda terms in de Bruijn notation to binary trees \(\Phi\) is defined as follows:
+    Translation from lambda terms in de Bruijn notation to binary trees, namely \(\Phi\), is defined as follows:
     \begin{itemize}
@@
 
-We use green edges to express the non-existing child of the node. Note that in order to get the exact value of the variable we had to take a look at a leaf with all successor nodes above it.
+We use green edges to express the non-existing child of a node. Note that in order to get the exact value of the variable we had to take a look at a leaf with all successor nodes above it.
 
@@
 
-As \(s\) represents the successor, it can be applied only to \(n \in \N\), but is applied to the lambda-abstracted term.
+As \(s\) represents the successor, it can be applied only to \(n \in \N\), but it is applied to the lambda-abstracted term.
 \end{example}
@@
         +& (n + 1) t_{n}
-\end{array}.\]
-
-Terms \(o\), \(l\), \(a\), and \(s\) appearing in the holonomic recurrence can be interpreted as list of kinds of nodes we need to use to extend smaller tree into bigger one.
+\end{array}\]
+
+Terms \(o\), \(l\), \(a\), and \(s\) appearing in the holonomic recurrence can be interpreted as a multiset of kinds of nodes we need to use to extend smaller tree into a bigger one.
 
@@
 You may notice that some summands have become oversimplified.
-For example \(((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) t_{n - 3}\) has become \(t_{n-3}\), which could be interpreted as simply set of trees of size \(n - 3\) without any pointing.
+For example \(((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) t_{n - 3}\) has become \(t_{n-3}\), which could be simply interpreted as a set of trees of size \(n - 3\) without any pointing.
 
@@
 We also created a~framework~\cite{transformator}, called Transformator, that may help visualize our work.
-It operates on binary trees and is based on the idea that every transformation expressed in bijective language is local, i.e.~transforms some node and a finite number of its surrounding nodes.
-
-To show the idea of such transformations, let's define transformation context with holes.
+It operates on binary trees and it is based on the idea that every transformation expressed in bijective language is local, i.e.~transforms some node and a finite number of its surrounding nodes.
+
+To show the idea of such transformations, let's define transformation context with holes. We will be matching them to some parts of trees.
 
@@
 Some of nodes can be left as holes, that may be later filled with trees.
-It also specifies type of the edge above the root of the context (i.e.~if that is actual edge, optional actual edge, virtual edge, or if there is no edge at all).
+It also specifies a type of the edge above the root of the context (i.e.~if that is an actual edge, optional actual edge, virtual edge, or if there is no edge at all).
+We cannot specify the direction of the edge above the root of the context (i.e.~if the root of the context has its parent on the right or left).
+\end{definition}
+
+When we match the context to a fragment of a tree, the holes will be filled with corresponding subtrees.
+
+\begin{definition}
+    The transformation is defined as a pair of transformation contexts, the starting and the target one.
 \end{definition}
@@
     \label{ex:transformation}%
-    We want to modify a node being right a child of its parent.
+    We want to modify a node being a right child of its parent.
 We do not care what is below that node (i.e.~if that is a leaf or if it has children).
-We want to add a new node of which the original one is left child.
+We want to add a new node of which the original one is a left child.
 We do not want the new node to have a right child.
@@
 \(H_1\), \(H_2\), and \(H_3\) are holes.
-Edge crossing the box around the context defines type of edge the context is connect to the rest of the tree (i.e.~optional actual edge).
+Edge crossing the box around the context defines the type of the edge by which the context is connected to the rest of the tree (i.e.~optional actual edge).
 We marked the node being described to clarify the picture.
@@
         \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_003}%
-    \item node has its parent on the left, i.e.~is right child of its parent (the node can be specified to be actual or virtual):\\
+    \item node has its parent on the left, i.e.~is a right child of its parent (the node can be specified to be actual or virtual):\\
         \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_004}%
         \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_004b}%
-    \item node has its parent on the right, i.e.~is the left child of its parent (the node can be specified to be actual or virtual):\\
+    \item node has its parent on the right, i.e.~is a left child of its parent (the node can be specified to be actual or virtual):\\
         \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_005}%
@@
 
-The latest two are introduced in order to make the analysis simpler, but do not have immediate interpretation in the world of holonomic recurrences.
+The latest two are introduced in order to make the analysis simpler, but do not have an immediate interpretation in the world of holonomic recurrences.
 However, if we use them both, it sums up to all nodes except root (as root is neither left nor right child), so in total there are \((n - 1)\) places where such a pair of contexts apply.
 
-The target of the transformation can be any context preserving all holes. This allows us to specify number of nodes added by the transformation.
+The target of the transformation can be any context preserving all holes and not decreasing the number of nodes. This allows us to specify the number of nodes added by the transformation.
 
@@
 
-Note that for each transformation we can specify number and kinds of the nodes added to the tree. Let's take a look at the transformation from Example~\ref{ex:transformation}:
+Note that for each transformation we can specify a number and kinds of the nodes added to the tree. Let's take a look at the transformation from Example~\ref{ex:transformation}:
 \begin{center}
@@
 
-We will be operating on transformation classes, sections. They will start being empty and we will be adding transformations to them.
-
-\(\tSection_\tau\), where \(\tau\) is list constructed from \(\{a, l, o, s\}\) (you can treat is as a~set, but with potential repetitions), stores transformation extending the tree with nodes \(\tau\).
-
-\(\tClass_i\), where \(i \in \N\) is defined as \(\bigcup_{\tau : |\tau| = i} \tSection_\tau\) (i.e.~set of all transformations adding exactly \(i\)~nodes to the tree).
+We will be operating on transformation classes and sections. We will begin with them being empty and then we will be adding transformations to them.
+
+\(\tSection_\tau\), where \(\tau\) is a multiset over \(\{a, l, o, s\}\), stores transformations extending the tree with nodes \(\tau\).
+
+\(\tClass_i\), where \(i \in \N\), is defined as a \(\bigcup_{\tau : |\tau| = i} \tSection_\tau\) (i.e.~set of all transformations adding exactly \(i\)~nodes to the tree).
+
+Since now we will be considering a constant \(n \in \N\) which defines a target size of the trees.
 
 We will be also talking about trees generated by the transformation.
-Let's consider constant \(n \in \N\).
-List of trees generated by the transformation from \(\tSection_\tau\) is defined as all trees generated by applying the transformation to all trees of size \((n - |\tau|)\).
-
-Analogically, we can specify list of trees generated by the \(\tSection_\tau\) and \(\tClass_i\) as list of trees generated by all transformations from them.
+Multiset of trees generated by the transformation from \(\tSection_\tau\) is defined as all trees generated by applying the transformation to all trees of size \((n - |\tau|)\).
+
+Analogically, we can specify a multiset of trees generated by the \(\tSection_\tau\) and \(\tClass_i\) as a multiset of trees generated by all transformations from them.
 
 Each section is associated with an expression coming from the holonomic recurrence.
-It defines expected number of trees that will be generated by each of them.
-Let \(k = n - |\tau|\) for each \(\tSection_\tau\).
-In the case of trees of lambda terms, we get following expressions associated to each section:
-
+It defines expected number of trees that will be generated by each of the sections.
+Let \(k := n - |\tau|\) for each \(\tSection_\tau\).
+
+Let's remind ourselves the holonomic recurrence for trees of lambda terms:
+
+\[\begin{array}{rl}
+        0 =& (n - 4) l^2 s^2 t_{n - 4}\\
+        +& ((4 n - 10) a o s - (2 n - 6) l^2 s - (2 n - 5) l s^2) t_{n - 3}\\
+        +& ((-4 n + 8) a o + (n - 2) l^2 + (4 n - 6) l s + (n - 1) s^2) t_{n - 2}\\
+        +& ((-2 n + 1) l - 2 n s) t_{n - 1}\\
+        +& (n + 1) t_{n}
+\end{array}\]
+
+The expressions associated to each section are then:
+
+\todo{make a table}
 \[\begin{array}{lcr}
@@
 
-Using \(k\) instead of \(n\) makes it easier to interpret, as we immediately see number of trees that should be generated by each section.
+Using \(k\) instead of \(n\) makes it easier to interpret, as we see number of trees that should be generated by each section.
 For example \(\tSection_{\{ll\}}\) should generate \(k t_k\) trees from trees of size \(k\), which can be interpreted as taking each actual node and adding two \(l\) nodes above it.
@@
 Note that some of these expressions will evaluate to negative numbers.
-It is because of the fact that sum of all sections is equal to zero.
+It is because of the fact that sum of all expressions should evaluate to zero.
 We will be generating two kinds of trees then: positive (contributing to the total number of trees being generated as \(1\)) and negative ones (contributing as \(-1\)).
@@
     \item \verb|[ ]| at the beginning means that we still need to generate some more trees. If we have generated all of them, it would be \verb|[x]|;
-    \item \verb|0,0| is class and section identifier, i.e. \(|\tau|\) and arbitrarily assigned section identifier;
+    \item \verb|0,0| is class and section identifier, i.e. \(|\tau|\) and arbitrarily assigned number;
     \item \verb|0 of 16| means that we have generated \(0\) trees from \(16\) expected;
@@
 From statistics above, we see that we should generate \(16\) trees.
-\((k + 1)\) suggests pointing to a~virtual leaf.
+\((k + 1)\) suggests pointing a~virtual leaf.
 Let's do so.
-We do that by defining following transformation:
+We do that by defining a following transformation:
 
@@
 We also get the \verb|Diff stats|.
-It shows us information about how we have unbalanced the positive and negative side of our equation.
-At the end we want to generate the same list of trees at the negative and positive site.
+It shows us information about how we have unbalanced the negative and positive side of our equation.
+At the end we want to generate the same multiset of trees at the negative and positive side.
 
@@
 
-We can also query Transformator framework to visualize the trees that are unbalanced. For \(\tClass_0\) those are:
+We can also query Transformator framework to visualize the trees that led to unbalance. For \(\tClass_0\) those are:
 
@@
 
-We need to generate all of these trees on the negative side of the equation.
+Since all thos trees are positive, we need to generate their negative counterpart.
 Let's take a look at the line (1).
@@
 
-It addresses all cases from the line (1), but also introduces an~incorrect lambda tree in which \(s\) node is the parent of \(l\) node, which cannot happen (i.e.~such tree does not correspond to valid lambda term).
+It addresses all cases from the line (1), but also introduces an~incorrect lambda tree in which \(s\) node is the parent of \(l\) node (such tree does not correspond to valid lambda term).
+However, we allow that.
 To mitigate this problem we will later use \(\tSection_{\{ls\}}\) and generate positive trees where \(s\) node is parent of \(l\) node.
@@
 \includeinlinesvg{.20}{lambda__trees_203__0}%
+
+These are exactly the trees we need.
 
@@
 
-Note that we have gotten rid of the \(\tSection_\emptyset\) in \verb|Diff stats|. It means that we have generated all negative counterpart of the trees generated by that.
-
-If we increase \(n\) (i.e.~target size of the trees), this construction still works:
+Note that we have gotten rid of the \(\tSection_\emptyset\) in \verb|Diff stats|. It means that we have generated all negative counterpart of the trees generated by this section.
+
+If we increase \(n\) (i.e.~target size of the trees), this construction still works. Here \(n = 10\):
 
@@
 The process can then be repeated for each section.
-We have chosen lexicographical order (i.e.~\(\tSection_\emptyset\); \(\tSection_{\{l\}}\); \(\tSection_{\{s\}}\); \(\tSection_{\{ao\}}\); \(\tSection_{\{ll\}}\); \(\ldots\)).
+We have chosen the order as above (i.e.~\(\tSection_\emptyset\); \(\tSection_{\{l\}}\); \(\tSection_{\{s\}}\); \(\tSection_{\{ao\}}\); \(\tSection_{\{ll\}}\); \(\ldots\)).
 
@@
 
-As you can see, \verb|Diff stats| are empty, so we managed to generate expected trees on both sides of the equation.
+As you can see, \verb|Diff stats| are empty, so we managed to generate two equal multisets of positive and negative trees.
 
@@
 
-You may remember our assumptions in Section~\ref{sub:the_framework} about the discrimination cases.
-We allowed ourselves to apply visitors only to one of the left and right children, which is not handled by our holonomic recurrence as the number of such nodes does not depend only on \(n\).
-
-To fix this, one can for example add construction for \(\tSection_{\{s\}}\) to generate all expected trees from it and then repeat the iteration in order to generate matching trees on the other side of the equation.
-We can see that we used \(2\) constructions visiting nodes with right parent and only one visiting node having left parent, so our missing construction should also visit nodes with left parent.
+You may remember our assumptions in Section~\ref{sub:the_framework} about the starting transformation contexts.
+We allowed ourselves to create transformations where the node was a left or a right child, which is not handled by our holonomic recurrence as the number of such nodes does not depend only on \(n\).
+
+To fix this, one can for example add transformation to \(\tSection_{\{s\}}\) to generate trees so that the total number of trees generated by \(\tSection_{\{s\}}\) is equal to the value of the expression associated with it.
+We can see that we used \(2\) constructions visiting nodes with a right parent and only one visiting node having a left parent, so our missing transformation should also visit nodes with left parent.
 
@@
 
-Please note that it is only an~example of missing construction. It is just the simplest one we could think about, and in that case, a~simple solution is most often the correct one.
+Please note that it is only an~example of missing transformation. It is just the simplest one we could think about, and in that case, a~simple solution is most often the correct one.
 
@@
 
-First thing to be done, that comes to mind immediately, is to finish the construction eliminating the cheat mentioned in Section~\ref{sub:the_cheat}.
+First thing to be done, that comes to mind immediately, is to finish the transformation eliminating the cheat mentioned in Section~\ref{sub:the_cheat}.
 
@@
 The probability that we miss some corner case is low, but even if we check large \(N\) values, it is always present.
-The formal algebraic proof would make us sure that the construction works.
-We would prioritize finishing the construction first.
+The formal algebraic proof would make us sure that the transformation works.
+We would prioritize finishing the transformation first.
 

### 2021-09-15 article/main.tex
Pre-release

@@
 
-\usepackage{todonotes}
+\usepackage[disable]{todonotes}
 \setlength{\marginparwidth}{2.5cm}
@@
 
-Generating functions are a way of describing infinite sequences using formal power series, where coefficients encode the consecutive elements.
-It allows us to incorporate many advanced methods of analysis of encoded objects.
-
-Most recursive structures can be described using a~generating function equation, which can be then solved and transformed into a~holonomic recurrence, i.e.~recurrence that in order to define \(n\)-th element of the sequence requires just finite number of previous ones and coefficients that are polynomials in \(n\).
-
-It allows us to quickly count objects of given structure with given size.
-At first glance, the recurrence seems to be closely related to the structure itself.
-It just seems like it should describe simple transformations resulting in constructing bigger objects from slightly smaller ones.
+Generating functions are a way of describing infinite sequences using formal power series, whose coefficients encode the consecutive elements.
+They allow us to incorporate many advanced methods of analysis of encoded objects.
+
+Many recursive structures can be described using a~generating function equation, which can be then solved and transformed into a~holonomic recurrence, i.e.~a~recurrence that in order to define the \(n\)-th element of the sequence requires just a finite number of previous ones and coefficients that are polynomials in \(n\).
+
+Holonomic recurrences allow us to quickly count objects of a given structure of a given size.
+At the first glance, the recurrence seems to be closely related to the associated structure.
+It just seems like it should describe some simple transformations resulting in constructing bigger objects from slightly smaller ones.
 In case of trees it could be for example adding nodes.
-However, there is no known method of interpreting it in the language of the combinatorial structures.
-
-Up to today only a few interpretations of holonomic recurrences on trees have been found, including interpretation of holonomic recurrences for binary trees~\cite{binary}, unary-binary trees~\cite{motzkin}, and Schröder trees~\cite{schroder}.
+However, there is no known method of interpreting the holonomic recurrence in the language of the combinatorial structures.
+
+Up to today only a few interpretations of holonomic recurrences on trees have been found, including interpretations of holonomic recurrences for binary trees~\cite{binary}, unary-binary trees~\cite{motzkin}, and Schröder trees~\cite{schroder}.
 Unfortunately, the mentioned interpretations do not come with a method of finding them that could be generalized to more complex cases.
@@
 A better understanding of them could allow us to improve programming language compilers and in consequence improve every aspect of our lives.
-The interpretation of holonomic recurrence for trees of lambda terms itself could allow us to discover new ways of generating random lambda terms via extending smaller ones in similar way to Rémy's algorithm for sampling binary trees~\cite{remy,note}.
+The interpretation of a holonomic recurrence for trees of lambda terms itself could allow us to discover new ways of generating random lambda terms via extending smaller ones in a similar way to Rémy's algorithm for sampling binary trees~\cite{remy,note}.
 
 Throughout the thesis we try to accumulate known results and techniques that may help solving the problem of finding combinatorial interpretations.
-We also propose an~approach that helped us finding an~intermediate solution for the problem of finding combinatorial interpretation for holonomic recurrence of trees of lambda terms in the unary de Bruijn notation.
+We also propose an~approach that helped us to provide an~intermediate solution for the problem of finding combinatorial interpretation for a holonomic recurrence of trees of lambda terms in the unary de Bruijn notation.
 We use the de Bruijn indices in order to get rid of letter-based variable names.
-Unary notation allows us to connect the size of the tree to the values of the de Bruijn indices.
+The unary notation allows us to connect the size of a tree to the values of the de Bruijn indices.
 
@@
 
-In Section~\ref{sec:approaches} we show approaches to the problem that helped to achieve the aforementioned results.
-All of them were tried in order to find the answer to the original problem of interpreting holonomic recurrence of trees of lambda terms in the unary de Bruijn notation.
+In Section~\ref{sec:approaches} we show approaches to the problem that helped us to achieve the aforementioned results.
+All of them were tried in order to find an answer to the original problem of interpreting the holonomic recurrence of trees of lambda terms in the unary de Bruijn notation.
 Unfortunately, none of them helped us enough to get the final result.
@@
 
-\(\poly\) is a~set of all polynomials.
+\(\poly\) is a~set of all polynomials.\todo{Fix poly definition}
 
@@
 
-\(f^{(n)}\) is implicitly defined as \(n\)-th derivative of function \(f\).
+\(f^{(n)}\) is implicitly defined as the \(n\)-th derivative of a function \(f\).
 
@@
 
-Sibling of the node \(v\) is defined as the node \(u\) having the same parent as \(v\).
-
-Uncle of the node \(v\) is defined as the~sibling of the parent of \(v\).
-
-We say that node \(v\) is an~oneling \(\textiff\) \(v\) has no siblings. Note that the root is an oneling even if it has no parent.
-
-We say that node \(v\) is a~twinling \(\textiff\) \(v\) has at least one sibling.
+Sibling of a node \(v\) is defined as a node \(u\) having the same parent as \(v\).
+
+Uncle of a node \(v\) is defined as a~sibling of the parent of \(v\).
+
+We say that a node \(v\) is an~oneling \(\textiff\) \(v\) has no siblings. Note that the root is an oneling even if it has no parent.
+
+We say that a node \(v\) is a~twinling \(\textiff\) \(v\) has at least one sibling.
 
@@
 
-Virtual node is an~artificially defined node that does not affect the structure definition (e.g.~we can define virtual leafs that are children of actual leaves of the binary tree.
+Virtual node is an~artificially defined node that does not affect the definition of a structure (e.g.~we can define virtual leafs that are children of actual leaves of a binary tree.
 Such virtual leaves are not included when counting the number of children of the node, so the actual leaves are still called leaves).
@@
 
-We say that node \(v\) is an~virtual-oneling \(\textiff\) \(v\) has no siblings being virtual nodes.
-
-We say that node \(v\) is virtual-twinling \(\textiff\) \(v\) has at least one sibling being virtual node.
-
-For a~binary tree, we say that node \(v\) is right (left) \(\textiff\) \(v\) is a~right (left) child of its parent.
-
-For a~binary tree, we say that node \(v\) has a~right (left) parent \(u\) \(\textiff\) \(v\) is a~left (right) child of \(u\).
+We say that a node \(v\) is a~virtual-oneling \(\textiff\) \(v\) has no siblings being a virtual nodes.
+
+We say that a node \(v\) is a~virtual-twinling \(\textiff\) \(v\) has at least one sibling being a virtual node.
+
+For a~binary tree, we say that a node \(v\) is right (left) \(\textiff\) \(v\) is a~right (left) child of its parent.
+
+For a~binary tree, we say that a node \(v\) has a~right (left) parent \(u\) \(\textiff\) \(v\) is a~left (right) child of \(u\).
 
@@
 
-Calligraphic \(\gf{X}\) is implicitly assumed to be a~generating function of the sequence \(X\) where \(X\) is any upper-case letter.
+Calligraphic \(\gf{X}\) is implicitly assumed to be a~generating function of the sequence \(X\), where \(X\) is any upper-case letter.
 
@@
 
-Note that in order to compute the \(k\)-th element of the sequence, namely \(a_k\), we just need to find the~constant corresponding to indeterminate \(z^k\).
-
-If we have a sequence counting some objects and a corresponding generating function, we say that this function counts the objects.
+Note that in order to compute the \(k\)-th element of the sequence, namely \(a_k\), we just need to find the~constant corresponding to the indeterminate \(z^k\).
+
+If we have a sequence counting some objects and the corresponding generating function, we say that this function counts the objects.
 
@@
     Let's consider the recursive definition of binary trees shown in Figure~\ref{fig:binary_recursion}.
-We can create a~functional equation to count trees with exactly \(n\) internal nodes.
+We can construct a~functional equation involving the generating function counting trees with exactly \(n\) internal nodes.
 To do so, we make internal nodes contribute to the generating function with \(z^1 = z\) and leaves with \(z^0 = 1\):
@@
                   &=& 1 + z\bigg(1 + z\Big(1 + z\gf{B}^2(z)\Big)\Big(1 + z\gf{B}^2(z)\Big)\bigg)\bigg(1 + z\Big(1 + z\gf{B}^2(z)\Big)\Big(1 + z\gf{B}^2(z)\Big)\bigg)\\
-                  &=& 1 + z + 2 z^2 + \bigg(2 \gf{B}^2(z) + {\Big(1 + z \gf{B}^2(z)\Big)}^2\bigg) z^3
+                  &=& 1 + z + 2 z^2 + \bigg(2 \gf{B}^2(z) + {\Big(1 + z \gf{B}^2(z)\Big)}^2\bigg) z^3.
 \end{array}\]
@@
 It is enough, as the term \(\bigg(2 \gf{B}^2(z) + {\Big(1 + z \gf{B}^2(z)\Big)}^2\bigg) z^3\) will contribute only to \(z^k\) where \(k > 2\).
-Therefore, we can see that there are \(2\) trees with exactly \(2\) internal nodes, as multiplier next to \(z^2\) is \(2\).
-
-To visualize it even more, let's take a~look at the line marked with \((*)\). The highlighted terms describe following tree:
+Therefore, we can see that there are \(2\) trees with exactly \(2\) internal nodes, as the multiplier next to \(z^2\) is \(2\).
+
+To visualize it even better, let's take a~look at the line marked with \((*)\). The highlighted terms describe the following tree:
 
@@
 \begin{example}
-    The sequence \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because it satisfies
+    The sequence \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because it satisfies the following equation:
     \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0.\]
@@
 
-The equivalence of these two definitions assures us that if we find a~generating function equation describing the desired objects satisfying Definition~\ref{def:holo_2}, we will be able to find holonomic recurrence mentioned in Definition~\ref{def:holo_1}~\cite{complexity}.
+The equivalence of these two definitions assures us that if we find a~generating function equation describing the desired objects satisfying Definition~\ref{def:holo_2}, we will be able to find a holonomic recurrence mentioned in Definition~\ref{def:holo_1}~\cite{complexity}.
 
@@
     \label{ex:gfun-rec}
-    For generating function counting full binary trees defined in Example~\ref{ex:bin_gf}, i.e.:
-    \[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
+    For the generating function counting full binary trees defined in Example~\ref{ex:bin_gf}, i.e.:
+    \[\gf{B}(z) = 1 + z\gf{B}^2(z),\]
     we can use GFUN~\cite{gfun} to immediately find a~holonomic recurrence of our interest:
@@
 
-    The most interesting part for us is the relation among the finite number of consecutive elements of the sequence.
+    The most interesting part for us is the relation among the finite number of consecutive elements of the sequence \((b_n)_{n \in \N}\).
 \end{example}
@@
 Combinatorial interpretation is just a~fancy name for something you probably know and use.
-For example if you know the binomial coefficient \(\binom{n}{k}\), I bet it was introduced to you as something like: ``let's assume you have \(n\) distinguishable balls.
+For example if you know the binomial coefficient \(\binom{n}{k}\), we can bet it was introduced to you as something like: ``let's assume you have \(n\) distinguishable balls.
 If you want to choose \(k\) from them, then you can do it in \(\binom{n}{k}\) ways'' and now, whenever you see the term \(\binom{n}{k}\), you interpret it as the number of ways to choose \(k\) objects from the set of size \(n\).
-This is the combinatorial interpretation of the binomial coefficient.
+This is a combinatorial interpretation of the binomial coefficient.
 
@@
 
-In the thesis we try to gather methods and results that may be helpful for anyone trying to find such an~interpretation, as we believe that it may give better insight into the nature of the structure and make it easier to study the structure's properties.
+In the thesis we try to gather methods and results that may be helpful for anyone trying to find such an~interpretation, as we believe that it may give a better insight into the nature of the structure and make it easier to study structure's properties.
 
@@
 
-In the thesis, if not stated otherwise, we will be working on rooted ordered unlabeled \(n\)-ary trees. To understand the terms, let's define them:
+In the thesis, if not stated otherwise, we will be working with rooted ordered unlabeled \(n\)-ary trees. To understand the terms, let's define them:
 \begin{itemize}
-    \item rooted tree is a~tree with single node marked as the root. This allows us to define a hierarchy of nodes using such terms as parent and child;
-    \item ordered trees introduce order on children from the leftmost to the rightmost;
-    \item unlabeled trees have nodes that are not distinguishable by their label.
-We will introduce soon kinds of nodes, but you shouldn't treat them as labels, but rather way to describe the structure of the node that is already present (e.g.~we can call node with just left child an~\(l\)~node, but it is not its label.
+    \item rooted tree is a~tree with a single node marked as the root. This allows us to define a hierarchy of nodes using such terms as parent and child;
+    \item ordered trees introduce an order on children from the leftmost to the rightmost;
+    \item unlabeled trees have nodes that do not have any labels we could use to distinguish them.
+We will introduce soon kinds of nodes, but you shouldn't treat them as labels, but rather a way to describe the structure of a node that is already present (e.g.~we can call a node with just a left child an~\(l\)~node, but it is not its label.
 If the right child was added to the \(l\)~node, it would not be an~\(l\)~node anymore).
 \end{itemize}
-Additionally we allow that an \(n\)-ary node has some of its children unset (e.g.~we can define a~binary node with just the left child set, but not the right one).
+Additionally we allow an \(n\)-ary node to have some of its children unset (e.g.~we can define a~binary node with just the left child set, but not the right one).
 
@@
 \begin{definition}
-    For a single node \(v\), the pre-order notation is defined as \(\enc{v}\).
-\end{definition}
-
-Here, \(\enc{v}\) is defined as follows:
+    For a single node \(v\), the pre-order notation is defined as \(\enc{v}\), where:
+
     \begin{itemize}
@@
     \end{itemize}
+\end{definition}
 
@@
 You can note that the encoding of a~given tree is unique. Unfortunately, not every sequence encodes a proper tree.
+\todo{example}
 
@@
     Let \(v\) be a~node described using the \(k\)-th symbol of\;\(\enc{T}\).
-The prefix of \(T\) in relation to \(v\), namely \(\tPre(T, v)\), is defined using pre-order notation as a~prefix of \enc{T} of size \((k - 1)\).
+The prefix of \(T\) in relation to \(v\), namely \(\tPre(T, v)\), is defined using the pre-order notation as a~prefix of \enc{T} of size \((k - 1)\).
 \end{definition}
@@
     Let \(n\) be the length of the sequence \(\enc{T}\).
-The suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined using pre-order notation as a~suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
-Note that the suffix may be an ordered forest.
-\end{definition}
-
-In other words, the prefix of the tree \(T\) in relation to \(v\) describes a~part of the tree that appears before the subtree rooted in \(v\) in pre-order notation.
-Suffix describes a part of the tree that appears after it.
+The suffix of \(T\) in relation to \(v\), namely \(\enc{\tSuf(T, v)}\), is defined using the pre-order notation as a~suffix of \enc{T} of size \(n - \size{\enc{\tPre(T, v)}} - \size{\enc{\tSub(v)}}\).
+Note that the suffix is an ordered forest (not necessarily a single tree).
+\end{definition}
+
+In other words, the prefix of a tree \(T\) in relation to \(v\) describes a~part of the tree that appears before the subtree rooted in \(v\) in the pre-order notation.
+The suffix describes a part of the tree that appears after it.
 
@@
 Throughout the thesis we define some operations using this notation.
-Valid pre-order notation of an \(n\)-ary tree (note that not all sequences are valid pre-order notations) can be easily translated back into a~tree.
+A valid pre-order notation of an \(n\)-ary tree (note that not all sequences are valid pre-order notations) can be easily translated back into a~tree.
 In order to do so, we just take the first symbol of the notation and create the root accordingly.
@@
 
-As \(T\) and \(\enc{T}\) describe the same structures, notation of trees \(T\) and its encoding \(\enc{T}\) will be used interchangeably.
+As \(T\) and \(\enc{T}\) describe the same structures, notation of a tree \(T\) and its encoding \(\enc{T}\) will be used interchangeably.
 
@@
 As to our knowledge these are the only tree classes that have commonly known combinatorial interpretations.
-Also the thought process leading to these interpretations is not obvious.
-
-Each of these interpretations has its unique character, like a different selection of the size definition or a different approach to arranging the terms of the holonomic recurrence.
-
-These interpretations have been a source of ideas that we were incorporating in order to make our partial interpretation for the case of trees of lambda terms in unary de Bruijn notation.
+Moreover, the thought process leading to these interpretations is not obvious.
+
+Each of these interpretations has its unique character, like a different selection of the size definition or a different approach to arranging the terms of a holonomic recurrence.
+
+These interpretations have been a source of ideas that we were incorporating in order to make our partial interpretation for the case of trees of lambda terms in the unary de Bruijn notation.
 
@@
 
-Let's start with probably the most known interpretation, full binary trees~\cite{binary}.
+Let's start with probably the most known interpretation, namely for full binary trees~\cite{binary}.
 
@@
 
-\[\gf{B}(z) = 1 + z\gf{B}^2(z)\]
+\[\gf{B}(z) = 1 + z\gf{B}^2(z).\]
 
@@
 
-This equation actually have \(2\) solutions, but we can eliminate one of them due to assumption that we are counting objects, i.e.~we are interested only in solutions that give us natural numbers.
+That equation has actually \(2\) solutions, but we can eliminate one of them due to assumption that we are counting objects, i.e.~we are interested only in solutions that give us natural numbers.
 
@@
 It is easy to see that a~tree of size \(n\) (i.e.~with \(n\) internal nodes) has \(n + 1\) leaves and therefore \(2n + 1\) nodes in total.
-Analogically the tree of size \(n + 1\) has \(n + 2\) leaves and \(2n + 3\) nodes in total.
+Analogically a tree of size \(n + 1\) has \(n + 2\) leaves and \(2n + 3\) nodes in total.
 If you see some resemblance to our holonomic recurrence, you are perfectly right.
@@
 
-At the moment the left side of the recurrence is related to the trees of size \(n + 1\), the right, on the other hand, of size \(n\). Therefore, we need to apply some transformations on the trees.
-
-Let's define two local operations for a tree \(T\) with a~single node \(v\) pointed: \(R_l(T, v)\) and \(R_r(T, v)\).
-The term \textit{local} means that the operation can operate on just some finite fragment of a~tree with predefined size (e.g.~node and its 2 children, but cannot traverse the whole tree).
+At the moment the left side of the recurrence is related to trees of size \(n + 1\), the right, on the other hand, of size \(n\). Therefore, we need to apply some transformations on the trees.
+
+Let's define two local operations on a tree \(T\) with a~single node \(v\) pointed: \(R_l(T, v)\) and \(R_r(T, v)\).
+The term \textit{local} means that the operation can operate on just some finite fragment of a~tree with predefined size (e.g.~a~node and its 2 children, but cannot traverse the whole tree).
 
 \begin{definition}
-    \(\enc{R_l(T, v)} = \enc{\tPre(T, v)} \n \pointed{\n} \no \no \enc{\tSub(v)} \enc{\tSuf(T, v)}\)
+    \(\enc{R_l(T, v)} := \enc{\tPre(T, v)} \n \pointed{\n} \no \no \enc{\tSub(v)} \enc{\tSuf(T, v)}\)
 \end{definition}
@@
 \begin{definition}
-    \(\enc{R_r(T, v)} = \enc{\tPre(T, v)} \n \enc{\tSub(v)} \pointed{\n} \no \no \enc{\tSuf(T, v)} \)
+    \(\enc{R_r(T, v)} := \enc{\tPre(T, v)} \n \enc{\tSub(v)} \pointed{\n} \no \no \enc{\tSuf(T, v)} \)
 \end{definition}
@@
 We can now take the bijective interpretation of \((2n + 1) B(n)\), i.e.~trees of size \(n\) with a~single node pointed.
-For each of such trees, namely \(T\), we create a new one by applying \(R_l\) and \(R_r\) to the pair \(T', v\), where \(T'\) is \(T\) with removed pointers and \(v\) is a~node that is pointed in \(T\).
+For each of such trees, namely \(T\), we create a new one by applying \(R_l\) and \(R_r\) to the pair \((T', v)\), where \(T'\) is \(T\) with removed pointers and \(v\) is a~node that is pointed in \(T\).
 Therefore we generate all trees from \(2(2n + 1) B(n)\).
@@
 
-The only thing that's left for us to verify is if we generate all the trees of size \(n + 1\) with pointed leaves.
-As from the recursion, we know that \(2 (2n + 1) B(n)\) describe trees with a single leaf pointed.
-It is enough to check if we do not generate any duplicate using \(R_l\) and \(R_r\).
+The only thing that is left for us is to verify if we generate all the trees of size \(n + 1\) with pointed leaves.
+As from the recursion, we know that \(2 (2n + 1) B(n)\) describes trees with a single leaf pointed.
+It is enough to check if we do not generate any duplicates using \(R_l\) and \(R_r\).
 It can happen in only 2 ways:
@@
 
-First case can also be split into 2 subcases. Without loss of generality we can analyze just one of the operations, let it be \(R_l\). The second case is symmetric.
+The first case can also be split into 2 subcases. Without loss of generality we can analyze just one of the operations, let it be \(R_l\). The second case is symmetric.
 \begin{itemize}
-    \item for some nodes \(u \neq v\), \(R_l(T, u) = R_l(T, v)\).
+    \item For some distinct nodes \(u\) and \(v\), \(R_l(T, u) = R_l(T, v)\).
 Let \(i_u, i_v\) be the indices of respectively \(\enc{u}\) and \(\enc{v}\) in \(\enc{T}\).
-Let \(\pointed{i}_u, \pointed{i}_v\) be the indices of pointed node respectively in \(\enc{R_l(T, u)}\) and \(\enc{R_l(T, v)}\).
+Let \(\pointed{i}_u, \pointed{i}_v\) be the indices of a pointed node respectively in \(\enc{R_l(T, u)}\) and \(\enc{R_l(T, v)}\).
 Due to the definition of \(R_l\), we get that \(\pointed{i}_u = i_u + 1\) and \(\pointed{i}_v = i_v + 1\), which implies that \(u = v\) what we assumed false.
-    \item for some trees \(T \neq S\), \(R_l(T, u) = R_l(S, v)\).
+    \item For some trees \(T \neq S\), \(R_l(T, u) = R_l(S, v)\).
 Let \(i_u, i_v\) be the indices of respectively \(\enc{u}\) in \(\enc{T}\) and \(\enc{v}\) in \(\enc{S}\).
-Let \(\pointed{i}_u, \pointed{i}_v\) be the indices of pointed node respectively in \(\enc{R_l(T, u)}\) and \(\enc{R_l(S, v)}\).
+Let \(\pointed{i}_u, \pointed{i}_v\) be the indices of a pointed node respectively in \(\enc{R_l(T, u)}\) and \(\enc{R_l(S, v)}\).
 If \(\pointed{i}_u \neq \pointed{i}_v\), this case is trivially false, so we can assume that \(\pointed{i}_u = \pointed{i}_v\).
@@
 In the second case it is enough to notice that \(R_l\) generates trees with pointed nodes being a~left child, and \(R_r\) generates trees with pointed nodes being a right child.
-That immediately provides us with the conclusion that we are generating no duplicates.
+This immediately provides us with the conclusion that we are generating no duplicates.
 
@@
     \label{def:unary_binary_tree}
-    An unary-binary tree is an~ordered tree in which any node can have either 0, 1 or 2 children.
-\end{definition}
-
-We do not allow nodes with gaps here, e.g.~a~binary node with just one child or unary node with no children.
-
-We will define the size as a number of edges. Note that a~tree having \(n\) edges has exactly \(n + 1\) nodes.
-
-We can easily derive the generating function:
-
-\[\gf{U}(z) = 1 + z\gf{U}(z) + z^2 \gf{U}^2(z)\]
-
-And with a~bit of Maple magic~\cite{gfun}, we immediately get the following recurrence:
-
-\[(n + 2)u_{n} = (2n + 1)u_{n - 1} + 3(n - 1)u_{n - 2}\]
+    A unary-binary tree is an~ordered tree in which any node can have either 0, 1 or 2 children.
+\end{definition}
+
+We do not allow nodes with gaps here, e.g.~a~binary node with just one child or a unary node with no children.
+
+We will define the size of a tree as the number of the edges. Note that a~tree having \(n\) edges has exactly \(n + 1\) nodes.
+
+We can easily derive the generating function equation:
+
+\[\gf{U}(z) = 1 + z\gf{U}(z) + z^2 \gf{U}^2(z).\]
+
+With a~bit of Maple magic~\cite{gfun}, we immediately get the following recurrence:
 
@@
     A left-leaning binary tree is a~binary tree with the following constraint added: if a~node has a~right child, it also has a~left child.
-Of course a node with just a left child can appear in such tree.
+Of course a node with just a left child can appear in such a tree.
 \end{definition}
@@
 The other cases translate immediately to themselves.
-Please note that this transformation preserves the size of the tree (i.e.~number of edges).
+Please note that this transformation preserves the size of a tree (i.e.~the~number of edges).
 
@@
 \begin{definition}
-    Virtual node is an~artificially defined node that does not affect the structure definition (i.e.~they are not included when counting the number of children of the node).
+    A virtual node is an~artificially defined node that does not affect the structure definition (i.e.~it is not included when counting the number of children of the node).
 \end{definition}
@@
 \begin{definition}
-    Actual node is a~node that is not virtual.
+    An actual node is a~node that is not virtual.
 \end{definition}
@@
 
-We will be using \(U(n)\) to describe sets of trees corresponding to \(u_n\) from the holonomic recurrence.
-The set \((n + 2) U(n)\) can be interpreted as trees of size \(n\) with a single virtual leaf pointed.
+We will be using \(U(n)\) to describe the set of trees corresponding to \(u_n\) from the holonomic recurrence.
+The set \((n + 2) U(n)\) can be interpreted as the set of trees of size \(n\) with a single virtual leaf pointed.
 
@@
 \begin{interpretation}
-To present the interpretation in bijective language, we will have to introduce several types of the nodes.
+To present the interpretation in the bijective language, we will have to introduce several types of nodes.
 
 \begin{enumerate}
-    \item Vro --- virtual leaf being right virtual-oneling;
-    \item Vrt --- virtual leaf being right virtual-twinling. We will divide this case into:
+    \item Vro --- virtual leaf being a~right virtual-oneling;
+    \item Vrt --- virtual leaf being a~right virtual-twinling. We will divide this case into:
         \begin{enumerate}
@@
         \end{enumerate}
-    \item Vlt --- virtual leaf left virtual-twinling. We can divide also this case into:
+    \item Vlt --- virtual leaf being a~left virtual-twinling. We can divide also this case into:
         \begin{enumerate}
@@
 
-All we need to show are transformations from the smaller cases, i.e.~pointed trees from \(U(n-1)\) and \(U(n-2)\) to \(U(n)\).
+All we need to show are transformations from smaller cases, i.e.~pointed trees from \(U(n-1)\) and \(U(n-2)\) to \(U(n)\).
 
@@
 
-In the case of \(U(n-2)\), the multiplier is \(3(n-1)\), which suggests that we should perform \(3\) distinct types of transformations on the trees with a~pointed actual node.
+In the case of \(U(n-2)\), the multiplier is \(3(n-1)\), which suggests that we should perform \(3\) distinct types of transformations on trees with a~pointed actual node.
 
 In the table below we show transformations that are applied to trees from \(U(n-1)\) and \(U(n-2)\) in order to achieve trees from \(U(n)\).
-We mark pointed node with \(\pointed{}\).
-You can find the case name in the bottom left corners of the cells.
+We mark a pointed node with \(\pointed{}\).
+You can find the case name in the bottom left corner of each cell.
 
@@
     \label{def:schroder_tree}
-    A Schröder tree is a~tree with no unary nodes. Empty children are not allowed (e.g.~binary node with just one child).
+    A Schröder tree is a~tree with no unary nodes. Empty children are not allowed (e.g.~a~binary node with just one child).
 \end{definition}
@@
 
-Let's represent node \(v\) with a~weight \(n\) as \(v\weighted{n}\).
-
-We can easily define the bijection \(\Phi\) between models from Definition~\ref{def:schroder_tree} and~\ref{def:well_weighted} using pre-order notation:
+Let's represent node \(v\) with a~weight \(w\) as \(v\weighted{w}\).
+
+We can easily define the bijection \(\Phi\) between models from Definition~\ref{def:schroder_tree} and~\ref{def:well_weighted} using the pre-order notation:
 \[\Phi(T) = \left\{\begin{array}{lcl}
@@
 
-Let's define the size of the tree as a~number of its leaves. As leaves are translated to leaves and internal nodes to internal nodes, the bijection \(\Phi\) is size-preserving.
+Let's define the size of a tree as the~number of its leaves. As leaves are translated to leaves and internal nodes to internal nodes, the bijection \(\Phi\) is size-preserving.
 
@@
             \gf{T}_1(z) &=& \gf{T}^2(z)\\
-            \gf{T}_2(z) &=& \gf{T}(z)(\gf{T}_1(z) + \gf{T}_2(z))
+            \gf{T}_2(z) &=& \gf{T}(z)(\gf{T}_1(z) + \gf{T}_2(z)),
 \end{array}\right.\]
 
-\(\gf{T}_1(z)\) and \(\gf{T}_2(z)\) are generating functions of trees rooted in nodes of weight \(1\) and \(2\) respectively.
-\(\gf{T}(z)\) is a~generating function for the whole well-weighted full binary tree.
-
-To be able to use Maple to generate the corresponding recurrence, we need to transform this system of equations to a~single one. We can eliminate \(\gf{T}_1(z)\) first.
+where \(\gf{T}_1(z)\) and \(\gf{T}_2(z)\) are generating functions of trees rooted in nodes of weight \(1\) and \(2\) respectively and \(\gf{T}(z)\) is a~generating function for whole well-weighted full binary trees.
+
+To be able to use Maple to generate the corresponding recurrence, we need to transform this system of equations to a~single one. We can eliminate \(\gf{T}_1(z)\) first:
 
@@
 
-As we cannot use division to get \(\gf{T}_2(z)\), let's multiply the first equation by \((1 - \gf{T}(z))\).
-
-\[\gf{T}(z)(1 - \gf{T}(z)) = \gf{T}^2(z)(1 - \gf{T}(z)) + \gf{T}^3(z) + z(1 - \gf{T}(z))\]
+As we cannot use division to get \(\gf{T}_2(z)\), let's multiply the first equation by \((1 - \gf{T}(z))\) obtaining
+
+\[\gf{T}(z)(1 - \gf{T}(z)) = \gf{T}^2(z)(1 - \gf{T}(z)) + \gf{T}^3(z) + z(1 - \gf{T}(z)).\]
 
@@
             t_2 &=& 1\\
-            3 (2 n - 1) t_n &=& (n - 2) t_{n - 1} + (n + 1) t_{n + 1}
+            3 (2 n - 1) t_n &=& (n - 2) t_{n - 1} + (n + 1) t_{n + 1}.
 \end{array}\right.\]
 
-This may seem counterintuitive, as by default we want to describe how to generate larger cases from the smaller ones, but it will make the interpretation simpler.
-
+This may seem counterintuitive, as by default we want to describe how to generate larger cases from smaller ones, but it will make the interpretation simpler.
+
+\begin{interpretation}
 Let's translate the recurrence to the bijective language then.
+
 \begin{itemize}
@@
 
-Let's define three transformations, \(L_1\), \(L_2\), and \(R_1\) that transform tree with a~pointed node \(s\) into a bigger tree, as follows. We use dashed edges 
+Let's define three transformations, \(L_1\), \(L_2\), and \(R_1\) that transform a tree with a~pointed node \(s\) into a bigger tree, as follows. We use dashed edges 
 \begin{minipage}{1.5em}
@@
 \end{minipage}
-to depict edges that may or may not exist (i.e.~when the node can have a parent or a child, but it does not have to). Whenever we use solid edge, we expect this edge to actually exist.
+to depict edges that may or may not exist (i.e.~when the node can have a parent or a child, but it does not have to). Whenever we use a solid edge, we expect this edge to actually exist.
 
@@
 
-When \(s\) is a~leaf, we will look at its parent. It can fall into one of following cases, where \(t'\) can be any tree and \(t''\) cannot be a~leaf.
+When \(s\) is a~leaf, we will look at its parent. It can fall into one of the following cases, where \(t'\) can be any tree and \(t''\) cannot be a~leaf.
 
@@
 
-When applying \(L_2\) we achieve following cases respectively:
+When applying \(L_2\) we achieve the following cases respectively:
 
@@
 
-In case 1.~and 2.~we can just swap the labels as follows:
+In cases 1.~and 2.~we can just swap the labels as follows:
 
@@
 
-        \includeinlinescaledsvg{.23}{.35}{schroder__proof__21} &
+        \includeinlinescaledsvg{.16}{.35}{schroder__proof__21} &
         \(\Rightarrow\)&
@@
 
-        \includeinlinescaledsvg{.23}{.35}{schroder__proof__11} &
+        \includeinlinescaledsvg{.16}{.35}{schroder__proof__11} &
         \(\Rightarrow\)&
@@
 
-        \includeinlinescaledsvg{.23}{.35}{schroder__proof__31} &
+        \includeinlinescaledsvg{.16}{.35}{schroder__proof__31} &
         \(\Rightarrow\)&
@@
 
-        \includeinlinescaledsvg{.23}{.35}{schroder__proof__51} &
+        \includeinlinescaledsvg{.16}{.35}{schroder__proof__51} &
         \(\Rightarrow\)&
@@
 
-        \includeinlinescaledsvg{.23}{.35}{schroder__proof__41} &
+        \includeinlinescaledsvg{.16}{.35}{schroder__proof__41} &
         \(\Rightarrow\)&
@@
 
-        \includeinlinescaledsvg{.23}{.35}{schroder__proof__61} &
+        \includeinlinescaledsvg{.16}{.35}{schroder__proof__61} &
         \(\Rightarrow\)&
@@
 
-        \includeinlinescaledsvg{.23}{.35}{schroder__proof__71} &
+        \includeinlinescaledsvg{.16}{.35}{schroder__proof__71} &
         \(\Rightarrow\)&
@@
 
-        \includeinlinescaledsvg{.23}{.35}{schroder__proof__81} &
+        \includeinlinescaledsvg{.16}{.35}{schroder__proof__81} &
         \(\Rightarrow\)&
@@
 In the left column you can see all the possibilities of selecting \(s\) from a~tree of size \(n\).
-In \(R_1\), \(L_1\) and \(L_2\) columns we show how they are then transformed.
+In columns \(R_1\), \(L_1\) and \(L_2\) we show how they are then transformed.
 It covers all the possible cases of selecting a~leaf from a~tree of size \(n + 1\) and selecting an~internal node from a~tree of size \(n - 1\).
+
+\qed%
+\end{interpretation}
 
@@
 
-We also created a~framework~\cite{transformator}, called Transformator, that may help visualize our work.
+We also created a~framework, called Transformator~\cite{transformator}, that may help visualize our work.
 It operates on binary trees and it is based on the idea that every transformation expressed in bijective language is local, i.e.~transforms some node and a finite number of its surrounding nodes.
 
-To show the idea of such transformations, let's define transformation context with holes. We will be matching them to some parts of trees.
+To show the idea of such transformations, let's define a transformation context with holes. We will be matching them to some parts of trees.
 
@@
     The transformation context is a rooted tree.
-Some of nodes can be left as holes, that may be later filled with trees.
+Some of nodes can be left as holes, that may be filled later with trees.
 It also specifies a type of the edge above the root of the context (i.e.~if that is an actual edge, optional actual edge, virtual edge, or if there is no edge at all).
@@
     The transformation is defined as a pair of transformation contexts, the starting and the target one.
+\end{definition}
+
+\begin{definition}
+    The result of an application of a transformation is defined as a multiset of trees.
+Such a multiset can be obtained by finding each part of the tree where the starting transformation context applies and for each of them, creating a new tree with such a part replaced with the target transformation context.
 \end{definition}
@@
     We want to modify a node being a right child of its parent.
-We do not care what is below that node (i.e.~if that is a leaf or if it has children).
+We do not care what is below that node (i.e.~if that is a leaf or if it has any children).
 We want to add a new node of which the original one is a left child.
@@
 
-\(H_1\), \(H_2\), and \(H_3\) are holes.
-Edge crossing the box around the context defines the type of the edge by which the context is connected to the rest of the tree (i.e.~optional actual edge).
+where \(H_1\), \(H_2\), and \(H_3\) are holes.
+The edge crossing the box around the context defines the type of the edge by which the context is connected to the rest of the tree (i.e.~optional actual edge).
 We marked the node being described to clarify the picture.
@@
 \begin{itemize}
-    \item node is a~virtual leaf (each tree with \(n\) actual nodes has exactly \((n + 1)\) places where such context apply):\\
+    \item the node is a~virtual leaf (each tree with \(n\) actual nodes has exactly \((n + 1)\) places where such a context applies):\\
         \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_001}%
-    \item node is an~actual node (tree with \(n\) actual nodes has exactly \(n\) places where such context apply):\\
+    \item the node is an~actual node (tree with \(n\) actual nodes has exactly \(n\) places where such a context applies):\\
         \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_002}%
-    \item node is a~root (each tree has exactly \(1\) place where such context apply):\\
+    \item the node is a~root (each tree has exactly \(1\) place where such a context applies):\\
         \includeinlinescaledsvg{1}{.7}{lambda__contexts__type_003}%
-    \item node has its parent on the left, i.e.~is a right child of its parent (the node can be specified to be actual or virtual):\\
+    \item the node has its parent on the left, i.e.~is a right child of its parent (the node can be specified to be actual or virtual):\\
         \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_004}%
         \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_004b}%
-    \item node has its parent on the right, i.e.~is a left child of its parent (the node can be specified to be actual or virtual):\\
+    \item the node has its parent on the right, i.e.~is a left child of its parent (the node can be specified to be actual or virtual):\\
         \includeinlinescaledsvg{.5}{.7}{lambda__contexts__type_005}%
@@
 The latest two are introduced in order to make the analysis simpler, but do not have an immediate interpretation in the world of holonomic recurrences.
-However, if we use them both, it sums up to all nodes except root (as root is neither left nor right child), so in total there are \((n - 1)\) places where such a pair of contexts apply.
-
-The target of the transformation can be any context preserving all holes and not decreasing the number of nodes. This allows us to specify the number of nodes added by the transformation.
+However, if we use them both, it sums up to all nodes except root (as root is neither left nor right child), so in total there are \((n - 1)\) places where such a pair of contexts applies.
+
+The target of the transformation can be any context preserving all holes not decreasing the number of nodes. This allows us to specify the number of nodes added by the transformation.
 
@@
 \end{center}
-It adds single \(l\) node.
+It adds a single \(l\) node.
 
@@
 
-\(\tSection_\tau\), where \(\tau\) is a multiset over \(\{a, l, o, s\}\), stores transformations extending the tree with nodes \(\tau\).
+\(\tSection_\tau\), where \(\tau\) is a multiset over \(\{a, l, o, s\}\), stores transformations extending the tree with nodes from~\(\tau\).
 
@@
 
-Since now we will be considering a constant \(n \in \N\) which defines a target size of the trees.
-
-We will be also talking about trees generated by the transformation.
-Multiset of trees generated by the transformation from \(\tSection_\tau\) is defined as all trees generated by applying the transformation to all trees of size \((n - |\tau|)\).
+Since now we will be considering a constant \(n \in \N\) which defines the target size of the trees.
+
+We will be also talking about trees generated by a transformation.
+A multiset of trees generated by the transformation from \(\tSection_\tau\) is defined as all trees generated by applying the transformation to all trees of size \((n - |\tau|)\).
 
@@
 Each section is associated with an expression coming from the holonomic recurrence.
-It defines expected number of trees that will be generated by each of the sections.
+It defines a potential number of trees that will be generated by each of the sections.
 Let \(k := n - |\tau|\) for each \(\tSection_\tau\).
@@
 
-The expressions associated to each section are then:
+The expressions associated to each \(\tSection_\tau\) are then:
 
@@
 
-Using \(k\) instead of \(n\) makes it easier to interpret, as we see number of trees that should be generated by each section.
+Using \(k\) instead of \(n\) makes it easier to interpret, as we see the number of trees that should be generated by each section.
 For example \(\tSection_{\{ll\}}\) should generate \(k t_k\) trees from trees of size \(k\), which can be interpreted as taking each actual node and adding two \(l\) nodes above it.
@@
 Note that some of these expressions will evaluate to negative numbers.
-It is because of the fact that sum of all expressions should evaluate to zero.
+It is because of the fact that the sum of all expressions should evaluate to zero.
 We will be generating two kinds of trees then: positive (contributing to the total number of trees being generated as \(1\)) and negative ones (contributing as \(-1\)).
@@
 
-As we want to make our work kind of organized, we are going to divide the process of finding interpretation into iterations. Each iteration should be a~small step towards solving the original problem.
-
-Our brains like small examples, so we will consider small constant \(n = 3\).
-It will be describing size of the trees we want to generate.
-Because we start with such small \(n\), some of expressions associated with some sections will be empty, but it is ok.
-That's less trees to look at and soon we will increase \(n\).
-
-We will be still using \(k = n - |\tau|\) when considering sections to make the view simpler.
+As we want to make our work kind of organized, we are going to divide the process of finding an interpretation into iterations.
+Each iteration should be a~small step towards solving the original problem.
+
+Our brains like small examples, so we will consider a small constant \(n = 3\).
+It will be describing the size of the trees we want to generate.
+Because we start with such a small \(n\), some of expressions associated with some sections will be empty, but it is ok.
+That is less trees to look at and soon we will increase \(n\).
+
+We will still be using \(k = n - |\tau|\) when considering sections to make the view simpler.
 
@@
 
-The listing above is statistics view from Transformator framework. Let's analyze the first line:
+The listing above is a statistics view from Transformator framework. Let's analyze the first line:
 \begin{itemize}
     \item \verb|[ ]| at the beginning means that we still need to generate some more trees. If we have generated all of them, it would be \verb|[x]|;
-    \item \verb|0,0| is class and section identifier, i.e. \(|\tau|\) and arbitrarily assigned number;
+    \item \verb|0,0| is a class and a section identifier, i.e. \(|\tau|\) and an arbitrarily assigned number;
     \item \verb|0 of 16| means that we have generated \(0\) trees from \(16\) expected;
@@
 We start with interpreting \(\tSection_\emptyset\).
-From statistics above, we see that we should generate \(16\) trees.
+From statistics above, we see that we should generate \(16\)~trees.
 \((k + 1)\) suggests pointing a~virtual leaf.
 Let's do so.
-We do that by defining a following transformation:
+We do that by defining the following transformation:
 
@@
 
-After such operation we get following statistics:
+After such a operation we get the following statistics:
 
@@
 
-Since all thos trees are positive, we need to generate their negative counterpart.
+Since all those trees are positive, we need to generate their negative counterpart.
 Let's take a look at the line (1).
-All of these trees share the same property, that the virtual leaf being pointed is child of \(l\)~node.
+All of these trees share the same property, that the virtual leaf being pointed is a child of an \(l\)~node.
 Analogically at the line (2) pointed virtual leaves are children of \(s\) nodes.
@@
 
-The transformation to resolve case of the line (1) is simple:
+The transformation to resolve the case of the line (1) is simple:
 
@@
         ["l", kind] + left + right + [(None, "*")]  # for each actual node we add
-                                                    # l node with right virtual
+                                                    # an l node with right virtual
                                                     # node pointed as a parent
@@
 
-We just add an \(l\) node above each actual one and point its right child being virtual leaf.
+We just add an \(l\) node above each actual one and point its right child being a virtual leaf.
 
@@
 
-It addresses all cases from the line (1), but also introduces an~incorrect lambda tree in which \(s\) node is the parent of \(l\) node (such tree does not correspond to valid lambda term).
+It addresses all the cases from the line (1), but also introduces an~incorrect tree of lambda term in which \(s\)~node is a parent of an \(l\) node (such tree does not correspond to valid lambda term).
 However, we allow that.
-To mitigate this problem we will later use \(\tSection_{\{ls\}}\) and generate positive trees where \(s\) node is parent of \(l\) node.
-
-To generate negative trees corresponding to the line (2), create following transformation for \(\tSection_{\{s\}}\).
+To mitigate this problem we will later use \(\tSection_{\{ls\}}\) and generate positive trees where an \(s\) node is a parent of an \(l\) node.
+
+To generate negative trees corresponding to the line (2), we create the following transformation for \(\tSection_{\{s\}}\).
 
@@
 
-Next, we can take care of cases from line (3). To do so, we will use both \(\tSection_{\{l\}}\) and \(\tSection_{\{s\}}\).
+Next, we can take care of the cases from the line (3). To do so, we will use both \(\tSection_{\{l\}}\) and \(\tSection_{\{s\}}\).
 
@@
 
-Basically, for each virtual leaf not being root (i.e.~having left or right parent), we point it and add \(l\) or \(s\) respectively above the parent.
+Basically, for each virtual leaf not being a root (i.e.~having a left or a right parent), we point it and add an \(l\) or an \(s\) node respectively above the parent.
 
@@
 
-The last row can be generated using \(\tSection_{\{ao\}}\):
+The trees from the line (4) can be generated using \(\tSection_{\{ao\}}\):
 
@@
 
-In other words, for each actual node, we add an \(a\) node as its left or right parent and add as a~second child \(o\) node as its sibling.
-We then point to the left or right virtual child of the newly created \(o\)~node:
+In other words, for each actual node, we add an \(a\) node as its left or right parent and as the~second child we add a pointed \(o\) node:
 
@@
 
-After such transformations, we get following statistics:
+After such transformations, we get the following statistics:
 
@@
 
-Note that we have gotten rid of the \(\tSection_\emptyset\) in \verb|Diff stats|. It means that we have generated all negative counterpart of the trees generated by this section.
-
-If we increase \(n\) (i.e.~target size of the trees), this construction still works. Here \(n = 10\):
+Note that we have gotten rid of the \(\tSection_\emptyset\) in \verb|Diff stats|. It means that we have generated all negative counterparts of the trees generated by this section.
+
+If we increase \(n\) (i.e.~target size of the trees), this construction still works. Here we show the statistics for \(n = 10\):
 
@@
 
-The process can then be repeated for each section.
-We have chosen the order as above (i.e.~\(\tSection_\emptyset\); \(\tSection_{\{l\}}\); \(\tSection_{\{s\}}\); \(\tSection_{\{ao\}}\); \(\tSection_{\{ll\}}\); \(\ldots\)).
+The process can be then repeated for each section.
+We have chosen the order as shown above (i.e.~\(\tSection_\emptyset\); \(\tSection_{\{l\}}\); \(\tSection_{\{s\}}\); \(\tSection_{\{ao\}}\); \(\tSection_{\{ll\}}\); \(\ldots\)).
 
@@
 
-After multiple iterations, we managed to come up with following construction:
+After multiple iterations, we have managed to come up with the following construction:
 
@@
         None if kind[0] is not None else
-        ["s", None, "s", None, "l", "l", parent_kind] + left + right + [(None, "*"), None]
+        ["s", None, "s", None, "l", "l", parent_kind] + left + right +
+                        [(None, "*"), None]
 )
@@
 
-It resulted in final statistics:
+It resulted in the final statistics:
 
@@
 
-You may also note that we did not generate all trees suggested by the recurrence. This is due to one cheat we used.
+You may also note that we did not generate all trees suggested by the holonomic recurrence. This is due to the one cheat we used.
 
@@
 
-You may remember our assumptions in Section~\ref{sub:the_framework} about the starting transformation contexts.
+You may remember our assumptions from Section~\ref{sub:the_framework} about the starting transformation contexts.
 We allowed ourselves to create transformations where the node was a left or a right child, which is not handled by our holonomic recurrence as the number of such nodes does not depend only on \(n\).
@@
 To fix this, one can for example add transformation to \(\tSection_{\{s\}}\) to generate trees so that the total number of trees generated by \(\tSection_{\{s\}}\) is equal to the value of the expression associated with it.
-We can see that we used \(2\) constructions visiting nodes with a right parent and only one visiting node having a left parent, so our missing transformation should also visit nodes with left parent.
+You can see that we used two transformations transforming nodes with a right parent and only one transforming nodes having a~left parent.
+Therefore, our missing transformation should also transform nodes with a left parent.
 
@@
 
-An example of transformation we may want to add can be:
+An example of a transformation we may want to add is:
 
@@
 
-Please note that it is only an~example of missing transformation. It is just the simplest one we could think about, and in that case, a~simple solution is most often the correct one.
+Please note that it is only an~example of a missing transformation. It is just the simplest one we could think about, and in that case, a~simple solution is most often the correct one.
 
@@
 You may also note that we are operating on specific \(N\).
-The probability that we miss some corner case is low, but even if we check large \(N\) values, it is always present.
-The formal algebraic proof would make us sure that the transformation works.
+The chance that we miss some corner case is low, but even if we check large \(N\) values, it is always present.
+The formal proof would make us sure that the transformation works.
 We would prioritize finishing the transformation first.
 
-The framework also is not perfect.
+The framework is also not perfect.
 It highly depends on the operator's intuition.
 We believe that the solving process can be automated.
-The simplest method that comes to mind is simply creating heuristic rules that then will be used by the framework to guess at least partial solutions.
+The easiest method that comes to mind is creating heuristic rules that will be used by the framework to guess at least a partial solution.
 
 With the proper interpretation, it may be possible to create a~sampling algorithm similar to Rémy's one for binary trees~\cite{remy,note}.
-It would have to take under consideration that some trees are being removed by other classes, so the probabilities would have to be set carefully.
+It would have to take under consideration that some trees are being removed by other transformation classes, so the probabilities would have to be set carefully.
 

### 2021-09-15 article/main.tex
Fix biblatex margins
Last fixes

@@
 \addbibresource{bibliography.bib}
+\appto{\bibsetup}{\sloppy}
+% \appto{\bibsetup}{\raggedright}
 
@@
 
-The method itself has proven to be helpful in order to divide the problem into smaller parts and find some corner cases.
+The method itself has proven to be helpful in order to divide the problem into smaller parts and to find some corner cases.
 Unfortunately, it does not give any immediate interpretation for applying the inductive step.
@@
     \begin{itemize}
-        \item if \(x\) is a~variable, then \(x \in \Lambda\)
-        \item if \(M, N \in \Lambda\), then \((M N) \in \Lambda\) (it can be interpreted as an application of a~function \(M\) to an~argument \(N\))
+        \item if \(x\) is a~variable, then \(x \in \Lambda\);
+        \item if \(M, N \in \Lambda\), then \((M N) \in \Lambda\) (it can be interpreted as an application of a~function \(M\) to an~argument \(N\));
         \item if \(x\) is a~variable and \(M \in \Lambda\), then \((\lambda x.
 M) \in \Lambda\) (it can be interpreted as an~abstraction, i.e.~creating a~function with an~argument \(x\) and binding each occurrence of \(x\) in \(M\) to this argument.
-We say that a variable \(x\) is abstracted by this lambda-abstraction)
+We say that a variable \(x\) is abstracted by this lambda-abstraction).
     \end{itemize}
@@
 
-This definition resembles tree-based structure of lambda terms, where:
+This definition resembles a tree-based structure of lambda terms, where:
 \begin{itemize}
@@
 The definition using named variables is quite popular, but it introduces several problems.
-One of them is a~problem of a potential collision of lambda-abstracted variable names and difficulty of finding to which lambda abstraction the variable is bound (or is it even a~free variable, i.e.~not bound).
+One of them is a~problem of a potential collision of lambda-abstracted variable names and difficulty of deciding to which lambda abstraction the variable is bound (or is it even a~free variable, i.e.~not bound).
 To address that, we can use de Bruijn indices.
@@
 \begin{definition}
-    Set of lambda terms \(\LambdadB\) is defined recursively:
+    The set \(\LambdadB\) of lambda terms in de Bruijn notation is defined recursively:
     \begin{itemize}
-        \item if \(n \in \N\), then \(n \in \LambdadB\) (\(n\) is a~variable bound to a lambda abstraction \(n\) levels above, i.e.~if you traverse the tree of the lambda term upwards, we have to ignore \(n\) lambda-abstraction nodes and the \((n+1)\)-st one is the one binding the variable.
-If we would have to go beyond the root of the tree, we say that the variable is free, i.e.~not bound)
-        \item if \(M, N \in \LambdadB\), then \((M N) \in \LambdadB\) (application)
-        \item if \(M \in \LambdadB\), then \((\lambda M) \in \LambdadB\) (abstraction)
+        \item if \(n \in \N\), then \(n \in \LambdadB\) (\(n\) is a~variable bound to a lambda abstraction \(n\) levels above, i.e.~if we traverse the tree of the lambda term upwards, we have to ignore \(n\) lambda-abstraction nodes and the \((n+1)\)-st one is the one binding the variable.
+If we have to go beyond the root of the tree, we say that the variable is free, i.e.~not bound);
+        \item if \(M, N \in \LambdadB\), then \((M N) \in \LambdadB\) (application);
+        \item if \(M \in \LambdadB\), then \((\lambda M) \in \LambdadB\) (abstraction).
     \end{itemize}
@@
 
-As we have our structure defined, let's create a generating function that will keep track of more than just the number of nodes, but also counts the number of each kind of node in the tree.
+As we have our structure defined, let's create a generating function that keeps track of more than just the number of nodes, but also counts the number of each kind of node in the tree.
 The generating function \(\gf{T}(z, o, l, a, s)\) will be parameterized then using the following arguments:
 \begin{itemize}
-    \item \(z\) marking all actual nodes
-    \item \(o\) marking variable nodes
-    \item \(l\) marking lambda abstraction nodes
-    \item \(a\) marking application nodes
-    \item \(s\) marking successors of variable nodes
+    \item \(z\) marking all actual nodes,
+    \item \(o\) marking variable nodes,
+    \item \(l\) marking lambda abstraction nodes,
+    \item \(a\) marking application nodes,
+    \item \(s\) marking successors of variable nodes.
 \end{itemize}
@@
         \begin{center}
-            \(\gf{S}\)\\
+            \(\gf{V}\)\\
             \includesvg[scale=0.5]{lambda__def__4}%
@@
 
-If we treat \(z\) as the only variable and make \(o\), \(l\), \(a\), and \(s\) constants, we can use a~little bit of Maple magic~\cite{gfun} to achieve the following holonomic recurrence.
+If we treat \(z\) as the only variable and make \(o\), \(l\), \(a\), and \(s\) constants, we can use a~little bit of Maple magic~\cite{gfun} to achieve the following holonomic recurrence:
 
@@
         +& ((-2 n + 1) l - 2 n s) t_{n - 1}\\
-        +& (n + 1) t_{n}
+        +& (n + 1) t_{n}.
 \end{array}\]
@@
         +& (-4 n + 1) t_{n - 1}\\
-        +& (1 + n) t_{n}
-\end{array}.\]
+        +& (1 + n) t_{n}.
+\end{array}\]
 
